### 2014-06-23 cyc-concepts/intro.tex
adds skeleton and authors

% Introduction :
% Why did I do the work?
% What were the central motivations and hypotheses?

\section{Introduction}
% The objectives of the work.

\emph{What will this work show?}

% The justification for the objectives.

\emph{Why is the work important?}

% Background

\emph{Who else has done what?}

\emph{How?}

\emph{What has this group previously done?}

% Guidance to the reader

\emph{What should the reader watch for in the paper?}

\emph{What are the interesting high points?}

\emph{What strategy did we use?}

% Summary/Conclusion

\emph{What should the reader expect as conclusion?}

### 2014-07-16 fundamentals/impl.tex
changes dir name

\section{Methodology and Implementation}
% What were the methods used?
% How was the problem designed?
% Driving concepts
% Equations
% Figures
\subsection{Framework Structure}
% (OO, cpp, xml, backends, inheritances, mixins, generic apis, etc.)
\subsection{Dynamically loadable libraries}
% (diagram)
\subsection{Agent Interchangability}
% interchangeability due to exchange behavior api
\subsection{Region/Institution/Facility hierarchy}
% (diagram)
\subsection{Discrete Object Tracking}
% Resources, Materials (note isotope tracking, decay behavior)
\subsection{Toolkit}
% library of tools
% contributions to the toolkit
% place for metrics
\subsection{Cycamore}
% base modules

### 2014-07-16 fundamentals/intro.tex

% Introduction :

\section{Introduction}

% Why did we do the work?
% What were the central motivations and hypotheses?
% The objectives of the work.
% What will this work show
% Why is it important?
% What should the reader watch for in the paper?
% What are the interesting high points?
% What strategy did we use?
% What should the reader expect as conclusion?

\subsection{Background}

% Who else has done what?
% How did they do that?
% What did we do before this?
% What is new?

% Common goals of fuel cycle simulation/simulators (driving r&d focus,
% approximating tech. impacts, etc.)
% Previous work (cite all the tools!)
% Limitations of previous simulators by others (fleet-based, closed
% development, inflexible infrastructure)
% Previous attempts by this group (GENIUS v1/v2)
% note NGFCS

\subsection{Motivation}
\subsubsection{Modular Architecture}
% Motivation for encapsulated plug-in architecture 
% enables ecosystem, ease of contribution across institutions
% enables myriad levels of simulation fidelity
% enables FC analyses that can compare ‘apples to apples'
\subsubsection{Agent-based Paradigm}
% superior detail in capturing simulation dynamics
% more flexible control over behavior
% describe Region/Institution/Facility hierarchy
% note importance of generic resource exchange paradigm
\subsubsection{Discrete Resource Tracking}
% enables more realistic models and metrics
% material routing metrics
% shadow fuel cycles
% etc.

### 2014-07-23 fundamentals/verification.tex
adds section for robustness of coding practices.

\section{Verification}
% Organize this section according to major topics
% give each topic a section heading in boldface.
% try to cover the major common points :
%
% problem design
% methods of measurement
% supporting models
% supporting data
% simulations run
% results

% Just write the section headings for each part and indicate what goes in that
% section with words :
%
% heading
% figures (with captions)
% schematics (with captions and footnotes)
% equations
% tables

% What does it mean?
% What did I actually test?
% What were the results?
% Did the work yield a new method?
% Did the work yield new knowledge?
% What measurements did I make?
% How were these measurements characterized?
% What methods were used?
% What were the results?
% How were the measurements made and characterized?

\subsection{Coding Practices}
% What have we done to ensure robustness ?
% Examples from Material class, Transactions, simulation IDs
\subsection{Testing Framework}
% Peer-review system (secretly a note on open source?)
\subsection{Benchmarks}
%Inpro benchmark?
%FCO code-to-code?

### 2014-07-23 fundamentals/intro.tex
adding helpful guiding comments
actual ntmanuscript class
adds draft topic sentences to intro.

@@
 % What were the central motivations and hypotheses?
-% The objectives of the work.
-% What will this work show
+% The objectives of the work?
+% What will this work show the reader?
 % Why is it important?
@@
 % What should the reader expect as conclusion?
+
+In nuclear fuel cycle simulation it is necessary to calculate and optimize 
+nuclear process physics, facility deployment, material routing, etc.
+
+Historically, nuclear fuel cycle simulators have addressed this with software 
+ranging from spreadsheet driven flow calculators to full detail industrial 
+models.
+
+An alternative to these approaches is a dynamic, agent-based simulator with an 
+open platform.
 
@@
 
+Simulators drive R\&D by calculating metrics that can be compared accross fuel 
+cycles.
+
+Previous simulators have been static or dynamic. Some have been discrete while 
+others have been fleet-based. Some have captured regional behavior, material 
+isotopics, transmutation detail, etc. Indeed, some tools have attempted 
+agent-based functionality.
+
+Historically, the national laboratories have driven development and regulated 
+the use of their own tools (cite VISION, DANESS, NFCSim, etc.), while 
+universities and industry have simultaneously developed tools of their own as 
+well.
+
+The Cyclus code arose out of the GENIUSv2 code. That software itself was the 
+result of lessons-learned from an LDRD project at INL called GENIUSv1.
+
 \subsection{Motivation}
+% Gently reiterate the above need. 
+% There should be a hero narrative here
+% There was a gap in the capabilities of simulators.
+% Cyclus, a hero, came in to fill that gap.
+
+Cyclus provides a sophisticated and modern, agent-based platform. Previous 
+codes were lacking in a number of ways. Cyclus has a number of features that 
+overcome those issues.
+
 \subsubsection{Modular Architecture}
@@
 % enables FC analyses that can compare ‘apples to apples'
+
+Draw from and cite the ``Open Architecture and Modular Paradigm'' ANS summary.
+
 \subsubsection{Agent-based Paradigm}
@@
 % note importance of generic resource exchange paradigm
+
+ABM is modern, sophisticated, true to reality, and it takes advantage of modern 
+computing resources.
+
 \subsubsection{Discrete Resource Tracking}
@@
 % etc.
+
+Not all simulations can be successfully run with a fleet-based model that 
+doesn't distinguish between discrete materials. Shadow fuel cycles are an 
+example.

### 2014-07-23 fundamentals/impl.tex
more topic sentences

@@
 % Figures
+
+Only a modular, agent-based approach is capable of adequately solving system 
+dynamics problems involving material routing, facility deployment, regional and 
+institutional hierarchies.
+
 \subsection{Framework Structure}
 % (OO, cpp, xml, backends, inheritances, mixins, generic apis, etc.)
+
+Agent-based modeling is inherently object oriented.
+
+The core of the simulator creates a set of key classes on which agent plugins 
+are based. In addtion, a set of key tools are also provided, to enrich the API 
+and provide a robust suite of behaviors for the developer.
+
+<diagram of core, modules, toolkit, etc>
+
+Agent plug-ins utilize the generic core API to interact with one another. 
+Mainly they do this by trading resources.
+
+<diagram of black box facilities>
+
 \subsection{Dynamically loadable libraries}

### 2014-07-23 fundamentals/impl.tex
more topic sentences

@@
 
+\subsection{Cluster-Ready Software}
+
+Because this doesn't rely on PowerSim, GoldSim, Excel, or any other COTS 
+Windows-based software, we can run singular instances of Cyclus 
+on large linux machines that have lots more capability than hacked together 
+Windows clusters.
+
 \subsection{Dynamically loadable libraries}
 % (diagram)
+
+A key innovation that has previously not been implemented in nuclear fuel cycle 
+simulators in the literature is implementing this generic API and modular 
+architecture into a suite of dynamically loadable ``plug-in'' libraries.
+
+This approach allows contribution to an ecosystem of libraries. The 
+scientist-developer can therefore focus on generating a model within their 
+sphere of expertise, while relying on the model contributions of others to fill 
+in the other technologies.
+
+This is implemented largely through a clean API and a modern build system.
+
 \subsection{Agent Interchangability}
 % interchangeability due to exchange behavior api
+
+This approach enables ``apples-to-apples'' comparisons, something that has been 
+sorely missing in previous simulators.
+
+By making the facilities interchangeable, it combinatorically increases the 
+number of scenarios that can be modeled. The user can choose to model just the 
+front end or just the back end of a fuel cycle.
+
+This is implemented with an API that focuses on treating the agents as black 
+boxes.
+
 \subsection{Region/Institution/Facility hierarchy}
 % (diagram)
+
+Not many fuel cycle simulators have this, it turns out. We used to implement 
+this with inheritance. Now I'm not so sure. . . <insert recent knowledge here>.
+
 \subsection{Discrete Object Tracking}
 % Resources, Materials (note isotope tracking, decay behavior)
+
+Discrete facility and material tracking is more realistic an dmore
+
 \subsection{Toolkit}
@@
 % place for metrics
+
+The toolkit is a place for developers and users to contribute common-use tools 
+for calculating metrics, managing process physics, handling data.
+
+This was implemented by liberal use of namespaces  and is populated with an 
+introductory suite of useful tools.
+
 \subsection{Cycamore}
 % base modules
+
+Cycamore contains a number of usefule facility models that are a mere base-set. 
+Additional modules are needed for full fuel cycle simulation. However, simple 
+fuel cycles can be generated with Cycamore and Cyclus alone.
+
+<diagram of a possible Cycamore-only simulation>

### 2014-07-23 fundamentals/verification.tex
actual ntmanuscript class
more topic sentences

@@
 
+Unfortunately, we can't wind forward the clock to compare our simulations to 
+the futures that we are attempting to model.
+
+However, Cyclus does implement a number of strategies for verification and 
+validation of code.
+
 \subsection{Coding Practices}
@@
 % Examples from Material class, Transactions, simulation IDs
+
+Some routines are implemented specifically to ensure robustness.
+
 \subsection{Testing Framework}
 % Peer-review system (secretly a note on open source?)
+
+We have reasonable test coverage and a code review system.
+
 \subsection{Benchmarks}
@@
 %FCO code-to-code?
+
+A simple transition scenario recently used for a code-to-code comparison within 
+the national laboratories can demonstrate the ability for Cyclus to conform to 
+externally defined specifications.

### 2014-07-23 fundamentals/examples.tex
topic sentences

--- 2014-07-23 fundamentals/verification.tex
@@
-\section{Verification}
+\section{Examples}
 % Organize this section according to major topics
@@
 
-\subsection{Coding Practices}
-% What have we done to ensure robustness ?
-% Examples from Material class, Transactions, simulation IDs
-\subsection{Testing Framework}
-% Peer-review system (secretly a note on open source?)
-\subsection{Benchmarks}
-%Inpro benchmark?
-%FCO code-to-code?
+Current and past simulations with the Cyclus simulator have already 
+demonstrated a range of uses.
+
+\subsection{Ecosystem}
+% Cycamore library
+% Cyder?
+
+External modules have been (cite cyder, separations, streamblender, demandinst, 
+commodconverter, etc.) and are being (cite brightlight, UTK module, etc.) 
+developed for contribution to the cyclus ecosystem of models.
+
+\subsection{Simulations}
+%FCO example (will be done soon.. publishable?)
+%Inpro example (is this still running or did we deprecate it with 1.0?)
+
+Simulations have been run in the past and more are being run. FCO is an 
+example.

### 2014-07-31 fundamentals/impl.tex
more content and comments added in intro, examples, impl, and verification

@@
 
-Only a modular, agent-based approach is capable of adequately solving system 
-dynamics problems involving material routing, facility deployment, regional and 
-institutional hierarchies.
+A modular, agent-based is an ideal approach for solving complicated
+physics-dependent supply chain problems involving material routing, facility
+deployment, regional and institutional hierarchies.
 
@@
 
-Not many fuel cycle simulators have this, it turns out. We used to implement 
-this with inheritance. Now I'm not so sure. . . <insert recent knowledge here>.
+Cyclus has three core agent classes that be subclassed to create a simulation
+archetype: Region, Institution, and Facility. At present, Regions, Institutions,
+and Facilities (RIF) conceptually form a nested structure in a Cyclus simulation,
+i.e., Facilities exist in (i.e., are managed by) Institutions and Institutions
+exist in Regions.
+
+Importantly, the RIF separation allows for preferential trading. For example,
+Facilities in the same Institution can preferentially trade with each
+other. Similarly, Regions can be given a location proxy, and the trade between
+Facilities can be informed by their regional proximity.
 
@@
 The toolkit is a place for developers and users to contribute common-use tools 
-for calculating metrics, managing process physics, handling data.
+for calculating metrics, managing process physics, and handling data.
 
 This was implemented by liberal use of namespaces and is populated with an
-introductory suite of useful tools.
+introductory suite of useful tools, including helper classes for managing
+facility deployment, minimum cost facility deployment decision making, and for
+enrichment-related calculations.
 
@@
 Cycamore contains a number of usefule facility models that are a mere base-set.
-Additional modules are needed for full fuel cycle simulation. However, simple 
-fuel cycles can be generated with Cycamore and Cyclus alone.
+Additional modules are needed for interesting fuel cycle simulation. However,
+simple, once-through fuel cycles can be generated with Cycamore and Cyclus alone.
 

### 2014-07-31 fundamentals/intro.tex
more topic sentences
more content and comments added in intro, examples, impl, and verification

@@
 
+% MJG - I'm hesitant about using the phrase 'full detail'. I think we can be
+% more precise.
+
 Historically, nuclear fuel cycle simulators have addressed this with software 
@@
 An alternative to these approaches is a dynamic, agent-based simulator with an 
-open platform.
+free, openly accessible simulation-logic kernel.
 
@@
 
+% MJG - We need to be very precise about the terms 'static' and 'dynamic'. They
+% should likely be defined before being used in this context.
+
 Previous simulators have been static or dynamic. Some have been discrete while 
@@
 isotopics, transmutation detail, etc. Indeed, some tools have attempted 
-agent-based functionality.
+agent-based functionality. % MJG - Which ones? The closest I can think of is
+                           % NFCSim, and it's implementation details are closed.
 
@@
 
+% MJG - @gonuke has always cited method-to-method comparisons as the primary
+% benefit Cyclus can bring to the table. Do we want to frame the hero narrative
+% in that context? The more I think about, the more I feel like this is a
+% secondary argument. I'll take a crack at a few sentences below.
+
 Cyclus provides a sophisticated and modern, agent-based platform. Previous 
@@
 overcome those issues.
+
+% MJG - I don't claim that all of this belongs in the beginning of this
+% subsection, but here's some more content.
+
+Modeling the growth of a physics-dependent, international nuclear fuel supply
+chain is a difficult problem. To date, it has been treated relatively
+lightly. Tools have either focused on macro effects, e.g., the fleet-level
+stocks and flows of commodities, or micro effects, e.g., the used fuel
+composition fast reactor fuel. Accordingly, each focus has driven the
+development of these tools, rendering the task of answering questions between
+the macro and micro levels either impossible or difficult and time consuming.
+
+Cyclus uses a divide-and-conquer approach, separating the problem of modeling a
+physics-dependent supply chain into a simulation kernel and archetypes that
+interact with the kernel during a simulation. The kernel is responsible for the
+deployment and interaction logic of entities in the simulation. Physics
+calculations are constrained to individual archetypes. Accordingly, specialists
+in a given field can utilize their time and resources in modeling a specific
+process associated with the nuclear fuel cycle, e.g. reprocessing and advance
+fuel fabrication, rather than also modeling the entirety of the cycle.
+
+% we could use a specific example of Cosi's equivalence method below
+Because Cyclus uses a modular archetype approach, comparing two archetypes is
+straightforward. Consider a case in which an analyst would like to compare the
+effect of using different models to determining input fuel composition for fast
+reactors. A variety fuel fabrication archetypes can be developed and used
+interchangably to analyze the effect of each on a simulation's output.
 
@@
 
+We expect that there are a number of types of users and developers who will 
+interact with the Cyclus framework. Those people fall into a number of 
+categories. All such people benefit from the modular architecture.
+
+% man that figure has gone quite a ways =)
+<modified-open-source collaboration diagram>
+
 \subsubsection{Agent-based Paradigm}
@@
 ABM is modern, sophisticated, true to reality, and it takes advantage of modern
-computing resources.
+computing resources. Furthermore, agent-based modeling provides an analyst a
+more natural perspective from which to model a given problem. In the nuclear
+fuel cycle context for example, an analyst can design an agent with
+reactor-related logic and a separate agent with fuel fabrication-related logic.
+
+System dynamics popular approach for modeling nuclear fuel cycles in current
+tools (cite VISION/CAFCA). It has been shown in the literature
+\cite{macal_agent-based_2010} that any system dynamics model can be translated
+into an agent-based model. Furthermore, it has been shown that agent-based
+techniques can provide a richer model than can system dynamics. Formally, the
+set of system dynamics models is a strict subset of agent-based models.
 
@@
 example.
+
+A discrete resource model allows for a range of modeling granularity. In the
+macroscopic extreme, it is equivalent to time-stepped continuous flow. In the
+microscopic extreme, the model is capable of representing individual fuel
+assemblies.

### 2014-08-11 fundamentals/intro.tex
addresses @gidden comment about 'full detail'

--- 2014-07-23 fundamentals/intro.tex
@@
 
-In nuclear fuel cycle simulation it is necessary to calculate and optimize 
-nuclear process physics, facility deployment, material routing, etc.
+In nuclear fuel cycle simulation, it is necessary to calculate and optimize 
+nuclear process physics, facility deployment, and material routing in order to 
+capture overall fuel cycle performance metrics.
 
 Historically, nuclear fuel cycle simulators have addressed this with software 
-ranging from spreadsheet driven flow calculators to full detail industrial 
+ranging from spreadsheet driven flow calculators to very high-fidelity industrial 
 models.
@@
 
+We expect that there are a number of types of users and developers who will 
+interact with the Cyclus framework. Those people fall into a number of 
+categories. All such people benefit from the modular architecture.
+
+<modified-open-source collaboration diagram>
+
 \subsubsection{Agent-based Paradigm}

### 2014-08-13 fundamentals/intro.tex
adds a sentence to the intro about why agent based alternative is good.
additions to intro

@@
 
-In nuclear fuel cycle simulation, it is necessary to calculate and optimize 
-nuclear process physics, facility deployment, and material routing in order to 
-capture overall fuel cycle performance metrics.
+In order to capture fuel cycle performance metrics, nuclear fuel cycle analysis 
+requires calculation and optimization of myriad physical, nuclear, chemical, industrial, 
+and political phenomena. Nuclear process physics, facility 
+deployment, and material routing each represent complex systems that must be 
+modeled simultaneously for even the simplest of nuclear fuel cycle analyses.
 
 Historically, nuclear fuel cycle simulators have addressed this with software 
-ranging from spreadsheet driven flow calculators to very high-fidelity industrial 
-models.
+ranging from spreadsheet driven flow calculators to very high-fidelity 
+industrial models.  To date, current tools are either static, fleet-based, or 
+privately distributed.  An alternative to these approaches is a dynamic, 
+agent-based simulator with an open platform.
 
-An alternative to these approaches is a dynamic, agent-based simulator with an 
-open platform.
+Modern insight indicates that dynamic nuclear 
+fuel cycle analysis more generically supports a broad range of simulation goals 
+\cite{piet_dynamic_2011}. Similarly, experience in the greater field of systems 
+analysis indicates that agent-based modeling supports a greater range of 
+simulations, without loss of generality \cite{thatpapermattsent}. Finally, 
+openness allows access, cross-institutional collaboration, and increases code 
+robustness \cite{softwarecarpentryresource}.
+
+Myriad challenges in nuclear fuel cycle analysis could be 
+addressed with an agent-based framework for simulation and tracking of 
+transformation and trade of resources between facilities within institutions 
+and regions.
 
@@
 
-Simulators drive R\&D by calculating metrics that can be compared accross fuel 
+Simulators drive \gls{RDD} by calculating metrics that can be compared across fuel 
 cycles.
@@
 Previous simulators have been static or dynamic. Some have been discrete while 
-others have been fleet-based. Some have captured regional behavior, material 
-isotopics, transmutation detail, etc. Indeed, some tools have attempted 
-agent-based functionality.
+others have been fleet-based. Some capture regional behavior, material 
+isotopics, and transmutation detail, while others do not. Indeed, some tools 
+have attempted agent-based functionality.
 
 Historically, the national laboratories have driven development and regulated 
-the use of their own tools (cite VISION, DANESS, NFCSim, etc.), while 
-universities and industry have simultaneously developed tools of their own as 
-well.
+the use of their own tools such as \gls{VISION}\cite{<++>}, 
+\gls{DANESS}\cite{<++>}, \gls{DYMOND}\cite{<++>}, and \gls{NFCSim}\cite{<++>}, 
+while universities and industry have simultaneously developed tools of their 
+  own as well, such as \gls{CAFCA}\cite{<++>}.
 
-The Cyclus code arose out of the GENIUSv2 code. That software itself was the 
-result of lessons-learned from an LDRD project at INL called GENIUSv1.
+The Cyclus code arose out of the \gls{GENIUSv2}\cite{<++>} code. That software 
+itself was the result of lessons-learned from an \gls{LDRD} project at 
+\gls{INL} called \gls{GENIUSv1}\cite{<++>}.
 

### 2014-08-19 fundamentals/intro.tex
adds some more intro citations and content

--- 2014-08-11 fundamentals/intro.tex
@@
 
-In nuclear fuel cycle simulation, it is necessary to calculate and optimize 
-nuclear process physics, facility deployment, and material routing in order to 
-capture overall fuel cycle performance metrics.
+In order to characterize performance metrics, nuclear fuel cycle analysis 
+requires calculation and optimization of myriad physical, nuclear, chemical, 
+industrial, and political phenomena. Furthermore, complex systems such as 
+nuclear process physics, facility deployment, and material routing each each 
+must be modeled simultaneously for even the simplest of nuclear fuel cycle 
+simulations.
 
 Historically, nuclear fuel cycle simulators have addressed this with software 
-ranging from spreadsheet driven flow calculators to very high-fidelity industrial 
-models.
+ranging from spreadsheet driven flow calculators to very high-fidelity 
+industrial models. To date, current tools are either static, fleet-based, or 
+privately distributed. An alternative to these approaches is a dynamic, 
+agent-based simulator with an open platform.
 
-An alternative to these approaches is a dynamic, agent-based simulator with an 
-open platform.
+Modern insight indicates that dynamic nuclear fuel cycle analysis more 
+realistically supports a broader range of simulation goals than static analysis 
+\cite{piet_dynamic_2011}. Similarly, experience in the greater field of systems 
+analysis indicates that agent-based modeling enables more flexible simulation 
+control, without loss of generality \cite{thatpapermattsent}. Finally, 
+openness allows cross-institutional collaboration, increases code robustness, 
+and enables the cultivation of an ecosystem of calculation options, 
+\cite{softwarecarpentryresource}.
+
+Myriad challenges in nuclear fuel cycle analysis could be 
+addressed with an agent-based framework for simulation and tracking of 
+transformation and trade of resources between facilities within institutions 
+and regions.
 
@@
 
-Simulators drive R\&D by calculating metrics that can be compared accross fuel 
-cycles.
+Simulators drive \gls{RDD} by calculating metrics that can be compared among fuel 
+cycles. Examples include measures of economic feasibility (i.e., \gls{LCOE}), 
+proliferation risk (i.e., total separated Pu), and environmental performance 
+(i.e., waste volume).
 
-Previous simulators have been static or dynamic. Some have been discrete while 
-others have been fleet-based. Some have captured regional behavior, material 
-isotopics, transmutation detail, etc. Indeed, some tools have attempted 
+Methods for calculating those metrics vary among simulators. Some model the fuel cycle at static equillibrium, while others 
+capture fuel cycle dynamics.  Similarly, while some simulators discretely model 
+material and and facilities, others track streams of materials and 
+fleets of facilities in an aggregated fashion. Depending on their intended use, 
+simulators often model some aspect of the fuel cycle in great detail. For this 
+reason, simulators specialize in economics, material isotopics, or 
+transmutation detail, where others do not. Some tools have even attempted 
 agent-based functionality.
@@
 Historically, the national laboratories have driven development and regulated 
-the use of their own tools (cite VISION, DANESS, NFCSim, etc.), while 
-universities and industry have simultaneously developed tools of their own as 
-well.
+the use of their own tools such as \gls{VISION}\cite{jacobson_verifiable_2010}, 
+\gls{DANESS}\cite{van_den_durpel_daness_2009}, 
+\gls{DYMOND}\cite{modeling_yacout_2005}, and 
+\gls{NFCSim}\cite{schneider_nfcsim:_2005}, while universities and industry have 
+simultaneously developed tools of their own as well, such as 
+\gls{CAFCA}\cite{guerin_benchmark_2006}.
 
-The Cyclus code arose out of the GENIUSv2 code. That software itself was the 
-result of lessons-learned from an LDRD project at INL called GENIUSv1.
+The Cyclus code arose out of the 
+\gls{GENIUSv2}\cite{oliver_studying_2009,huff_geniusv2_2009} code. That software 
+itself was the result of lessons-learned from an \gls{LDRD} project at 
+\gls{INL}, 
+\gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006} which 
+captured regional behaviors in fuel cycle scenarios.
 

### 2014-08-21 fundamentals/acros.tex

\newacronym{MIT}{MIT}{the Massachusettes Institute of Technology}
\newacronym{UW}{UW}{University of Wisconsin}
\newacronym{US}{US}{United States}
\newacronym{IAEA}{IAEA}{International Atomic Energy Agency}
\newacronym{SNF}{SNF}{spent nuclear fuel}
\newacronym{HLW}{HLW}{high level waste}
\newacronym{FEHM}{FEHM}{Finite Element Heat and Mass Transfer}
\newacronym{DOE}{DOE}{Department of Energy}
\newacronym{GENIUSv1}{GENIUS}{Global Evaluation of Nuclear Infrastructure 
Utilization Scenarios, Version 1}
\newacronym{GENIUSv2}{GENIUS}{Global Evaluation of Nuclear Infrastructure Utilization Scenarios, Version 2}
\newacronym{CNERG}{CNERG}{Computational Nuclear Engineering Research Group}
\newacronym{GDSM}{GDSM}{Generic Disposal System Model}
\newacronym{GDSE}{GDSE}{Generic Disposal Sytem Environment}
\newacronym{GPAM}{GPAM}{Generic Performance Asessment Model}
\newacronym{FEPs}{FEPs}{Features, Events, and Processes}
\newacronym{EBS}{EBS}{Engineered Barrier System}
\newacronym{EDZ}{EDZ}{Excavation Disturbed Zone}
\newacronym{YMR}{YMR}{Yucca Mountain Repository Site}
\newacronym{EPA}{EPA}{Environmental Protection Agency}
\newacronym{PEI}{PEI}{Peak Environmental Impact}
\newacronym{VISION}{VISION}{the Verifiable Fuel Cycle Simulation Model}
\newacronym{NUWASTE}{NUWASTE}{Nuclear Waste Assessment System for Technical Evaluation}
\newacronym{NWTRB}{NWTRB}{Nuclear Waste Technical Review Board}
\newacronym{OCRWM}{OCRWM}{Office of Civillian Radioactive Waste Management}
\newacronym{UFD}{UFD}{Used Fuel Disposition}
\newacronym{DYMOND}{DYMOND}{Dynamic Model of Nuclear Development }
\newacronym{DANESS}{DANESS}{Dynamic Analysis of Nuclear Energy System Strategies}
\newacronym{CAFCA}{CAFCA}{ Code for Advanced Fuel Cycles Assessment }
\newacronym{ORION}{ORION}{O..}
\newacronym{NFCSim}{NFCSim}{Nuclear Fuel Cycle Simulator}
\newacronym{COSI}{COSI}{Commelini-Sicard}
\newacronym{FCT}{FCT}{Fuel Cycle Technology}
\newacronym{SWF}{SWF}{Separations and Waste Forms}
\newacronym{FCO}{FCO}{Fuel Cycle Options}
\newacronym{RDD}{RD\&D}{Research Development and Design}
\newacronym{WIPP}{WIPP}{Waste Isolation Pilot Plant}
\newacronym{ANDRA}{ANDRA}{Agence Nationale pour la gestion des D\'echets RAdioactifs, the French National Agency for Radioactive Waste Management}
\newacronym{TSM}{TSM}{Total System Model}
\newacronym{LANL}{LANL}{Los Alamos National Laboratory}
\newacronym{INL}{INL}{Idaho National Laboratory}
\newacronym{ANL}{ANL}{Argonne National Laboratory}
\newacronym{SNL}{SNL}{Sandia National Laboratory}
\newacronym{LBNL}{LBNL}{Lawrence Berkeley National Laboratory}
\newacronym{LLNL}{LLNL}{Lawrence Livermore National Laboratory}
\newacronym{NAGRA}{NAGRA}{National Cooperative for the Disposal of Radioactive Waste}
\newacronym{CUBIT}{CUBIT}{CUBIT Geometry and Mesh Generation Toolkit}
\newacronym{CSNF}{CSNF}{Commercial Spent Nuclear Fuel}
\newacronym{DSNF}{DSNF}{DOE Spent Nuclear Fuel}
\newacronym{MTHM}{MTHM}{Metric Ton of Heavy Metal}
\newacronym{HTGR}{HTGR}{High Temperature Gas Reactor}
\newacronym{TRISO}{TRISO}{Tristructural Isotropic}
\newacronym{MA}{MA}{Minor Actinide}
\newacronym{CEA}{CEA}{Commissariat a l'Energie Atomique et aux Energies Alternatives}
\newacronym{SKB}{SKB}{Svensk Karnbranslehantering AB}
\newacronym{SINDAG}{SINDA{\textbackslash}G}{Systems Improved Numerical Differencing Analyzer $\backslash$ Gaski}
\newacronym{STC}{STC}{Specific Temperature Change}
\newacronym{LDRD}{LDRD}{Laboratory Directed Research and Development}
%\newacronym{<++>}{<++>}{<++>}

### 2014-08-21 fundamentals/intro.tex
removed reference to agent-based. We can address that previous work later.

@@
 
+% MJG - I'm hesitant about using the phrase 'full detail'. I think we can be
+% more precise.
+
 Historically, nuclear fuel cycle simulators have addressed this with software 
-ranging from spreadsheet driven flow calculators to very high-fidelity 
-industrial models. To date, current tools are either static, fleet-based, or 
+ranging from spreadsheet driven flow calculators to full detail industrial 
+models. To date, current tools are either static, fleet-based, or 
 privately distributed. An alternative to these approaches is a dynamic, 
@@
 reason, simulators specialize in economics, material isotopics, or 
-transmutation detail, where others do not. Some tools have even attempted 
-agent-based functionality.
+transmutation detail, where others do not.
 
@@
 
+% man that figure has gone quite a ways =)
 <modified-open-source collaboration diagram>

### 2014-08-21 fundamentals/verification.tex
more content and comments added in intro, examples, impl, and verification
removed benchmark section, belongs in examples. also changed title of the verification section to qa.

@@
-\section{Verification}
+\section{Quality Assurance}
 % Organize this section according to major topics
@@
 
-\subsection{Benchmarks}
-%Inpro benchmark?
-%FCO code-to-code?
+\subsubsection{Unit Tests}
 
-A simple transition scenario recently used for a code-to-code comparison within 
-the national laboratories can demonstrate the ability for Cyclus to conform to 
-externally defined specifications.
+Testing individual units of 'work'.
+
+\subsubsection{Regression Tests}
+
+Testing identical output for each pull request.
+
+\subsubsection{Integration Tests}
+
+Testing aggregate answers for each pull request. Specifically, previous
+simulations used in publications are integration tested to confirm their output
+is maintained.

### 2014-08-30 fundamentals/intro.tex
adds fundamentals.bib

@@
 
-Cyclus provides a sophisticated and modern, agent-based platform. Previous 
-codes were lacking in a number of ways. Cyclus has a number of features that 
-overcome those issues.
+In addition to providing the fundamental features expected in fuel cycle 
+simulators, the Cyclus paradigm enables two major capabilites that previous 
+simulators were lacking. First, it enables simulations at multiple levels of 
+fidelity.  It also facilitates direct comparison of modeling methodologies.
 
@@
 
-Modeling the growth of a physics-dependent, international nuclear fuel supply
+Modeling the evolution of a physics-dependent, international nuclear fuel supply
 chain is a difficult problem. To date, it has been treated relatively

### 2014-08-30 fundamentals/qa.tex
QA intro

\section{Quality Assurance}
% Organize this section according to major topics
% give each topic a section heading in boldface.
% try to cover the major common points :
%
% problem design
% methods of measurement
% supporting models
% supporting data
% simulations run
% results

% Just write the section headings for each part and indicate what goes in that
% section with words :
%
% heading
% figures (with captions)
% schematics (with captions and footnotes)
% equations
% tables

% What does it mean?
% What did I actually test?
% What were the results?
% Did the work yield a new method?
% Did the work yield new knowledge?
% What measurements did I make?
% How were these measurements characterized?
% What methods were used?
% What were the results?
% How were the measurements made and characterized?

Simulation science - like experimental science - has since the begining had the 
problem of identifying trustworthy results from the nonsensical and the noise.
This is epitomized in the Charles Babbage quote, ``On two occasions I have been asked, 
`Pray, Mr. Babbage, if you put into the machine wrong figures, will the right 
answers come out?' ... I am not able rightly to apprehend the kind of confusion 
of ideas that could provoke such a question.'' \cite{babbage2011passages}. 
The \emph{garbage in, garbage out} phenomenon is not the only scenario which a
simulator must gaurd against; ensuring correctness is equally important.

Multiple strategies collectively known a \emph{quality assurance} (QA) have 
been invented over the years to mitigate the structural and algorithmic errors
on the part of simulators themselves. These include \emph{verification and validation}
(V&V) \cite{boehm1989software}, \emph{uncertainty quantification} (UQ) 
\cite{sacks1989design}, testing, and others. V&V and UQ come from 
a distinctly computational science background while testing \emph{et al.} come from 
a software development bent.

Nuclear enginerering code quality is often governed by NQA-1, an ASME specification 
whose latest revision appeared in 2009 \cite{NQA-1a-2009}. This is primarily 
used for designing reactors. However, it is general enough to apply to 
cyclus. Cyclus has adopted an \emph{agile} development process \cite{larman2004agile}, 
interpreting NQA-1 in a manner similar to NEAMS \cite{neams-qa} or PyNE \cite{pyne-vv}.

Cyclus acknowledges that quality assurance is an on-going process throughout the 
entire life of the code. As a simulator where most modeling descisions are made 
by third party archetype developers or users, the most important feature of QA 
is verification. Validation may be impossible and UQ is beyond the scope.

Verification may be defined as the question, ``Is cyclus being built correctly?'' 
To answer this question we turn to the software development of notions of testing,
documentation, version control, style guidelines, and continuous integration. 
This suite of process controls supplies mechanims for reliable and reproducible 
software. The impetus to implement these correctly is even stronger in a scientific 
context because of the emphasis on reproducibility and provenance. These are 
discussed below individually.

Validation on the other hand may be defined as the question, 
``Is cyclus the correct tool?''
Since cyclus is alone in its class as an agent-based fuel cycle simulator logitudnal 
validation is not possible. Still code-to-code comparisons with fuel cycle
simulators with other modeling paradigms are underway, if nascent. However, such 
exercises are more likely to bring into relief the differences between the modeling
paradigms than be useful for QA and validation.

Lastly, uncertainty quantification is a process that is used on specific simulation
instantiations to statistically determine its quality. Since the cyclus 
kernel requires an input file written by the user, UQ is a process that applies 
more to those running cyclus than to those running it.  Furthermore, any UQ
results that are generated are applicable only to the scenario that is under 
analysis. Thus for cyclus UQ is well beyond the scope of core development.

% Unfortunately, we can't wind forward the clock to compare our simulations to 
% the futures that we are attempting to model.

% However, Cyclus does implement a number of strategies for verification and 
% validation of code.

\subsection{Coding Practices}
% What have we done to ensure robustness ?
% Examples from Material class, Transactions, simulation IDs

Some routines are implemented specifically to ensure robustness.

\subsection{Testing}
% Peer-review system (secretly a note on open source?)

We have reasonable test coverage and a code review system.

\subsubsection{Unit Tests}

Testing individual units of 'work'.

\subsubsection{Regression Tests}

Testing identical output for each pull request.

\subsubsection{Integration Tests}

Testing aggregate answers for each pull request. Specifically, previous
simulations used in publications are integration tested to confirm their output
is maintained.

### 2014-08-30 fundamentals/qa.tex
now it builds

@@
 on the part of simulators themselves. These include \emph{verification and validation}
-(V&V) \cite{boehm1989software}, \emph{uncertainty quantification} (UQ) 
-\cite{sacks1989design}, testing, and others. V&V and UQ come from 
+(V\&V) \cite{boehm1989software}, \emph{uncertainty quantification} (UQ) 
+\cite{sacks1989design}, testing, and others. V\&V and UQ come from 
 a distinctly computational science background while testing \emph{et al.} come from 

### 2014-08-30 fundamentals/qa.tex
added testing section

@@
 
-% Unfortunately, we can't wind forward the clock to compare our simulations to 
-% the futures that we are attempting to model.
+\subsection{Testing}
 
-% However, Cyclus does implement a number of strategies for verification and 
-% validation of code.
+Automated software \emph{testing} is the first line of defense against
+errors in implementation. It also acts as an early warning sign that the
+simulator does or does not work as intended on a new system.
+Testing serves a critical role in QA because it directly compares the 
+results of running software versus the expected behavior of the software.
+In cyclus, three categories of tests are defined: unit tests, integration 
+tests, and regression tests.
 
-\subsection{Coding Practices}
-% What have we done to ensure robustness ?
-% Examples from Material class, Transactions, simulation IDs
-
-Some routines are implemented specifically to ensure robustness.
-
-\subsection{Testing}
-% Peer-review system (secretly a note on open source?)
-
-We have reasonable test coverage and a code review system.
+It is important to note that before a proposed
+code changes is allowed into main stream cyclus, all of the tests must pass
+and the change must be covered by a test, either new or existing. This is 
+matter of policy for the developers. Additionally, test code is equally likely 
+as the code it is testing to contain errors. To prevent an infinite recurrsion 
+of testing-the-tests, it is assumed that dilligence and one level of testing 
+is sufficient to meet the aims of the quality assurance.
 
@@
 
-Testing individual units of 'work'.
+Unit tests are those which compare the results of the smallest code \emph{unit}, 
+typically a single function or a class. What constitutes a the smallest code
+unit depends on the context of the specific unit in question. While this is 
+an ambiquous defintiion, combined with a philosophy of keeping units as small
+as possible it is often clear in practice what needs to be tested.
+
+Cyclus uses the Google Test framework \cite{gtest} as a harness for running unit 
+tests. Sufficient unit tests are required for any proposed change to the cyclus
+code base. Currently cyclus implements over 450 unit tests and cycamore has 
+85.  These cover approximately 65\% of their respective code bases. This number 
+is expected to grow over time.
+
+\subsubsection{Integration Tests}
+
+Intergration tests are any tests that combine multiple elemnents of the 
+cyclus interface and test that they work correctly with each other.  By analogy, 
+simply because the gears (units) are made correctly does not imply that the 
+clock (integration) will run smoothly, run at all, or give the correct time.
+In cyclus and cycamore, integration tests are performed by running sample
+simulations and verifying that results are what would be expected ahead of 
+time. Precanned input files have thus been contsructed. Their results 
+are inspected and compared via nose \cite{nosetests}, a Python test framework.
+Python will run cyclus as a subprocess for each integration test. In this
+way cyclus code units are tested in the full context that they will
+executed. This category of testing is especially useful for ensuring that 
+major cyclus components are functioning as expected.
 
@@
 
-Testing identical output for each pull request.
-
-\subsubsection{Integration Tests}
-
-Testing aggregate answers for each pull request. Specifically, previous
-simulations used in publications are integration tested to confirm their output
-is maintained.
+Regression tests are tests which ensure that significant changes do not 
+occur over the course of cyclus development. Such a change is called a 
+\emph{regression} because the new version is almost always wrong.
+Regression tests are implemeneted similarly to integration tests.
+Nose is used to execute fully fledged cyclus simulations whose results
+are then compared. In this category however the comparison is done against 
+the output of the same input file when run with a previous version of cyclus, 
+typically the last released version.
+In some sense, regression tests are `dumb' in that they do 
+not care about the contents of a simulation being correct, only whether or not 
+it changed. They thus pick up glaring time-sensitive mistakes that may 
+not appear elsewhere though they do not purport to make claims about the
+quality of the physics modeled. The cycamore project is the primary location of
+regression tests. This is because the archetypes here are sophisticated enough
+to make interesting input files. Only a handful ($<10$) time steps are needed 
+for regression testing.

### 2014-08-30 fundamentals/qa.tex
more has been written

@@
 for regression testing.
+
+\subsection{Documentation}
+
+All of the public interface (the API) must be documented as part of cyclus
+QA policy. This certifies that the intention for a code unit is communicated 
+in way that is separate from its implementation. This policy is important 
+because implementations are often wrong, hence bugs. They are thus unreliable 
+resources about themselves. Truly trustworthy communication about what 
+software should be doing comes from the author explicitly stating the 
+goals of an API in prose form. Furure development of the code is then able to 
+compare the implemetation versus the documentation to discern whether or not they 
+are in agreement. Documentation is thus a secondary higher-level information 
+stream.  In cyclus, this information is aggregated together into static 
+websites with the doxygen \cite{van2008doxygen} and sphinx \cite{brandl2014sphinx} 
+tools. These websites are placed online at \url{http://fuelcycle.org}.
+
+\subsection{Version Control}
+
+Version control is the history-preserving mechanism by which the provenance of 
+a code is recored. Cyclus uses a well-established tool called git \cite{git_2014}
+for this purpose. Git is currently the most popular utilty in the recent wave
+of \emph{distributed version control}. Briefly stated, this means that every 
+user has a complete local copy of the \emph{repository} (the version control
+term for the collection of all possible histories).
+Though there and many praises and criticisms of git, one 
+feature that the tool performs exceptionally well is the notion of code branches.
+These are distinct pathways in the history that branch out of a mainline source
+tree and then may be \emph{merged} back into the mainline. Multiple simeltaneous
+branches may exist at all point in time. Every change to the code is recorded
+in the history, along with metadata such as the author, a timestamp, and an 
+accompanying message. Thus 
+it is possible for cyclus to accurarely replay the entirety of who did what to the
+code when.
+
+Cyclus uses a strategy known as \emph{git flow} \cite{kalliamvakou2014code} 
+to manage topical branches where individuals develop code, the mainline development
+branch (simply known as develop), and the stable branch (called master).
+In addition to these rules and delineation, cyclus also imposes rules on 
+when it is accecptable from a quality control standpoint to merge code from 
+the personal topical branches into develop. All software at this stage 
+must have sufficient and passing tests and reasonable documentation. Without
+these core pieces proposed changes are not allowed into cyclus.
+
+The act of proposing a change is known as a \emph{pull request}. The main cyclus is 
+hosted remotely on the GitHub website \cite{dabbish2012social}. The online
+mechanism for pull requests allows for code review by a member of the cyclus 
+core team other than the author prior to any change being included. Non-members
+of the cyclus development team are allowed and encouraged to submit and review 
+pull requests. However, only members of the cyclus core team are allowed to 
+merge in any changes and only after the QA standards have been met.
+
+\subsection{Style Guide}
+
+In any multi-person software project, there is a tension between how individuals
+wish to write code. Every person tends to have their own custom style. To remedy this
+coding style guides are the software analogy to the natural language ones, 
+such as the Chicago Manual of Style. Cyclus strictly enforces the use of the 
+Google C++ Style Guide \cite{weinberger2008google} for all software contributions.

### 2014-08-31 fundamentals/intro.tex
adds Cyclus smallcaps command

@@
 
-The Cyclus code arose out of the 
+The \Cyclus code arose out of the 
 \gls{GENIUSv2}\cite{oliver_studying_2009,huff_geniusv2_2009} code. That software 
@@
 % There was a gap in the capabilities of simulators.
-% Cyclus, a hero, came in to fill that gap.
+% \Cyclus, a hero, came in to fill that gap.
 
 % MJG - @gonuke has always cited method-to-method comparisons as the primary
-% benefit Cyclus can bring to the table. Do we want to frame the hero narrative
+% benefit \Cyclus can bring to the table. Do we want to frame the hero narrative
 % in that context? The more I think about, the more I feel like this is a
@@
 In addition to providing the fundamental features expected in fuel cycle 
-simulators, the Cyclus paradigm enables two major capabilites that previous 
+simulators, the \Cyclus paradigm enables two major capabilites that previous 
 simulators were lacking. First, it enables simulations at multiple levels of 
-fidelity.  It also facilitates direct comparison of modeling methodologies.
+fidelity. Second, it facilitates direct comparison of modeling methodologies.
 
@@
 
-Cyclus uses a divide-and-conquer approach, separating the problem of modeling a
+\Cyclus separates the problem of modeling a
 physics-dependent supply chain into a simulation kernel and archetypes that
@@
 % we could use a specific example of Cosi's equivalence method below
-Because Cyclus uses a modular archetype approach, comparing two archetypes is
+Because \Cyclus uses a modular archetype approach, comparing two archetypes is
 straightforward. Consider a case in which an analyst would like to compare the
@@
 We expect that there are a number of types of users and developers who will 
-interact with the Cyclus framework. Those people fall into a number of 
+interact with the \Cyclus framework. Those people fall into a number of 
 categories. All such people benefit from the modular architecture.
 
-% man that figure has gone quite a ways =)
-<modified-open-source collaboration diagram>
+\begin{figure}[htbp!]
+\begin{center}
+\includegraphics{modifiedopen.eps}
+\end{center}
+\caption{The \Cyclus framework enables fully open, partially open, and fully 
+closed collaborations.}
+\label{fig:modifiedopen}
+\end{figure}
 

### 2014-08-31 fundamentals/intro.tex
makes an image directory for images
edits motivation section for conciseness

@@
 
-Methods for calculating those metrics vary among simulators. Some model the fuel cycle at static equillibrium, while others 
-capture fuel cycle dynamics.  Similarly, while some simulators discretely model 
-material and and facilities, others track streams of materials and 
-fleets of facilities in an aggregated fashion. Depending on their intended use, 
-simulators often model some aspect of the fuel cycle in great detail. For this 
-reason, simulators specialize in economics, material isotopics, or 
-transmutation detail, where others do not.
+Methods for calculating those metrics vary among simulators. Some model the 
+fuel cycle at static equillibrium, while others capture fuel cycle dynamics.  
+Similarly, while some simulators discretely model material and and facilities, 
+others track streams of materials and fleets of facilities in an aggregated 
+fashion. Depending on their intended use, simulators often overspecialize, 
+modeling a single aspect of the fuel cycle in great detail. For this reason, 
+some simulators specialize in economics, material isotopics, or transmutation 
+detail, where others do not.
 
@@
 simultaneously developed tools of their own as well, such as 
-\gls{CAFCA}\cite{guerin_benchmark_2006}.
+\gls{CAFCA}\cite{guerin_benchmark_2006} and \gls{COSI}\cite{cosi}.
 
-The \Cyclus code arose out of the 
+The \Cyclus simulator arose out of the 
 \gls{GENIUSv2}\cite{oliver_studying_2009,huff_geniusv2_2009} code. That software 
@@
 \gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006} which 
-captured regional behaviors in fuel cycle scenarios.
+captured regional behaviors in fuel cycle scenarios. \Cyclus is a dynamic 
+simulator that treats both materials and facilities discretely, with an 
+architecture that permits simulations with multiple and variable levels of 
+fidelity.
 
@@
 
-% MJG - @gonuke has always cited method-to-method comparisons as the primary
-% benefit \Cyclus can bring to the table. Do we want to frame the hero narrative
-% in that context? The more I think about, the more I feel like this is a
-% secondary argument. I'll take a crack at a few sentences below.
-
 In addition to providing the fundamental features expected in fuel cycle 
-simulators, the \Cyclus paradigm enables two major capabilites that previous 
-simulators were lacking. First, it enables simulations at multiple levels of 
-fidelity. Second, it facilitates direct comparison of modeling methodologies.
-
-% MJG - I don't claim that all of this belongs in the beginning of this
-% subsection, but here's some more content.
+simulators, the \Cyclus paradigm enables major capabilites that previous 
+simulators lack. First, its \emph{modular and open architecture}  
+facilitates targeted contribution 
+and collaboration within the nuclear fuel cycle analysis community. 
+Additionally, \emph{agent interchangability} facilitates direct comparison of modeling 
+methodologies. Finally, the flexibility and generality of its \emph{\gls{ABM}} 
+paradigm and \emph{discrete, object-oriented approach} emphasizes applicability of the \Cyclus tool accross a broader range 
+of applications than other simulators.
 
@@
 \begin{center}
-\includegraphics{modifiedopen.eps}
+\includegraphics{./images/modifiedopen.eps}
 \end{center}
@@
 
-ABM is modern, sophisticated, true to reality, and it takes advantage of modern
+\gls{ABM} is modern, sophisticated, true to reality, and it takes advantage of modern
 computing resources. Furthermore, agent-based modeling provides an analyst a
@@
 System dynamics popular approach for modeling nuclear fuel cycles in current
-tools (cite VISION/CAFCA). It has been shown in the literature
+tools \cite{VISION,CAFCA}. It has been shown in the literature
 \cite{macal_agent-based_2010} that any system dynamics model can be translated

### 2014-08-31 fundamentals/intro.tex
improvement of the discrete objects section

@@
 simulators, the \Cyclus paradigm enables major capabilites that previous 
-simulators lack. First, its \emph{modular and open architecture}  
-facilitates targeted contribution 
-and collaboration within the nuclear fuel cycle analysis community. 
-Additionally, \emph{agent interchangability} facilitates direct comparison of modeling 
-methodologies. Finally, the flexibility and generality of its \emph{\gls{ABM}} 
-paradigm and \emph{discrete, object-oriented approach} emphasizes applicability of the \Cyclus tool accross a broader range 
-of applications than other simulators.
+simulators lack. First, its \emph{modular and open architecture}  facilitates 
+targeted contribution and collaboration within the nuclear fuel cycle analysis 
+community.  Additionally, \emph{agent interchangability} facilitates direct 
+comparison of modeling methodologies. Finally, the flexibility and generality 
+of its \emph{\gls{ABM}} paradigm and \emph{discrete, object-oriented approach} 
+emphasizes applicability of the \Cyclus tool accross a broader range of 
+applications than other simulators.
 
@@
 
-\subsubsection{Discrete Resource Tracking}
+\subsubsection{Discrete Objects}
 % enables more realistic models and metrics
@@
 
-Not all simulations can be successfully run with a fleet-based model that 
-doesn't distinguish between discrete materials. Shadow fuel cycles are an 
-example.
+\Cyclus models facilities, institutions, regions, and resources as discrete 
+objects. A discrete resource model allows for a range of modeling granularity. In the
+macroscopic extreme, it is equivalent to time-stepped continuous flow. In the
+microscopic extreme, the model is capable of representing arbitrarily small 
+material objects at isotopic resolution. In this way, the \Cyclus simulator is 
+applicable across the full range of modeling extremes.
 
-A discrete resource model allows for a range of modeling granularity. In the
-macroscopic extreme, it is equivalent to time-stepped continuous flow. In the
-microscopic extreme, the model is capable of representing individual fuel
-assemblies.
+This generality specifically permits the use cases that cannot be acheived with 
+fleet-based models. That is, some questions require resolution at the level of 
+individual facilities and individual materials.  Since fleet-based, 
+lumped-material models do not distinguish between discrete facility entities or 
+discrete materials, many detailed performance metrics cannot be captured with 
+those tools.
+
+One example use case seeks to capture system vulnerability to nefarious 
+material diversion. This type of analysis requires discrete simulation of a 
+target facility and the individual materials modified within it and is only 
+acheivable with discretely-modeled objects like those in the \Cyclus simulator.

### 2014-08-31 fundamentals/intro.tex
abm section

@@
 industrial, and political phenomena. Furthermore, complex systems such as 
-nuclear process physics, facility deployment, and material routing each each 
+nuclear process physics, facility deployment, and material routing each 
 must be modeled simultaneously for even the simplest of nuclear fuel cycle 
@@
 Historically, nuclear fuel cycle simulators have addressed this with software 
-ranging from spreadsheet driven flow calculators to full detail industrial 
+ranging from spreadsheet driven flow calculators to high-fidelity industrial 
 models. To date, current tools are either static, fleet-based, or 
@@
 
-\gls{ABM} is modern, sophisticated, true to reality, and it takes advantage of modern
-computing resources. Furthermore, agent-based modeling provides an analyst a
-more natural perspective from which to model a given problem. In the nuclear
-fuel cycle context for example, an analyst can design an agent with
-reactor-related logic and a separate agent with fuel fabrication-related logic.
+\Cyclus utilizes an \gls{ABM} paradigm.  \gls{ABM} is modern, sophisticated, 
+true to reality, and it takes advantage of modern computing resources. 
+Furthermore, agent-based modeling provides an analyst a more natural 
+perspective from which to model a given problem. In the nuclear fuel cycle 
+context for example, an analyst can design an agent with reactor-related logic 
+and a separate agent with fuel fabrication-related logic.
 

### 2014-08-31 fundamentals/intro.tex
modular arch."

@@
 in a given field can utilize their time and resources in modeling a specific
-process associated with the nuclear fuel cycle, e.g. reprocessing and advance
-fuel fabrication, rather than also modeling the entirety of the cycle.
-
-% we could use a specific example of Cosi's equivalence method below
-Because \Cyclus uses a modular archetype approach, comparing two archetypes is
-straightforward. Consider a case in which an analyst would like to compare the
-effect of using different models to determining input fuel composition for fast
-reactors. A variety fuel fabrication archetypes can be developed and used
-interchangably to analyze the effect of each on a simulation's output.
+process associated with the nuclear fuel cycle (e.g., reprocessing and advanced
+fuel fabrication), rather than also modeling the entirety of the cycle.
 
@@
 
-Draw from and cite the ``Open Architecture and Modular Paradigm'' ANS summary.
+The encapsulated plug-in architecture within the \Cyclus tool allows developers 
+to define nuclear fuel cycle facility processes independent of the simulation 
+logic. This design choice acheives two things. First, analysts across 
+institutions can take advantage of the simulation logic \gls{API} and 
+archetype ecosystem when they apply \Cyclus to their specific problem. The effort they 
+undertake can thereby be focused on creating or customizing 
+nuclear facility, institution, resource, and toolkit models within their 
+specific area of expertise.
+
+% we could use a specific example of Cosi's equivalence method below
+Second, because \Cyclus uses a modular archetype approach, comparing two 
+archetypes is straightforward. Consider a case in which an analyst would like 
+to compare the effect of using different models to determining input fuel 
+composition for fast reactors. A variety fuel fabrication archetypes can be 
+developed and used interchangably to analyze the effect of each on a 
+simulation's output.
 
@@
 categories. All such people benefit from the modular architecture.
-
-\begin{figure}[htbp!]
-\begin{center}
-\includegraphics{./images/modifiedopen.eps}
-\end{center}
-\caption{The \Cyclus framework enables fully open, partially open, and fully 
-closed collaborations.}
-\label{fig:modifiedopen}
-\end{figure}
 

### 2014-08-31 fundamentals/impl.tex
spelling
moved the modified open figure to the implementation section.

@@
 This is implemented largely through a clean API and a modern build system.
+
+Additionally, the clean plug-in architecture loads modules without any
+modifications to the \Cyclus kernel. Thus, as in Figure \ref{fig:modifiedopen},
+closed-source archetypes can be used with the simulator alongside open-source
+archetypes. This architecture therefore allows closed-source libraries (e.g.,
+those representing sensitive nuclear processes and subject to export control)
+to be developed and used privately.
+
+\begin{figure}[htbp!]
+\begin{center}
+\includegraphics{./images/modifiedopen.eps}
+\end{center}
+\caption{The \Cyclus framework enables fully open, partially open, and fully
+closed collaborations.}
+\label{fig:modifiedopen}
+\end{figure}
 
@@
 
-Cycamore contains a number of usefule facility models that are a mere base-set.
+Cycamore contains a number of useful facility models that are a mere base-set.
 Additional modules are needed for interesting fuel cycle simulation. However,

### 2014-08-31 fundamentals/intro.tex
bold words

@@
 
-Myriad challenges in nuclear fuel cycle analysis could be 
-addressed with an agent-based framework for simulation and tracking of 
-transformation and trade of resources between facilities within institutions 
-and regions.
+The fundamental concepts of the \Cyclus nuclear fuel cycle simulator capture 
+these modern insights so that challenges in nuclear fuel cycle analysis can be 
+better addressed.
 
@@
 \gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006} which 
-captured regional behaviors in fuel cycle scenarios. \Cyclus is a dynamic 
-simulator that treats both materials and facilities discretely, with an 
+captured regional behaviors in fuel cycle scenarios.
+
+\Cyclus is a dynamic simulator that treats both materials and facilities discretely, with an 
 architecture that permits simulations with multiple and variable levels of 
-fidelity.
+fidelity. Its agent-based framework for simulation and tracking of 
+transformation and trade of resources between facilities within institutions 
+and regions greatly improves upon the existing field of fuel cycle simulators.
 

### 2014-08-31 fundamentals/impl.tex
dynamically loadable libraries implementation section closely follows katy's dissertation discussion on this topic. Some slight paraphrasing was employed to avoid self-plaigarism

--- 2014-07-31 fundamentals/impl.tex
@@
 
-\subsection{Dynamically loadable libraries}
+\subsection{Dynamically Loadable Libraries}
 % (diagram)
@@
 architecture into a suite of dynamically loadable ``plug-in'' libraries. 
+This is implemented largely through a clean API and a modern build system.
 
-This approach allows contribution to an ecosystem of libraries. The 
+Dynamically-loadable libraries are the primary mechanism for extending \Cyclus' capability. 
+This approach provides encapsulation: the core of the code operates
+completely independently from the individual libraries. Thus, any
+customization or extension is implemented only in the loadable
+library.
+
+This approach allows efficient, targeted contribution to the ecosystem of libraries.  The 
 scientist-developer can therefore focus on generating a model within their 
 sphere of expertise, while relying on the model contributions of others to fill 
-in the other technologies.
+in the other technologies.  This strategy also allows individual developers to
+explore different levels of complexity within their archetypes, including
+wrapping other simulation tools as loadable libraries within the \Cyclus
+framework.
 
-This is implemented largely through a clean API and a modern build system.
+A secondary benefit is the ability for
+contributors to choose different distribution and licensing strategies
+for their contributions. By allowing models to have varied
+availability, the security concerns of developers can be
+assuaged (See Figure \ref{fig:modifiedopen}).
+
+\begin{figure}[htbp!]
+\begin{center}
+\includegraphics{./images/modifiedopen.eps}
+\end{center}
+\caption{The \Cyclus framework enables fully open, partially open, and fully
+closed collaborations\cite{wilson_cyclus:_2012}.}
+\label{fig:modifiedopen}
+\end{figure}
+
+In particular, since the clean plug-in architecture loads libraries without any
+modifications to the \Cyclus kernel, closed-source archetypes can be used with
+the simulator alongside open-source archetypes. This architecture therefore
+allows closed-source libraries (e.g., those representing sensitive nuclear
+processes and subject to export control) to be developed and licensed privately.
+
+This last benefit of dynamically-loadable libraries addresses
+another goal of \Cyclus: ubiquity amongst its potential user base. By
+engineering \Cyclus to easily handle varying levels of complexity, a single
+simulation engine can be used by both users interested in big-picture policy
+questions as well as users focused on more detailed, technical
+analyses.
 

### 2014-08-31 fundamentals/qa.tex

@@
 
+Sections \ref{sec:qa-testing}-\ref{sec:qa-ci} discuss in greater detail the software 
+development components that comprise the cyclus verification strategy.
+Each of these on its own is a valuable addition to QA but is cannot be the 
+entire answer to the requirements imposed by NQA-1. Taken together and strictly 
+adhered to they present a fortress through which undeisrable code may siege, 
+but never take.
+
 \subsection{Testing}
+\label{sec:qa-testing}
 
@@
 Google C++ Style Guide \cite{weinberger2008google} for all software contributions.
+This means that all developers of cyclus nominally write cyclus code in the same 
+way.  This homogenization may be a hurdle to new developers but ultimately 
+makes the it much more legible. Adoption of a single style guide also settles
+timeless arguments over what style is `the best.' Having only one means that 
+there is a common enemy for all developers to dislike equally.
+
+\subsection{Continuous Integration}
+\label{sec:qa-ci}
+
+Continuous integration (CI) the idea that software should be tested and validated 
+as it is being developed, rather than as a final stage in a longer development 
+cycle.  Under CI every pull request is tested independently immeadiately after 
+it is proposed. Such tests shoudl be run on all officially supported platforms. 
+Cyclus uses a CI platform called Polyphemus \cite{polyphemus_2014}.
+
+Polyphemus serves as an intermediary between GitHub pull requests on the frontend 
+and temporary cyclus servers on the backend. These servers are hosted by 
+the Build \& Test Laboratory (BaTLab) \cite{batlab_2014} at the University of 
+Wisconsin-Madison. Whenever a pull request is created, Polyphemus performs 
+the following actions:
+
+\begin{enumerate}
+    \item Copies cyclus with the pull requested code to BaTLab,
+    \item Initiliazes Linux and Mac OSX servers,
+    \item Builds cyclus on all platforms,
+    \item Runs the complete cyclus test suite, 
+    \item Reports back whether the above steps succeeded or not.
+\end{enumerate}
+
+Since these steps are performed for all incoming code, it is easy for the 
+cyclus core team to determine whether or not an indivudual pull request 
+actually works. This helps identify build and test problems prior to 
+broken code being allowed into the develop branch.
+
+CI has become a neccessary but not sufficient addition to the cyclus QA
+system. Its merit is that it keeps bad code out. However, cyclus will always
+require human eyes and human hands to let good code in.

### 2014-09-16 fundamentals/impl.tex
notes on discrete resources and materials and tracking

@@
 
-Discrete facility and material tracking is more realistic an dmore
+TODO: add blurb about discrete agent/facility tracking.
+
+In Cyclus, agents can transfer discrete resource objects between each other.
+Cyclus supports two types of resources:
+
+\begin{itemize}
+
+  \item Materials: These represent typical nuclear materials with
+      nuclide-based compositions.
+
+  \item Products: These can represent any user-defined thing - e.g. carbon
+      credits, build permits, employees, etc.
+
+\end{itemize}
+
+All operations performed on every resource object (splitting, combining,
+decay, etc.) are tracked in detail.  This information includes the creating
+agent for when resources are newly created and introduced into the simulation.
+The parentage of each resource is also tracked. This makes it possible to
+follow the travel history of resource objects as they are transferred between
+agents.
+
+In large simulations there may be many material objects changing frequently.
+Material decay can also contribute significantly to such changes.  In order to
+help avoid unnecessary runtime performance and database space impacts,
+compositions in Cyclus have some special features.  Compositions in Cyclus are
+immutable.  This immutability allows multiple material objects to all hold
+references to the same composition object safely.  When operations are
+performed on a material that don't change the composition, any new resulting
+materials hold a reference to the same, originating composition object.
+Although the decay operation generates a new, separate composition (preserving
+immutability), a reference to the new composition is placed in a cache shared
+by the new an originating compositions. The next time the originating
+composition is decayed, this cache will be checked for a prior calculation
+with the same cumulative decay time.  If one exists, the cached composition is
+used.  This cache is shared by all compositions that transitively come from
+the same origin.  Composition immutability in concert with decay history
+caching help eliminate many redundant decay calculations in addition to
+reducing the total number of composition objects.  Since each composition
+object is only recorded in the database once, significant space savings also
+occurs.
 

### 2014-09-19 fundamentals/impl.tex
rough draft paragraphs on interchangability

--- 2014-08-31 fundamentals/impl.tex
@@
 \subsection{Agent Interchangability}
-% interchangeability due to exchange behavior api
 
-This approach enables ``apples-to-apples'' comparisons, something that has been 
-sorely missing in previous simulators.
+A key compontent of the \Cyclus kernel architecture is the ability for
+implementations of actors in a given simulation to be easily
+interchanged. Critically, this novel functionality enables the comparison
+between agent implementations. For example, a low-physics-fidelity
+implementation of a reactor can be comparied to an implementation with higher
+physics fidelity, allowing an analyst to discern the effect of reactor physical
+fidelity on a given fuel cycle. Interchangability is accomplished by providing
+APIs that define agent-to-agent interaction and agent-to-environment
+interaction, primarily through the \Class{Agent} and \Class{Trader} interfaces.
 
-By making the facilities interchangeable, it combinatorically increases the 
-number of scenarios that can be modeled. The user can choose to model just the 
-front end or just the back end of a fuel cycle.
-
-This is implemented with an API that focuses on treating the agents as black 
-boxes.
+The \Class{Agent} interface provides a notion of parent-child hierarchichal
+relationship, where parents can choose to \textit{build} child agents and
+\textit{decommission} child agents. The \Class{Trader} interface allows
+agent-agent interaction through the trading of \Class{Resource}s. Usabe
+archetypes in a \Cyclus simulation must implement the \Class{Agent} interface
+and may optionally implement the \Class{Trader} interface. For example, a
+\Class{Region} implements only the \Class{Agent} interface, whereas a
+\Class{Facility} implements both the \Class{Agent} and \Class{Trader} interface,
+allowing any \Class{Facility} to trade with another \Class{Facility}.
 

### 2014-09-19 fundamentals/impl.tex
moved last sentence back to second p

@@
 physics fidelity, allowing an analyst to discern the effect of reactor physical
-fidelity on a given fuel cycle. Interchangability is accomplished by providing
-APIs that define agent-to-agent interaction and agent-to-environment
-interaction, primarily through the \Class{Agent} and \Class{Trader} interfaces.
+fidelity on a given fuel cycle.
 
-The \Class{Agent} interface provides a notion of parent-child hierarchichal
-relationship, where parents can choose to \textit{build} child agents and
-\textit{decommission} child agents. The \Class{Trader} interface allows
-agent-agent interaction through the trading of \Class{Resource}s. Usabe
-archetypes in a \Cyclus simulation must implement the \Class{Agent} interface
-and may optionally implement the \Class{Trader} interface. For example, a
-\Class{Region} implements only the \Class{Agent} interface, whereas a
-\Class{Facility} implements both the \Class{Agent} and \Class{Trader} interface,
-allowing any \Class{Facility} to trade with another \Class{Facility}.
+Interchangability is accomplished by providing APIs that define agent-to-agent
+interaction and agent-to-environment interaction, primarily through the
+\Class{Agent} and \Class{Trader} interfaces. The \Class{Agent} interface
+provides a notion of parent-child hierarchichal relationship, where parents can
+choose to \textit{build} child agents and \textit{decommission} child
+agents. The \Class{Trader} interface allows agent-agent interaction through the
+trading of \Class{Resource}s. Usabe archetypes in a \Cyclus simulation must
+implement the \Class{Agent} interface and may optionally implement the
+\Class{Trader} interface. For example, a \Class{Region} implements only the
+\Class{Agent} interface, whereas a \Class{Facility} implements both the
+\Class{Agent} and \Class{Trader} interface, allowing any \Class{Facility} to
+trade with another \Class{Facility}.
 

### 2014-09-19 fundamentals/impl.tex
initial sentence regarding hierarchy

@@
 \subsection{Agent Interchangability}
+% interchangeability due to exchange behavior api
 
-A key compontent of the \Cyclus kernel architecture is the ability for
-implementations of actors in a given simulation to be easily
-interchanged. Critically, this novel functionality enables the comparison
-between agent implementations. For example, a low-physics-fidelity
-implementation of a reactor can be comparied to an implementation with higher
-physics fidelity, allowing an analyst to discern the effect of reactor physical
-fidelity on a given fuel cycle.
+This approach enables ``apples-to-apples'' comparisons, something that has been 
+sorely missing in previous simulators.
 
-Interchangability is accomplished by providing APIs that define agent-to-agent
-interaction and agent-to-environment interaction, primarily through the
-\Class{Agent} and \Class{Trader} interfaces. The \Class{Agent} interface
-provides a notion of parent-child hierarchichal relationship, where parents can
-choose to \textit{build} child agents and \textit{decommission} child
-agents. The \Class{Trader} interface allows agent-agent interaction through the
-trading of \Class{Resource}s. Usabe archetypes in a \Cyclus simulation must
-implement the \Class{Agent} interface and may optionally implement the
-\Class{Trader} interface. For example, a \Class{Region} implements only the
-\Class{Agent} interface, whereas a \Class{Facility} implements both the
-\Class{Agent} and \Class{Trader} interface, allowing any \Class{Facility} to
-trade with another \Class{Facility}.
+By making the facilities interchangeable, it combinatorically increases the 
+number of scenarios that can be modeled. The user can choose to model just the 
+front end or just the back end of a fuel cycle.
 
-\subsection{Region/Institution/Facility hierarchy}
-% (diagram)
+This is implemented with an API that focuses on treating the agents as black 
+boxes.
+
+\subsection{Regions, Institutions, and Facilities}
+
+\Cyclus provides a novel representation of entities in the nuclear fuel cycle,
+including facilities, institutions managing those facilities, and regions. While
+some simulators (TODO cite DESAE) have provided a notion of static regional
+effects, \Cyclus allows for both regions and institutions to be first-class
+actors in simulated fuel cycles.
 

### 2014-09-19 fundamentals/impl.tex
rough draft of RIF section

@@
 
-\subsection{Agent Interchangability}
+\subsection{Agent Interchangability}\label{sec:interchangeability}
 % interchangeability due to exchange behavior api
@@
 including facilities, institutions managing those facilities, and regions. While
-some simulators (TODO cite DESAE) have provided a notion of static regional
+some simulators (\TODO{cite DESAE}) have provided a notion of static regional
 effects, \Cyclus allows for both regions and institutions to be first-class
@@
 
-Cyclus has three core agent classes that be subclassed to create a simulation
-archetype: Region, Institution, and Facility. At present, Regions, Institutions,
-and Facilities (RIF) conceptually form a nested structure in a Cyclus simulation,
-i.e., Facilities exist in (i.e., are managed by) Institutions and Institutions
-exist in Regions.
+The basic interaction models for each entity is implemented by a corresponding
+archetype class in \Cyclus, i.e., the \Class{Region} class, \Class{Institution}
+class, and \Class{Facility} class. Archetype developers can then build on the
+provided functionality by subclassing the appropriate class.
 
-Importantly, the RIF separation allows for preferential trading. For example,
-Facilities in the same Institution can preferentially trade with each
-other. Similarly, Regions can be given a location proxy, and the trade between
-Facilities can be informed by their regional proximity.
+\Cyclus implements a Region-Institution-Facility (RIF) relationship through the
+parent-child hierarchy described in \S \ref{sec:interchangeability}, where
+regions are the parents of institutions which are, in turn, the parents of
+facilities. In other words, RIF hierarchies form a directed acyclic graph (DAG),
+with regions as root nodes and facilities as leaf nodes.
+
+Two primary consequences arise from this structure. First, institutions are
+responsible for building and decommissioning facilities. Accordingly, advanced
+logic regarding building and decommissioning can be obtained by subclassing the
+\Class{Institution} interface. Second, the \Class{Facility} class implmenets the
+\Class{Trader} interface, and thus institutions and regions, respectively, can
+adjust the resource flow preferences of their managed facilities. Importantly,
+this novel capability allows for the modeling of preferential regional trading
+of resources (e.g., tariffs) as well as preferential institutional trading
+(e.g., long-term contracts).
 

### 2014-09-19 fundamentals/impl.tex

--- 2014-09-19 fundamentals/impl.tex
@@
 
-Because this doesn't rely on PowerSim, GoldSim, Excel, or any other COTS 
-Windows-based software, we can run singular instances of Cyclus 
-on large linux machines that have lots more capability than hacked together 
-Windows clusters.
+\Cyclus is primarily written in \texttt{C++}, and support is currently provided
+for Linux-based (including Ubuntu and OSX) platforms. Furthermore, the core
+infrastructure and related archetypes are free and open-source, BSD-3-clause
+licsened. No part of \Cyclus is proprietary or based on commercial, off the
+shelf (COTS) software. Accordingly, it can be easily deployed on large compute
+systems, such as high-throughput computing (HTC) systems.
+
+Cyclopts (\TODO{cite}), a proof of principle design and implementation of such a
+system, uses UW-Madison's HTCondor HTC infrastructure to perform sensitivity
+studies on \Cyclus' resource exchange optimization solvers. To date, it has been
+used run over $10^4$ jobs, or (\TODO{compute time}) total compute hours, using
+the \Cyclus library via its resource exchange API.
 
@@
 
-\subsection{Regions, Institutions, and Facilities}
-
-\Cyclus provides a novel representation of entities in the nuclear fuel cycle,
-including facilities, institutions managing those facilities, and regions. While
-some simulators (TODO cite DESAE) have provided a notion of static regional
-effects, \Cyclus allows for both regions and institutions to be first-class
-actors in simulated fuel cycles.
+\subsection{Region/Institution/Facility hierarchy}
+% (diagram)
 

### 2014-09-22 fundamentals/impl.tex

@@
 \subsection{Agent Interchangability}\label{sec:interchangeability}
-% interchangeability due to exchange behavior api
 
-This approach enables ``apples-to-apples'' comparisons, something that has been 
-sorely missing in previous simulators.
+A key compontent of the \Cyclus kernel architecture is the ability for
+implementations of actors in a given simulation to be easily
+interchanged. Critically, this novel functionality enables the comparison
+between agent implementations. For example, a low-physics-fidelity
+implementation of a reactor can be comparied to an implementation with higher
+physics fidelity, allowing an analyst to discern the effect of reactor physical
+fidelity on a given fuel cycle.
 
-By making the facilities interchangeable, it combinatorically increases the 
-number of scenarios that can be modeled. The user can choose to model just the 
-front end or just the back end of a fuel cycle.
-
-This is implemented with an API that focuses on treating the agents as black 
-boxes.
+Interchangability is accomplished by providing APIs that define agent-to-agent
+interaction and agent-to-environment interaction, primarily through the
+\Class{Agent} and \Class{Trader} interfaces. The \Class{Agent} interface
+provides a notion of parent-child hierarchichal relationship, where parents can
+choose to \textit{build} child agents and \textit{decommission} child
+agents. The \Class{Trader} interface allows agent-agent interaction through the
+trading of \Class{Resource}s. Usabe archetypes in a \Cyclus simulation must
+implement the \Class{Agent} interface and may optionally implement the
+\Class{Trader} interface. For example, a \Class{Region} implements only the
+\Class{Agent} interface, whereas a \Class{Facility} implements both the
+\Class{Agent} and \Class{Trader} interface, allowing any \Class{Facility} to
+trade with another \Class{Facility}.
 

### 2014-09-22 fundamentals/impl.tex
added a toolkit section, closes #22

@@
 \subsection{Toolkit}
-% library of tools
-% contributions to the toolkit
-% place for metrics
 
-The toolkit is a place for developers and users to contribute common-use tools 
-for calculating metrics, managing process physics, and handling data.
+In addition to the core functionality of the \Cyclus kernel, which is focused on
+the minimal set of capabilities needed to implement an agent-based simulation
+with dynamic resource exchange, a toolkit is provided that assists developers
+and users with related simulation and nuclear engineering tasks. The toolkit is
+an activly developed module module of \Cyclus, with a primary forward-looking
+focus on supporting interesting \textit{in situ} (i.e., in simulation) and
+\textit{ex situ} (i.e., post-processing) metric analysis tools.
 
-This was implemented by liberal use of namespaces and is populated with an
-introductory suite of useful tools, including helper classes for managing
-facility deployment, minimum cost facility deployment decision making, and for
-enrichment-related calculations.
+\subsubsection{Simulation Tools}
+
+A series of utility classes are provided to support demand-constrained agent
+(e.g. facility) deployment. Symbolic function representations of linear,
+expontential, and piecewise functions are supported via the
+\Class{SymbFunctionFactory} class. Such functions are used with other toolkit
+classes to determine commodity demand (e.g., power demand) from user input. Four
+mixin classes provide the basis for in-simulation deployment determination:
+\Class{CommodityProducer}, \Class{CommodityProducerManager}, \Class{Builder},
+\Class{BuildingManager}. The \Class{CommodityProducer} class provides an
+interface for querying the \textit{prototypes} which have some nameplate
+capacity to produce a given commdity, and the \Class{CommodityProducerManager}
+provides an interface for registering \Class{CommodityProducer}s and querying
+the current capacity (supply) of a commodity. The \Class{Builder} class provides
+an interface for querying which prototypes can be built and interacts with the
+\Class{BuildingManager}, which orders prototypes to be built. The
+\Class{BuildingManager} uses a simple minimum cost algorithm to determine how
+many of each prototype, $y_i$, to build given a demand, $\Phi$, capacities,
+$\phi_i$, and costs $c_i$.
+
+\begin{equation}
+\begin{aligned}
+ \min & \sum_{i=1}^{N}c_i y_i \\
+ s.t. & \sum_{i=1}^{N}\phi_i y_i \ge \Phi \\
+      & n_i \in [0,\infty) \:\: \forall i \in I, \:\: y_i \:\: \text{integer} 
+\end{aligned}
+\end{equation}
+
+\subsubsection{Nuclear Engineering Tools}
+
+The \Cyclus toolkit provides two useful modules for querying \Class{Material}
+objects regarding physical parameters. First the \Class{MatQuery} module
+provides a basic querying API, including the atom and mass fractions of
+nuclides, the number of moles of a nuclide in a material, and also the amount of
+aggregate nuclides, i.e., a \Class{Composition}, in a material. The
+\Class{enrichment} module provides an API for determining enrichment-related
+parameters of a material, including the separative work units (SWU) and natural
+uranium required to enrich a material given provided feed, product, and tails
+assays.
 

### 2014-09-25 fundamentals/examples.tex
more content and comments added in intro, examples, impl, and verification
adds some basic stuff to the ecosystem examples section.

@@
 
-Current and past simulations with the Cyclus simulator have already 
-demonstrated a range of uses.
-
 \subsection{Ecosystem}
@@
 
-External modules have been (cite cyder, separations, streamblender, demandinst, 
-commodconverter, etc.) and are being (cite brightlight, UTK module, etc.) 
-developed for contribution to the cyclus ecosystem of models.
+The archetypes created by user-developers 
+and the archetypes provided in the \Cycamore repository of additional modules 
+together form an `ecosystem' of capabilities. Since the long term vision for 
+the \Cyclus framework includes an ever-expanding ecosystem of both general and 
+specialized capability extensions within that ecosytem. The early growth and 
+cross-institutional contributions to this ecosystem demonstrates a significant 
+acheivement by the \Cyclus framework.
+
+\subsubsection{The Cyclus Additional Modules Repository}
+
+\Cycamore, the \Cyclus additional modules repository, provides a fundamental 
+set of agent archetypes for basic simulation functionality within \Cyclus.
+Since the \Cyclus framework relies on external archetypes to represent the 
+agents within a simulation, 
+\Cycamore provides the basic archetypes a new user needs to get started running 
+simple simulations. 
+These archetypes support a minimal set of fuel cycle simulation goals and 
+provide, by example, a guide to new developers who would seek to contribute 
+their own archetypes outside of \Cycamore.
+
+\subsubsection{External Modules}
+External modules have been 
+\cite{cyder,separations,streamblender,mktdriveninst,commodconverter} and are 
+being \cite{britelite,utk} developed for contribution to the cyclus ecosystem 
+of models.
 
@@
 
+% MJG - INPRO should be tried again. @rwcarlsen has been running lots of
+% simulations with the batch reactor, and its the second generation of my
+% reactor models. We could easily use the same demand schedule and enrichment
+% facility parameters and run it again.
+
 Simulations have been run in the past and more are being run. FCO is an 

### 2014-09-25 fundamentals/examples.tex
citation

@@
 
-The archetypes created by user-developers 
-and the archetypes provided in the \Cycamore repository of additional modules 
+The archetypes created by user-developers and the archetypes provided in the 
+\Cycamore \cite{carlsen_cycamore_2014} repository of additional modules 
 together form an `ecosystem' of capabilities. Since the long term vision for 

### 2014-09-25 fundamentals/examples.tex
first cut at recycle scenario graphs and charts

@@
 example.
+
+Some simple examples of recycle scenarios in Cyclus follow.  In \Cyclus,
+because material is tracked as discrete objects, single-pass mox recycle is
+easy to implement.  The \em{BatchReactor} archetype from \Cycamore has the
+ability to accept fuel from multiple input sources with non-uniform
+preference.  The dynamic resource exchange makes it easy for a reactor to
+preferrentially accept recycled MOX fuel over fresh UOX fuel.  The material
+flows for this simulation are shown below in figure \ref{fig:flow-modopen}.
+
+\begin{figure}
+\label{fig:flow-modopen}
+\caption{Modified open 1-pass MOX recycle fuel cycle material flows.}
+\begin{center}
+\includegraphics{./images/flow-mod-open-1.eps}
+\end{center}
+\end{figure}
+
+To switch to a fully closed fuel cycle, all that needs to be done is change
+the output commodity for the \em{BatchReactor}'s spent MOX fuel.  All this
+requires is a single word change in the input file resulting in the material
+flows in Figure \ref{fig:flow-closed}.  Note that because the
+\em{BatchReactor} always transmutes fuel into the same composition, the
+nuclide level flows are not realistic for the full, multipass recycle case.
+
+\TODO{mention how fuel fab mixes fissile and filler streams}
+
+\begin{figure}
+\label{fig:flow-closed}
+\caption{Full MOX recycle (multi-pass) fuel cycle material flows.}
+\begin{center}
+\includegraphics{./images/flow-closed-1.eps}
+\end{center}
+\end{figure}
+
+\TODO{discuss Pu buildup charts}
+
+\begin{figure}
+\label{fig:puseries-1}
+\caption{bla}
+\begin{center}
+\includegraphics{./images/puseries-1.eps}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\label{fig:puseries-n}
+\caption{bla}
+\begin{center}
+\includegraphics{./images/puseries-n.eps}
+\end{center}
+\end{figure}

### 2014-09-26 fundamentals/examples.tex
fix italics formatting. make figs place where defined

@@
 
-Some simple examples of recycle scenarios in Cyclus follow.  In \Cyclus,
+Some simple examples of recycle scenarios in \Cyclus follow.  In \Cyclus,
 because material is tracked as discrete objects, single-pass mox recycle is
-easy to implement.  The \em{BatchReactor} archetype from \Cycamore has the
+easy to implement.  The \textit{BatchReactor} archetype from \Cycamore has the
 ability to accept fuel from multiple input sources with non-uniform
@@
 
-\begin{figure}
+\begin{figure}[!]
 \label{fig:flow-modopen}
@@
 To switch to a fully closed fuel cycle, all that needs to be done is change
-the output commodity for the \em{BatchReactor}'s spent MOX fuel.  All this
+the output commodity for the \textit{BatchReactor}'s spent MOX fuel.  All this
 requires is a single word change in the input file resulting in the material
 flows in Figure \ref{fig:flow-closed}.  Note that because the
-\em{BatchReactor} always transmutes fuel into the same composition, the
+\textit{BatchReactor} always transmutes fuel into the same composition, the
 nuclide level flows are not realistic for the full, multipass recycle case.
@@
 
-\begin{figure}
+\begin{figure}[!]
 \label{fig:flow-closed}
@@
 
-\begin{figure}
+\begin{figure}[!]
 \label{fig:puseries-1}
@@
 
-\begin{figure}
+\begin{figure}[!]
 \label{fig:puseries-n}

### 2014-10-08 fundamentals/impl.tex
added more details about materials and decay and info about arbitrary agent hierarchies

@@
 
-\subsection{Discrete Object Tracking}
+Although concept of the RIF hierarchy is provided, the \Cyclus kernel is
+really designed to handle hierarchies of arbitrary depth.  It is just as easy
+to run a simulation without regions and institutions (i.e.  only facilities)
+or a simulation having archetypes that are the parents' of regions.  By
+convention, institutions are mainly responsible for facility deployment, but
+any archetype can have access to \Cyclus' agent deployment mechanism.  It easy
+to implement agents that deploy copies of themselves, or that schedule their
+own decommissioning.  Because regions, institutions, and facilities are all
+just agents, they can all be implemented to excersize the full set of features
+offerred to by the \Cyclus kernel.
+
+\subsection{Resources and Materials}
 % Resources, Materials (note isotope tracking, decay behavior)
@@
 The parentage of each resource is also tracked. This makes it possible to
-follow the travel history of resource objects as they are transferred between
-agents.
+follow the travel history of discrete resource objects as they are transferred
+between agents.
+
+The \Cyclus kernel has built-in experimental support for decay calculations.
+Materials "remember" the time since their last decay and agents are free to
+invoke the decay function on them as desired to decay them to the current
+simulation time.  Cyclus can currently operate in 2 decay modes with 2 other
+modes likely to be added in future releases:
+
+\begin{itemize}
+
+    \item "manual" (currently implemented) is the default mode just described where agents decay
+        materials as needed.
+
+    \item "never" (currently implemented) globally turns off all decay.  Materials' decay function
+        does nothing.
+
+    \item "periodic" (future) automatically decays all materials in a
+        simulation with some fixed frequency.
+
+    \item "lazy" (future) decays any material whenever its composition is
+        viewed (e.g. an agent queries information about a material's
+        $^{239}Pu$ content).
+
+\end{itemize}
+
+\TODO{describe decay algorithm and how it might be improved}.
+
+\Cyclus has no notion of "tracked" nuclides.  In cyclus, a  material's
+composition represents an arbitrarily large list (potentially thousands) of
+nuclides.  Agents are free to treat nuclides present in materials any way they
+please - including ignoring them.  It is the responsibility of archetype
+developers to choose how to handle potentially full-fidelity compositions.
 

### 2014-10-08 fundamentals/impl.tex
describe decay shortcut

@@
 
-    \item "manual" (currently implemented) is the default mode just described where agents decay
-        materials as needed.
+    \item "manual" (currently implemented) is the default mode just described
+        where agents decay materials as needed.
 
-    \item "never" (currently implemented) globally turns off all decay.  Materials' decay function
-        does nothing.
+    \item "never" (currently implemented) globally turns off all decay.
+        Materials' decay function does nothing.
 
@@
     \item "lazy" (future) decays any material whenever its composition is
-        viewed (e.g. an agent queries information about a material's
+        viewed (e.g. when an agent queries information about a material's
         $^{239}Pu$ content).
@@
 
+In order to avoid excess decay calculations, when a material's decay function
+is invoked, the material checks to see if it contains any nuclides with decay
+constants that are significant with respect to the time delta for the current
+decay operation.  If all the decay constants are not significant, no decay
+calculation is performed and the material remains unchanged.  This error does
+not accumulate because the next time the material's decay function is invoked,
+the time delta will be larger. \TODO{want more detail on this decay shortcut?}
 \TODO{describe decay algorithm and how it might be improved}.

### 2014-10-08 fundamentals/impl.tex
remove a few therefores and be consisteng about plug-in vs plugin

@@
 
-Agent plug-ins utilize the generic core API to interact with one another. 
+Agent plugins utilize the generic core API to interact with one another. 
 Mainly they do this by trading resources.
@@
 simulators in the literature is implementing this generic API and modular 
-architecture into a suite of dynamically loadable ``plug-in'' libraries. 
+architecture into a suite of dynamically loadable ``plugin'' libraries.
 This is implemented largely through a clean API and a modern build system.
@@
 This approach provides encapsulation: the core of the code operates
-completely independently from the individual libraries. Thus, any
+completely independently from the individual plugin libraries. Thus, any
 customization or extension is implemented only in the loadable
@@
 This approach allows efficient, targeted contribution to the ecosystem of libraries.  The 
-scientist-developer can therefore focus on generating a model within their 
+scientist-developer can focus on generating a model within their
 sphere of expertise, while relying on the model contributions of others to fill 
@@
 
-In particular, since the clean plug-in architecture loads libraries without any
+In particular, since the clean plugin architecture loads libraries without any
 modifications to the \Cyclus kernel, closed-source archetypes can be used with
-the simulator alongside open-source archetypes. This architecture therefore
+the simulator alongside open-source archetypes. This architecture
 allows closed-source libraries (e.g., those representing sensitive nuclear
@@
 between agent implementations. For example, a low-physics-fidelity
-implementation of a reactor can be comparied to an implementation with higher
+implementation of a reactor can be compared to an implementation with higher
 physics fidelity, allowing an analyst to discern the effect of reactor physical

### 2014-10-08 fundamentals/examples.tex
add more recycle scenario details. Added in some xml snippets

--- 2014-09-25 fundamentals/examples.tex
@@
 
-Simulations have been run in the past and more are being run. FCO is an 
-example.
+\TODO{discuss FCO?}
+
+Results of some simple recycle scenarios run in \Cyclus follow.  In \Cyclus,
+because material is tracked as discrete objects, single-pass MOX recycle is
+easy to implement.  The simulation initially included one provider of fresh
+UOX fuel, one recycled fuel fabrication facility, one reactor, one separations
+facility, and one repository. The simulation duration was set to 1100 months.
+
+The \Class{BatchReactor} archetype from \Cycamore has the ability to accept
+fuel materials from an arbitrary number of different sources dilineated by
+commodity. Custom, non-uniform preferences can be set for each different fuel
+commodity.  The dynamic resource exchange makes it easy for a reactor to
+preferrentially accept recycled MOX fuel over fresh UOX fuel.  The
+\Class{BatchReactor} was configured to run with a 3 batch core on 18 month cycles and
+a 2-month refueling period.  Adjusting and setting parameters such as these is
+as simple as editing numbers in an input file such as:
+
+\begin{lstlisting}[language=xml]
+  ...
+  <BatchReactor>
+      ...
+      <processtime>18</processtime>
+      <nbatches>3</nbatches>
+      <batchsize>20000</batchsize>
+      <refueltime>2</refueltime>
+      ...
+  </BatchReactor>
+  ...
+\end{lstlisting}
+
+The \Class{Source} and \Class{Sink} modules from \Cycamore were also used as a
+source of fresh, enriched uranium and a repository respectively. A simple
+custom recycled fuel fabrication facility was used.  This fabrication facility
+mixes fissile and fertile streams to match target fuel compositions as closely
+as possible.  The method used for this matching is approximately the same as
+that used by the Cosi fuel cycle simulator \TODO{cite COSI equivalence
+method}. The material flows for this simulation are shown below in figure
+\ref{fig:flow-modopen}.
+
+\begin{figure}[!]
+\label{fig:flow-modopen}
+\caption{Modified open 1-pass MOX recycle fuel cycle material flows.}
+\begin{center}
+\includegraphics{./images/flow-mod-open-1.eps}
+\end{center}
+\end{figure}
+
+To switch to a fully closed fuel cycle, all that needs to be done is change
+the output commodity for the \Class{BatchReactor}'s spent MOX fuel.  All this
+requires is a one-word change in the input file:
+
+\begin{lstlisting}[language=diff]
+  --- mod-open-1.xml	2014-10-08 08:31:33.892523173 -0500
+  +++ closed-1.xml	2014-10-08 08:31:33.892523173 -0500
+  @@ -108,7 +108,7 @@
+           <fuel>         
+             <incommodity>mox_fuel</incommodity>
+             <inrecipe>lwr_mox_fuel</inrecipe>
+  -          <outcommodity>spent_mox</outcommodity>
+  +          <outcommodity>spent_fuel</outcommodity>
+             <outrecipe>mox_spent_fuel</outrecipe>
+           </fuel>
+\end{lstlisting}
+
+This results in new the material flows in Figure \ref{fig:flow-closed}. Note
+that because the \Class{BatchReactor} always transmutes fuel into the same
+composition, the nuclide level flows are not very realistic for the full, multipass
+recycle case.
+
+\begin{figure}[!]
+\label{fig:flow-closed}
+\caption{Full MOX recycle (multi-pass) fuel cycle material flows.}
+\begin{center}
+\includegraphics{./images/flow-closed-1.eps}
+\end{center}
+\end{figure}
+
+\TODO{discuss Pu buildup charts}
+
+\begin{figure}[!]
+\label{fig:puseries-1}
+\caption{bla}
+\begin{center}
+\includegraphics{./images/puseries-1.eps}
+\end{center}
+\end{figure}
+
+\begin{figure}[!]
+\label{fig:puseries-n}
+\caption{bla}
+\begin{center}
+\includegraphics{./images/puseries-n.eps}
+\end{center}
+\end{figure}

### 2014-10-08 fundamentals/impl.tex
todo note
add more recycle scenario details. Added in some xml snippets

@@
 own decommissioning.  Because regions, institutions, and facilities are all
-just agents, they can all be implemented to excersize the full set of features
-offerred to by the \Cyclus kernel.
+just agents, they can all be implemented to exercise the full set of features
+offered by the \Cyclus kernel.
 
@@
         viewed (e.g. when an agent queries information about a material's
-        $^{239}Pu$ content).
+        $^{239}$Pu content).
 
@@
 object is only recorded in the database once, significant space savings also
-occurs.
+occurs. \TODO{do we want a diagram helping show this composition caching?}
 

### 2014-10-08 fundamentals/examples.tex
discuss pu buildup data

@@
 method}. The material flows for this simulation are shown below in figure
-\ref{fig:flow-modopen}.
+\ref{fig:flowmodopen}.
 
-\begin{figure}[!]
-\label{fig:flow-modopen}
+\begin{figure}[H]
+\label{fig:flowmodopen}
 \caption{Modified open 1-pass MOX recycle fuel cycle material flows.}
@@
 
-This results in new the material flows in Figure \ref{fig:flow-closed}. Note
+This results in new the material flows in Figure \ref{fig:flowclosed}. Note
 that because the \Class{BatchReactor} always transmutes fuel into the same
@@
 
-\begin{figure}[!]
-\label{fig:flow-closed}
+\begin{figure}[H]
+\label{fig:flowclosed}
 \caption{Full MOX recycle (multi-pass) fuel cycle material flows.}
@@
 
-\TODO{discuss Pu buildup charts}
+Figure \ref{fig:puseries1} shows the full-system plutonium buildup for open
+(no recycle), modified open, and closed (infinite-pass recycle) variations of
+the scenario described above (all just a single reactor).  The figure was
+generated directly from \Cyclus output data. After several batch cycles (near
+month 300) in the modified open and closed cases, enough separated fissile
+material accumulates in the fuel fabrication facility to generate a full
+recycled batch.  When this batch is transmuted, more plutonium is burned than
+created.  This results in a drop in the total fuel cycle system plutonium
+inventory.  This pattern repeats roughly every 10 cycles (200 months) for the
+modified open case and every 9 cycles (180 months) for the closed case.
+Because the modified open scenario does not re-recycle material, it takes the
+fabrication facility 1 cycle longer to accumulate a full batch worth of
+fissile material.  Because facilities are represented individually and
+transact discrete materials as discrete events, realistic non-uniform patterns
+in facility behavior can be observed affecting total system behavior in ways
+that are less commonly observed in fleet-based, continuous material flow
+modeling.
 
-\begin{figure}[!]
-\label{fig:puseries-1}
-\caption{bla}
+\begin{figure}[H]
+\label{fig:puseries1}
+\caption{System plutonium buildup with one reactor.}
 \begin{center}
@@
 
-\begin{figure}[!]
-\label{fig:puseries-n}
-\caption{bla}
+The open, modified open, and closed scenarios can easily be modified to have
+several reactors each with staggered refueling times.  As the number of
+reactors increases, the behavior of the system approaches a more steady
+average reminiscent of continuous material flow models.  The plutonium buildup
+for these three multi-reactor variations is shown in Figure
+\ref{fig:puseriesn}.
+
+\begin{figure}[H]
+\label{fig:puseriesn}
+\caption{System plutonium buildup with staggered refueling for many reactors.}
 \begin{center}

### 2014-10-10 fundamentals/intro.tex
dynamically loadable libraries implementation section closely follows katy's dissertation discussion on this topic. Some slight paraphrasing was employed to avoid self-plaigarism
editing intro

@@
 
-In order to characterize performance metrics, nuclear fuel cycle analysis 
+In order to characterize the performance of nuclear fuel cycle tecnhologies and performance metrics, nuclear fuel cycle analysis 
 requires calculation and optimization of myriad physical, nuclear, chemical, 
@@
 and regions greatly improves upon the existing field of fuel cycle simulators.
+
+Associated with \Cyclus is Cycamore (the additional modules repository).
 

### 2014-10-13 fundamentals/intro.tex
improvements to intro

@@
 
-In order to characterize the performance of nuclear fuel cycle tecnhologies and performance metrics, nuclear fuel cycle analysis 
-requires calculation and optimization of myriad physical, nuclear, chemical, 
-industrial, and political phenomena. Furthermore, complex systems such as 
-nuclear process physics, facility deployment, and material routing each 
-must be modeled simultaneously for even the simplest of nuclear fuel cycle 
-simulations.
-
-% MJG - I'm hesitant about using the phrase 'full detail'. I think we can be
-% more precise.
+As nuclear power expands both domestically and internationally, nuclear fuel cycle
+performance on technical, economic, political, and environmental axes increases 
+in importance. In order to characterize the performance of nuclear fuel cycles, 
+nuclear fuel cycle analysis requires calculation of myriad physical, nuclear, 
+chemical, industrial, and political 
+phenomena. Coupled simulation of complex systems such as nuclear process physics, 
+facility deployment, and material routing
+for even the simplest of nuclear fuel cycle simulations.
 

### 2014-10-14 fundamentals/intro.tex
intro done

--- 2014-10-10 fundamentals/intro.tex
@@
 
-In order to characterize the performance of nuclear fuel cycle tecnhologies and performance metrics, nuclear fuel cycle analysis 
-requires calculation and optimization of myriad physical, nuclear, chemical, 
-industrial, and political phenomena. Furthermore, complex systems such as 
-nuclear process physics, facility deployment, and material routing each 
-must be modeled simultaneously for even the simplest of nuclear fuel cycle 
-simulations.
+As nuclear power expands both domestically and internationally, nuclear fuel cycle
+performance analysis on technical, economic, political, and environmental axes increases 
+in importance. Appropriate nuclear fuel cycle analysis requires calculation of myriad physical, nuclear, 
+chemical, industrial, and political phenomena. Nuclear fuel cycle simulators 
+therefore couple complex systems such as nuclear process physics, 
+facility deployment, and material routing. However, most nuclear fuel cycle 
+simulators have not incorporated modern insights in simulation science and 
+software architecture that can enable more efficient, accurate, robust, and 
+validated analysis. The Cyclus Nuclear Fuel Cycle Simulator Framework and 
+its modeling ecosystem answer the need for a next generation nuclear fuel cycle 
+simulator.
 
-% MJG - I'm hesitant about using the phrase 'full detail'. I think we can be
-% more precise.
+Historically, nuclear fuel cycle simulators have estimated 
+nuclear fuel cycle performance using software 
+ranging from ad hoc spreadsheet-driven flow calculators to highly specialized 
+proprietary models. To date, current tools are either static, fleet-based, 
+privately distributed, or all of the above. Each of these qualities present a 
+severe challenge to modeling fidelity, generality, effciiency, robustness, and 
+scientific transparency.
 
-Historically, nuclear fuel cycle simulators have addressed this with software 
-ranging from spreadsheet driven flow calculators to high-fidelity industrial 
-models. To date, current tools are either static, fleet-based, or 
-privately distributed. An alternative to these approaches is a dynamic, 
-agent-based simulator with an open platform.
-
-Modern insight indicates that dynamic nuclear fuel cycle analysis more 
-realistically supports a broader range of simulation goals than static analysis 
+An alternative to these approaches is a dynamic, agent-based simulator with an 
+open platform and an ecosystem of research-driven capabilities.  Modern 
+insight indicates that dynamic nuclear fuel cycle analysis more realistically 
+supports a broader range of simulation goals than static analysis 
 \cite{piet_dynamic_2011}. Similarly, experience in the greater field of systems 
 analysis indicates that agent-based modeling enables more flexible simulation 
-control, without loss of generality \cite{thatpapermattsent}. Finally, 
-openness allows cross-institutional collaboration, increases code robustness, 
-and enables the cultivation of an ecosystem of calculation options, 
-\cite{softwarecarpentryresource}.
-
-The fundamental concepts of the \Cyclus nuclear fuel cycle simulator capture 
-these modern insights so that challenges in nuclear fuel cycle analysis can be 
-better addressed.
+control, without loss of generality \cite{thatpapermattsent}. Finally, openness 
+allows cross-institutional collaboration, increases code robustness, and 
+enables the cultivation of an ecosystem of calculation options, 
+\cite{softwarecarpentryresource}.  The fundamental concepts of the \Cyclus 
+nuclear fuel cycle simulator capture these modern insights so that challenges 
+in nuclear fuel cycle analysis can be better addressed.
 

### 2014-10-15 fundamentals/intro.tex
more intro

@@
 software architecture that can enable more efficient, accurate, robust, and 
-validated analysis. The Cyclus Nuclear Fuel Cycle Simulator Framework and 
-its modeling ecosystem answer the need for a next generation nuclear fuel cycle 
-simulator.
+validated analysis.
+
+The \Cyclus Nuclear Fuel Cycle Simulator framework and 
+its modeling ecosystem answer this need for a next generation nuclear fuel cycle 
+simulator. Dynamic simulation of nuclear fuel cycles with discrete agents 
+and up to isotopic resolution support 
+levels of detail appropriate for a varied community of analysts
+interested in a range of analysis types. Additionally \Cyclus employs an 
+open development process that supports user access and 
+encourages developer extensions.
 
@@
 
-Simulators drive \gls{RDD} by calculating metrics that can be compared among fuel 
-cycles. Examples include measures of economic feasibility (i.e., \gls{LCOE}), 
-proliferation risk (i.e., total separated Pu), and environmental performance 
-(i.e., waste volume).
+Nuclear fuel cycle simulators can drive \gls{RDD} by calculating `metrics', 
+quantitative measures of performance that 
+can be compared among fuel cycle options. The feasibility of technology 
+strategies, dynamics of transitions between fuel cycles, and many other 
+measures of performance can be expressed in terms of these metrics. For example, 
+economic feasibility is often measured in \gls{LCOE} while proliferation risk 
+can be proportional to total kilograms of separated Pu, and environmental 
+performance might be measured in spent fuel volume, toxicity, or mined uranium.
 
 Methods for calculating those metrics vary among simulators. Some model the 
-fuel cycle at static equillibrium, while others capture fuel cycle dynamics.  
-Similarly, while some simulators discretely model material and and facilities, 
-others track streams of materials and fleets of facilities in an aggregated 
+system of facilities, economics, and materials at static equillibrium, while 
+others capture its dynamics.  
+Similarly, while some simulators discretely model material and facilities, 
+others treat materials in streams and facilities in fleets, in an aggregated 
 fashion. Depending on their intended use, simulators often overspecialize, 
-modeling a single aspect of the fuel cycle in great detail. For this reason, 
-some simulators specialize in economics, material isotopics, or transmutation 
-detail, where others do not.
+modeling a single aspect of the fuel cycle in great detail while neglecting 
+others. A simulator created for policy modeling might have excellent 
+capability in economics while material isotopics and transmutation detail are 
+neglected.
 
@@
 \gls{DYMOND}\cite{modeling_yacout_2005}, and 
-\gls{NFCSim}\cite{schneider_nfcsim:_2005}, while universities and industry have 
-simultaneously developed tools of their own as well, such as 
-\gls{CAFCA}\cite{guerin_benchmark_2006} and \gls{COSI}\cite{cosi}.
+\gls{NFCSim}\cite{schneider_nfcsim:_2005}. With limited access to those tools, 
+universities and industry have simultaneously developed tools of their own, 
+such as \gls{CAFCA}\cite{guerin_benchmark_2006} and \gls{COSI}\cite{cosi}.
 

### 2014-10-15 fundamentals/intro.tex
background edits

@@
 
-Methods for calculating those metrics vary among simulators. Some model the 
+Historically, researchers create new nuclear fuel cycle simulation tools when 
+existing tools are not available or not sufficiently general to calculate their 
+metrics of interest with their method of choice.
+
+Historically, the national laboratories have driven development and regulated 
+the use of their own tools such as \gls{VISION}\cite{jacobson_verifiable_2010}, 
+\gls{DANESS}\cite{van_den_durpel_daness_2009}, 
+\gls{DYMOND}\cite{modeling_yacout_2005}, and 
+\gls{NFCSim}\cite{schneider_nfcsim:_2005}. With limited access to those tools 
+and a need to customize them for research purposes, 
+universities and private industry researchers ``reinvent the wheel'' by 
+developing tools of their own from scratch and tailored to their own needs (e.g., 
+\gls{CAFCA}\cite{guerin_benchmark_2006} and \gls{COSI}\cite{cosi} 
+respectively).
+
+This cycle has resulted in a a proliferation of specialized, limited-access 
+fuel cycle simulators for the calculation of fuel cycle metrics, and methods 
+for calculating those metrics vary among simulators. Some model the 
 system of facilities, economics, and materials at static equillibrium, while 
@@
 
-Historically, the national laboratories have driven development and regulated 
-the use of their own tools such as \gls{VISION}\cite{jacobson_verifiable_2010}, 
-\gls{DANESS}\cite{van_den_durpel_daness_2009}, 
-\gls{DYMOND}\cite{modeling_yacout_2005}, and 
-\gls{NFCSim}\cite{schneider_nfcsim:_2005}. With limited access to those tools, 
-universities and industry have simultaneously developed tools of their own, 
-such as \gls{CAFCA}\cite{guerin_benchmark_2006} and \gls{COSI}\cite{cosi}.
-
-The \Cyclus simulator arose out of the 
-\gls{GENIUSv2}\cite{oliver_studying_2009,huff_geniusv2_2009} code. That software 
-itself was the result of lessons-learned from an \gls{LDRD} project at 
+When the \Cyclus simulator arose out of the 
+\gls{GENIUSv2}\cite{oliver_studying_2009,huff_geniusv2_2009} code
+was the result of lessons-learned from an \gls{LDRD} project at 
 \gls{INL}, 

### 2014-10-15 fundamentals/intro.tex
improved discussion of background

@@
 
-This cycle has resulted in a a proliferation of specialized, limited-access 
-fuel cycle simulators for the calculation of fuel cycle metrics, and methods 
+This cycle has resulted in a a proliferation of specialized
+fuel cycle simulators for the calculation of fuel cycle metrics.  Accordingly, methods 
 for calculating those metrics vary among simulators. Some model the 
@@
 
-When the \Cyclus simulator arose out of the 
-\gls{GENIUSv2}\cite{oliver_studying_2009,huff_geniusv2_2009} code
-was the result of lessons-learned from an \gls{LDRD} project at 
-\gls{INL}, 
-\gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006} which 
-captured regional behaviors in fuel cycle scenarios.
+Accordingly, the \gls{GENIUSv2}\cite{oliver_studying_2009,huff_geniusv2_2009} code
+was created to provide and extensible interface to facilitate collaboration. 
+The \gls{GENIUSv2} project relied on lessons-learned from an \gls{LDRD} project 
+at \gls{INL}, 
+\gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006}.
 
-\Cyclus is a dynamic simulator that treats both materials and facilities discretely, with an 
-architecture that permits simulations with multiple and variable levels of 
-fidelity. Its agent-based framework for simulation and tracking of 
-transformation and trade of resources between facilities within institutions 
-and regions greatly improves upon the existing field of fuel cycle simulators.
-
-Associated with \Cyclus is Cycamore (the additional modules repository).
+The \Cyclus project, in turn, improved upon the \gls{GENIUSv2} project by 
+implementing increased modularity and encapsulation.
+The result is  a dynamic simulator that treats both materials and facilities 
+discretely, with an architecture that permits simulations with multiple and 
+variable levels of fidelity. Its agent-based framework for simulation and 
+tracking of transformation and trade of resources between facilities within 
+institutions and regions greatly improves upon the existing field of fuel cycle 
+simulators.
 

### 2014-10-16 fundamentals/intro.tex
spellcheck

@@
 privately distributed, or all of the above. Each of these qualities present a 
-severe challenge to modeling fidelity, generality, effciiency, robustness, and 
+severe challenge to modeling fidelity, generality, efficiency, robustness, and 
 scientific transparency.
@@
 
-% Common goals of fuel cycle simulation/simulators (driving r&d focus,
+% Common goals of fuel cycle simulation/simulators (driving &d focus,
 % approximating tech. impacts, etc.)
@@
 
-This cycle has resulted in a a proliferation of specialized
+This cycle has resulted in a proliferation of specialized
 fuel cycle simulators for the calculation of fuel cycle metrics.  Accordingly, methods 
 for calculating those metrics vary among simulators. Some model the 
-system of facilities, economics, and materials at static equillibrium, while 
+system of facilities, economics, and materials at static equilibrium, while 
 others capture its dynamics.  
@@
 In addition to providing the fundamental features expected in fuel cycle 
-simulators, the \Cyclus paradigm enables major capabilites that previous 
+simulators, the \Cyclus paradigm enables major capabilities that previous 
 simulators lack. First, its \emph{modular and open architecture}  facilitates 
 targeted contribution and collaboration within the nuclear fuel cycle analysis 
-community.  Additionally, \emph{agent interchangability} facilitates direct 
+community.  Additionally, \emph{agent interchangeability} facilitates direct 
 comparison of modeling methodologies. Finally, the flexibility and generality 
 of its \emph{\gls{ABM}} paradigm and \emph{discrete, object-oriented approach} 
-emphasizes applicability of the \Cyclus tool accross a broader range of 
+emphasizes applicability of the \Cyclus tool across a broader range of 
 applications than other simulators.
@@
 Modeling the evolution of a physics-dependent, international nuclear fuel supply
-chain is a difficult problem. To date, it has been treated relatively
-lightly. Tools have either focused on macro effects, e.g., the fleet-level
+chain is a multiscale problem. Tools have either focused on macro effects, e.g., the fleet-level
 stocks and flows of commodities, or micro effects, e.g., the used fuel
@@
 to define nuclear fuel cycle facility processes independent of the simulation 
-logic. This design choice acheives two things. First, analysts across 
+logic. This design choice achieves two things. First, analysts across 
 institutions can take advantage of the simulation logic \gls{API} and 
@@
 composition for fast reactors. A variety fuel fabrication archetypes can be 
-developed and used interchangably to analyze the effect of each on a 
+developed and used interchangeably to analyze the effect of each on a 
 simulation's output.
@@
 
-This generality specifically permits the use cases that cannot be acheived with 
+This generality specifically permits the use cases that cannot be achieved with 
 fleet-based models. That is, some questions require resolution at the level of 
@@
 target facility and the individual materials modified within it and is only 
-acheivable with discretely-modeled objects like those in the \Cyclus simulator.
+achievable with discretely-modeled objects like those in the \Cyclus simulator.

### 2014-10-16 fundamentals/intro.tex
cleaning up

@@
 simulators, the \Cyclus paradigm enables major capabilities that previous 
-simulators lack. First, its \emph{modular and open architecture}  facilitates 
+simulators lack. First, its its \emph{modular and open architecture}  facilitates 
 targeted contribution and collaboration within the nuclear fuel cycle analysis 
@@
 emphasizes applicability of the \Cyclus tool across a broader range of 
-applications than other simulators.
-
-Modeling the evolution of a physics-dependent, international nuclear fuel supply
-chain is a multiscale problem. Tools have either focused on macro effects, e.g., the fleet-level
-stocks and flows of commodities, or micro effects, e.g., the used fuel
-composition fast reactor fuel. Accordingly, each focus has driven the
-development of these tools, rendering the task of answering questions between
-the macro and micro levels either impossible or difficult and time consuming.
+fidelities, scales, and applications than other simulators.
 
@@
 fuel fabrication), rather than also modeling the entirety of the cycle.
+
+Furthermore, modeling the evolution of a physics-dependent, international nuclear fuel supply
+chain is a multiscale problem, but existing tools are not sufficiently 
+multi-scale. Tools have either focused on macro effects, e.g., the fleet-level
+stocks and flows of commodities, or micro effects, e.g., the used fuel
+composition fast reactor fuel. Accordingly, each focus has driven the
+development of these tools, rendering the task of answering questions between
+the macro and micro levels either impossible or difficult and time consuming. 
+However, an extensible architecture and discrete object tracking allow 
+the creation and exchange ability of custom \Cyclus archetypes at any level of fidelity.
 
@@
 We expect that there are a number of types of users and developers who will 
-interact with the \Cyclus framework. Those people fall into a number of 
+interact with the \Cyclus framework. National laboratory researchers,
+graduate student and faculty researchers  Those people fall into a number of 
 categories. All such people benefit from the modular architecture.

### 2014-10-17 fundamentals/intro.tex
motivation

@@
 development of these tools, rendering the task of answering questions between
-the macro and micro levels either impossible or difficult and time consuming. 
+the macro and micro levels challenging within a single tool. 
 However, an extensible architecture and discrete object tracking allow 
@@
 
-The encapsulated plug-in architecture within the \Cyclus tool allows developers 
-to define nuclear fuel cycle facility processes independent of the simulation 
-logic. This design choice achieves two things. First, analysts across 
-institutions can take advantage of the simulation logic \gls{API} and 
-archetype ecosystem when they apply \Cyclus to their specific problem. The effort they 
-undertake can thereby be focused on creating or customizing 
+The architecture within the \Cyclus tool allows developers 
+to define nuclear fuel cycle agents and processes independent of the simulation 
+logic. This `encapsulated,' `plug-in'
+design choice achieves two things. First, analysts across 
+research institutions can take advantage of the simulation logic \gls{API} and 
+archetype ecosystem when they apply \Cyclus to their specific problem. This 
+extensibility, magnified by an open source development process, frees the 
+community of users to contribute desired features independen from the team of 
+\Cyclus core developers. This mend-and-extend 
+paradigm, common in modern software development, reduces maintenance overhead 
+and improves code robustness \cite{citation_needed}. Finally, the researcher 
+can therefore focus on creating or customizing 
 nuclear facility, institution, resource, and toolkit models within their 
-specific area of expertise.
+specific area of technical expertise.
 
@@
 interact with the \Cyclus framework. National laboratory researchers,
-graduate student and faculty researchers  Those people fall into a number of 
-categories. All such people benefit from the modular architecture.
+academic researchers, private-industry economic forcasters, and even students. 
+in engineering courses will benefit from the ease of development and ease of 
+customization provided by the modular architecture of \Cyclus.
 
@@
 context for example, an analyst can design an agent with reactor-related logic 
-and a separate agent with fuel fabrication-related logic.
+and a separate agent with fuel fabrication-related logic. In the \Cyclus 
+agent-based context, defining the behavior of both agents according to the 
+\gls{API} contract is sufficient for them to interact with one another as 
+bonafide actors in the simulation. The two archetype libraries, therefore, need 
+not have any shared knowledge of one another for them to be building blocks in 
+the same simulation.
 
@@
 material diversion. This type of analysis requires discrete simulation of a 
-target facility and the individual materials modified within it and is only 
-achievable with discretely-modeled objects like those in the \Cyclus simulator.
+target facility and the individual materials modified within it. 
+Provenance and trade-history of distinct materials is the fundamental 
+information unit in such studies. 
+Material risk analysis, therefore, demands discretely modeled objects like those 
+in the \Cyclus simulator.

### 2014-10-18 fundamentals/intro.tex
cleanup

@@
 logic. This `encapsulated,' `plug-in'
-design choice achieves two things. First, analysts across 
-research institutions can take advantage of the simulation logic \gls{API} and 
-archetype ecosystem when they apply \Cyclus to their specific problem. This 
-extensibility, magnified by an open source development process, frees the 
-community of users to contribute desired features independen from the team of 
-\Cyclus core developers. This mend-and-extend 
-paradigm, common in modern software development, reduces maintenance overhead 
-and improves code robustness \cite{citation_needed}. Finally, the researcher 
-can therefore focus on creating or customizing 
-nuclear facility, institution, resource, and toolkit models within their 
-specific area of technical expertise.
+design choice achieves two things.
+
+First, analysts across research institutions can take advantage of the 
+simulation logic \gls{API} and archetype ecosystem when they apply \Cyclus to 
+their specific problem. This extensibility, magnified by an open source 
+development process, frees the community of users to contribute desired 
+features independen from the team of \Cyclus core developers. This 
+mend-and-extend paradigm, common in modern software development, reduces 
+maintenance overhead and improves code robustness \cite{citation_needed}. 
+Finally, the researcher can therefore focus on creating or customizing nuclear 
+facility, institution, resource, and toolkit models within their specific area 
+of technical expertise.
 
@@
 context for example, an analyst can design an agent with reactor-related logic 
-and a separate agent with fuel fabrication-related logic. In the \Cyclus 
-agent-based context, defining the behavior of both agents according to the 
+and a separate agent with fuel fabrication-related logic. 
+ Defining the behavior of both agents according to the 
 \gls{API} contract is sufficient for them to interact with one another as 
@@
 
-System dynamics popular approach for modeling nuclear fuel cycles in current
-tools \cite{VISION,CAFCA}. It has been shown in the literature
-\cite{macal_agent-based_2010} that any system dynamics model can be translated
-into an agent-based model. Furthermore, it has been shown that agent-based
-techniques can provide a richer model than can system dynamics. Formally, the
+System dynamics is a popular approach for modeling nuclear fuel cycles in current
+tools \cite{VISION,CAFCA}. However, it has been shown in systems analysis literature
+\cite{macal_agent-based_2010} that, formally, the
 set of system dynamics models is a strict subset of agent-based models.
+That is, any system dynamics model can be translated
+into an agent-based model. Furthermore, agent-based
+techniques can provide a richer model than can system dynamics. To enable the 
+broadest range of simulations in a generic fashion, \gls{ABM} is therefore 
+superior to system dynamics.
 
@@
 
-This generality specifically permits the use cases that cannot be achieved with 
+This generality specifically permits many use cases that cannot be achieved with 
 fleet-based models. That is, some questions require resolution at the level of 

### 2014-10-18 fundamentals/impl.tex
no

@@
 The core of the simulator creates a set of key classes on which agent plugins 
-are based. In addtion, a set of key tools are also provided, to enrich the API 
+are based. In addtion, a set of key tools are also provided to enrich the API 
 and provide a robust suite of behaviors for the developer.
@@
 
-Agent plugins utilize the generic core API to interact with one another. 
-Mainly they do this by trading resources.
+Agent plugins utilize the generic core API to interact with one another.  For 
+example, agents rely on the dynamic loading and paradigm for clean plugin 
+behavior at the start of the simulation. They also use the resource exchange 
+paradigm \gls{API} for trading resources with one another.
 

### 2014-10-18 fundamentals/impl.tex
cleaning up implementation, adding content

@@
 
-A modular, agent-based is an ideal approach for solving complicated
+A modular, agent-based is an ideal approach for solving complex, coupled,
 physics-dependent supply chain problems involving material routing, facility
-deployment, regional and institutional hierarchies.
+deployment, regional and institutional hierarchies. Additionally, the choice to 
+build \Cyclus on open source libraries in modern programming languages enables 
+both remote and mutiprocess execution on a number of platforms.
+
+\subsection{Cluster-Ready Software}
+
+Many fuel cycle simulators rely on \gls{COTS} and Windows-only software that limits 
+performance on resource computing infrastructures. This limitation severely 
+increases the wall-clock time necessary to conduct parameterized sensitivity 
+analyses and other multi-simulation studies.
+
+\Cyclus, on the other hand, is primarily written in \texttt{C++} and relies on 
+libraries supported by Linux and UNIX (including Ubuntu and OSX) platforms. 
+Furthermore, the core infrastructure and related archetypes are free and 
+open-source, BSD-3-clause licsened. No part of \Cyclus is proprietary or based 
+on \gls{COTS}, Windows-based software. Accordingly, it can be easily deployed 
+on large compute systems, such as high-throughput computing (HTC) systems.
+
+Cyclopts (\TODO{cite}), a proof of principle design and implementation of such a
+system, uses UW-Madison's HTCondor HTC infrastructure to perform sensitivity
+studies on \Cyclus' resource exchange optimization solvers. To date, it has been
+used run over $10^4$ jobs, or (\TODO{compute time}) total compute hours, using
+the \Cyclus library via its resource exchange API.
 
@@
 
-\subsection{Cluster-Ready Software}
-
-\Cyclus is primarily written in \texttt{C++}, and support is currently provided
-for Linux-based (including Ubuntu and OSX) platforms. Furthermore, the core
-infrastructure and related archetypes are free and open-source, BSD-3-clause
-licsened. No part of \Cyclus is proprietary or based on commercial, off the
-shelf (COTS) software. Accordingly, it can be easily deployed on large compute
-systems, such as high-throughput computing (HTC) systems.
-
-Cyclopts (\TODO{cite}), a proof of principle design and implementation of such a
-system, uses UW-Madison's HTCondor HTC infrastructure to perform sensitivity
-studies on \Cyclus' resource exchange optimization solvers. To date, it has been
-used run over $10^4$ jobs, or (\TODO{compute time}) total compute hours, using
-the \Cyclus library via its resource exchange API.
-
 \subsection{Dynamically Loadable Libraries}
@@
 
-A key innovation that has previously not been implemented in nuclear fuel cycle 
-simulators in the literature is implementing this generic API and modular 
-architecture into a suite of dynamically loadable ``plugin'' libraries.
-This is implemented largely through a clean API and a modern build system.
+A key innovation in \Cyclus is implementing this generic API and modular 
+architecture into a suite of dynamically loadable ``plugin'' libraries.  Though 
+common in modern software architecture, such a ``plugin'' pattern has 
+previously not been implemented in nuclear fuel cycle simulators in the 
+literature.  In \Cyclus, this is made possible primarily by the clean, 
+object-oriented \gls{API} and modern build system already described.
 
@@
 
-This approach allows efficient, targeted contribution to the ecosystem of libraries.  The 
-scientist-developer can focus on generating a model within their
-sphere of expertise, while relying on the model contributions of others to fill 
-in the other technologies.  This strategy also allows individual developers to
+This approach encourages efficient, targeted contribution to the ecosystem of 
+archetype libraries.  The 
+scientist-developer can focus on generating an archetype model within their
+sphere of expertise, while relying on the contributions of others to fill 
+in the other technologies in the simulation.  This strategy also allows individual developers to
 explore different levels of complexity within their archetypes, including
@@
 questions as well as users focused on more detailed, technical
-analyses.
+analyses. They merely choose their preferred level of fidelity from amongst 
+available libraries.
 
@@
 
-A key compontent of the \Cyclus kernel architecture is the ability for
-implementations of actors in a given simulation to be easily
+Due to this ``plugin'' architecture
+implementations of actors in a given simulation can be easily
 interchanged. Critically, this novel functionality enables the comparison
@@
 
-\Cyclus provides a novel representation of entities in the nuclear fuel cycle,
+\Cyclus provides a novel representation of entities in the nuclear fuel cycle 
+which mimics the reality in international nuclear power production
 including facilities, institutions managing those facilities, and regions. While
@@
 
-The basic interaction models for each entity is implemented by a corresponding
+The fundamental interactions for each entity are implemented in a corresponding
 archetype class in \Cyclus, i.e., the \Class{Region} class, \Class{Institution}
 class, and \Class{Facility} class. Archetype developers can then build on the
-provided functionality by subclassing the appropriate class.
+provided functionality by inheriting from the appropriate class.
 
-\Cyclus implements a Region-Institution-Facility (RIF) relationship through the
+\Cyclus implements a \gls{RIF} relationship through the
 parent-child hierarchy described in \S \ref{sec:interchangeability}, where
@@
 follow the travel history of discrete resource objects as they are transferred
-between agents.
+between agents and powerfully impacts the ability to model 
+non-proliferation-related simulation goals.
 
 The \Cyclus kernel has built-in experimental support for decay calculations.
-Materials "remember" the time since their last decay and agents are free to
+Materials ``remember'' the time since their last decay and agents are free to
 invoke the decay function on them as desired to decay them to the current
@@
 
-In large simulations there may be many material objects changing frequently.
+In large simulations there may be many material objects changing frequently, on 
+the day or month timescale.
 Material decay can also contribute significantly to such changes.  In order to

### 2014-10-18 fundamentals/intro.tex
cleaning up implementation, adding content

@@
 context for example, an analyst can design an agent with reactor-related logic 
-and a separate agent with fuel fabrication-related logic. 
- Defining the behavior of both agents according to the 
+entirely independently from a separate agent with fuel fabrication-related 
+logic. Defining the behavior of both agents according to the 
 \gls{API} contract is sufficient for them to interact with one another as 

### 2014-10-20 fundamentals/examples.tex
no
erasing out of date comments
filling in examples intro.

@@
 
-The archetypes created by user-developers and the archetypes provided in the 
-\Cycamore \cite{carlsen_cycamore_2014} repository of additional modules 
-together form an `ecosystem' of capabilities. Since the long term vision for 
-the \Cyclus framework includes an ever-expanding ecosystem of both general and 
-specialized capability extensions within that ecosytem. The early growth and 
-cross-institutional contributions to this ecosystem demonstrates a significant 
-acheivement by the \Cyclus framework.
+The \Cyclus `Ecosystem' is the collection of tools, calculation libraries, 
+archetypes, data, and input files intended for use with the \Cyclus simulator. 
+Members of the ecosystem include:
+\begin{itemize}
+\item the archetypes provided in the \Cycamore \cite{carlsen_cycamore_2014} 
+repository of additional modules,
+\item the archetypes created by user-developers,
+\item isotopic composition data,
+\item historical facility deployment data,
+\item the \Cyclus \gls{GUI} tools, Cycic and Cyclist,
+\item and the tools in the \Cyclus toolkit.
+\end{itemize}
+All together, these form an `ecosystem' of capabilities. Over time, this 
+ecosystem will grow as archetype-developers, kernel-developers, and 
+even users contribute capabilities developed for their own needs. Indeed, the 
+long-term vision for the \Cyclus framework predicts an ever-expanding ecosystem 
+of both general and specialized capability extensions within that ecosytem.
+
+Already, the ecosystem is growing. Early cross-institutional contributions to 
+the ecosystem demonstrate a significant acheivement by the \Cyclus framework 
+and provide hope for a community-driven development model.
 
@@
 \subsection{Simulations}
-%FCO example (will be done soon.. publishable?)
 %Inpro example (is this still running or did we deprecate it with 1.0?)
@@
 % facility parameters and run it again.
-
-\TODO{discuss FCO?}
 

### 2014-10-20 fundamentals/impl.tex
filling in examples intro.

@@
 
-In Cyclus, agents can transfer discrete resource objects between each other.
+In \Cyclus, agents can transfer discrete resource objects between each other.
 Cyclus supports two types of resources:
@@
 invoke the decay function on them as desired to decay them to the current
-simulation time.  Cyclus can currently operate in 2 decay modes with 2 other
+simulation time. \Cyclus can currently operate in 2 decay modes with 2 other
 modes likely to be added in future releases:
@@
 help avoid unnecessary runtime performance and database space impacts,
-compositions in Cyclus have some special features.  Compositions in Cyclus are
+compositions in \Cyclus have some special features.  Compositions in \Cyclus are
 immutable.  This immutability allows multiple material objects to all hold
@@
 
-Cycamore contains a number of useful facility models that are a mere base-set.
-Additional modules are needed for interesting fuel cycle simulation. However,
-simple, once-through fuel cycles can be generated with Cycamore and Cyclus alone.
+\Cycamore \cite{carlsen_cycamore_2014} contains a number of useful facility, 
+region, and institution archetypes. 
+As future contributions are vetted, the capabilities in \Cycamore may grow. 
+However, the current \Cycamore release provides only 
+basic functionality, enabling simple fuel cycle analyses. 
+\Cycamore is provided so that users can get started quickly with simple 
+analyses.
 
+Figure \ref{fig:cyc_sim} shows an example of a simple, once-through fuel cycle 
+that can be generated with \Cycamore and \Cyclus alone.
+
+\begin{figure}[htbp!]
+\begin{center}
 <diagram of a possible Cycamore-only simulation>
+\end{center}
+\caption{A simple once-through fuel cycle possible with only \Cycamore and 
+\Cyclus.}
+\label{fig:<+label+>}
+\end{figure}<++>

### 2014-10-21 fundamentals/intro.tex
breaking the cycle with cyclus

@@
 
-Historically, researchers create new nuclear fuel cycle simulation tools when 
-existing tools are not available or not sufficiently general to calculate their 
-metrics of interest with their method of choice.
-
 Historically, the national laboratories have driven development and regulated 
@@
 \gls{DYMOND}\cite{modeling_yacout_2005}, and 
-\gls{NFCSim}\cite{schneider_nfcsim:_2005}. With limited access to those tools 
-and a need to customize them for research purposes, 
-universities and private industry researchers ``reinvent the wheel'' by 
-developing tools of their own from scratch and tailored to their own needs (e.g., 
-\gls{CAFCA}\cite{guerin_benchmark_2006} and \gls{COSI}\cite{cosi} 
-respectively).
+\gls{NFCSim}\cite{schneider_nfcsim:_2005}. 
+Outside of the national laboratories, researchers create new nuclear fuel cycle 
+simulation tools when existing tools are not available or not sufficiently 
+general to calculate their metrics of interest with their method of choice.  
+With limited access to the national laboratory tools and a need to customize 
+them for research purposes, universities and private industry researchers 
+``reinvent the wheel'' by developing tools of their own from scratch and 
+tailored to their own needs (e.g., \gls{CAFCA}\cite{guerin_benchmark_2006} and 
+\gls{COSI}\cite{cosi} respectively).
 
@@
 
-Accordingly, the \gls{GENIUSv2}\cite{oliver_studying_2009,huff_geniusv2_2009} code
-was created to provide and extensible interface to facilitate collaboration. 
-The \gls{GENIUSv2} project relied on lessons-learned from an \gls{LDRD} project 
-at \gls{INL}, 
-\gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006}.
-
-The \Cyclus project, in turn, improved upon the \gls{GENIUSv2} project by 
-implementing increased modularity and encapsulation.
-The result is  a dynamic simulator that treats both materials and facilities 
-discretely, with an architecture that permits simulations with multiple and 
-variable levels of fidelity. Its agent-based framework for simulation and 
-tracking of transformation and trade of resources between facilities within 
-institutions and regions greatly improves upon the existing field of fuel cycle 
-simulators.
+The \Cyclus simulator emerged from a line of tools seeking to break that cycle.  
+An \gls{LDRD} project begun at \gls{INL}, 
+\gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006} sought 
+to provide generic regional capability.  Based on lessons learned from 
+\gls{GENIUSv1}, the 
+\gls{GENIUSv2}\cite{oliver_studying_2009,huff_geniusv2_2009} code sought to 
+provide more generality and an extensible interface to facilitate 
+collaboration.  The \Cyclus project, in turn, improved upon the \gls{GENIUSv2} 
+project by implementing increased modularity and encapsulation.  The result is  
+a dynamic simulator that treats both materials and facilities discretely, with 
+an architecture that permits simulations with multiple and variable levels of 
+fidelity. Its agent-based framework for simulation and tracking of 
+transformation and trade of resources between facilities within institutions 
+and regions greatly improves upon the existing field of fuel cycle simulators.
 

### 2014-10-21 fundamentals/impl.tex
adds inheritance diagrams

@@
 on \gls{COTS}, Windows-based software. Accordingly, it can be easily deployed 
-on large compute systems, such as high-throughput computing (HTC) systems.
+on large compute systems, such as \acrlong{HTC} systems.
 
@@
 used run over $10^4$ jobs, or (\TODO{compute time}) total compute hours, using
-the \Cyclus library via its resource exchange API.
+the \Cyclus library via its resource exchange \gls{API}.
 
@@
 
-Agent-based modeling is inherently object oriented.
+Agent-based modeling is inherently object oriented. Since agents are
 
@@
 previously not been implemented in nuclear fuel cycle simulators in the 
-literature.  In \Cyclus, this is made possible primarily by the clean, 
+literature.  In \Cyclus, this implementation maximizes the potential of the clean, 
 object-oriented \gls{API} and modern build system already described.
@@
 interaction and agent-to-environment interaction, primarily through the
-\Class{Agent} and \Class{Trader} interfaces. The \Class{Agent} interface
+\Class{Agent} and \Class{Trader} interfaces. Figure \ref{fig:agent_uml} shows 
+the ``inheritance'' structure of the \Class{Agent} class in a \gls{UML} diagram 
+format. It shows how the \Class{Agent} interface
 provides a notion of parent-child hierarchichal relationship, where parents can
 choose to \textit{build} child agents and \textit{decommission} child
-agents. The \Class{Trader} interface allows agent-agent interaction through the
+agents. For the archetype developer, this interface provides enormous power, 
+very simply. The \gls{API} exposes \Class{Agent} helpful functionality for 
+interacting with the \Cyclus simulation kernel while abstracting away unnecessary 
+detail.
+
+\begin{figure}[htbp!]
+\begin{center}
+\includegraphics{agent_uml}
+\end{center}
+\caption{The inheritance structure in the \Class{Agent} class abstracts away 
+unneccesary details while exposing powerful functionality.}
+\label{fig:agent_uml}
+\end{figure}
+
+In a similar fasion, the \Class{Trader} interface allows agent-agent interaction through the
 trading of \Class{Resource}s. Usabe archetypes in a \Cyclus simulation must
@@
 objects regarding physical parameters. First the \Class{MatQuery} module
-provides a basic querying API, including the atom and mass fractions of
+provides a basic querying \gls{API}, including the atom and mass fractions of
 nuclides, the number of moles of a nuclide in a material, and also the amount of
 aggregate nuclides, i.e., a \Class{Composition}, in a material. The
-\Class{enrichment} module provides an API for determining enrichment-related
+\Class{enrichment} module provides an \gls{API} for determining enrichment-related
 parameters of a material, including the separative work units (SWU) and natural

### 2014-10-22 fundamentals/impl.tex
adds diagram

@@
 
-Agent-based modeling is inherently object oriented. Since agents are
+\acrlong{ABM} is inherently object-oriented. Since agents represent 
+discrete, independently acting objects, object-orientation is the natural 
+paradigm in which to conduct \gls{ABM}.
 
-The core of the simulator creates a set of key classes on which agent plugins 
-are based. In addtion, a set of key tools are also provided to enrich the API 
-and provide a robust suite of behaviors for the developer.
+The core of the \Cyclus simulator creates a set of key classes on which agent plugins 
+are based. In addtion, a set of key tools are also provided to enrich the 
+\gls{API} and provide a robust suite of behaviors for the developer.
 
-<diagram of core, modules, toolkit, etc>
+\begin{figure}[htbp!]
+\begin{center}
+\includegraphics[width=\textwidth]{./images/framework}
+\end{center}
+\caption{The \Cyclus core provides \gls{API}s that abstract away the details in 
+the kernel and allow the archetypes to be loaded into the simulation in a modular 
+fashion.}
+\label{fig:framework}
+\end{figure}
 
-Agent plugins utilize the generic core API to interact with one another.  For 
+Agent plugins utilize the generic core \gls{API} to interact with one another.  For 
 example, agents rely on the dynamic loading and paradigm for clean plugin 
@@
 
-<diagram of black box facilities>
-
 \subsection{Dynamically Loadable Libraries}
@@
 
-A key innovation in \Cyclus is implementing this generic API and modular 
+A key innovation in \Cyclus is implementing this generic \gls{API} and modular 
 architecture into a suite of dynamically loadable ``plugin'' libraries.  Though 
@@
 
-Interchangability is accomplished by providing APIs that define agent-to-agent
+Interchangability is accomplished by providing \glspl{API} that define agent-to-agent
 interaction and agent-to-environment interaction, primarily through the
@@
 \begin{center}
-\includegraphics{agent_uml}
+\includegraphics[width=0.5\textwidth]{./images/agent_uml}
 \end{center}
-\caption{The inheritance structure in the \Class{Agent} class abstracts away 
-unneccesary details while exposing powerful functionality.}
+\caption{The inheritance in \Cyclus classes, such as the \Class{Agent}, 
+\Class{Facility}, \Class{Institution}, and \Class{Region} classes abstract away 
+unneccesary details while exposing powerful functionality. In the above 
+example, the \Class{Dummy} archetype simply inherits from \Class{Region} in 
+order to become a bonified Region-type \Class{Agent}.}
 \label{fig:agent_uml}
@@
 trade with another \Class{Facility}.
+
+In this way, a researcher can directly compare two different reactor modeling 
+implementations (perhaps \Class{DetailedReactor} and \Class{SimpleReactor} 
+simply by exchanging the two corresponding archetypes. That is, two reactor 
+archetypes, inheriting from the \Class{Facility} class, are indistinguishable 
+from a simulation perspective. Two simulations, one using 
+\Class{DetailedReactor} and the other using \Class{SimpleReactor} can therefore 
+be compared directly to determine the impact of using one or the other model.
+This can be done with any agent type, where agents can be ``Regions,'' 
+``Institutions,'' or ``Facilities.''
 
@@
 regions are the parents of institutions which are, in turn, the parents of
-facilities. In other words, RIF hierarchies form a directed acyclic graph (DAG),
+facilities. In other words, \gls{RIF} hierarchies form a directed acyclic graph (DAG),
 with regions as root nodes and facilities as leaf nodes.
@@
 
-Although concept of the RIF hierarchy is provided, the \Cyclus kernel is
+Although concept of the \gls{RIF} hierarchy is provided, the \Cyclus kernel is
 really designed to handle hierarchies of arbitrary depth.  It is just as easy
@@
 
-TODO: add blurb about discrete agent/facility tracking.
+\TODO{add blurb about discrete agent/facility tracking.}
 
@@
 
+\subsubsection{Toolkit Extensions}
+
+In addition to those that already exist, tools and computational patterns will 
+emerge from the archetypes that are developed within the community of 
+developers. As those tools gain adoption between projects and demonstrate their 
+utility to the developer community, they will be considered for screening and 
+adoption into the kernel as toolkit extensions. Likely extensions include:
+
+\begin{itemize}
+\item fuel cycle metrics calculators
+\item supportive data tables
+\item policy models
+\item economic models
+\item etc.
+\end{itemize}
+
 \subsection{Cycamore}
@@
 \Cyclus.}
-\label{fig:<+label+>}
-\end{figure}<++>
+\label{fig:simplesim}
+\end{figure}

### 2014-10-22 fundamentals/examples.tex
moves cyamore bit to the other cycamore bit

@@
-\section{Examples}
+\section{Demonstration}
 % Organize this section according to major topics
@@
 
+The early success of the \Cyclus simulator can be measured in many ways. 
+The most compelling are demonstrations of the feasibility of the \Cyclus community-driven development 
+model and of fundamental simulation capability. Nascent, promising growth of the \Cyclus 
+ecosystem at multiple institutions indicates that a fuel cycle simulator can be 
+improved by
+
 \subsection{Ecosystem}
@@
 and provide hope for a community-driven development model.
-
-\subsubsection{The Cyclus Additional Modules Repository}
-
-\Cycamore, the \Cyclus additional modules repository, provides a fundamental 
-set of agent archetypes for basic simulation functionality within \Cyclus.
-Since the \Cyclus framework relies on external archetypes to represent the 
-agents within a simulation, 
-\Cycamore provides the basic archetypes a new user needs to get started running 
-simple simulations. 
-These archetypes support a minimal set of fuel cycle simulation goals and 
-provide, by example, a guide to new developers who would seek to contribute 
-their own archetypes outside of \Cycamore.
 

### 2014-10-22 fundamentals/examples.tex
better tables

@@
 model and of fundamental simulation capability. Nascent, promising growth of the \Cyclus 
-ecosystem at multiple institutions indicates that a fuel cycle simulator can be 
-improved by
+ecosystem at multiple institutions indicates that a fuel cycle simulator can 
+advance in a community-drive development paradigm. Additionally, simple 
+simulations as well as more complex recycling simulations demonstrate that 
+\Cyclus posesses fundamental fuel cycle simulation capabilities.
 
@@
 \item the \Cyclus \gls{GUI} tools, Cycic and Cyclist,
-\item and the tools in the \Cyclus toolkit.
+\item the tools in the \Cyclus toolkit
+\item and other tools for \Cyclus optimization, parallelization, and development.
 \end{itemize}
@@
 
-\subsubsection{External Modules}
-External modules have been 
-\cite{cyder,separations,streamblender,mktdriveninst,commodconverter} and are 
-being \cite{britelite,utk} developed for contribution to the cyclus ecosystem 
-of models.
+\subsubsection{Supplementary Projects}
+
+A number of projects and tools outside of the core simulation kernel have been 
+developed which improve the scope and the diversity of the capabilities in the \Cyclus 
+ecosystem. Table \ref{tab:coretools} lists the tools and projects developed 
+under close integration with the \Cyclus kernel.
+\begin{table}
+\centering
+\begin{tabularx}{\textwidth}{|r|X|r|}
+\hline
+\textbf{Name} & \textbf{Description} & \textbf{Citation} \\
+\hline
+Cycic &  Input control - embedded in Cyclist & \cite{cycic}\\
+Cyclist & Interactive data exploration environment & \cite{cyclist} \\
+Ciclus & Continuous Integration scripts for \Cyclus & \cite{ciclus}\\
+Cycstub & Skeleton for clean slate module development & \cite{cycstub}\\
+Cyan & \Cyclus analysis tool & \cite{cyan}\\
+Cloudlus & Tools for running \Cyclus in a cloud environment & \cite{cloudlus} \\
+\hline
+\end{tabularx}
+\caption{Many tools outside of the scope of the \Cyclus kernel have been 
+developed for improved user, developer, and analyst experinces with \Cyclus.}
+\label{tab:coretools}
+\end{table}
+
+\subsubsection{Archetype Contributions}
+
+Many archetypes external to the \Cycamore library  
+have been \cite{huff_cyder_2013,,streamblender,commodconverter} 
+and are being \cite{britelite,utk,mktdriveninst} developed for contribution to the 
+\Cyclus ecosystem. These archetypes provide the first examples of 
+developer-contributed capabilities.
+
+\begin{table}
+\centering
+\begin{tabularx}{\textwidth}{|r|X|r|}
+\hline
+\textbf{Name} & \textbf{Description} & \textbf{Citation} \\
+\hline
+Brite-lite & A physics-based reactor archetype and fuel fabrication archetype & \cite{brightlite} \\
+Nuclear Fuel Inventory Model & A flexible, ORIGEN-based, reactor analysis module & \cite{NFIM} \\
+CommodConverter & A simple commodity converting storage facility archetype  & \cite{commodconverter} \\
+MktDrivenInst & An institution that controls deployment based on commodity availability & \cite{mktdriveninst} \\
+SeparationsMatrix & A facility for elemental separations of used fuel & \cite{streamblender} \\
+StreamBlender & A facility for fuel fabrication from reprocessed streams & \cite{streamblender} \\
+\hline
+\end{tabularx}
+\caption{A diverse set of archetypes under development reflect the diverse 
+needs of researchers at various institutions. These archetypes, contributed 
+outside of the \Cyclus core and \Cycamore libraries are the first demonstration 
+of community-driven development in a fuel cycle simulator.}
+\label{tab:archetypes}
+\end{table}
 

### 2014-10-22 fundamentals/impl.tex
better tables

--- 2014-10-20 fundamentals/impl.tex
@@
 
-\Cycamore \cite{carlsen_cycamore_2014} contains a number of useful facility, 
-region, and institution archetypes. 
+\Cycamore \cite{carlsen_cycamore_2014}, the \Cyclus additional modules 
+repository, provides a fundamental set of agent archetypes for basic simulation 
+functionality within \Cyclus.  Since the \Cyclus framework relies on external 
+archetypes to represent the agents within a simulation, \Cycamore provides the 
+basic archetypes a new user needs to get started running simple simulations.  
+These archetypes support a minimal set of fuel cycle simulation goals and 
+provide, by example, a guide to new developers who would seek to contribute 
+their own archetypes outside of \Cycamore.
+
+As of version 1.0, \Cycamore contains four facility archetypes, one region 
+archetype, and two institution archetypes. Short descriptions of those 
+functions can be found in Table \ref{tab:cycamore}.
+
+\begin{table}
+\centering
+\begin{tabularx}{\textwidth}{|r|l|l|}
+\hline
+\textbf{Agent Type} & \textbf{Archetype} & \textbf{Functionality} \\
+\hline
+Facility & BatchReactor & A reactor model that handles batch refuelling, based on pre-determined recipes of compositions. \\
+Facility & Source & This facility generates material of the composition and commodity type specified as input.  \\
+Facility & Sink & This facility is capable of accepting a finite or infinite quantity of some commodity produced in the simulation \\
+Facility & EnrichmentFacility & This facility enriches uranium at a specified capacity. \\
+Institution& ManagerInst & The manager institution manages production of commodiites among its facilities by building new necessary ones \\
+Institution & DeployInst &  This institution deploys specific facilities as defined explicitly in the input file. \\
+Region & GrowthRegion & This region determines whether there is a need to meet a certain capacity (as defined via input) at each time step \\
+\hline
+\end{tabularx}
+\caption{The Archetypes in \Cycamore seek to cover a large range of simple simulation use cases.}
+\label{tab:cycamore}
+\end{table}
+
 As future contributions are vetted, the capabilities in \Cycamore may grow. 
@@
 \begin{center}
-<diagram of a possible Cycamore-only simulation>
+\includegraphics{./images/simplesim}
 \end{center}
-\caption{A simple once-through fuel cycle possible with only \Cycamore and 
-\Cyclus.}
-\label{fig:<+label+>}
+\caption{Material flows through a simple dynamic simulation created with only the simplest \Cycamore archetypes, \Class{Sink} and \Class{Source}.}
+\label{fig:simplesim}
 \end{figure}<++>

### 2014-10-22 fundamentals/impl.tex

--- 2014-10-22 fundamentals/impl.tex
@@
 \begin{center}
-<diagram of a possible Cycamore-only simulation>
+\includegraphics{./images/simplesim}
 \end{center}
-\caption{A simple once-through fuel cycle possible with only \Cycamore and 
-\Cyclus.}
+\caption{Material flows through a simple dynamic simulation created with only the simplest \Cycamore archetypes, \Class{Sink} and \Class{Source}.}
 \label{fig:simplesim}

### 2014-10-22 fundamentals/conclusion.tex
adds concluision

\section{Conclusions}
% summarize the conclusions of the paper as a list of short phrases or
% sentences. Do not repeat the results section unless special emphasis is
% needed. The conclusion is just that, not a summary. It should add a new,
% higher level of analysis and should explicitly indicate the significance of
% the work.
% What does it all mean?
% What hypotheses were proven or disproven?
% What was learned?
% Why does it make a difference?

%Modularity encourages ecosystem development
%Enables cross-institutional collaboration
%Open paradigm allows community oversight, testing, verification
%Enables apples to apples comparisons

The \Cyclus nuclear fuel cycle framework presents a more generic and flexible 
alternative to existing fuel cycles simulators.

Where, previous nuclear fuel cycle simulators have had limited distribution, 
uncertain provenance, and restricted customizability, \Cyclus emphasizes an 
open access and development strategy.  Open development, with transparent 
publication of the source code, not only provides much-needed accessibility, 
but also enables transparency and community oversight.

The object-oriented \arclong{ABM} simulation paradigm ensures more generic 
simulation capability. It allows \Cyclus to address common analyses in a more 
flexible fashion and enables analyses that are impossible with system dynamics 
codes.

Similarly, discrete, fidelity-agnostic object tracking facilitates simulations 
at every level of detail. Simulations relying on arbitrarily complex isotopic 
compositions are possible in \Cyclus, as are  toy simulations not employing any 
physics at all. Indeed, agents of such varying fidelity can even exist in the 
same simulation. Researchers no longer need to reinvent the wheel in order to 
model a simulation focused on the aspects of the fuel cycle that their research 
focuses on.

Furthermore, when the capabilities within \Cyclus, \Cycamore, and the rest of 
the ecosystem are insufficient, adding custom functionality is simplified by a 
modular, plug-in architcture. A clean, modern \acrlong{API} simplifies 
customization and independent archetype development so that researchers can 
create models within their domain of expertise without modifying the core 
simulation kernel. Throughout the \Cyclus 
infrastructure, architecture choices have sought to enable cross-institutional 
collaboration and sustainable, community-driven development. The ecosystem 
of capabilities, already growing, may someday reflect the full diversity of use 
cases in the nuclear fuel cycle simulation domain.

### 2014-10-22 fundamentals/examples.tex
tables where I put them
reduces the chaos in the bibliographies to just one file of chaos

@@
 under close integration with the \Cyclus kernel.
-\begin{table}
+\begin{table}[h]
 \centering
@@
 \hline
-Cycic &  Input control - embedded in Cyclist & \cite{cycic}\\
-Cyclist & Interactive data exploration environment & \cite{cyclist} \\
-Ciclus & Continuous Integration scripts for \Cyclus & \cite{ciclus}\\
-Cycstub & Skeleton for clean slate module development & \cite{cycstub}\\
-Cyan & \Cyclus analysis tool & \cite{cyan}\\
-Cloudlus & Tools for running \Cyclus in a cloud environment & \cite{cloudlus} \\
+Cycic &  Input control - embedded in Cyclist & \cite{flanagan_input_2013}\\
+Cyclist & Interactive data exploration environment & \cite{livnat_cyclist_2014} \\
+Ciclus & Continuous Integration scripts for \Cyclus & \cite{scopatz_ciclus_2014}\\
+Cycstub & Skeleton for clean slate module development & \cite{carlsen_cycstub_2014}\\
+Cyan & \Cyclus analysis tool & \cite{carlsen_cyan_2014}\\
+Cloudlus & Tools for running \Cyclus in a cloud environment & \cite{carlsen_cloudlus_2014} \\
 \hline
@@
 Many archetypes external to the \Cycamore library  
-have been \cite{huff_cyder_2013,,streamblender,commodconverter} 
-and are being \cite{britelite,utk,mktdriveninst} developed for contribution to the 
+have been 
+\cite{huff_streamblender_2014,huff_commodconverter_2014}
+and are being 
+\cite{flanagan_bright-lite_2014,skutnik_nuclear_2014,huff_mktdriveninst_2014} developed for contribution to the 
 \Cyclus ecosystem. These archetypes provide the first examples of 
@@
 
-\begin{table}
+\begin{table}[h]
 \centering
@@
 \hline
-Brite-lite & A physics-based reactor archetype and fuel fabrication archetype & \cite{brightlite} \\
-Nuclear Fuel Inventory Model & A flexible, ORIGEN-based, reactor analysis module & \cite{NFIM} \\
-CommodConverter & A simple commodity converting storage facility archetype  & \cite{commodconverter} \\
-MktDrivenInst & An institution that controls deployment based on commodity availability & \cite{mktdriveninst} \\
-SeparationsMatrix & A facility for elemental separations of used fuel & \cite{streamblender} \\
-StreamBlender & A facility for fuel fabrication from reprocessed streams & \cite{streamblender} \\
+Brite-lite & A physics-based reactor archetype and fuel fabrication archetype & \cite{flanagan_bright-lite_2014} \\
+Nuclear Fuel Inventory Model & A flexible, ORIGEN-based, reactor analysis module & \cite{skutnik_nuclear_2014} \\
+CommodConverter & A simple commodity converting storage facility archetype  & \cite{huff_commodconverter_2014} \\
+MktDrivenInst & An institution that controls deployment based on commodity availability & \cite{huff_mktdriveninst_2014} \\
+SeparationsMatrix & A facility for elemental separations of used fuel & \cite{huff_streamblender_2014} \\
+StreamBlender & A facility for fuel fabrication from reprocessed streams & \cite{huff_streamblender_2014} \\
 \hline

### 2014-10-22 fundamentals/intro.tex
reduces the chaos in the bibliographies to just one file of chaos

@@
 analysis indicates that agent-based modeling enables more flexible simulation 
-control, without loss of generality \cite{thatpapermattsent}. Finally, openness 
+control, without loss of generality \cite{macal_agent-based_2010}. Finally, openness 
 allows cross-institutional collaboration, increases code robustness, and 
@@
 \gls{DANESS}\cite{van_den_durpel_daness_2009}, 
-\gls{DYMOND}\cite{modeling_yacout_2005}, and 
+\gls{DYMOND}\cite{yacout_modeling_2005}, and 
 \gls{NFCSim}\cite{schneider_nfcsim:_2005}. 
@@
 ``reinvent the wheel'' by developing tools of their own from scratch and 
-tailored to their own needs (e.g., \gls{CAFCA}\cite{guerin_benchmark_2006} and 
-\gls{COSI}\cite{cosi} respectively).
+tailored to their own needs (e.g., \gls{CAFCA}\cite{guerin_impact_2009} and 
+\gls{COSI}\cite{boucher_cosi_2005,boucher_cosi:_2006,meyer_new_2009,coquelet-pascal_comparison_2011} respectively).
 
@@
 System dynamics is a popular approach for modeling nuclear fuel cycles in current
-tools \cite{VISION,CAFCA}. However, it has been shown in systems analysis literature
+tools 
+\cite{jacobson_vision_2009,van_den_durpel_daness_2009,guerin_impact_2009,guerin_benchmark_2009}. However, it has been shown in systems analysis literature
 \cite{macal_agent-based_2010} that, formally, the

### 2014-10-22 fundamentals/qa.tex
reduces the chaos in the bibliographies to just one file of chaos

@@
 answers come out?' ... I am not able rightly to apprehend the kind of confusion 
-of ideas that could provoke such a question.'' \cite{babbage2011passages}. 
+of ideas that could provoke such a question.'' \cite{babbage_passages_2011}. 
 The \emph{garbage in, garbage out} phenomenon is not the only scenario which a
@@
 on the part of simulators themselves. These include \emph{verification and validation}
-(V\&V) \cite{boehm1989software}, \emph{uncertainty quantification} (UQ) 
-\cite{sacks1989design}, testing, and others. V\&V and UQ come from 
+(V\&V) \cite{boehm_software_1989}, \emph{uncertainty quantification} (UQ) 
+\cite{sacks_design_1989}, testing, and others. V\&V and UQ come from 
 a distinctly computational science background while testing \emph{et al.} come from 
@@
 Nuclear enginerering code quality is often governed by NQA-1, an ASME specification 
-whose latest revision appeared in 2009 \cite{NQA-1a-2009}. This is primarily 
+whose latest revision appeared in 2009 \cite{asme_nqa-1a-2009_2009}. This is primarily 
 used for designing reactors. However, it is general enough to apply to 
-cyclus. Cyclus has adopted an \emph{agile} development process \cite{larman2004agile}, 
-interpreting NQA-1 in a manner similar to NEAMS \cite{neams-qa} or PyNE \cite{pyne-vv}.
+cyclus. Cyclus has adopted an \emph{agile} development process 
+\cite{larman_agile_2004}, 
+interpreting NQA-1 in a manner similar to NEAMS \cite{neams_nuclear_2013} or 
+PyNE \cite{biondo_quality_2014}.
 
@@
 
-Cyclus uses the Google Test framework \cite{gtest} as a harness for running unit 
+Cyclus uses the Google Test framework \cite{inc_googletest_2008} as a harness for running unit 
 tests. Sufficient unit tests are required for any proposed change to the cyclus
@@
 time. Precanned input files have thus been contsructed. Their results 
-are inspected and compared via nose \cite{nosetests}, a Python test framework.
+are inspected and compared via nose \cite{pellerin_nose_2007}, a Python test framework.
 Python will run cyclus as a subprocess for each integration test. In this
@@
 stream.  In cyclus, this information is aggregated together into static 
-websites with the doxygen \cite{van2008doxygen} and sphinx \cite{brandl2014sphinx} 
+websites with the doxygen \cite{van_heesch_doxygen:_2008} and sphinx 
+\cite{brandl_sphinx_2014} 
 tools. These websites are placed online at \url{http://fuelcycle.org}.
@@
 Version control is the history-preserving mechanism by which the provenance of 
-a code is recored. Cyclus uses a well-established tool called git \cite{git_2014}
+a code is recored. Cyclus uses a well-established tool called git 
+\cite{software_freedom_conservancy_git_2014}
 for this purpose. Git is currently the most popular utilty in the recent wave
@@
 
-Cyclus uses a strategy known as \emph{git flow} \cite{kalliamvakou2014code} 
+Cyclus uses a strategy known as \emph{git flow} 
+\cite{kalliamvakou_code-centric_2014} 
 to manage topical branches where individuals develop code, the mainline development
@@
 The act of proposing a change is known as a \emph{pull request}. The main cyclus is 
-hosted remotely on the GitHub website \cite{dabbish2012social}. The online
+hosted remotely on the GitHub website \cite{dabbish_social_2012}. The online
 mechanism for pull requests allows for code review by a member of the cyclus 
@@
 such as the Chicago Manual of Style. Cyclus strictly enforces the use of the 
-Google C++ Style Guide \cite{weinberger2008google} for all software contributions.
+Google C++ Style Guide \cite{weinberger_google_2008} for all software contributions.
 This means that all developers of cyclus nominally write cyclus code in the same 
@@
 it is proposed. Such tests shoudl be run on all officially supported platforms. 
-Cyclus uses a CI platform called Polyphemus \cite{polyphemus_2014}.
+Cyclus uses a CI platform called Polyphemus \cite{scopatz_polyphemus_2014}.
 
@@
 and temporary cyclus servers on the backend. These servers are hosted by 
-the Build \& Test Laboratory (BaTLab) \cite{batlab_2014} at the University of 
+the Build \& Test Laboratory (BaTLab) \cite{uw_batlab_team_batlab_2014} at the University of 
 Wisconsin-Madison. Whenever a pull request is created, Polyphemus performs 

### 2014-10-28 fundamentals/impl.tex
tables where I put them
reduces the chaos in the bibliographies to just one file of chaos
note about robert's htc usage

@@
 the \Cyclus library via its resource exchange \gls{API}.
+The HTC infrastructure has also been utilized to run and collect
+information from full \Cyclus simulations running in parallel on $10^3$
+machines reliably for order $10^5$ simulations.
 
@@
 \caption{The \Cyclus framework enables fully open, partially open, and fully
-closed collaborations\cite{wilson_cyclus:_2012}.}
+closed collaborations\cite{carlsen_cyclus_2014}.}
 \label{fig:modifiedopen}
@@
 
-\begin{table}
+\begin{table}[h]
 \centering
-\begin{tabularx}{\textwidth}{|r|l|l|}
+\begin{tabularx}{\textwidth}{|r|l|X|}
 \hline

### 2014-10-30 fundamentals/intro.tex
minor revisions to I

@@
 levels of detail appropriate for a varied community of analysts
-interested in a range of analysis types. Additionally \Cyclus employs an 
+interested in a range of analysis types. Additionally, \Cyclus employs an 
 open development process that supports user access and 
@@
 allows cross-institutional collaboration, increases code robustness, and 
-enables the cultivation of an ecosystem of calculation options, 
+enables the cultivation of an ecosystem of calculation options 
 \cite{softwarecarpentryresource}.  The fundamental concepts of the \Cyclus 
@@
 tailored to their own needs (e.g., \gls{CAFCA}\cite{guerin_impact_2009} and 
-\gls{COSI}\cite{boucher_cosi_2005,boucher_cosi:_2006,meyer_new_2009,coquelet-pascal_comparison_2011} respectively).
+\gls{COSI}\cite{boucher_cosi_2005,boucher_cosi:_2006,meyer_new_2009,coquelet-pascal_comparison_2011}, respectively).
 
-This cycle has resulted in a proliferation of specialized
+This trend has resulted in a proliferation of specialized
 fuel cycle simulators for the calculation of fuel cycle metrics.  Accordingly, methods 
@@
 modeling a single aspect of the fuel cycle in great detail while neglecting 
-others. A simulator created for policy modeling might have excellent 
+others. For example, a simulator created for policy modeling might have excellent 
 capability in economics while material isotopics and transmutation detail are 
@@
 
-The \Cyclus simulator emerged from a line of tools seeking to break that cycle.  
-An \gls{LDRD} project begun at \gls{INL}, 
+The \Cyclus simulator emerged from a line of tools seeking to break this practice.  
+A \gls{LDRD} project that began at \gls{INL}, 
 \gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006} sought 
@@
 an architecture that permits simulations with multiple and variable levels of 
-fidelity. Its agent-based framework for simulation and tracking of 
+fidelity. The simulator's agent-based framework for tracking of 
 transformation and trade of resources between facilities within institutions 
-and regions greatly improves upon the existing field of fuel cycle simulators.
+and regions greatly improves upon the existing fuel cycle simulators.
 
@@
 simulators, the \Cyclus paradigm enables major capabilities that previous 
-simulators lack. First, its its \emph{modular and open architecture}  facilitates 
+simulators lack. First, its \emph{modular and open architecture}  facilitates 
 targeted contribution and collaboration within the nuclear fuel cycle analysis 
@@
 chain is a multiscale problem, but existing tools are not sufficiently 
-multi-scale. Tools have either focused on macro effects, e.g., the fleet-level
+multiscale. Tools have either focused on macro effects, e.g., the fleet-level
 stocks and flows of commodities, or micro effects, e.g., the used fuel
-composition fast reactor fuel. Accordingly, each focus has driven the
+composition of fast reactor fuel. Each focus has driven the
 development of these tools, rendering the task of answering questions between
@@
 However, an extensible architecture and discrete object tracking allow 
-the creation and exchange ability of custom \Cyclus archetypes at any level of fidelity.
+the creation and exchangeability of custom \Cyclus archetypes at any level of fidelity.
 
@@
 logic. This `encapsulated,' `plug-in'
-design choice achieves two things.
+design choice provides two major benefits.
 
@@
 development process, frees the community of users to contribute desired 
-features independen from the team of \Cyclus core developers. This 
+features, independent from the team of \Cyclus core developers. This 
 mend-and-extend paradigm, common in modern software development, reduces 
 maintenance overhead and improves code robustness \cite{citation_needed}. 
-Finally, the researcher can therefore focus on creating or customizing nuclear 
+The researcher can therefore focus on creating or customizing nuclear 
 facility, institution, resource, and toolkit models within their specific area 
@@
 archetypes is straightforward. Consider a case in which an analyst would like 
-to compare the effect of using different models to determining input fuel 
-composition for fast reactors. A variety fuel fabrication archetypes can be 
-developed and used interchangeably to analyze the effect of each on a 
-simulation's output.
+to compare the effect of using different models to determine the input fuel 
+composition for fast reactors. A variety of fuel fabrication archetypes can be 
+developed and interchanged to analyze the effect of each on the 
+simulation output.
 
-We expect that there are a number of types of users and developers who will 
+There are a number of types of users and developers who will 
 interact with the \Cyclus framework. National laboratory researchers,
-academic researchers, private-industry economic forcasters, and even students. 
-in engineering courses will benefit from the ease of development and ease of 
+academic researchers, private-industry economic forcasters, and even students 
+in engineering courses may benefit from the ease of development and
 customization provided by the modular architecture of \Cyclus.
@@
 \Cyclus utilizes an \gls{ABM} paradigm.  \gls{ABM} is modern, sophisticated, 
-true to reality, and it takes advantage of modern computing resources.  
-Furthermore, agent-based modeling provides an analyst a more natural 
+true to reality, and takes advantage of modern computing resources.  
+Furthermore, \gls{ABM} provides an analyst a more natural 
 perspective from which to model a given problem. In the nuclear fuel cycle 
 context for example, an analyst can design an agent with reactor-related logic 
-entirely independently from a separate agent with fuel fabrication-related 
+entirely independent from a separate agent with fuel fabrication-related 
 logic. Defining the behavior of both agents according to the 
@@
 fleet-based models. That is, some questions require resolution at the level of 
-individual facilities and individual materials.  Since fleet-based, 
+individual facilities and materials.  Since fleet-based, 
 lumped-material models do not distinguish between discrete facility entities or 
-discrete materials, many detailed performance metrics cannot be captured with 
+materials, many detailed performance metrics cannot be captured with 
 those tools.

### 2014-10-30 fundamentals/impl.tex
minor revisions for II

@@
 
-A modular, agent-based is an ideal approach for solving complex, coupled,
+A modular, agent-based simulator is an ideal approach for solving complex, coupled,
 physics-dependent supply chain problems involving material routing, facility
-deployment, regional and institutional hierarchies. Additionally, the choice to 
+deployment, and regional and institutional hierarchies. Additionally, the choice to 
 build \Cyclus on open source libraries in modern programming languages enables 
@@
 open-source, BSD-3-clause licsened. No part of \Cyclus is proprietary or based 
-on \gls{COTS}, Windows-based software. Accordingly, it can be easily deployed 
-on large compute systems, such as \acrlong{HTC} systems.
+on \gls{COTS}, Windows-based software. It can be easily deployed 
+on large computer systems, such as \acrlong{HTC} systems.
 
@@
 studies on \Cyclus' resource exchange optimization solvers. To date, it has been
-used run over $10^4$ jobs, or (\TODO{compute time}) total compute hours, using
+used run over $10^4$ jobs, or (\TODO{compute time}) total computer hours, using
 the \Cyclus library via its resource exchange \gls{API}.
@@
 The core of the \Cyclus simulator creates a set of key classes on which agent plugins 
-are based. In addtion, a set of key tools are also provided to enrich the 
-\gls{API} and provide a robust suite of behaviors for the developer.
+are based. In addition, a set of key tools are also provided to enrich the 
+\gls{API} and supply a robust suite of behaviors for the developer.
 
@@
 
-Dynamically-loadable libraries are the primary mechanism for extending \Cyclus' capability. 
+Dynamically loadable libraries are the primary mechanism for extending \Cyclus' capability. 
 This approach provides encapsulation: the core of the code operates
@@
 scientist-developer can focus on generating an archetype model within their
-sphere of expertise, while relying on the contributions of others to fill 
-in the other technologies in the simulation.  This strategy also allows individual developers to
+sphere of expertise, while relying on the contributions of others to furnish
+the other technologies in the simulation.  This strategy also allows individual developers to
 explore different levels of complexity within their archetypes, including
@@
 
-This last benefit of dynamically-loadable libraries addresses
+This last benefit of dynamically loadable libraries addresses
 another goal of \Cyclus: ubiquity amongst its potential user base. By
@@
 questions as well as users focused on more detailed, technical
-analyses. They merely choose their preferred level of fidelity from amongst 
+analyses. They merely choose their preferred level of fidelity from the 
 available libraries.
@@
 
-Due to this ``plugin'' architecture
+Due to this ``plugin'' architecture,
 implementations of actors in a given simulation can be easily
@@
 
-In a similar fasion, the \Class{Trader} interface allows agent-agent interaction through the
-trading of \Class{Resource}s. Usabe archetypes in a \Cyclus simulation must
+In a similar fashion, the \Class{Trader} interface allows agent-to-agent interaction through the
+trading of \Class{Resource}s. Usable archetypes in a \Cyclus simulation must
 implement the \Class{Agent} interface and may optionally implement the
@@
 In this way, a researcher can directly compare two different reactor modeling 
-implementations (perhaps \Class{DetailedReactor} and \Class{SimpleReactor} 
+implementations (perhaps \Class{DetailedReactor} and \Class{SimpleReactor}) 
 simply by exchanging the two corresponding archetypes. That is, two reactor 
-archetypes, inheriting from the \Class{Facility} class, are indistinguishable 
+archetypes both inheriting from the \Class{Facility} class are indistinguishable 
 from a simulation perspective. Two simulations, one using 
@@
 Two primary consequences arise from this structure. First, institutions are
-responsible for building and decommissioning facilities. Accordingly, advanced
+responsible for building and decommissioning facilities, so advanced
 logic regarding building and decommissioning can be obtained by subclassing the
-\Class{Institution} interface. Second, the \Class{Facility} class implmenets the
-\Class{Trader} interface, and thus institutions and regions, respectively, can
-adjust the resource flow preferences of their managed facilities. Importantly,
+\Class{Institution} interface. Second, the \Class{Facility} class implemenets the
+\Class{Trader} interface, and thus institutions and regions, can
+adjust the resource flow preferences of their managed facilities, respectively. Importantly,
 this novel capability allows for the modeling of preferential regional trading
@@
 Although concept of the \gls{RIF} hierarchy is provided, the \Cyclus kernel is
-really designed to handle hierarchies of arbitrary depth.  It is just as easy
-to run a simulation without regions and institutions (i.e.  only facilities)
-or a simulation having archetypes that are the parents' of regions.  By
+designed to handle hierarchies of arbitrary depth.
+A simulation can proceed without regions and institutions (i.e.,  only facilities)
+or with archetypes that are the parents of regions.  By
 convention, institutions are mainly responsible for facility deployment, but
-any archetype can have access to \Cyclus' agent deployment mechanism.  It easy
-to implement agents that deploy copies of themselves, or that schedule their
+any archetype can have access to \Cyclus' agent deployment mechanism.  It straightforward
+to implement agents that deploy copies of themselves or schedule their
 own decommissioning.  Because regions, institutions, and facilities are all
-just agents, they can all be implemented to exercise the full set of features
+agents, they can all be implemented to exercise the full set of features
 offered by the \Cyclus kernel.
@@
 
-  \item Products: These can represent any user-defined thing - e.g. carbon
+  \item Products: These can represent any user-defined measure - e.g. carbon
       credits, build permits, employees, etc.
@@
 
-All operations performed on every resource object (splitting, combining,
+All operations performed on resource objects (splitting, combining,
 decay, etc.) are tracked in detail.  This information includes the creating
@@
 The parentage of each resource is also tracked. This makes it possible to
-follow the travel history of discrete resource objects as they are transferred
-between agents and powerfully impacts the ability to model 
+follow the history of discrete resource objects as they are transferred
+between agents, powerfully impacting the ability to model 
 non-proliferation-related simulation goals.
@@
 In order to avoid excess decay calculations, when a material's decay function
-is invoked, the material checks to see if it contains any nuclides with decay
-constants that are significant with respect to the time delta for the current
+is invoked, the material compares the decay constants of its nuclides with
+the time delta for the current
 decay operation.  If all the decay constants are not significant, no decay
@@
 
-\Cyclus has no notion of "tracked" nuclides.  In cyclus, a  material's
+\Cyclus has no notion of "tracked" nuclides.  In \Cyclus, a  material's
 composition represents an arbitrarily large list (potentially thousands) of
@@
 help avoid unnecessary runtime performance and database space impacts,
-compositions in \Cyclus have some special features.  Compositions in \Cyclus are
-immutable.  This immutability allows multiple material objects to all hold
+compositions in \Cyclus have some special features, such as immutability.
+Immutable compositions allow multiple material objects to all hold
 references to the same composition object safely.  When operations are
-performed on a material that don't change the composition, any new resulting
+performed on a material that do not alter the composition, any new resulting
 materials hold a reference to the same, originating composition object.
@@
 immutability), a reference to the new composition is placed in a cache shared
-by the new an originating compositions. The next time the originating
+by the new and originating compositions. The next time the originating
 composition is decayed, this cache will be checked for a prior calculation
@@
 and users with related simulation and nuclear engineering tasks. The toolkit is
-an activly developed module module of \Cyclus, with a primary forward-looking
+an actively developed module of \Cyclus, with a primary forward-looking
 focus on supporting interesting \textit{in situ} (i.e., in simulation) and
@@
 A series of utility classes are provided to support demand-constrained agent
-(e.g. facility) deployment. Symbolic function representations of linear,
-expontential, and piecewise functions are supported via the
+(e.g., facility) deployment. Symbolic function representations of linear,
+exponential, and piecewise functions are supported via the
 \Class{SymbFunctionFactory} class. Such functions are used with other toolkit
@@
 \Class{CommodityProducer}, \Class{CommodityProducerManager}, \Class{Builder},
-\Class{BuildingManager}. The \Class{CommodityProducer} class provides an
-interface for querying the \textit{prototypes} which have some nameplate
+and \Class{BuildingManager}. The \Class{CommodityProducer} class provides an
+interface for querying the \textit{prototypes} that have some nameplate
 capacity to produce a given commdity, and the \Class{CommodityProducerManager}
@@
 many of each prototype, $y_i$, to build given a demand, $\Phi$, capacities,
-$\phi_i$, and costs $c_i$.
+$\phi_i$, and costs, $c_i$.
 
@@
 The \Cyclus toolkit provides two useful modules for querying \Class{Material}
-objects regarding physical parameters. First the \Class{MatQuery} module
-provides a basic querying \gls{API}, including the atom and mass fractions of
+objects regarding physical parameters. First, the \Class{MatQuery} module
+provides a basic querying \gls{API}, including the atomic and mass fractions of
 nuclides, the number of moles of a nuclide in a material, and also the amount of
@@
 parameters of a material, including the separative work units (SWU) and natural
-uranium required to enrich a material given provided feed, product, and tails
+uranium required to enrich a material provided knowledge of feed, product, and tails
 assays.
@@
 Facility & Source & This facility generates material of the composition and commodity type specified as input.  \\
-Facility & Sink & This facility is capable of accepting a finite or infinite quantity of some commodity produced in the simulation \\
+Facility & Sink & This facility is capable of accepting a finite or infinite quantity of some commodity produced in the simulation. \\
 Facility & EnrichmentFacility & This facility enriches uranium at a specified capacity. \\
-Institution& ManagerInst & The manager institution manages production of commodiites among its facilities by building new necessary ones \\
+Institution & ManagerInst & The manager institution manages production of commodiites among its facilities by building new necessary ones. \\
 Institution & DeployInst &  This institution deploys specific facilities as defined explicitly in the input file. \\
-Region & GrowthRegion & This region determines whether there is a need to meet a certain capacity (as defined via input) at each time step \\
+Region & GrowthRegion & This region determines whether there is a need to meet a certain capacity (as defined via input) at each time step. \\
 \hline
@@
 
-Figure \ref{fig:cyc_sim} shows an example of a simple, once-through fuel cycle 
+Figure \ref{fig:simplesim} shows an example of a simple, once-through fuel cycle 
 that can be generated with \Cycamore and \Cyclus alone.

### 2014-10-30 fundamentals/conclusion.tex
fixes arclong to acrlong
updated minor edits

@@
 
-The object-oriented \arclong{ABM} simulation paradigm ensures more generic 
+The object-oriented \acrlong{ABM} simulation paradigm ensures more generic 
 simulation capability. It allows \Cyclus to address common analyses in a more 
@@
 at every level of detail. Simulations relying on arbitrarily complex isotopic 
-compositions are possible in \Cyclus, as are  toy simulations not employing any 
+compositions are possible in \Cyclus, as are simulations not employing any 
 physics at all. Indeed, agents of such varying fidelity can even exist in the 

### 2014-10-30 fundamentals/examples.tex
updated minor edits

@@
 
-The early success of the \Cyclus simulator can be measured in many ways. 
+The success of the \Cyclus simulator can be measured in many ways. 
 The most compelling are demonstrations of the feasibility of the \Cyclus community-driven development 
-model and of fundamental simulation capability. Nascent, promising growth of the \Cyclus 
+model and of fundamental simulation capability. Nascent promising growth of the \Cyclus 
 ecosystem at multiple institutions indicates that a fuel cycle simulator can 
@@
 repository of additional modules,
-\item the archetypes created by user-developers,
+\item the archetypes created by researchers,
 \item isotopic composition data,
 \item historical facility deployment data,
-\item the \Cyclus \gls{GUI} tools, Cycic and Cyclist,
+\item the \Cyclus \gls{GUI} tool Cyclist,
 \item the tools in the \Cyclus toolkit
@@
 Results of some simple recycle scenarios run in \Cyclus follow.  In \Cyclus,
-because material is tracked as discrete objects, single-pass MOX recycle is
+because material is tracked as discrete objects, single-pass mixed-oxide (MOX) 
+recycle is
 easy to implement.  The simulation initially included one provider of fresh
-UOX fuel, one recycled fuel fabrication facility, one reactor, one separations
+uranium oxide (UOX) fuel, one recycled fuel fabrication facility, one reactor, one separations
 facility, and one repository. The simulation duration was set to 1100 months.
@@
 
-The \Class{Source} and \Class{Sink} modules from \Cycamore were also used as a
+The \Class{Source} and \Class{Sink} archetypes from \Cycamore were also used as a
 source of fresh, enriched uranium and a repository respectively. A simple

### 2014-10-30 fundamentals/impl.tex
updated minor edits

--- 2014-10-28 fundamentals/impl.tex
@@
 
-A modular, agent-based is an ideal approach for solving complex, coupled,
+A modular, agent-based approach is ideal for solving complex, coupled,
 physics-dependent supply chain problems involving material routing, facility
@@
 Dynamically-loadable libraries are the primary mechanism for extending \Cyclus' capability. 
-This approach provides encapsulation: the core of the code operates
+This approach provides encapsulation. The core of the code operates
 completely independently from the individual plugin libraries. Thus, any
@@
 archetype libraries.  The 
-scientist-developer can focus on generating an archetype model within their
+researchercan focus on generating an archetype model within their
 sphere of expertise, while relying on the contributions of others to fill 
@@
 provides a notion of parent-child hierarchichal relationship, where parents can
-choose to \textit{build} child agents and \textit{decommission} child
+choose to \textit{deploy} child agents and \textit{decommission} child
 agents. For the archetype developer, this interface provides enormous power, 
@@
 In a similar fasion, the \Class{Trader} interface allows agent-agent interaction through the
-trading of \Class{Resource}s. Usabe archetypes in a \Cyclus simulation must
+trading of \Class{Resource}s. Archetypes in a \Cyclus simulation must
 implement the \Class{Agent} interface and may optionally implement the
@@
 \Cyclus provides a novel representation of entities in the nuclear fuel cycle 
-which mimics the reality in international nuclear power production
-including facilities, institutions managing those facilities, and regions. While
+which models the reality in international nuclear power production
+encompassing facilities, institutions managing those facilities, and regions. While
 some simulators (\TODO{cite DESAE}) have provided a notion of static regional
@@
 Two primary consequences arise from this structure. First, institutions are
-responsible for building and decommissioning facilities. Accordingly, advanced
+nominally
+responsible for deploying and decommissioning facilities. Accordingly, advanced
 logic regarding building and decommissioning can be obtained by subclassing the
@@
 adjust the resource flow preferences of their managed facilities. Importantly,
-this novel capability allows for the modeling of preferential regional trading
+this capability allows for the modeling of preferential regional trading
 of resources (e.g., tariffs) as well as preferential institutional trading
@@
 Although concept of the \gls{RIF} hierarchy is provided, the \Cyclus kernel is
-really designed to handle hierarchies of arbitrary depth.  It is just as easy
-to run a simulation without regions and institutions (i.e.  only facilities)
-or a simulation having archetypes that are the parents' of regions.  By
+designed to handle hierarchies of arbitrary depth.  It is capable of 
+running a simulation without regions and institutions (i.e.  only facilities)
+or a simulation having archetypes that are the parents of regions.  By
 convention, institutions are mainly responsible for facility deployment, but
-any archetype can have access to \Cyclus' agent deployment mechanism.  It easy
+any archetype can have access to the \Cyclus agent deployment mechanism.  It easy
 to implement agents that deploy copies of themselves, or that schedule their
 own decommissioning.  Because regions, institutions, and facilities are all
-just agents, they can all be implemented to exercise the full set of features
+agents, they can all be implemented to exercise the full set of features
 offered by the \Cyclus kernel.
@@
 In \Cyclus, agents can transfer discrete resource objects between each other.
-Cyclus supports two types of resources:
+Cyclus currently supports two types of resources:
 
@@
   \item Materials: These represent typical nuclear materials with
-      nuclide-based compositions.
+      nuclide compositions.
 
@@
 All operations performed on every resource object (splitting, combining,
-decay, etc.) are tracked in detail.  This information includes the creating
+decay, etc.) are tracked in detail as they are performed.  This information includes 
+the creating
 agent for when resources are newly created and introduced into the simulation.
 The parentage of each resource is also tracked. This makes it possible to
-follow the travel history of discrete resource objects as they are transferred
-between agents and powerfully impacts the ability to model 
+follow the history of resources as they are transferred
+between agents.  This powerfully impacts the ability to model 
 non-proliferation-related simulation goals.
@@
 The \Cyclus kernel has built-in experimental support for decay calculations.
-Materials ``remember'' the time since their last decay and agents are free to
+Materials store the time since their last decay and agents are free to
 invoke the decay function on them as desired to decay them to the current
@@
     \item "never" (currently implemented) globally turns off all decay.
-        Materials' decay function does nothing.
+        Materials decay function does nothing.
 
@@
 
-In order to avoid excess decay calculations, when a material's decay function
+In order to avoid excess decay calculations, when decay 
 is invoked, the material checks to see if it contains any nuclides with decay
@@
 
-In large simulations there may be many material objects changing frequently, on 
-the day or month timescale.
+In large simulations there may be many material objects changing frequently.
 Material decay can also contribute significantly to such changes.  In order to
@@
 references to the same composition object safely.  When operations are
-performed on a material that don't change the composition, any new resulting
+performed on a material that do not change the composition, any new resulting
 materials hold a reference to the same, originating composition object.
@@
 immutability), a reference to the new composition is placed in a cache shared
-by the new an originating compositions. The next time the originating
-composition is decayed, this cache will be checked for a prior calculation
+by the new originating compositions. The next time the originating
+composition is decayed, the cache will be checked for a prior calculation
 with the same cumulative decay time.  If one exists, the cached composition is
@@
 In addition to the core functionality of the \Cyclus kernel, which is focused on
-the minimal set of capabilities needed to implement an agent-based simulation
+the set of capabilities needed to implement an agent-based simulation
 with dynamic resource exchange, a toolkit is provided that assists developers
 and users with related simulation and nuclear engineering tasks. The toolkit is
-an activly developed module module of \Cyclus, with a primary forward-looking
-focus on supporting interesting \textit{in situ} (i.e., in simulation) and
-\textit{ex situ} (i.e., post-processing) metric analysis tools.
+an activly developed part of \Cyclus, with a primarily forward-looking
+focus on supporting interesting \textit{in situ} metric analysis tools.
 
@@
 A series of utility classes are provided to support demand-constrained agent
-(e.g. facility) deployment. Symbolic function representations of linear,
+facility deployment. Symbolic function representations of linear,
 expontential, and piecewise functions are supported via the
@@
 \Class{BuildingManager}. The \Class{CommodityProducer} class provides an
-interface for querying the \textit{prototypes} which have some nameplate
-capacity to produce a given commdity, and the \Class{CommodityProducerManager}
+interface for querying the \textit{prototypes} which have the
+capacity to produce a given commdity. The \Class{CommodityProducerManager}
 provides an interface for registering \Class{CommodityProducer}s and querying
@@
 
-The \Cyclus toolkit provides two useful modules for querying \Class{Material}
+The \Cyclus toolkit provides two useful interfaces for querying \Class{Material}
 objects regarding physical parameters. First the \Class{MatQuery} module
@@
 
-\Cycamore \cite{carlsen_cycamore_2014}, the \Cyclus additional modules 
+\Cycamore \cite{carlsen_cycamore_2014}, the \Cyclus additional module
 repository, provides a fundamental set of agent archetypes for basic simulation 
@@
 As of version 1.0, \Cycamore contains four facility archetypes, one region 
-archetype, and two institution archetypes. Short descriptions of those 
+archetype, and two institution archetypes. Short descriptions of these 
 functions can be found in Table \ref{tab:cycamore}.
@@
 \hline
-\textbf{Agent Type} & \textbf{Archetype} & \textbf{Functionality} \\
+\textbf{Entity} & \textbf{Archetype} & \textbf{Functionality} \\
 \hline

### 2014-10-30 fundamentals/intro.tex
updated minor edits

--- 2014-10-22 fundamentals/intro.tex
@@
 simulator. Dynamic simulation of nuclear fuel cycles with discrete agents 
-and up to isotopic resolution support 
+and per nuclide species resolution support 
 levels of detail appropriate for a varied community of analysts
@@
 ranging from ad hoc spreadsheet-driven flow calculators to highly specialized 
+system dynamics
 proprietary models. To date, current tools are either static, fleet-based, 
@@
 supports a broader range of simulation goals than static analysis 
-\cite{piet_dynamic_2011}. Similarly, experience in the greater field of systems 
+\cite{piet_dynamic_2011}. Similarly, experience in the broader field of systems 
 analysis indicates that agent-based modeling enables more flexible simulation 
@@
 ``reinvent the wheel'' by developing tools of their own from scratch and 
-tailored to their own needs (e.g., \gls{CAFCA}\cite{guerin_impact_2009} and 
-\gls{COSI}\cite{boucher_cosi_2005,boucher_cosi:_2006,meyer_new_2009,coquelet-pascal_comparison_2011} respectively).
+tailored to their own needs, for example \gls{CAFCA}\cite{guerin_impact_2009} and 
+\gls{COSI}\cite{boucher_cosi_2005,boucher_cosi:_2006,meyer_new_2009,coquelet-pascal_comparison_2011} respectively.
 
@@
 for calculating those metrics vary among simulators. Some model the 
-system of facilities, economics, and materials at static equilibrium, while 
-others capture its dynamics.  
+system of facilities, economics, and materials at static equilibrium. Meanwhile 
+other simulators capture its dynamics.  
 Similarly, while some simulators discretely model material and facilities, 
@@
 collaboration.  The \Cyclus project, in turn, improved upon the \gls{GENIUSv2} 
-project by implementing increased modularity and encapsulation.  The result is  
+effort by implementing increased modularity and encapsulation.  The result is  
 a dynamic simulator that treats both materials and facilities discretely, with 
@@
 chain is a multiscale problem, but existing tools are not sufficiently 
-multi-scale. Tools have either focused on macro effects, e.g., the fleet-level
+multiscale. Tools have either focused on macro effects, e.g., the fleet-level
 stocks and flows of commodities, or micro effects, e.g., the used fuel
@@
 maintenance overhead and improves code robustness \cite{citation_needed}. 
-Finally, the researcher can therefore focus on creating or customizing nuclear 
+The researcher can therefore focus on creating or customizing nuclear 
 facility, institution, resource, and toolkit models within their specific area 
@@
 We expect that there are a number of types of users and developers who will 
-interact with the \Cyclus framework. National laboratory researchers,
-academic researchers, private-industry economic forcasters, and even students. 
+interact with the \Cyclus framework: national laboratory researchers,
+academic researchers, private-industry economic forcasters, and students
 in engineering courses will benefit from the ease of development and ease of 
@@
 
-\Cyclus utilizes an \gls{ABM} paradigm.  \gls{ABM} is modern, sophisticated, 
+\Cyclus implements an \gls{ABM} paradigm.  \gls{ABM} is modern, sophisticated, 
 true to reality, and it takes advantage of modern computing resources.  
@@
 \gls{API} contract is sufficient for them to interact with one another as 
-bonafide actors in the simulation.  The two archetype libraries, therefore, need 
+bonafide actors in the simulation.  The two archetypes, therefore, need 
 not have any shared knowledge of one another for them to be building blocks in 
@@
 
-System dynamics is a popular approach for modeling nuclear fuel cycles in current
-tools 
+System dynamics is a popular approach for modeling nuclear fuel cycles 
 \cite{jacobson_vision_2009,van_den_durpel_daness_2009,guerin_impact_2009,guerin_benchmark_2009}. However, it has been shown in systems analysis literature

### 2014-10-30 fundamentals/qa.tex
updated minor edits

@@
 It is important to note that before a proposed
-code changes is allowed into main stream cyclus, all of the tests must pass
-and the change must be covered by a test, either new or existing. This is 
+code change is allowed into mainline cyclus, all of the tests must pass
+and the change must be covered by a test, either new or existing. This is a
 matter of policy for the developers. Additionally, test code is equally likely 
@@
 
-Intergration tests are any tests that combine multiple elemnents of the 
+Intergration tests are any tests that combine multiple elements of the 
 cyclus interface and test that they work correctly with each other.  By analogy, 
@@
 Python will run cyclus as a subprocess for each integration test. In this
-way cyclus code units are tested in the full context that they will
+way cyclus code units are tested in the full context that they will be
 executed. This category of testing is especially useful for ensuring that 
@@
 occur over the course of cyclus development. Such a change is called a 
-\emph{regression} because the new version is almost always wrong.
+\emph{regression} because the new version is almost always wrong version in the 
+event of a difference.
 Regression tests are implemeneted similarly to integration tests.
@@
 
-All of the public interface (the API) must be documented as part of cyclus
+All of the public interfaces must be documented as part of cyclus
 QA policy. This certifies that the intention for a code unit is communicated 
 in way that is separate from its implementation. This policy is important 
-because implementations are often wrong, hence bugs. They are thus unreliable 
+because implementations are often wrong. Software implementations are unreliable 
 resources about themselves. Truly trustworthy communication about what 
@@
 are in agreement. Documentation is thus a secondary higher-level information 
-stream.  In cyclus, this information is aggregated together into static 
+source.  In cyclus, this information is aggregated together into static 
 websites with the doxygen \cite{van_heesch_doxygen:_2008} and sphinx 
@@
 tree and then may be \emph{merged} back into the mainline. Multiple simeltaneous
-branches may exist at all point in time. Every change to the code is recorded
+branches may exist at all points in time. Every change to the code is recorded
 in the history, along with metadata such as the author, a timestamp, and an 
@@
 must have sufficient and passing tests and reasonable documentation. Without
-these core pieces proposed changes are not allowed into cyclus.
+these core pieces, proposed changes are not allowed into cyclus.
 
@@
 
-Continuous integration (CI) the idea that software should be tested and validated 
+Continuous integration (CI) is the idea that software should be tested and validated 
 as it is being developed, rather than as a final stage in a longer development 

### 2014-10-31 fundamentals/impl.tex
fixed possesion

--- 2014-10-30 fundamentals/impl.tex
@@
 studies on \Cyclus' resource exchange optimization solvers. To date, it has been
-used run over $10^4$ jobs, or (\TODO{compute time}) total computer hours, using
+used run over $10^4$ jobs, or (\TODO{compute time}) total compute hours, using
 the \Cyclus library via its resource exchange \gls{API}.
@@
 \Class{Institution} interface. Second, the \Class{Facility} class implemenets the
-\Class{Trader} interface, and thus institutions and regions, can
+\Class{Trader} interface, and thus institutions and regions can
 adjust the resource flow preferences of their managed facilities, respectively. Importantly,
@@
 convention, institutions are mainly responsible for facility deployment, but
-any archetype can have access to \Cyclus' agent deployment mechanism.  It straightforward
+any archetype can have access to \Cyclus' agent deployment mechanism.  It is straightforward
 to implement agents that deploy copies of themselves or schedule their
@@
 objects regarding physical parameters. First, the \Class{MatQuery} module
-provides a basic querying \gls{API}, including the atomic and mass fractions of
+provides a basic querying \gls{API}, including the atom and mass fractions of
 nuclides, the number of moles of a nuclide in a material, and also the amount of

### 2014-10-31 fundamentals/examples.tex
helps with glossary

@@
 Results of some simple recycle scenarios run in \Cyclus follow.  In \Cyclus,
-because material is tracked as discrete objects, single-pass mixed-oxide (MOX) 
+because material is tracked as discrete objects, single-pass \gls{MOX} 
 recycle is
 easy to implement.  The simulation initially included one provider of fresh
-uranium oxide (UOX) fuel, one recycled fuel fabrication facility, one reactor, one separations
+\gls{UOX} fuel, one recycled fuel fabrication facility, one reactor, one separations
 facility, and one repository. The simulation duration was set to 1100 months.
@@
 commodity.  The dynamic resource exchange makes it easy for a reactor to
-preferrentially accept recycled MOX fuel over fresh UOX fuel.  The
+preferrentially accept recycled \gls{MOX} fuel over fresh \gls{UOX} fuel.  The
 \Class{BatchReactor} was configured to run with a 3 batch core on 18 month cycles and
@@
 \label{fig:flowmodopen}
-\caption{Modified open 1-pass MOX recycle fuel cycle material flows.}
+\caption{Modified open 1-pass \gls{MOX} recycle fuel cycle material flows.}
 \begin{center}
@@
 To switch to a fully closed fuel cycle, all that needs to be done is change
-the output commodity for the \Class{BatchReactor}'s spent MOX fuel.  All this
+the output commodity for the \Class{BatchReactor}'s spent \gls{MOX} fuel.  All this
 requires is a one-word change in the input file:
@@
 \label{fig:flowclosed}
-\caption{Full MOX recycle (multi-pass) fuel cycle material flows.}
+\caption{Full \gls{MOX} recycle (multi-pass) fuel cycle material flows.}
 \begin{center}

### 2014-10-31 fundamentals/qa.tex
helps with glossary

@@
 
-Continuous integration (CI) is the idea that software should be tested and validated 
+\gls{CI} is the idea that software should be tested and validated 
 as it is being developed, rather than as a final stage in a longer development 
-cycle.  Under CI every pull request is tested independently immeadiately after 
+cycle.  Under \gls{CI} every pull request is tested independently immeadiately after 
 it is proposed. Such tests shoudl be run on all officially supported platforms. 
-Cyclus uses a CI platform called Polyphemus \cite{scopatz_polyphemus_2014}.
+Cyclus uses a \gls{CI} platform called Polyphemus \cite{scopatz_polyphemus_2014}.
 
@@
 
-CI has become a neccessary but not sufficient addition to the cyclus QA
+\gls{CI} has become a neccessary but not sufficient addition to the cyclus QA
 system. Its merit is that it keeps bad code out. However, cyclus will always

### 2014-10-31 fundamentals/intro.tex
arrielle's first comment about the long sentence in the intro

--- 2014-10-30 fundamentals/intro.tex
@@
 its modeling ecosystem answer this need for a next generation nuclear fuel cycle 
-simulator. Dynamic simulation of nuclear fuel cycles with discrete agents 
-and up to isotopic resolution support 
-levels of detail appropriate for a varied community of analysts
-interested in a range of analysis types. Additionally, \Cyclus employs an 
+simulator. This dynamic simulator employs discrete agents, time, and materials 
+up to isotopic resolution in order to support a range of analysis types, levels of 
+detail, and fuel cycle analysts.
+Additionally, \Cyclus employs a modular architecture and 
 open development process that supports user access and 

### 2014-10-31 fundamentals/intro.tex
removes proliferation metric phrasing

@@
 measures of performance can be expressed in terms of these metrics. For example, 
-economic feasibility is often measured in \gls{LCOE} while proliferation risk 
-can be proportional to total kilograms of separated Pu, and environmental 
-performance might be measured in spent fuel volume, toxicity, or mined uranium.
+economic feasibility is often measured in \gls{LCOE}
+while environmental performance might be measured in spent fuel volume, 
+  toxicity, or mined uranium.
 

### 2014-10-31 fundamentals/intro.tex
went with essential instead of major

@@
 In addition to providing the fundamental features expected in fuel cycle 
-simulators, the \Cyclus paradigm enables major capabilities that previous 
+simulators, the \Cyclus paradigm enables essential capabilities that previous 
 simulators lack. First, its \emph{modular and open architecture}  facilitates 

### 2014-10-31 fundamentals/impl.tex
went with plug-in, cuz google said so.

@@
 
-The core of the \Cyclus simulator creates a set of key classes on which agent plugins 
+The core of the \Cyclus simulator creates a set of key classes on which agent 
+plug-ins 
 are based. In addition, a set of key tools are also provided to enrich the 
@@
 
-Agent plugins utilize the generic core \gls{API} to interact with one another.  For 
-example, agents rely on the dynamic loading and paradigm for clean plugin 
+Agent plug-ins utilize the generic core \gls{API} to interact with one another.  For 
+example, agents rely on the dynamic loading and paradigm for clean plug-in 
 behavior at the start of the simulation. They also use the resource exchange 
@@
 A key innovation in \Cyclus is implementing this generic \gls{API} and modular 
-architecture into a suite of dynamically loadable ``plugin'' libraries.  Though 
-common in modern software architecture, such a ``plugin'' pattern has 
+architecture into a suite of dynamically loadable plug-in libraries.  Though 
+common in modern software architecture, such a plug-in pattern has 
 previously not been implemented in nuclear fuel cycle simulators in the 
@@
 This approach provides encapsulation: the core of the code operates
-completely independently from the individual plugin libraries. Thus, any
+completely independently from the individual plug-in libraries. Thus, any
 customization or extension is implemented only in the loadable
@@
 
-In particular, since the clean plugin architecture loads libraries without any
+In particular, since the clean plug-in architecture loads libraries without any
 modifications to the \Cyclus kernel, closed-source archetypes can be used with
@@
 
-Due to this ``plugin'' architecture,
+Due to this plug-in architecture,
 implementations of actors in a given simulation can be easily

### 2014-10-31 fundamentals/impl.tex
went with open source, cuz google

@@
 Furthermore, the core infrastructure and related archetypes are free and 
-open-source, BSD-3-clause licsened. No part of \Cyclus is proprietary or based 
+open source, BSD-3-clause licsened. No part of \Cyclus is proprietary or based 
 on \gls{COTS}, Windows-based software. It can be easily deployed 
@@
 modifications to the \Cyclus kernel, closed-source archetypes can be used with
-the simulator alongside open-source archetypes. This architecture
+the simulator alongside open source archetypes. This architecture
 allows closed-source libraries (e.g., those representing sensitive nuclear

### 2014-10-31 fundamentals/impl.tex
adds gls commands

@@
 Cyclopts (\TODO{cite}), a proof of principle design and implementation of such a
-system, uses UW-Madison's HTCondor HTC infrastructure to perform sensitivity
+system, uses UW-Madison's HTCondor \gls{HTC} infrastructure to perform sensitivity
 studies on \Cyclus' resource exchange optimization solvers. To date, it has been
@@
 the \Cyclus library via its resource exchange \gls{API}.
-The HTC infrastructure has also been utilized to run and collect
+The \gls{HTC} infrastructure has also been utilized to run and collect
 information from full \Cyclus simulations running in parallel on $10^3$

### 2014-10-31 fundamentals/impl.tex
fixes htc problem. I guess acrlong isn't really that good.. eh.
changed originating to original

@@
 on \gls{COTS}, Windows-based software. It can be easily deployed 
-on large computer systems, such as \acrlong{HTC} systems.
+on large computer systems, such as \gls{HTC} systems.
 
@@
 performed on a material that do not alter the composition, any new resulting
-materials hold a reference to the same, originating composition object.
+materials hold a reference to the same, original composition object.
 Although the decay operation generates a new, separate composition (preserving
 immutability), a reference to the new composition is placed in a cache shared
-by the new and originating compositions. The next time the originating
+by the new and original compositions. The next time the original
 composition is decayed, this cache will be checked for a prior calculation

### 2014-10-31 fundamentals/examples.tex
fixed in other branch

--- 2014-10-22 fundamentals/examples.tex
@@
 simulations as well as more complex recycling simulations demonstrate that 
-\Cyclus posesses fundamental fuel cycle simulation capabilities.
+\Cyclus possesses fundamental fuel cycle simulation capabilities.
 
@@
 long-term vision for the \Cyclus framework predicts an ever-expanding ecosystem 
-of both general and specialized capability extensions within that ecosytem.
+of both general and specialized capability extensions within that ecosystem.
 
 Already, the ecosystem is growing. Early cross-institutional contributions to 
-the ecosystem demonstrate a significant acheivement by the \Cyclus framework 
+the ecosystem demonstrate a significant achievement by the \Cyclus framework 
 and provide hope for a community-driven development model.
@@
 \caption{Many tools outside of the scope of the \Cyclus kernel have been 
-developed for improved user, developer, and analyst experinces with \Cyclus.}
+developed for improved user, developer, and analyst experiences with \Cyclus.}
 \label{tab:coretools}
@@
 \hline
-Brite-lite & A physics-based reactor archetype and fuel fabrication archetype & \cite{flanagan_bright-lite_2014} \\
+Bright-lite & A physics-based reactor archetype and fuel fabrication archetype & \cite{flanagan_bright-lite_2014} \\
 Nuclear Fuel Inventory Model & A flexible, ORIGEN-based, reactor analysis module & \cite{skutnik_nuclear_2014} \\
@@
 The \Class{BatchReactor} archetype from \Cycamore has the ability to accept
-fuel materials from an arbitrary number of different sources dilineated by
+fuel materials from an arbitrary number of different sources delineated by
 commodity. Custom, non-uniform preferences can be set for each different fuel
 commodity.  The dynamic resource exchange makes it easy for a reactor to
-preferrentially accept recycled MOX fuel over fresh UOX fuel.  The
+preferentially accept recycled MOX fuel over fresh UOX fuel.  The
 \Class{BatchReactor} was configured to run with a 3 batch core on 18 month cycles and
@@
 as possible.  The method used for this matching is approximately the same as
-that used by the Cosi fuel cycle simulator \TODO{cite COSI equivalence
+that used by the \gls{COSI} fuel cycle simulator \TODO{cite COSI equivalence
 method}. The material flows for this simulation are shown below in figure
@@
 
-To switch to a fully closed fuel cycle, all that needs to be done is change
-the output commodity for the \Class{BatchReactor}'s spent MOX fuel.  All this
-requires is a one-word change in the input file:
+Simply changing the output commodity name of spent \gls{MOX} fuel from the 
+\Class{BatchReactor} transforms this simulation into a closed fuel cycle. Only 
+a one-word change in the input file:
 
@@
 that because the \Class{BatchReactor} always transmutes fuel into the same
-composition, the nuclide level flows are not very realistic for the full, multipass
+composition, the nuclide level flows are not very realistic for the full, 
+multi-pass
 recycle case.

### 2014-10-31 fundamentals/impl.tex
fixed in other branch

--- 2014-10-31 fundamentals/impl.tex
@@
 Furthermore, the core infrastructure and related archetypes are free and 
-open source, BSD-3-clause licsened. No part of \Cyclus is proprietary or based 
+open source, BSD-3-clause licensed. No part of \Cyclus is proprietary or based 
 on \gls{COTS}, Windows-based software. It can be easily deployed 
@@
 
-The core of the \Cyclus simulator creates a set of key classes on which agent 
-plug-ins 
+The core of the \Cyclus simulator creates a set of key classes on which agent plugins 
 are based. In addition, a set of key tools are also provided to enrich the 
@@
 
-Agent plug-ins utilize the generic core \gls{API} to interact with one another.  For 
-example, agents rely on the dynamic loading and paradigm for clean plug-in 
+Agent plugins utilize the generic core \gls{API} to interact with one another.  For 
+example, agents rely on the dynamic loading and paradigm for clean plugin 
 behavior at the start of the simulation. They also use the resource exchange 
@@
 A key innovation in \Cyclus is implementing this generic \gls{API} and modular 
-architecture into a suite of dynamically loadable plug-in libraries.  Though 
-common in modern software architecture, such a plug-in pattern has 
+architecture into a suite of dynamically loadable ``plugin'' libraries.  Though 
+common in modern software architecture, such a ``plugin'' pattern has 
 previously not been implemented in nuclear fuel cycle simulators in the 
@@
 This approach provides encapsulation: the core of the code operates
-completely independently from the individual plug-in libraries. Thus, any
+completely independently from the individual plugin libraries. Thus, any
 customization or extension is implemented only in the loadable
@@
 
-In particular, since the clean plug-in architecture loads libraries without any
+In particular, since the clean plugin architecture loads libraries without any
 modifications to the \Cyclus kernel, closed-source archetypes can be used with
-the simulator alongside open source archetypes. This architecture
+the simulator alongside open-source archetypes. This architecture
 allows closed-source libraries (e.g., those representing sensitive nuclear
@@
 
-\subsection{Agent Interchangability}\label{sec:interchangeability}
+\subsection{Agent Interchangeability}\label{sec:interchangeability}
 
-Due to this plug-in architecture,
+Due to this ``plugin'' architecture,
 implementations of actors in a given simulation can be easily
@@
 
-Interchangability is accomplished by providing \glspl{API} that define agent-to-agent
+Interchangeability is accomplished by providing \glspl{API} that define agent-to-agent
 interaction and agent-to-environment interaction, primarily through the
@@
 format. It shows how the \Class{Agent} interface
-provides a notion of parent-child hierarchichal relationship, where parents can
+provides a notion of parent-child hierarchical relationship, where parents can
 choose to \textit{build} child agents and \textit{decommission} child
@@
 \Class{Facility}, \Class{Institution}, and \Class{Region} classes abstract away 
-unneccesary details while exposing powerful functionality. In the above 
+unnecessary details while exposing powerful functionality. In the above 
 example, the \Class{Dummy} archetype simply inherits from \Class{Region} in 
-order to become a bonified Region-type \Class{Agent}.}
+order to become a bona fide Region-type \Class{Agent}.}
 \label{fig:agent_uml}
@@
 responsible for building and decommissioning facilities, so advanced
-logic regarding building and decommissioning can be obtained by subclassing the
-\Class{Institution} interface. Second, the \Class{Facility} class implemenets the
+logic regarding building and decommissioning can be obtained by sub-classing the
+\Class{Institution} interface. Second, the \Class{Facility} class implements the
 \Class{Trader} interface, and thus institutions and regions can
@@
 Facility & EnrichmentFacility & This facility enriches uranium at a specified capacity. \\
-Institution & ManagerInst & The manager institution manages production of commodiites among its facilities by building new necessary ones. \\
+Institution & ManagerInst & The manager institution manages production of commodities among its facilities by building new necessary ones. \\
 Institution & DeployInst &  This institution deploys specific facilities as defined explicitly in the input file. \\

### 2014-10-31 fundamentals/intro.tex
fixed in other branch

--- 2014-10-31 fundamentals/intro.tex
@@
 its modeling ecosystem answer this need for a next generation nuclear fuel cycle 
-simulator. This dynamic simulator employs discrete agents, time, and materials 
-up to isotopic resolution in order to support a range of analysis types, levels of 
-detail, and fuel cycle analysts.
-Additionally, \Cyclus employs a modular architecture and 
+simulator. Dynamic simulation of nuclear fuel cycles with discrete agents 
+and up to isotopic resolution support 
+levels of detail appropriate for a varied community of analysts
+interested in a range of analysis types. Additionally, \Cyclus employs an 
 open development process that supports user access and 
@@
 measures of performance can be expressed in terms of these metrics. For example, 
-economic feasibility is often measured in \gls{LCOE}
-while environmental performance might be measured in spent fuel volume, 
-  toxicity, or mined uranium.
+economic feasibility is often measured in \gls{LCOE} while proliferation risk 
+can be proportional to total kilograms of separated Pu, and environmental 
+performance might be measured in spent fuel volume, toxicity, or mined uranium.
 
@@
 However, an extensible architecture and discrete object tracking allow 
-the creation and exchangeability of custom \Cyclus archetypes at any level of fidelity.
+the creation and interchangeability of custom \Cyclus archetypes at any level of fidelity.
 
@@
 interact with the \Cyclus framework. National laboratory researchers,
-academic researchers, private-industry economic forcasters, and even students 
+academic researchers, private-industry economic forecasters, and even students 
 in engineering courses may benefit from the ease of development and
@@
 \gls{API} contract is sufficient for them to interact with one another as 
-bonafide actors in the simulation.  The two archetype libraries, therefore, need 
+bona fide actors in the simulation.  The two archetype libraries, therefore, need 
 not have any shared knowledge of one another for them to be building blocks in 

### 2014-10-31 fundamentals/acros.tex
adds ABM to the glossary
modular arch."
cleaning up implementation, adding content
fixes broken
adds inheritance diagrams
adds diagram
helps with glossary
adds acros

@@
 \newacronym{LDRD}{LDRD}{Laboratory Directed Research and Development}
+\newacronym{LCOE}{LCOE}{Levelized Cost of Electricity}
+\newacronym{ABM}{ABM}{Agent-Based Modeling}
+\newacronym{COTS}{COTS}{Commercial, Off-The-Shelf}
+\newacronym{API}{API}{Application Programming Interface}
+\newacronym{RIF}{RIF}{Region-Institution-Facility}
+\newacronym{GUI}{GUI}{Graphical User Interface}
+\newacronym{HPC}{HPC}{High-Performace Computing}
+\newacronym{HTC}{HTC}{High-Throughput Computing}
+\newacronym{UML}{UML}{Unified Modeling Language}
+\newacronym{DAG}{DAG}{Directed Acyclic Graph}
+\newacronym{QA}{QA}{Quality Assurance}
+\newacronym{NQA1}{NQA-1}{Nuclear Quality Assurance - 1}
+\newacronym{VV}{V\&V}{Verificaion and Validation}
+\newacronym{UQ}{UQ}{Uncertainty Quantification}
+\newacronym{ASME}{ASME}{American Society of Mechanical Engineers}
 %\newacronym{<++>}{<++>}{<++>}

### 2014-10-31 fundamentals/qa.tex
lots of spelling stuff

--- 2014-10-22 fundamentals/qa.tex
@@
 
-Simulation science - like experimental science - has since the begining had the 
+Simulation science - like experimental science - has since the beginning had the 
 problem of identifying trustworthy results from the nonsensical and the noise.
@@
 The \emph{garbage in, garbage out} phenomenon is not the only scenario which a
-simulator must gaurd against; ensuring correctness is equally important.
+simulator must guard against; ensuring correctness is equally important.
 
-Multiple strategies collectively known a \emph{quality assurance} (QA) have 
+Multiple strategies collectively known as \emph{\gls{QA}} have 
 been invented over the years to mitigate the structural and algorithmic errors
-on the part of simulators themselves. These include \emph{verification and validation}
-(V\&V) \cite{boehm_software_1989}, \emph{uncertainty quantification} (UQ) 
-\cite{sacks_design_1989}, testing, and others. V\&V and UQ come from 
+on the part of simulators themselves. These include \emph{\gls{VV}}
+\cite{boehm_software_1989}, \emph{\gls{UQ}} 
+\cite{sacks_design_1989}, testing, and others. \gls{VV} and \gls{UQ} come from 
 a distinctly computational science background while testing \emph{et al.} come from 
@@
 
-Nuclear enginerering code quality is often governed by NQA-1, an ASME specification 
+Nuclear engineering code quality is often governed by \gls{NQA1}, an 
+\gls{ASME} specification 
 whose latest revision appeared in 2009 \cite{asme_nqa-1a-2009_2009}. This is primarily 
 used for designing reactors. However, it is general enough to apply to 
-cyclus. Cyclus has adopted an \emph{agile} development process 
+\Cyclus. \Cyclus has adopted an \emph{agile} development process 
 \cite{larman_agile_2004}, 
-interpreting NQA-1 in a manner similar to NEAMS \cite{neams_nuclear_2013} or 
-PyNE \cite{biondo_quality_2014}.
+interpreting \gls{NQA1} in a manner similar to the process adopted by the 
+\gls{DOE} within \gls{NEAMS} \cite{neams_nuclear_2013} or the 
+PyNE toolkit \cite{biondo_quality_2014}.
 
 Cyclus acknowledges that quality assurance is an on-going process throughout the 
-entire life of the code. As a simulator where most modeling descisions are made 
+entire life of the code. As a simulator where most modeling decisions are made 
 by third party archetype developers or users, the most important feature of QA 
-is verification. Validation may be impossible and UQ is beyond the scope.
+is verification. Validation may be impossible and \gls{UQ} is beyond the scope.
 
-Verification may be defined as the question, ``Is cyclus being built correctly?'' 
+Verification may be defined as the question, ``Is \Cyclus being built correctly?'' 
 To answer this question we turn to the software development of notions of testing,
 documentation, version control, style guidelines, and continuous integration. 
-This suite of process controls supplies mechanims for reliable and reproducible 
+This suite of process controls supplies mechanism for reliable and reproducible 
 software. The impetus to implement these correctly is even stronger in a scientific 
@@
 Validation on the other hand may be defined as the question, 
-``Is cyclus the correct tool?''
-Since cyclus is alone in its class as an agent-based fuel cycle simulator logitudnal 
+``Is \Cyclus the correct tool?''
+Since \Cyclus is alone in its class as an agent-based fuel cycle simulator, longitudinal 
 validation is not possible. Still code-to-code comparisons with fuel cycle
@@
 Lastly, uncertainty quantification is a process that is used on specific simulation
-instantiations to statistically determine its quality. Since the cyclus 
-kernel requires an input file written by the user, UQ is a process that applies 
-more to those running cyclus than to those running it.  Furthermore, any UQ
+instantiations to statistically determine its quality. Since the \Cyclus 
+kernel requires an input file written by the user, \gls{UQ} is a process that applies 
+more to those running \Cyclus than to those running it.  Furthermore, any 
+\gls{UQ}
 results that are generated are applicable only to the scenario that is under 
-analysis. Thus for cyclus UQ is well beyond the scope of core development.
+analysis. Thus for \Cyclus \gls{UQ} is well beyond the scope of core development.
 
 Sections \ref{sec:qa-testing}-\ref{sec:qa-ci} discuss in greater detail the software 
-development components that comprise the cyclus verification strategy.
+development components that comprise the \Cyclus verification strategy.
 Each of these on its own is a valuable addition to QA but is cannot be the 
-entire answer to the requirements imposed by NQA-1. Taken together and strictly 
-adhered to they present a fortress through which undeisrable code may siege, 
+entire answer to the requirements imposed by \gls{NQA1}. Taken together and strictly 
+adhered to they present a fortress through which undesirable code may siege, 
 but never take.
@@
 results of running software versus the expected behavior of the software.
-In cyclus, three categories of tests are defined: unit tests, integration 
+In \Cyclus, three categories of tests are defined: unit tests, integration 
 tests, and regression tests.
@@
 It is important to note that before a proposed
-code changes is allowed into main stream cyclus, all of the tests must pass
+code changes is allowed into main stream \Cyclus, all of the tests must pass
 and the change must be covered by a test, either new or existing. This is 
 matter of policy for the developers. Additionally, test code is equally likely 
-as the code it is testing to contain errors. To prevent an infinite recurrsion 
-of testing-the-tests, it is assumed that dilligence and one level of testing 
+as the code it is testing to contain errors. To prevent an infinite recursion 
+of testing-the-tests, it is assumed that diligence and one level of testing 
 is sufficient to meet the aims of the quality assurance.
@@
 Unit tests are those which compare the results of the smallest code \emph{unit}, 
-typically a single function or a class. What constitutes a the smallest code
+typically a single function or a class. What constitutes the smallest code
 unit depends on the context of the specific unit in question. While this is 
-an ambiquous defintiion, combined with a philosophy of keeping units as small
+an ambiguous definition, combined with a philosophy of keeping units as small
 as possible it is often clear in practice what needs to be tested.
@@
 Cyclus uses the Google Test framework \cite{inc_googletest_2008} as a harness for running unit 
-tests. Sufficient unit tests are required for any proposed change to the cyclus
-code base. Currently cyclus implements over 450 unit tests and cycamore has 
+tests. Sufficient unit tests are required for any proposed change to the \Cyclus
+code base. Currently \Cyclus implements over 450 unit tests and \Cycamore has 
 85.  These cover approximately 65\% of their respective code bases. This number 
@@
 
-Intergration tests are any tests that combine multiple elemnents of the 
-cyclus interface and test that they work correctly with each other.  By analogy, 
+Integration tests are any tests that combine multiple elements of the 
+\Cyclus interface and test that they work correctly with each other.  By analogy, 
 simply because the gears (units) are made correctly does not imply that the 
 clock (integration) will run smoothly, run at all, or give the correct time.
-In cyclus and cycamore, integration tests are performed by running sample
+In \Cyclus and \Cycamore, integration tests are performed by running sample
 simulations and verifying that results are what would be expected ahead of 
-time. Precanned input files have thus been contsructed. Their results 
+time. Pre-canned input files have thus been constructed. Their results 
 are inspected and compared via nose \cite{pellerin_nose_2007}, a Python test framework.
-Python will run cyclus as a subprocess for each integration test. In this
-way cyclus code units are tested in the full context that they will
+Python will run \Cyclus as a subprocess for each integration test. In this
+way \Cyclus code units are tested in the full context that they will
 executed. This category of testing is especially useful for ensuring that 
-major cyclus components are functioning as expected.
+major \Cyclus components are functioning as expected.
 
@@
 Regression tests are tests which ensure that significant changes do not 
-occur over the course of cyclus development. Such a change is called a 
+occur over the course of \Cyclus development. Such a change is called a 
 \emph{regression} because the new version is almost always wrong.
-Regression tests are implemeneted similarly to integration tests.
-Nose is used to execute fully fledged cyclus simulations whose results
+Regression tests are implemented similarly to integration tests.
+Nose is used to execute fully fledged \Cyclus simulations whose results
 are then compared. In this category however the comparison is done against 
-the output of the same input file when run with a previous version of cyclus, 
+the output of the same input file when run with a previous version of \Cyclus, 
 typically the last released version.
@@
 not appear elsewhere though they do not purport to make claims about the
-quality of the physics modeled. The cycamore project is the primary location of
+quality of the physics modeled. The \Cycamore project is the primary location of
 regression tests. This is because the archetypes here are sophisticated enough
@@
 
-All of the public interface (the API) must be documented as part of cyclus
+All of the public interface (the \gls{API}) must be documented as part of \Cyclus
 QA policy. This certifies that the intention for a code unit is communicated 
@@
 software should be doing comes from the author explicitly stating the 
-goals of an API in prose form. Furure development of the code is then able to 
-compare the implemetation versus the documentation to discern whether or not they 
+goals of an \gls{API} in prose form. Future development of the code is then able to 
+compare the implementation versus the documentation to discern whether or not they 
 are in agreement. Documentation is thus a secondary higher-level information 
-stream.  In cyclus, this information is aggregated together into static 
-websites with the doxygen \cite{van_heesch_doxygen:_2008} and sphinx 
+stream.  In \Cyclus, this information is aggregated together into static 
+websites with the Doxygen \cite{van_heesch_doxygen:_2008} and Sphinx 
 \cite{brandl_sphinx_2014} 
@@
 \cite{software_freedom_conservancy_git_2014}
-for this purpose. Git is currently the most popular utilty in the recent wave
+for this purpose. Git is currently the most popular utility in the recent wave
 of \emph{distributed version control}. Briefly stated, this means that every 
@@
 These are distinct pathways in the history that branch out of a mainline source
-tree and then may be \emph{merged} back into the mainline. Multiple simeltaneous
+tree and then may be \emph{merged} back into the mainline. Multiple simultaneous
 branches may exist at all point in time. Every change to the code is recorded
@@
 accompanying message. Thus 
-it is possible for cyclus to accurarely replay the entirety of who did what to the
+it is possible for \Cyclus to accurately replay the entirety of who did what to the
 code when.
@@
 branch (simply known as develop), and the stable branch (called master).
-In addition to these rules and delineation, cyclus also imposes rules on 
-when it is accecptable from a quality control standpoint to merge code from 
+In addition to these rules and delineation, \Cyclus also imposes rules on 
+when it is acceptable from a quality control standpoint to merge code from 
 the personal topical branches into develop. All software at this stage 
-must have sufficient and passing tests and reasonable documentation. Without
-these core pieces proposed changes are not allowed into cyclus.
+must have sufficient and passing tests and comprehensive documentation. Without
+these core pieces proposed changes are not allowed into \Cyclus. A schematic of 
+the development stages between reporting a bug and merging the fix is shown in 
+Figure \ref{fig:gitprocess}.
 
-The act of proposing a change is known as a \emph{pull request}. The main cyclus is 
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[height=0.6\textheight]{./images/gitprocess}
+\end{center}
+\caption{A version-control enabled process for finding, reporting, fixing a bug 
+can take place within an issue tracker alongside multiple stages of code 
+testing and review. In the \Cyclus case, the final review stage includes unit 
+and integration testing as well as manual code inspection.}
+\label{fig:gitprocess}
+\end{figure}
+
+The act of proposing a change is known as a \emph{pull request}. The main \Cyclus is 
 hosted remotely on the GitHub website \cite{dabbish_social_2012}. The online
-mechanism for pull requests allows for code review by a member of the cyclus 
+mechanism for pull requests allows for code review by a member of the \Cyclus 
 core team other than the author prior to any change being included. Non-members
-of the cyclus development team are allowed and encouraged to submit and review 
-pull requests. However, only members of the cyclus core team are allowed to 
-merge in any changes and only after the QA standards have been met.
+of the \Cyclus development team are allowed and encouraged to submit and review 
+pull requests. However, only members of the \Cyclus core team are allowed to 
+merge in any changes and only after the \gls{QA} standards have been met.
 
@@
 Google C++ Style Guide \cite{weinberger_google_2008} for all software contributions.
-This means that all developers of cyclus nominally write cyclus code in the same 
+This means that all developers of \Cyclus nominally write \Cyclus code in the same 
 way.  This homogenization may be a hurdle to new developers but ultimately 
@@
 as it is being developed, rather than as a final stage in a longer development 
-cycle.  Under CI every pull request is tested independently immeadiately after 
-it is proposed. Such tests shoudl be run on all officially supported platforms. 
+cycle.  Under CI every pull request is tested independently immediately after 
+it is proposed. Such tests should be run on all officially supported platforms. 
 Cyclus uses a CI platform called Polyphemus \cite{scopatz_polyphemus_2014}.
@@
 Polyphemus serves as an intermediary between GitHub pull requests on the frontend 
-and temporary cyclus servers on the backend. These servers are hosted by 
+and temporary \Cyclus servers on the backend. These servers are hosted by 
 the Build \& Test Laboratory (BaTLab) \cite{uw_batlab_team_batlab_2014} at the University of 
@@
 \begin{enumerate}
-    \item Copies cyclus with the pull requested code to BaTLab,
-    \item Initiliazes Linux and Mac OSX servers,
-    \item Builds cyclus on all platforms,
-    \item Runs the complete cyclus test suite, 
+    \item Copies \Cyclus with the pull requested code to BaTLab,
+    \item Initializes Linux and Mac OSX servers,
+    \item Builds \Cyclus on all platforms,
+    \item Runs the complete \Cyclus test suite, 
     \item Reports back whether the above steps succeeded or not.
@@
 Since these steps are performed for all incoming code, it is easy for the 
-cyclus core team to determine whether or not an indivudual pull request 
+\Cyclus core team to determine whether or not an individual pull request 
 actually works. This helps identify build and test problems prior to 
@@
 
-CI has become a neccessary but not sufficient addition to the cyclus QA
-system. Its merit is that it keeps bad code out. However, cyclus will always
+CI has become a necessary but not sufficient addition to the \Cyclus QA
+system. Its merit is that it keeps bad code out. However, \Cyclus will always
 require human eyes and human hands to let good code in.

### 2014-10-31 fundamentals/qa.tex
mostly including gls

@@
 
-Cyclus acknowledges that quality assurance is an on-going process throughout the 
+\Cyclus acknowledges that quality assurance is an on-going process throughout the 
 entire life of the code. As a simulator where most modeling decisions are made 
-by third party archetype developers or users, the most important feature of QA 
-is verification. Validation may be impossible and \gls{UQ} is beyond the scope.
+by third party archetype developers or users, the most important feature of 
+\gls{QA} is verification. Validation may be impossible and \gls{UQ} is beyond 
+he scope.
 
@@
 development components that comprise the \Cyclus verification strategy.
-Each of these on its own is a valuable addition to QA but is cannot be the 
+Each of these on its own is a valuable addition to \gls{QA} but is cannot be the 
 entire answer to the requirements imposed by \gls{NQA1}. Taken together and strictly 
@@
 simulator does or does not work as intended on a new system.
-Testing serves a critical role in QA because it directly compares the 
+Testing serves a critical role in \gls{QA} because it directly compares the 
 results of running software versus the expected behavior of the software.
@@
 All of the public interface (the \gls{API}) must be documented as part of \Cyclus
-QA policy. This certifies that the intention for a code unit is communicated 
+\gls{QA} policy. This certifies that the intention for a code unit is communicated 
 in way that is separate from its implementation. This policy is important 
@@
 
-CI has become a necessary but not sufficient addition to the \Cyclus QA
+CI has become a necessary but not sufficient addition to the \Cyclus \gls{QA}
 system. Its merit is that it keeps bad code out. However, \Cyclus will always

### 2014-10-31 fundamentals/qa.tex
mostly gls and \Cyclus

@@
 
-Cyclus uses the Google Test framework \cite{inc_googletest_2008} as a harness for running unit 
+\Cyclus uses the Google Test framework \cite{inc_googletest_2008} as a harness for running unit 
 tests. Sufficient unit tests are required for any proposed change to the \Cyclus
@@
 Version control is the history-preserving mechanism by which the provenance of 
-a code is recored. Cyclus uses a well-established tool called git 
+a code is recored. \Cyclus uses a well-established tool called git 
 \cite{software_freedom_conservancy_git_2014}
@@
 
-Cyclus uses a strategy known as \emph{git flow} 
+\Cyclus uses a strategy known as \emph{git flow} 
 \cite{kalliamvakou_code-centric_2014} 
@@
 coding style guides are the software analogy to the natural language ones, 
-such as the Chicago Manual of Style. Cyclus strictly enforces the use of the 
+such as the Chicago Manual of Style. \Cyclus strictly enforces the use of the 
 Google C++ Style Guide \cite{weinberger_google_2008} for all software contributions.
@@
 
-Continuous integration (CI) the idea that software should be tested and validated 
+\emph{\acrfull{CI}} the idea that software should be tested and validated 
 as it is being developed, rather than as a final stage in a longer development 
-cycle.  Under CI every pull request is tested independently immediately after 
+cycle.  Under \gls{CI} every pull request is tested independently immediately after 
 it is proposed. Such tests should be run on all officially supported platforms. 
-Cyclus uses a CI platform called Polyphemus \cite{scopatz_polyphemus_2014}.
+\Cyclus uses a \gls{CI} platform called Polyphemus \cite{scopatz_polyphemus_2014}.
 

### 2014-10-31 fundamentals/qa.tex
commas

@@
 Python will run \Cyclus as a subprocess for each integration test. In this
-way \Cyclus code units are tested in the full context that they will
+way, \Cyclus code units are tested in the full context that they will
 executed. This category of testing is especially useful for ensuring that 
@@
 Nose is used to execute fully fledged \Cyclus simulations whose results
-are then compared. In this category however the comparison is done against 
+are then compared. In this category, however, the comparison is done against 
 the output of the same input file when run with a previous version of \Cyclus, 

### 2014-10-31 fundamentals/acros.tex
added neams
adds CI
misspelled some acros

@@
-\newacronym{MIT}{MIT}{the Massachusettes Institute of Technology}
+\newacronym{MIT}{MIT}{the Massachusetts Institute of Technology}
 \newacronym{UW}{UW}{University of Wisconsin}
@@
 \newacronym{GDSM}{GDSM}{Generic Disposal System Model}
-\newacronym{GDSE}{GDSE}{Generic Disposal Sytem Environment}
-\newacronym{GPAM}{GPAM}{Generic Performance Asessment Model}
+\newacronym{GDSE}{GDSE}{Generic Disposal System Environment}
+\newacronym{GPAM}{GPAM}{Generic Performance Assessment Model}
 \newacronym{FEPs}{FEPs}{Features, Events, and Processes}
@@
 \newacronym{NWTRB}{NWTRB}{Nuclear Waste Technical Review Board}
-\newacronym{OCRWM}{OCRWM}{Office of Civillian Radioactive Waste Management}
+\newacronym{OCRWM}{OCRWM}{Office of Civilian Radioactive Waste Management}
 \newacronym{UFD}{UFD}{Used Fuel Disposition}
@@
 \newacronym{GUI}{GUI}{Graphical User Interface}
-\newacronym{HPC}{HPC}{High-Performace Computing}
+\newacronym{HPC}{HPC}{High-Performance Computing}
 \newacronym{HTC}{HTC}{High-Throughput Computing}
@@
 \newacronym{NQA1}{NQA-1}{Nuclear Quality Assurance - 1}
-\newacronym{VV}{V\&V}{Verificaion and Validation}
+\newacronym{VV}{V\&V}{Verification and Validation}
 \newacronym{UQ}{UQ}{Uncertainty Quantification}
 \newacronym{ASME}{ASME}{American Society of Mechanical Engineers}
+\newacronym{NEAMS}{NEAMS}{Nuclear Engineering Advanced Modeling and Simulation}
+\newacronym{CI}{CI}{Continuous Integration}
 %\newacronym{<++>}{<++>}{<++>}

### 2014-11-02 fundamentals/conclusion.tex

@@
 the ecosystem are insufficient, adding custom functionality is simplified by a 
-modular, plug-in architcture. A clean, modern \acrlong{API} simplifies 
+modular, plug-in architecture. A clean, modern \gls{API} simplifies 
 customization and independent archetype development so that researchers can 

### 2014-11-02 fundamentals/examples.tex
adds acros

@@
 Results of some simple recycle scenarios run in \Cyclus follow.  In \Cyclus,
-because material is tracked as discrete objects, single-pass MOX recycle is
+because material is tracked as discrete objects, single-pass \gls{MOX} 
+recycle is
 easy to implement.  The simulation initially included one provider of fresh
-UOX fuel, one recycled fuel fabrication facility, one reactor, one separations
+\gls{UOX} fuel, one recycled fuel fabrication facility, one reactor, one separations
 facility, and one repository. The simulation duration was set to 1100 months.
@@
 commodity.  The dynamic resource exchange makes it easy for a reactor to
-preferentially accept recycled MOX fuel over fresh UOX fuel.  The
+preferrentially accept recycled \gls{MOX} fuel over fresh \gls{UOX} fuel.  The
 \Class{BatchReactor} was configured to run with a 3 batch core on 18 month cycles and
@@
 
-Simply changing the output commodity name of spent \gls{MOX} fuel from the 
-\Class{BatchReactor} transforms this simulation into a closed fuel cycle. Only 
-a one-word change in the input file:
+To switch to a fully closed fuel cycle, all that needs to be done is change
+the output commodity for the \Class{BatchReactor}'s spent \gls{MOX} fuel.  All this
+requires is a one-word change in the input file:
 

### 2014-11-02 fundamentals/qa.tex
regression

--- 2014-10-31 fundamentals/qa.tex
@@
 been invented over the years to mitigate the structural and algorithmic errors
-on the part of simulators themselves. These include \emph{\gls{VV}}
-\cite{boehm_software_1989}, \emph{\gls{UQ}} 
-\cite{sacks_design_1989}, testing, and others. \gls{VV} and \gls{UQ} come from 
+on the part of simulators themselves. These include \emph{verification and validation}
+(V\&V) \cite{boehm_software_1989}, \emph{uncertainty quantification} (UQ) 
+\cite{sacks_design_1989}, testing, and others. V\&V and UQ come from 
 a distinctly computational science background while testing \emph{et al.} come from 
@@
 
-Nuclear engineering code quality is often governed by \gls{NQA1}, an 
-\gls{ASME} specification 
+Nuclear enginerering code quality is often governed by NQA-1, an ASME specification 
 whose latest revision appeared in 2009 \cite{asme_nqa-1a-2009_2009}. This is primarily 
 used for designing reactors. However, it is general enough to apply to 
-\Cyclus. \Cyclus has adopted an \emph{agile} development process 
+cyclus. Cyclus has adopted an \emph{agile} development process 
 \cite{larman_agile_2004}, 
-interpreting \gls{NQA1} in a manner similar to the process adopted by the 
-\gls{DOE} within \gls{NEAMS} \cite{neams_nuclear_2013} or the 
-PyNE toolkit \cite{biondo_quality_2014}.
+interpreting NQA-1 in a manner similar to NEAMS \cite{neams_nuclear_2013} or 
+PyNE \cite{biondo_quality_2014}.
 
-\Cyclus acknowledges that quality assurance is an on-going process throughout the 
-entire life of the code. As a simulator where most modeling decisions are made 
-by third party archetype developers or users, the most important feature of 
-\gls{QA} is verification. Validation may be impossible and \gls{UQ} is beyond 
-he scope.
+Cyclus acknowledges that quality assurance is an on-going process throughout the 
+entire life of the code. As a simulator where most modeling descisions are made 
+by third party archetype developers or users, the most important feature of QA 
+is verification. Validation may be impossible and UQ is beyond the scope.
 
-Verification may be defined as the question, ``Is \Cyclus being built correctly?'' 
+Verification may be defined as the question, ``Is cyclus being built correctly?'' 
 To answer this question we turn to the software development of notions of testing,
 documentation, version control, style guidelines, and continuous integration. 
-This suite of process controls supplies mechanism for reliable and reproducible 
+This suite of process controls supplies mechanims for reliable and reproducible 
 software. The impetus to implement these correctly is even stronger in a scientific 
@@
 Validation on the other hand may be defined as the question, 
-``Is \Cyclus the correct tool?''
-Since \Cyclus is alone in its class as an agent-based fuel cycle simulator, longitudinal 
+``Is cyclus the correct tool?''
+Since cyclus is alone in its class as an agent-based fuel cycle simulator logitudnal 
 validation is not possible. Still code-to-code comparisons with fuel cycle
@@
 Lastly, uncertainty quantification is a process that is used on specific simulation
-instantiations to statistically determine its quality. Since the \Cyclus 
-kernel requires an input file written by the user, \gls{UQ} is a process that applies 
-more to those running \Cyclus than to those running it.  Furthermore, any 
-\gls{UQ}
+instantiations to statistically determine its quality. Since the cyclus 
+kernel requires an input file written by the user, UQ is a process that applies 
+more to those running cyclus than to those running it.  Furthermore, any UQ
 results that are generated are applicable only to the scenario that is under 
-analysis. Thus for \Cyclus \gls{UQ} is well beyond the scope of core development.
+analysis. Thus for cyclus UQ is well beyond the scope of core development.
 
 Sections \ref{sec:qa-testing}-\ref{sec:qa-ci} discuss in greater detail the software 
-development components that comprise the \Cyclus verification strategy.
-Each of these on its own is a valuable addition to \gls{QA} but is cannot be the 
-entire answer to the requirements imposed by \gls{NQA1}. Taken together and strictly 
-adhered to they present a fortress through which undesirable code may siege, 
+development components that comprise the cyclus verification strategy.
+Each of these on its own is a valuable addition to QA but is cannot be the 
+entire answer to the requirements imposed by NQA-1. Taken together and strictly 
+adhered to they present a fortress through which undeisrable code may siege, 
 but never take.
@@
 simulator does or does not work as intended on a new system.
-Testing serves a critical role in \gls{QA} because it directly compares the 
+Testing serves a critical role in QA because it directly compares the 
 results of running software versus the expected behavior of the software.
-In \Cyclus, three categories of tests are defined: unit tests, integration 
+In cyclus, three categories of tests are defined: unit tests, integration 
 tests, and regression tests.
@@
 It is important to note that before a proposed
-code changes is allowed into main stream \Cyclus, all of the tests must pass
-and the change must be covered by a test, either new or existing. This is 
+code change is allowed into mainline cyclus, all of the tests must pass
+and the change must be covered by a test, either new or existing. This is a
 matter of policy for the developers. Additionally, test code is equally likely 
-as the code it is testing to contain errors. To prevent an infinite recursion 
-of testing-the-tests, it is assumed that diligence and one level of testing 
+as the code it is testing to contain errors. To prevent an infinite recurrsion 
+of testing-the-tests, it is assumed that dilligence and one level of testing 
 is sufficient to meet the aims of the quality assurance.
@@
 Unit tests are those which compare the results of the smallest code \emph{unit}, 
-typically a single function or a class. What constitutes the smallest code
+typically a single function or a class. What constitutes a the smallest code
 unit depends on the context of the specific unit in question. While this is 
-an ambiguous definition, combined with a philosophy of keeping units as small
+an ambiquous defintiion, combined with a philosophy of keeping units as small
 as possible it is often clear in practice what needs to be tested.
@@
 Cyclus uses the Google Test framework \cite{inc_googletest_2008} as a harness for running unit 
-tests. Sufficient unit tests are required for any proposed change to the \Cyclus
-code base. Currently \Cyclus implements over 450 unit tests and \Cycamore has 
+tests. Sufficient unit tests are required for any proposed change to the cyclus
+code base. Currently cyclus implements over 450 unit tests and cycamore has 
 85.  These cover approximately 65\% of their respective code bases. This number 
@@
 
-Integration tests are any tests that combine multiple elements of the 
-\Cyclus interface and test that they work correctly with each other.  By analogy, 
+Intergration tests are any tests that combine multiple elements of the 
+cyclus interface and test that they work correctly with each other.  By analogy, 
 simply because the gears (units) are made correctly does not imply that the 
 clock (integration) will run smoothly, run at all, or give the correct time.
-In \Cyclus and \Cycamore, integration tests are performed by running sample
+In cyclus and cycamore, integration tests are performed by running sample
 simulations and verifying that results are what would be expected ahead of 
-time. Pre-canned input files have thus been constructed. Their results 
+time. Precanned input files have thus been contsructed. Their results 
 are inspected and compared via nose \cite{pellerin_nose_2007}, a Python test framework.
-Python will run \Cyclus as a subprocess for each integration test. In this
-way \Cyclus code units are tested in the full context that they will
+Python will run cyclus as a subprocess for each integration test. In this
+way cyclus code units are tested in the full context that they will be
 executed. This category of testing is especially useful for ensuring that 
-major \Cyclus components are functioning as expected.
+major cyclus components are functioning as expected.
 
@@
 Regression tests are tests which ensure that significant changes do not 
-occur over the course of \Cyclus development. Such a change is called a 
-\emph{regression} because the new version is almost always wrong.
-Regression tests are implemented similarly to integration tests.
-Nose is used to execute fully fledged \Cyclus simulations whose results
+occur over the course of cyclus development. Such a change is called a 
+\emph{regression} because the new version is almost always wrong version in the 
+event of a difference.
+Regression tests are implemeneted similarly to integration tests.
+Nose is used to execute fully fledged cyclus simulations whose results
 are then compared. In this category however the comparison is done against 
-the output of the same input file when run with a previous version of \Cyclus, 
+the output of the same input file when run with a previous version of cyclus, 
 typically the last released version.
@@
 not appear elsewhere though they do not purport to make claims about the
-quality of the physics modeled. The \Cycamore project is the primary location of
+quality of the physics modeled. The cycamore project is the primary location of
 regression tests. This is because the archetypes here are sophisticated enough
@@
 
-All of the public interface (the \gls{API}) must be documented as part of \Cyclus
-\gls{QA} policy. This certifies that the intention for a code unit is communicated 
+All of the public interfaces must be documented as part of cyclus
+QA policy. This certifies that the intention for a code unit is communicated 
 in way that is separate from its implementation. This policy is important 
-because implementations are often wrong, hence bugs. They are thus unreliable 
+because implementations are often wrong. Software implementations are unreliable 
 resources about themselves. Truly trustworthy communication about what 
 software should be doing comes from the author explicitly stating the 
-goals of an \gls{API} in prose form. Future development of the code is then able to 
-compare the implementation versus the documentation to discern whether or not they 
+goals of an API in prose form. Furure development of the code is then able to 
+compare the implemetation versus the documentation to discern whether or not they 
 are in agreement. Documentation is thus a secondary higher-level information 
-stream.  In \Cyclus, this information is aggregated together into static 
-websites with the Doxygen \cite{van_heesch_doxygen:_2008} and Sphinx 
+source.  In cyclus, this information is aggregated together into static 
+websites with the doxygen \cite{van_heesch_doxygen:_2008} and sphinx 
 \cite{brandl_sphinx_2014} 
@@
 \cite{software_freedom_conservancy_git_2014}
-for this purpose. Git is currently the most popular utility in the recent wave
+for this purpose. Git is currently the most popular utilty in the recent wave
 of \emph{distributed version control}. Briefly stated, this means that every 
@@
 These are distinct pathways in the history that branch out of a mainline source
-tree and then may be \emph{merged} back into the mainline. Multiple simultaneous
-branches may exist at all point in time. Every change to the code is recorded
+tree and then may be \emph{merged} back into the mainline. Multiple simeltaneous
+branches may exist at all points in time. Every change to the code is recorded
 in the history, along with metadata such as the author, a timestamp, and an 
 accompanying message. Thus 
-it is possible for \Cyclus to accurately replay the entirety of who did what to the
+it is possible for cyclus to accurarely replay the entirety of who did what to the
 code when.
@@
 branch (simply known as develop), and the stable branch (called master).
-In addition to these rules and delineation, \Cyclus also imposes rules on 
-when it is acceptable from a quality control standpoint to merge code from 
+In addition to these rules and delineation, cyclus also imposes rules on 
+when it is accecptable from a quality control standpoint to merge code from 
 the personal topical branches into develop. All software at this stage 
-must have sufficient and passing tests and comprehensive documentation. Without
-these core pieces proposed changes are not allowed into \Cyclus. A schematic of 
-the development stages between reporting a bug and merging the fix is shown in 
-Figure \ref{fig:gitprocess}.
+must have sufficient and passing tests and reasonable documentation. Without
+these core pieces, proposed changes are not allowed into cyclus.
 
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[height=0.6\textheight]{./images/gitprocess}
-\end{center}
-\caption{A version-control enabled process for finding, reporting, fixing a bug 
-can take place within an issue tracker alongside multiple stages of code 
-testing and review. In the \Cyclus case, the final review stage includes unit 
-and integration testing as well as manual code inspection.}
-\label{fig:gitprocess}
-\end{figure}
-
-The act of proposing a change is known as a \emph{pull request}. The main \Cyclus is 
+The act of proposing a change is known as a \emph{pull request}. The main cyclus is 
 hosted remotely on the GitHub website \cite{dabbish_social_2012}. The online
-mechanism for pull requests allows for code review by a member of the \Cyclus 
+mechanism for pull requests allows for code review by a member of the cyclus 
 core team other than the author prior to any change being included. Non-members
-of the \Cyclus development team are allowed and encouraged to submit and review 
-pull requests. However, only members of the \Cyclus core team are allowed to 
-merge in any changes and only after the \gls{QA} standards have been met.
+of the cyclus development team are allowed and encouraged to submit and review 
+pull requests. However, only members of the cyclus core team are allowed to 
+merge in any changes and only after the QA standards have been met.
 
@@
 Google C++ Style Guide \cite{weinberger_google_2008} for all software contributions.
-This means that all developers of \Cyclus nominally write \Cyclus code in the same 
+This means that all developers of cyclus nominally write cyclus code in the same 
 way.  This homogenization may be a hurdle to new developers but ultimately 
@@
 
-Continuous integration (CI) the idea that software should be tested and validated 
+\gls{CI} is the idea that software should be tested and validated 
 as it is being developed, rather than as a final stage in a longer development 
-cycle.  Under CI every pull request is tested independently immediately after 
-it is proposed. Such tests should be run on all officially supported platforms. 
-Cyclus uses a CI platform called Polyphemus \cite{scopatz_polyphemus_2014}.
+cycle.  Under \gls{CI} every pull request is tested independently immeadiately after 
+it is proposed. Such tests shoudl be run on all officially supported platforms. 
+Cyclus uses a \gls{CI} platform called Polyphemus \cite{scopatz_polyphemus_2014}.
 
 Polyphemus serves as an intermediary between GitHub pull requests on the frontend 
-and temporary \Cyclus servers on the backend. These servers are hosted by 
+and temporary cyclus servers on the backend. These servers are hosted by 
 the Build \& Test Laboratory (BaTLab) \cite{uw_batlab_team_batlab_2014} at the University of 
@@
 \begin{enumerate}
-    \item Copies \Cyclus with the pull requested code to BaTLab,
-    \item Initializes Linux and Mac OSX servers,
-    \item Builds \Cyclus on all platforms,
-    \item Runs the complete \Cyclus test suite, 
+    \item Copies cyclus with the pull requested code to BaTLab,
+    \item Initiliazes Linux and Mac OSX servers,
+    \item Builds cyclus on all platforms,
+    \item Runs the complete cyclus test suite, 
     \item Reports back whether the above steps succeeded or not.
@@
 Since these steps are performed for all incoming code, it is easy for the 
-\Cyclus core team to determine whether or not an individual pull request 
+cyclus core team to determine whether or not an indivudual pull request 
 actually works. This helps identify build and test problems prior to 
@@
 
-CI has become a necessary but not sufficient addition to the \Cyclus \gls{QA}
-system. Its merit is that it keeps bad code out. However, \Cyclus will always
+\gls{CI} has become a neccessary but not sufficient addition to the cyclus QA
+system. Its merit is that it keeps bad code out. However, cyclus will always
 require human eyes and human hands to let good code in.

### 2014-11-02 fundamentals/intro.tex

@@
 ``reinvent the wheel'' by developing tools of their own from scratch and 
-tailored to their own needs (e.g., \gls{CAFCA}\cite{guerin_impact_2009} and 
-\gls{COSI}\cite{boucher_cosi_2005,boucher_cosi:_2006,meyer_new_2009,coquelet-pascal_comparison_2011}, respectively).
+tailored to their own needs, for example \gls{CAFCA}\cite{guerin_impact_2009} and 
+\gls{COSI}\cite{boucher_cosi_2005,boucher_cosi:_2006,meyer_new_2009,coquelet-pascal_comparison_2011} respectively.
 
@@
 
+\Cyclus implements an \gls{ABM} paradigm.  \gls{ABM} is modern, sophisticated, 
+true to reality, and it takes advantage of modern computing resources.  
+Furthermore, agent-based modeling provides an analyst a more natural 
 \Cyclus utilizes an \gls{ABM} paradigm.  \gls{ABM} is modern, sophisticated, 

### 2014-11-02 fundamentals/qa.tex
fixes #52

@@
 Lastly, uncertainty quantification is a process that is used on specific simulation
-instantiations to statistically determine its quality. Since the cyclus 
+instantiations to statistically determine its quality. Since the \Cyclus 
 kernel requires an input file written by the user, UQ is a process that applies 
-more to those running cyclus than to those running it.  Furthermore, any UQ
-results that are generated are applicable only to the scenario that is under 
-analysis. Thus for cyclus UQ is well beyond the scope of core development.
+to the running of many \Cyclus simulations. The kernel itself, as a generic fuel cycle 
+simulator, cannot make reliable statements about the uncertainty of a particular fuel 
+cycle. Any UQ results are applicable only to the scenario that is under 
+analysis. \Cyclus is not a panacea for due dillegence on behalf of the fuel 
+cycle modeler. Thus, UQ is envisioned to be beyond the scope of core development 
+and in the domain of the expert user.
 

### 2014-11-02 fundamentals/intro.tex

@@
 simulator. Dynamic simulation of nuclear fuel cycles with discrete agents 
-and per nuclide species resolution support 
+and per-nuclide species resolution support 
 levels of detail appropriate for a varied community of analysts

### 2014-11-02 fundamentals/examples.tex
minor revisions

--- 2014-10-31 fundamentals/examples.tex
@@
 ecosystem at multiple institutions indicates that a fuel cycle simulator can 
-advance in a community-drive development paradigm. Additionally, simple 
+advance in a community-driven development paradigm. Simple 
 simulations as well as more complex recycling simulations demonstrate that 
@@
 \end{itemize}
-All together, these form an `ecosystem' of capabilities. Over time, this 
-ecosystem will grow as archetype-developers, kernel-developers, and 
+All together, these form an `ecosystem' of capabilities, 
+which will grow over time as archetype-developers, kernel-developers, and 
 even users contribute capabilities developed for their own needs. Indeed, the 
@@
 the ecosystem demonstrate a significant achievement by the \Cyclus framework 
-and provide hope for a community-driven development model.
+and initiated community-driven development.
 
@@
 A number of projects and tools outside of the core simulation kernel have been 
-developed which improve the scope and the diversity of the capabilities in the \Cyclus 
+developed to improve the scope and capabilities of the \Cyclus 
 ecosystem. Table \ref{tab:coretools} lists the tools and projects developed 
@@
 \end{tabularx}
-\caption{A diverse set of archetypes under development reflect the diverse 
+\caption{The range of  archetypes under development reflect the diverse 
 needs of researchers at various institutions. These archetypes, contributed 
@@
 
-Results of some simple recycle scenarios run in \Cyclus follow.  In \Cyclus,
+Results of some simple recycle scenarios simulated via \Cyclus follow.  In \Cyclus,
 because material is tracked as discrete objects, single-pass MOX recycle is
-easy to implement.  The simulation initially included one provider of fresh
-UOX fuel, one recycled fuel fabrication facility, one reactor, one separations
-facility, and one repository. The simulation duration was set to 1100 months.
+easy to implement.  The simulation duration was 1100 months and included one
+of each of the following: fresh
+UOX fuel fabrication, recycled MOX fuel fabrication, reactor, separations
+facility, and repository.
 
-The \Class{BatchReactor} archetype from \Cycamore has the ability to accept
-fuel materials from an arbitrary number of different sources delineated by
-commodity. Custom, non-uniform preferences can be set for each different fuel
-commodity.  The dynamic resource exchange makes it easy for a reactor to
+The \Class{BatchReactor} archetype from \Cycamore accepts
+fuel materials from an arbitrary number of sources delineated by
+commodity. Custom, non-uniform preferences can be set for each fuel
+commodity.  The \gls{DRE} enables reactors to
 preferentially accept recycled MOX fuel over fresh UOX fuel.  The
-\Class{BatchReactor} was configured to run with a 3 batch core on 18 month cycles and
-a 2-month refueling period.  Adjusting and setting parameters such as these is
-as simple as editing numbers in an input file such as:
+\Class{BatchReactor} was configured with a 3-batch core on 18-month cycles and
+a 2-month refueling period.  Adjusting and setting parameters such as these
+simply requires editing input file numbers, as shown below:
 
@@
 
-The \Class{Source} and \Class{Sink} modules from \Cycamore were also used as a
-source of fresh, enriched uranium and a repository respectively. A simple
-custom recycled fuel fabrication facility was used.  This fabrication facility
-mixes fissile and fertile streams to match target fuel compositions as closely
-as possible.  The method used for this matching is approximately the same as
+The \Class{Source} and \Class{Sink} modules from \Cycamore were chosen to be a
+source of fresh, enriched uranium and a repository, respectively. The simple
+recycled fuel fabrication facility was designed to
+mix fissile and fertile streams to match target fuel compositions as closely
+as possible.  The method used for this matching is similar to
 that used by the \gls{COSI} fuel cycle simulator \TODO{cite COSI equivalence
-method}. The material flows for this simulation are shown below in figure
+method}. The material flows for this simulation are shown below in Figure
 \ref{fig:flowmodopen}.
@@
 \begin{figure}[H]
-\label{fig:flowmodopen}
-\caption{Modified open 1-pass MOX recycle fuel cycle material flows.}
 \begin{center}
@@
 \end{center}
+\caption{Modified open 1-pass MOX recycle fuel cycle material flows.}
+\label{fig:flowmodopen}
 \end{figure}
 
-Simply changing the output commodity name of spent \gls{MOX} fuel from the 
-\Class{BatchReactor} transforms this simulation into a closed fuel cycle. Only 
-a one-word change in the input file:
+Simply changing the output commodity name of spent MOX fuel from the 
+\Class{BatchReactor} transforms this simulation into a closed fuel cycle.
+The one-word change in the input file is shown below:
 
@@
 
-This results in new the material flows in Figure \ref{fig:flowclosed}. Note
+This new simulation results in the material flows seen in Figure \ref{fig:flowclosed}. Note
 that because the \Class{BatchReactor} always transmutes fuel into the same
-composition, the nuclide level flows are not very realistic for the full, 
+composition, the nuclide level flows are not accurate for the full, 
 multi-pass
@@
 \begin{figure}[H]
-\label{fig:flowclosed}
-\caption{Full MOX recycle (multi-pass) fuel cycle material flows.}
 \begin{center}
@@
 \end{center}
+\caption{Full MOX recycle (multi-pass) fuel cycle material flows.}
+\label{fig:flowclosed}
 \end{figure}
@@
 (no recycle), modified open, and closed (infinite-pass recycle) variations of
-the scenario described above (all just a single reactor).  The figure was
+the single-reactor scenario described above.  The figure was
 generated directly from \Cyclus output data. After several batch cycles (near
-month 300) in the modified open and closed cases, enough separated fissile
+month 300) in both the modified open and closed cases, enough separated fissile
 material accumulates in the fuel fabrication facility to generate a full
@@
 modified open case and every 9 cycles (180 months) for the closed case.
-Because the modified open scenario does not re-recycle material, it takes the
-fabrication facility 1 cycle longer to accumulate a full batch worth of
+Because the modified open scenario does not re-recycle material, the
+fabrication facility takes 1 additional cycle to accumulate a full batch of
 fissile material.  Because facilities are represented individually and
-transact discrete materials as discrete events, realistic non-uniform patterns
-in facility behavior can be observed affecting total system behavior in ways
-that are less commonly observed in fleet-based, continuous material flow
+transact materials as discrete events, realistic non-uniform patterns
+in facility behavior can be observed that affect total system behavior in ways
+less commonly observed in fleet-based, continuous material flow
 modeling.
@@
 \begin{figure}[H]
-\label{fig:puseries1}
-\caption{System plutonium buildup with one reactor.}
 \begin{center}
@@
 \end{center}
+\caption{System plutonium buildup with one reactor.}
+\label{fig:puseries1}
 \end{figure}
 
-The open, modified open, and closed scenarios can easily be modified to have
-several reactors each with staggered refueling times.  As the number of
-reactors increases, the behavior of the system approaches a more steady
-average reminiscent of continuous material flow models.  The plutonium buildup
+The open, modified open, and closed scenarios can easily be configured to
+stagger the refueling times of the reactors.  As the number of
+reactors increases, the behavior of the system approaches an average behavior,
+reminiscent of continuous material flow models.  The plutonium buildup
 for these three multi-reactor variations is shown in Figure
@@
 \begin{figure}[H]
-\label{fig:puseriesn}
-\caption{System plutonium buildup with staggered refueling for many reactors.}
 \begin{center}
@@
 \end{center}
+\caption{System plutonium buildup with staggered refueling for many reactors.}
+\label{fig:puseriesn}
 \end{figure}

### 2014-11-02 fundamentals/impl.tex
minor revisions

@@
 the minimal set of capabilities needed to implement an agent-based simulation
-with dynamic resource exchange, a toolkit is provided that assists developers
+with \gls{DRE}, a toolkit is provided that assists developers
 and users with related simulation and nuclear engineering tasks. The toolkit is

### 2014-11-02 fundamentals/qa.tex
minor revisions

--- 2014-11-02 fundamentals/qa.tex
@@
 been invented over the years to mitigate the structural and algorithmic errors
-on the part of simulators themselves. These include \emph{verification and validation}
-(V\&V) \cite{boehm_software_1989}, \emph{uncertainty quantification} (UQ) 
-\cite{sacks_design_1989}, testing, and others. V\&V and UQ come from 
-a distinctly computational science background while testing \emph{et al.} come from 
-a software development bent.
+on the part of simulators themselves. These include \emph{\gls{VV}}
+\cite{boehm_software_1989}, \emph{\gls{UQ}} 
+\cite{sacks_design_1989}, testing, and others. \gls{VV} and \gls{UQ} derive from 
+a distinctly computational science background while testing \emph{et al.}
+proceed from a software development bent.
 
@@
 used for designing reactors. However, it is general enough to apply to 
-cyclus. Cyclus has adopted an \emph{agile} development process 
+\Cyclus. \Cyclus has adopted an \emph{agile} development process 
 \cite{larman_agile_2004}, 
@@
 
-Cyclus acknowledges that quality assurance is an on-going process throughout the 
+\Cyclus acknowledges that quality assurance is an on-going process throughout the 
 entire life of the code. As a simulator where most modeling descisions are made 
-by third party archetype developers or users, the most important feature of QA 
-is verification. Validation may be impossible and UQ is beyond the scope.
+by third party archetype developers or users, the most important feature of
+\gls{QA} 
+is verification. Validation may be impossible and \gls{UQ} is beyond the scope.
 
-Verification may be defined as the question, ``Is cyclus being built correctly?'' 
-To answer this question we turn to the software development of notions of testing,
+Verification may be defined as the question, ``Is \Cyclus being built correctly?'' 
+This question can be answered by the software development of notions of testing,
 documentation, version control, style guidelines, and continuous integration. 
-This suite of process controls supplies mechanims for reliable and reproducible 
+This suite of process controls supplies mechanisms for reliable and reproducible 
 software. The impetus to implement these correctly is even stronger in a scientific 
@@
 Validation on the other hand may be defined as the question, 
-``Is cyclus the correct tool?''
-Since cyclus is alone in its class as an agent-based fuel cycle simulator logitudnal 
+``Is \Cyclus the correct tool?''
+Since \Cyclus is alone in its class as an agent-based fuel cycle simulator longitudnal 
 validation is not possible. Still code-to-code comparisons with fuel cycle
@@
 It is important to note that before a proposed
-code change is allowed into mainline cyclus, all of the tests must pass
-and the change must be covered by a test, either new or existing. This is a
+code changes is allowed into main stream cyclus, all of the tests must pass
+and the change must be covered by a test, either new or existing. This is 
 matter of policy for the developers. Additionally, test code is equally likely 
@@
 
-Intergration tests are any tests that combine multiple elements of the 
+Intergration tests are any tests that combine multiple elemnents of the 
 cyclus interface and test that they work correctly with each other.  By analogy, 
@@
 Python will run cyclus as a subprocess for each integration test. In this
-way cyclus code units are tested in the full context that they will be
+way cyclus code units are tested in the full context that they will
 executed. This category of testing is especially useful for ensuring that 
@@
 occur over the course of cyclus development. Such a change is called a 
-\emph{regression} because the new version is almost always wrong version in the 
-event of a difference.
+\emph{regression} because the new version is almost always wrong.
 Regression tests are implemeneted similarly to integration tests.
@@
 
-All of the public interfaces must be documented as part of cyclus
+All of the public interface (the API) must be documented as part of cyclus
 QA policy. This certifies that the intention for a code unit is communicated 
 in way that is separate from its implementation. This policy is important 
-because implementations are often wrong. Software implementations are unreliable 
+because implementations are often wrong, hence bugs. They are thus unreliable 
 resources about themselves. Truly trustworthy communication about what 
@@
 are in agreement. Documentation is thus a secondary higher-level information 
-source.  In cyclus, this information is aggregated together into static 
+stream.  In cyclus, this information is aggregated together into static 
 websites with the doxygen \cite{van_heesch_doxygen:_2008} and sphinx 
@@
 tree and then may be \emph{merged} back into the mainline. Multiple simeltaneous
-branches may exist at all points in time. Every change to the code is recorded
+branches may exist at all point in time. Every change to the code is recorded
 in the history, along with metadata such as the author, a timestamp, and an 
@@
 must have sufficient and passing tests and reasonable documentation. Without
-these core pieces, proposed changes are not allowed into cyclus.
+these core pieces proposed changes are not allowed into cyclus.
 
@@
 
-\gls{CI} is the idea that software should be tested and validated 
+Continuous integration (CI) the idea that software should be tested and validated 
 as it is being developed, rather than as a final stage in a longer development 
-cycle.  Under \gls{CI} every pull request is tested independently immeadiately after 
+cycle.  Under CI every pull request is tested independently immeadiately after 
 it is proposed. Such tests shoudl be run on all officially supported platforms. 
-Cyclus uses a \gls{CI} platform called Polyphemus \cite{scopatz_polyphemus_2014}.
+Cyclus uses a CI platform called Polyphemus \cite{scopatz_polyphemus_2014}.
 
@@
 
-\gls{CI} has become a neccessary but not sufficient addition to the cyclus QA
+CI has become a neccessary but not sufficient addition to the cyclus QA
 system. Its merit is that it keeps bad code out. However, cyclus will always

### 2014-11-02 fundamentals/impl.tex

@@
 
-A modular, agent-based simulator is an ideal approach for solving complex, coupled,
+A modular, agent-based approach is ideal for solving complex, coupled,
 physics-dependent supply chain problems involving material routing, facility
@@
 
-Dynamically loadable libraries are the primary mechanism for extending \Cyclus' capability. 
-This approach provides encapsulation: the core of the code operates
+Dynamically-loadable libraries are the primary mechanism for extending \Cyclus' capability. 
+This approach provides encapsulation. The core of the code operates
 completely independently from the individual plugin libraries. Thus, any
@@
 archetype libraries.  The 
-scientist-developer can focus on generating an archetype model within their
-sphere of expertise, while relying on the contributions of others to furnish
-the other technologies in the simulation.  This strategy also allows individual developers to
+researcher can focus on generating an archetype model within their
+sphere of expertise, while relying on the contributions of others to fill 
+in the other technologies in the simulation.  This strategy also allows individual developers to
 explore different levels of complexity within their archetypes, including
@@
 format. It shows how the \Class{Agent} interface
-provides a notion of parent-child hierarchical relationship, where parents can
-choose to \textit{build} child agents and \textit{decommission} child
+provides a notion of parent-child hierarchichal relationship, where parents can
+choose to \textit{deploy} child agents and \textit{decommission} child
 agents. For the archetype developer, this interface provides enormous power, 
@@
 
-In a similar fashion, the \Class{Trader} interface allows agent-to-agent interaction through the
-trading of \Class{Resource}s. Usable archetypes in a \Cyclus simulation must
+In a similar fashion, the \Class{Trader} interface allows agent-agent interaction through the
+trading of \Class{Resource}s. Archetypes in a \Cyclus simulation must
 implement the \Class{Agent} interface and may optionally implement the
@@
 Two primary consequences arise from this structure. First, institutions are
-responsible for building and decommissioning facilities, so advanced
-logic regarding building and decommissioning can be obtained by sub-classing the
-\Class{Institution} interface. Second, the \Class{Facility} class implements the
-\Class{Trader} interface, and thus institutions and regions can
-adjust the resource flow preferences of their managed facilities, respectively. Importantly,
-this novel capability allows for the modeling of preferential regional trading
+nominally
+responsible for deploying and decommissioning facilities. Accordingly, advanced
+logic regarding building and decommissioning can be obtained by subclassing the
+\Class{Institution} interface. Second, the \Class{Facility} class implmenets the
+\Class{Trader} interface, and thus institutions and regions, respectively, can
+adjust the resource flow preferences of their managed facilities. Importantly,
+this capability allows for the modeling of preferential regional trading
 of resources (e.g., tariffs) as well as preferential institutional trading
@@
 Although concept of the \gls{RIF} hierarchy is provided, the \Cyclus kernel is
-designed to handle hierarchies of arbitrary depth.
-A simulation can proceed without regions and institutions (i.e.,  only facilities)
-or with archetypes that are the parents of regions.  By
+designed to handle hierarchies of arbitrary depth.  It is capable of 
+running a simulation without regions and institutions (i.e.  only facilities)
+or a simulation having archetypes that are the parents of regions.  By
 convention, institutions are mainly responsible for facility deployment, but
-any archetype can have access to \Cyclus' agent deployment mechanism.  It is straightforward
-to implement agents that deploy copies of themselves or schedule their
+any archetype can have access to the \Cyclus agent deployment mechanism.  It easy
+to implement agents that deploy copies of themselves, or that schedule their
 own decommissioning.  Because regions, institutions, and facilities are all
@@
 
-All operations performed on resource objects (splitting, combining,
-decay, etc.) are tracked in detail.  This information includes the creating
+All operations performed on every resource object (splitting, combining,
+decay, etc.) are tracked in detail as they are performed.  This information includes 
+the creating
 agent for when resources are newly created and introduced into the simulation.
 The parentage of each resource is also tracked. This makes it possible to
-follow the history of discrete resource objects as they are transferred
-between agents, powerfully impacting the ability to model 
+follow the history of resources as they are transferred
+between agents.  This powerfully impacts the ability to model 
 non-proliferation-related simulation goals.
@@
     \item "never" (currently implemented) globally turns off all decay.
-        Materials' decay function does nothing.
+        The Material decay function does nothing.
 
@@
 
-In order to avoid excess decay calculations, when a material's decay function
-is invoked, the material compares the decay constants of its nuclides with
-the time delta for the current
+In order to avoid excess decay calculations, when decay 
+is invoked, the material checks to see if it contains any nuclides with decay
+constants that are significant with respect to the time delta for the current
 decay operation.  If all the decay constants are not significant, no decay
@@
 references to the same composition object safely.  When operations are
-performed on a material that do not alter the composition, any new resulting
+performed on a material that do not change the composition, any new resulting
 materials hold a reference to the same, originating composition object.
@@
 immutability), a reference to the new composition is placed in a cache shared
-by the new and originating compositions. The next time the originating
-composition is decayed, this cache will be checked for a prior calculation
+by the new originating compositions. The next time the originating
+composition is decayed, the cache will be checked for a prior calculation
 with the same cumulative decay time.  If one exists, the cached composition is
@@
 In addition to the core functionality of the \Cyclus kernel, which is focused on
-the minimal set of capabilities needed to implement an agent-based simulation
-with \gls{DRE}, a toolkit is provided that assists developers
+the set of capabilities needed to implement an agent-based simulation
+with dynamic resource exchange, a toolkit is provided that assists developers
 and users with related simulation and nuclear engineering tasks. The toolkit is
-an actively developed module of \Cyclus, with a primary forward-looking
-focus on supporting interesting \textit{in situ} (i.e., in simulation) and
-\textit{ex situ} (i.e., post-processing) metric analysis tools.
+an activly developed part of \Cyclus, with a primarily forward-looking
+focus on supporting interesting \textit{in situ} metric analysis tools.
 
@@
 A series of utility classes are provided to support demand-constrained agent
-(e.g., facility) deployment. Symbolic function representations of linear,
-exponential, and piecewise functions are supported via the
+facility deployment. Symbolic function representations of linear,
+expontential, and piecewise functions are supported via the
 \Class{SymbFunctionFactory} class. Such functions are used with other toolkit
@@
 \Class{CommodityProducer}, \Class{CommodityProducerManager}, \Class{Builder},
-and \Class{BuildingManager}. The \Class{CommodityProducer} class provides an
-interface for querying the \textit{prototypes} that have some nameplate
-capacity to produce a given commdity, and the \Class{CommodityProducerManager}
+\Class{BuildingManager}. The \Class{CommodityProducer} class provides an
+interface for querying the \textit{prototypes} which have the
+capacity to produce a given commdity. The \Class{CommodityProducerManager}
 provides an interface for registering \Class{CommodityProducer}s and querying
@@
 
-The \Cyclus toolkit provides two useful modules for querying \Class{Material}
+The \Cyclus toolkit provides two useful interfaces for querying \Class{Material}
 objects regarding physical parameters. First, the \Class{MatQuery} module

### 2014-11-02 fundamentals/qa.tex
minor revisions

@@
 \cite{boehm_software_1989}, \emph{\gls{UQ}} 
-\cite{sacks_design_1989}, testing, and others. \gls{VV} and \gls{UQ} derive from 
-a distinctly computational science background while testing \emph{et al.}
-proceed from a software development bent.
+\cite{sacks_design_1989}, testing, and others. \gls{VV} and \gls{UQ} come from 
+a distinctly computational science background while testing \emph{et al.} come from 
+a software development bent.
 
-Nuclear enginerering code quality is often governed by NQA-1, an ASME specification 
+Nuclear engineering code quality is often governed by \gls{NQA1}, an 
+\gls{ASME} specification 
 whose latest revision appeared in 2009 \cite{asme_nqa-1a-2009_2009}. This is primarily 
@@
 \cite{larman_agile_2004}, 
-interpreting NQA-1 in a manner similar to NEAMS \cite{neams_nuclear_2013} or 
-PyNE \cite{biondo_quality_2014}.
+interpreting \gls{NQA1} in a manner similar to the process adopted by the 
+\gls{DOE} within \gls{NEAMS} \cite{neams_nuclear_2013} or the 
+PyNE toolkit \cite{biondo_quality_2014}.
 
 \Cyclus acknowledges that quality assurance is an on-going process throughout the 
-entire life of the code. As a simulator where most modeling descisions are made 
+entire life of the code. As a simulator where most modeling decisions are made 
 by third party archetype developers or users, the most important feature of 
-\gls{QA} 
-is verification. Validation may be impossible and \gls{UQ} is beyond the scope.
+\gls{QA} is verification. Validation may be impossible and \gls{UQ} is beyond 
+he scope.
 
 Verification may be defined as the question, ``Is \Cyclus being built correctly?'' 
-This question can be answered by the software development of notions of testing,
+To answer this question we turn to the software development of notions of testing,
 documentation, version control, style guidelines, and continuous integration. 
-This suite of process controls supplies mechanisms for reliable and reproducible 
+This suite of process controls supplies mechanism for reliable and reproducible 
 software. The impetus to implement these correctly is even stronger in a scientific 
@@
 ``Is \Cyclus the correct tool?''
-Since \Cyclus is alone in its class as an agent-based fuel cycle simulator longitudnal 
+Since \Cyclus is alone in its class as an agent-based fuel cycle simulator, longitudinal 
 validation is not possible. Still code-to-code comparisons with fuel cycle
@@
 exercises are more likely to bring into relief the differences between the modeling
-paradigms than be useful for QA and validation.
+paradigms than be useful for \gls{QA} and validation.
 
-Lastly, uncertainty quantification is a process that is used on specific simulation
-instantiations to statistically determine its quality. Since the cyclus 
-kernel requires an input file written by the user, UQ is a process that applies 
-more to those running cyclus than to those running it.  Furthermore, any UQ
-results that are generated are applicable only to the scenario that is under 
-analysis. Thus for cyclus UQ is well beyond the scope of core development.
+Lastly, \gls{UQ} is a process that is used on specific simulation
+instantiations to statistically determine its quality. Since the \Cyclus 
+kernel requires an input file written by the user, \gls{UQ} is a process that applies 
+to the running of many \Cyclus simulations. The kernel itself, as a generic fuel cycle 
+simulator, cannot make reliable statements about the uncertainty of a particular fuel 
+cycle. Any \gls{UQ} results are applicable only to the scenario that is under 
+analysis. \Cyclus is not a panacea for due dillegence on behalf of the fuel 
+cycle modeler. Thus, \gls{UQ} is envisioned to be beyond the scope of core development 
+and in the domain of the expert user.
 
 Sections \ref{sec:qa-testing}-\ref{sec:qa-ci} discuss in greater detail the software 
-development components that comprise the cyclus verification strategy.
-Each of these on its own is a valuable addition to QA but is cannot be the 
-entire answer to the requirements imposed by NQA-1. Taken together and strictly 
-adhered to they present a fortress through which undeisrable code may siege, 
+development components that comprise the \Cyclus verification strategy.
+Each of these on its own is a valuable addition to \gls{QA} but is cannot be the 
+entire answer to the requirements imposed by \gls{NQA1}. Taken together and strictly 
+adhered to they present a fortress through which undesirable code may siege, 
 but never take.
@@
 simulator does or does not work as intended on a new system.
-Testing serves a critical role in QA because it directly compares the 
+Testing serves a critical role in \gls{QA} because it directly compares the 
 results of running software versus the expected behavior of the software.
-In cyclus, three categories of tests are defined: unit tests, integration 
+In \Cyclus, three categories of tests are defined: unit tests, integration 
 tests, and regression tests.
@@
 It is important to note that before a proposed
-code changes is allowed into main stream cyclus, all of the tests must pass
+code change is allowed into \Cyclus, all of the tests must pass
 and the change must be covered by a test, either new or existing. This is 
 matter of policy for the developers. Additionally, test code is equally likely 
-as the code it is testing to contain errors. To prevent an infinite recurrsion 
-of testing-the-tests, it is assumed that dilligence and one level of testing 
-is sufficient to meet the aims of the quality assurance.
+as the code it is testing to contain errors. To prevent an infinite recursion 
+of testing-the-tests, it is assumed that diligence and one level of testing 
+is sufficient to meet the aims of \gls{QA}.
 
@@
 Unit tests are those which compare the results of the smallest code \emph{unit}, 
-typically a single function or a class. What constitutes a the smallest code
+typically a single function or a class. What constitutes the smallest code
 unit depends on the context of the specific unit in question. While this is 
-an ambiquous defintiion, combined with a philosophy of keeping units as small
+an ambiguous definition, combined with a philosophy of keeping units as small
 as possible it is often clear in practice what needs to be tested.
 
-Cyclus uses the Google Test framework \cite{inc_googletest_2008} as a harness for running unit 
-tests. Sufficient unit tests are required for any proposed change to the cyclus
-code base. Currently cyclus implements over 450 unit tests and cycamore has 
+\Cyclus uses the Google Test framework \cite{inc_googletest_2008} as a harness for running unit 
+tests. Sufficient unit tests are required for any proposed change to the \Cyclus
+code base. Currently \Cyclus implements over 450 unit tests and \Cycamore has 
 85.  These cover approximately 65\% of their respective code bases. This number 
@@
 
-Intergration tests are any tests that combine multiple elemnents of the 
-cyclus interface and test that they work correctly with each other.  By analogy, 
+Integration tests are any tests that combine multiple elements of the 
+\Cyclus interface and test that they work correctly with each other.  By analogy, 
 simply because the gears (units) are made correctly does not imply that the 
 clock (integration) will run smoothly, run at all, or give the correct time.
-In cyclus and cycamore, integration tests are performed by running sample
+In \Cyclus and \Cycamore, integration tests are performed by running sample
 simulations and verifying that results are what would be expected ahead of 
-time. Precanned input files have thus been contsructed. Their results 
+time. Pre-canned input files have thus been constructed. Their results 
 are inspected and compared via nose \cite{pellerin_nose_2007}, a Python test framework.
 Python will run cyclus as a subprocess for each integration test. In this
-way cyclus code units are tested in the full context that they will
+way, \Cyclus code units are tested in the full context that they will be
 executed. This category of testing is especially useful for ensuring that 
-major cyclus components are functioning as expected.
+major \Cyclus components are functioning as expected.
 
@@
 
-Regression tests are tests which ensure that significant changes do not 
-occur over the course of cyclus development. Such a change is called a 
+Regression tests are tests that ensure significant changes do not 
+occur over the course of \Cyclus development. Such a change is called a 
 \emph{regression} because the new version is almost always wrong.
-Regression tests are implemeneted similarly to integration tests.
-Nose is used to execute fully fledged cyclus simulations whose results
-are then compared. In this category however the comparison is done against 
-the output of the same input file when run with a previous version of cyclus, 
+Regression tests are implemented similarly to integration tests.
+Nose is used to execute fully fledged \Cyclus simulations whose results
+are then compared. In this category, however, the comparison is done against 
+the output of the same input file when run with a previous version of \Cyclus, 
 typically the last released version.
@@
 not appear elsewhere though they do not purport to make claims about the
-quality of the physics modeled. The cycamore project is the primary location of
+quality of the physics modeled. The \Cycamore project is the primary location of
 regression tests. This is because the archetypes here are sophisticated enough
-to make interesting input files. Only a handful ($<10$) time steps are needed 
+to make interesting input files. Only a handful ($<10$) of time steps are needed 
 for regression testing.
@@
 
-All of the public interface (the API) must be documented as part of cyclus
-QA policy. This certifies that the intention for a code unit is communicated 
+All of the public interface (the \gls{API}) must be documented as part of \Cyclus
+\gls{QA} policy. This certifies that the intention for a code unit is communicated 
 in way that is separate from its implementation. This policy is important 
-because implementations are often wrong, hence bugs. They are thus unreliable 
+because implementations are often wrong; software implementations are unreliable 
 resources about themselves. Truly trustworthy communication about what 
 software should be doing comes from the author explicitly stating the 
-goals of an API in prose form. Furure development of the code is then able to 
-compare the implemetation versus the documentation to discern whether or not they 
+goals of an \gls{API} in prose form. Future development of the code is then able to 
+compare the implementation versus the documentation to discern whether or not they 
 are in agreement. Documentation is thus a secondary higher-level information 
-stream.  In cyclus, this information is aggregated together into static 
-websites with the doxygen \cite{van_heesch_doxygen:_2008} and sphinx 
+stream.  In \Cyclus, this information is aggregated together into static 
+websites with the Doxygen \cite{van_heesch_doxygen:_2008} and Sphinx 
 \cite{brandl_sphinx_2014} 
@@
 Version control is the history-preserving mechanism by which the provenance of 
-a code is recored. Cyclus uses a well-established tool called git 
+a code is recorded. \Cyclus uses a well-established tool called git 
 \cite{software_freedom_conservancy_git_2014}
-for this purpose. Git is currently the most popular utilty in the recent wave
+for this purpose. Git is currently the most popular utility in the recent wave
 of \emph{distributed version control}. Briefly stated, this means that every 
@@
 These are distinct pathways in the history that branch out of a mainline source
-tree and then may be \emph{merged} back into the mainline. Multiple simeltaneous
-branches may exist at all point in time. Every change to the code is recorded
+tree and then may be \emph{merged} back into the mainline. Multiple simultaneous
+branches may exist at all points in time. Every change to the code is recorded
 in the history, along with metadata such as the author, a timestamp, and an 
 accompanying message. Thus 
-it is possible for cyclus to accurarely replay the entirety of who did what to the
+it is possible for \Cyclus to accurately replay the entirety of who did what to the
 code when.
 
-Cyclus uses a strategy known as \emph{git flow} 
+\Cyclus uses a strategy known as \emph{git flow} 
 \cite{kalliamvakou_code-centric_2014} 
@@
 branch (simply known as develop), and the stable branch (called master).
-In addition to these rules and delineation, cyclus also imposes rules on 
-when it is accecptable from a quality control standpoint to merge code from 
+In addition to these rules and delineation, \Cyclus also imposes rules on 
+when it is acceptable from a quality control standpoint to merge code from 
 the personal topical branches into develop. All software at this stage 
-must have sufficient and passing tests and reasonable documentation. Without
-these core pieces proposed changes are not allowed into cyclus.
+must have sufficient and passing tests and comprehensive documentation. Without
+these core pieces, proposed changes are not allowed into \Cyclus. A schematic of 
+the development stages between reporting a bug and merging the fix is shown in 
+Figure \ref{fig:gitprocess}.
 
-The act of proposing a change is known as a \emph{pull request}. The main cyclus is 
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[height=0.6\textheight]{./images/gitprocess}
+\end{center}
+\caption{A version-control enabled process for finding, reporting, and fixing a bug 
+can take place within an issue tracker alongside multiple stages of code 
+testing and review. In the \Cyclus case, the final review stage includes unit, 
+regression, and integration testing as well as manual code inspection.}
+\label{fig:gitprocess}
+\end{figure}
+
+The act of proposing a change is known as a \emph{pull request}. The main \Cyclus is 
 hosted remotely on the GitHub website \cite{dabbish_social_2012}. The online
-mechanism for pull requests allows for code review by a member of the cyclus 
+mechanism for pull requests allows for code review by a member of the \Cyclus 
 core team other than the author prior to any change being included. Non-members
-of the cyclus development team are allowed and encouraged to submit and review 
-pull requests. However, only members of the cyclus core team are allowed to 
-merge in any changes and only after the QA standards have been met.
+of the \Cyclus development team are allowed and encouraged to submit and review 
+pull requests. However, only members of the \Cyclus core team are allowed to 
+merge in any changes and only after the \gls{QA} standards have been met.
 
@@
 wish to write code. Every person tends to have their own custom style. To remedy this
-coding style guides are the software analogy to the natural language ones, 
-such as the Chicago Manual of Style. Cyclus strictly enforces the use of the 
+coding style guides are the software analogy to those for written language,
+such as the Chicago Manual of Style. \Cyclus strictly enforces the use of the 
 Google C++ Style Guide \cite{weinberger_google_2008} for all software contributions.
-This means that all developers of cyclus nominally write cyclus code in the same 
+This means that all developers of \Cyclus nominally write \Cyclus code in the same 
 way.  This homogenization may be a hurdle to new developers but ultimately 
-makes the it much more legible. Adoption of a single style guide also settles
+improves code legibility. Adoption of a single style guide also settles
 timeless arguments over what style is `the best.' Having only one means that 
@@
 
-Continuous integration (CI) the idea that software should be tested and validated 
+\emph{\acrfull{CI}} the idea that software should be tested and validated 
 as it is being developed, rather than as a final stage in a longer development 
-cycle.  Under CI every pull request is tested independently immeadiately after 
-it is proposed. Such tests shoudl be run on all officially supported platforms. 
-Cyclus uses a CI platform called Polyphemus \cite{scopatz_polyphemus_2014}.
+cycle.  Under \gls{CI}, every pull request is tested independently immediately after 
+it is proposed. Such tests should be run on all officially supported platforms. 
+\Cyclus uses a \gls{CI} platform called Polyphemus \cite{scopatz_polyphemus_2014}.
 
 Polyphemus serves as an intermediary between GitHub pull requests on the frontend 
-and temporary cyclus servers on the backend. These servers are hosted by 
+and temporary \Cyclus servers on the backend. These servers are hosted by 
 the Build \& Test Laboratory (BaTLab) \cite{uw_batlab_team_batlab_2014} at the University of 
@@
 
-CI has become a neccessary but not sufficient addition to the cyclus QA
-system. Its merit is that it keeps bad code out. However, cyclus will always
-require human eyes and human hands to let good code in.
+\gls{CI} has become a necessary but not sufficient addition to the \Cyclus \gls{QA}
+system. Its merit is that it prevents bad code from being implemeted. However, \Cyclus will always
+require human eyes and hands to let good code in.

### 2014-11-02 fundamentals/impl.tex

--- 2014-10-31 fundamentals/impl.tex
@@
 on \gls{COTS}, Windows-based software. It can be easily deployed 
-on large computer systems, such as \acrlong{HTC} systems.
+on large computer systems, such as \gls{HTC} systems.
 
 Cyclopts (\TODO{cite}), a proof of principle design and implementation of such a
-system, uses UW-Madison's HTCondor HTC infrastructure to perform sensitivity
+system, uses UW-Madison's HTCondor \gls{HTC} infrastructure to perform sensitivity
 studies on \Cyclus' resource exchange optimization solvers. To date, it has been
@@
 
-In particular, since the clean plugin architecture loads libraries without any
+In particular, since the clean plug-in architecture loads libraries without any
 modifications to the \Cyclus kernel, closed-source archetypes can be used with
-the simulator alongside open-source archetypes. This architecture
+the simulator alongside open source archetypes. This architecture
 allows closed-source libraries (e.g., those representing sensitive nuclear

### 2014-11-02 fundamentals/qa.tex

--- 2014-11-02 fundamentals/qa.tex
@@
 been invented over the years to mitigate the structural and algorithmic errors
-on the part of simulators themselves. These include \emph{\gls{VV}}
-\cite{boehm_software_1989}, \emph{\gls{UQ}} 
-\cite{sacks_design_1989}, testing, and others. \gls{VV} and \gls{UQ} derive from 
-a distinctly computational science background while testing \emph{et al.}
-proceed from a software development bent.
+on the part of simulators themselves. These include \emph{verification and validation}
+(V\&V) \cite{boehm_software_1989}, \emph{uncertainty quantification} (UQ) 
+\cite{sacks_design_1989}, testing, and others. V\&V and UQ come from 
+a distinctly computational science background while testing \emph{et al.} come from 
+a software development bent.
 
@@
 used for designing reactors. However, it is general enough to apply to 
-\Cyclus. \Cyclus has adopted an \emph{agile} development process 
+cyclus. Cyclus has adopted an \emph{agile} development process 
 \cite{larman_agile_2004}, 
@@
 
-\Cyclus acknowledges that quality assurance is an on-going process throughout the 
+Cyclus acknowledges that quality assurance is an on-going process throughout the 
 entire life of the code. As a simulator where most modeling descisions are made 
-by third party archetype developers or users, the most important feature of
-\gls{QA} 
-is verification. Validation may be impossible and \gls{UQ} is beyond the scope.
+by third party archetype developers or users, the most important feature of QA 
+is verification. Validation may be impossible and UQ is beyond the scope.
 
-Verification may be defined as the question, ``Is \Cyclus being built correctly?'' 
-This question can be answered by the software development of notions of testing,
+Verification may be defined as the question, ``Is cyclus being built correctly?'' 
+To answer this question we turn to the software development of notions of testing,
 documentation, version control, style guidelines, and continuous integration. 
-This suite of process controls supplies mechanisms for reliable and reproducible 
+This suite of process controls supplies mechanims for reliable and reproducible 
 software. The impetus to implement these correctly is even stronger in a scientific 
@@
 Validation on the other hand may be defined as the question, 
-``Is \Cyclus the correct tool?''
-Since \Cyclus is alone in its class as an agent-based fuel cycle simulator longitudnal 
+``Is cyclus the correct tool?''
+Since cyclus is alone in its class as an agent-based fuel cycle simulator logitudnal 
 validation is not possible. Still code-to-code comparisons with fuel cycle

### 2014-11-02 fundamentals/impl.tex

--- 2014-11-02 fundamentals/impl.tex
@@
 
-Dynamically-loadable libraries are the primary mechanism for extending \Cyclus' capability. 
-This approach provides encapsulation. The core of the code operates
-completely independently from the individual plugin libraries. Thus, any
+Dynamically loadable libraries are the primary mechanism for extending \Cyclus' capability. 
+This approach provides encapsulation: the core of the code operates
+completely independently from the individual plug-in libraries. Thus, any
 customization or extension is implemented only in the loadable
@@
 references to the same composition object safely.  When operations are
-performed on a material that do not change the composition, any new resulting
-materials hold a reference to the same, originating composition object.
+performed on a material that do not alter the composition, any new resulting
+materials hold a reference to the same, original composition object.
 Although the decay operation generates a new, separate composition (preserving
 immutability), a reference to the new composition is placed in a cache shared
-by the new originating compositions. The next time the originating
-composition is decayed, the cache will be checked for a prior calculation
+by the new and original compositions. The next time the original
+composition is decayed, this cache will be checked for a prior calculation
 with the same cumulative decay time.  If one exists, the cached composition is

### 2014-11-02 fundamentals/intro.tex

--- 2014-11-02 fundamentals/intro.tex
@@
 its modeling ecosystem answer this need for a next generation nuclear fuel cycle 
-simulator. Dynamic simulation of nuclear fuel cycles with discrete agents 
-and per-nuclide species resolution support 
-levels of detail appropriate for a varied community of analysts
-interested in a range of analysis types. Additionally, \Cyclus employs an 
+simulator. This dynamic simulator employs discrete agents, time, and materials 
+up to isotopic resolution in order to support a range of analysis types, levels of 
+detail, and fuel cycle analysts.
+Additionally, \Cyclus employs a modular architecture and 
 open development process that supports user access and 

### 2014-11-02 fundamentals/qa.tex

--- 2014-11-02 fundamentals/qa.tex
@@
 exercises are more likely to bring into relief the differences between the modeling
-paradigms than be useful for \gls{QA} and validation.
+paradigms than be useful for QA and validation.
 
-Lastly, \gls{UQ} is a process that is used on specific simulation
+Lastly, uncertainty quantification is a process that is used on specific simulation
 instantiations to statistically determine its quality. Since the \Cyclus 
-kernel requires an input file written by the user, \gls{UQ} is a process that applies 
+kernel requires an input file written by the user, UQ is a process that applies 
 to the running of many \Cyclus simulations. The kernel itself, as a generic fuel cycle 
 simulator, cannot make reliable statements about the uncertainty of a particular fuel 
-cycle. Any \gls{UQ} results are applicable only to the scenario that is under 
+cycle. Any UQ results are applicable only to the scenario that is under 
 analysis. \Cyclus is not a panacea for due dillegence on behalf of the fuel 
-cycle modeler. Thus, \gls{UQ} is envisioned to be beyond the scope of core development 
+cycle modeler. Thus, UQ is envisioned to be beyond the scope of core development 
 and in the domain of the expert user.
@@
 It is important to note that before a proposed
-code change is allowed into \Cyclus, all of the tests must pass
+code changes is allowed into main stream \Cyclus, all of the tests must pass
 and the change must be covered by a test, either new or existing. This is 
@@
 of testing-the-tests, it is assumed that diligence and one level of testing 
-is sufficient to meet the aims of \gls{QA}.
+is sufficient to meet the aims of the quality assurance.
 
@@
 Python will run cyclus as a subprocess for each integration test. In this
-way, \Cyclus code units are tested in the full context that they will be
+way cyclus code units are tested in the full context that they will be
 executed. This category of testing is especially useful for ensuring that 
@@
 
-Regression tests are tests that ensure significant changes do not 
+Regression tests are tests which ensure that significant changes do not 
 occur over the course of \Cyclus development. Such a change is called a 
@@
 regression tests. This is because the archetypes here are sophisticated enough
-to make interesting input files. Only a handful ($<10$) of time steps are needed 
+to make interesting input files. Only a handful ($<10$) time steps are needed 
 for regression testing.
@@
 in way that is separate from its implementation. This policy is important 
-because implementations are often wrong; software implementations are unreliable 
+because implementations are often wrong. Software implementations are unreliable 
 resources about themselves. Truly trustworthy communication about what 
@@
 Version control is the history-preserving mechanism by which the provenance of 
-a code is recorded. \Cyclus uses a well-established tool called git 
+a code is recored. \Cyclus uses a well-established tool called git 
 \cite{software_freedom_conservancy_git_2014}
@@
 tree and then may be \emph{merged} back into the mainline. Multiple simultaneous
-branches may exist at all points in time. Every change to the code is recorded
+branches may exist at all point in time. Every change to the code is recorded
 in the history, along with metadata such as the author, a timestamp, and an 
@@
 must have sufficient and passing tests and comprehensive documentation. Without
-these core pieces, proposed changes are not allowed into \Cyclus. A schematic of 
+these core pieces proposed changes are not allowed into \Cyclus. A schematic of 
 the development stages between reporting a bug and merging the fix is shown in 
@@
 \end{center}
-\caption{A version-control enabled process for finding, reporting, and fixing a bug 
+\caption{A version-control enabled process for finding, reporting, fixing a bug 
 can take place within an issue tracker alongside multiple stages of code 
@@
 wish to write code. Every person tends to have their own custom style. To remedy this
-coding style guides are the software analogy to those for written language,
+coding style guides are the software analogy to the natural language ones, 
 such as the Chicago Manual of Style. \Cyclus strictly enforces the use of the 
@@
 way.  This homogenization may be a hurdle to new developers but ultimately 
-improves code legibility. Adoption of a single style guide also settles
+makes the it much more legible. Adoption of a single style guide also settles
 timeless arguments over what style is `the best.' Having only one means that 
@@
 as it is being developed, rather than as a final stage in a longer development 
-cycle.  Under \gls{CI}, every pull request is tested independently immediately after 
+cycle.  Under \gls{CI} every pull request is tested independently immediately after 
 it is proposed. Such tests should be run on all officially supported platforms. 
@@
 
-\gls{CI} has become a necessary but not sufficient addition to the \Cyclus \gls{QA}
-system. Its merit is that it prevents bad code from being implemeted. However, \Cyclus will always
-require human eyes and hands to let good code in.
+CI has become a necessary but not sufficient addition to the \Cyclus \gls{QA}
+system. Its merit is that it keeps bad code out. However, \Cyclus will always
+require human eyes and human hands to let good code in.

### 2014-11-02 fundamentals/conclusion.tex

@@
 The \Cyclus nuclear fuel cycle framework presents a more generic and flexible 
-alternative to existing fuel cycles simulators.
+alternative to existing fuel cycle simulators.
 
-Where, previous nuclear fuel cycle simulators have had limited distribution, 
+Where previous nuclear fuel cycle simulators have had limited distribution, 
 uncertain provenance, and restricted customizability, \Cyclus emphasizes an 
@@
 same simulation. Researchers no longer need to reinvent the wheel in order to 
-model a simulation focused on the aspects of the fuel cycle that their research 
-focuses on.
+model a simulation focused on the aspects of the fuel cycle
+relevant to their research.
 

### 2014-11-06 fundamentals/intro.tex
minor edits

@@
 facility deployment, and material routing. However, most nuclear fuel cycle 
-simulators have not incorporated modern insights in simulation science and 
+simulators have not incorporated modern insights into simulation science and 
 software architecture that can enable more efficient, accurate, robust, and 
@@
 
-The \Cyclus Nuclear Fuel Cycle Simulator framework and 
-its modeling ecosystem answer this need for a next generation nuclear fuel cycle 
-simulator. This dynamic simulator employs discrete agents, time, and materials 
-up to isotopic resolution in order to support a range of analysis types, levels of 
-detail, and fuel cycle analysts.
+The \Cyclus nuclear fuel cycle simulator framework and 
+its modeling ecosystem address this need for a next-generation nuclear fuel cycle 
+simulator. This dynamic simulator employs discrete agents, time, and isotopic resolution of materials 
+and supports a range of analysis types, levels of 
+detail, and analyst sophistication.
 Additionally, \Cyclus employs a modular architecture and 
@@
 proprietary models. To date, current tools are either static, fleet-based, 
-privately distributed, or all of the above. Each of these qualities present a 
+privately distributed, or all of the above. Each of these qualities presents a 
 severe challenge to modeling fidelity, generality, efficiency, robustness, and 
@@
 An alternative to these approaches is a dynamic, agent-based simulator with an 
-open platform and an ecosystem of research-driven capabilities.  Modern 
-insight indicates that dynamic nuclear fuel cycle analysis more realistically 
-supports a broader range of simulation goals than static analysis 
+open platform and an ecosystem of research-driven capabilities.  
+Dynamic nuclear fuel cycle analysis more realistically 
+supports a range of simulation goals than static analysis 
 \cite{piet_dynamic_2011}. Similarly, experience in the broader field of systems 
@@
 allows cross-institutional collaboration, increases code robustness, and 
-enables the cultivation of an ecosystem of calculation options 
+cultivates an ecosystem of calculation options 
 \cite{softwarecarpentryresource}.  The fundamental concepts of the \Cyclus 
@@
 
-Nuclear fuel cycle simulators can drive \gls{RDD} by calculating `metrics', 
+Nuclear fuel cycle simulators drive \gls{RDD} by calculating `metrics', 
 quantitative measures of performance that 

### 2014-11-06 fundamentals/intro.tex
more edits

@@
 Historically, the national laboratories have driven development and regulated 
-the use of their own tools such as \gls{VISION}\cite{jacobson_verifiable_2010}, 
+the use of their own tools: \gls{VISION}\cite{jacobson_verifiable_2010}, 
 \gls{DANESS}\cite{van_den_durpel_daness_2009}, 
@@
 \gls{NFCSim}\cite{schneider_nfcsim:_2005}. 
-Outside of the national laboratories, researchers create new nuclear fuel cycle 
-simulation tools when existing tools are not available or not sufficiently 
+Outside the national laboratories, researchers have created new nuclear fuel cycle 
+simulation tools when existing tools were not available or not sufficiently 
 general to calculate their metrics of interest with their method of choice.  
 With limited access to the national laboratory tools and a need to customize 
-them for research purposes, universities and private industry researchers 
-``reinvent the wheel'' by developing tools of their own from scratch and 
+them for research purposes, universities and private industry researchers have 
+``reinvented the wheel'' by developing tools of their own from scratch and 
 tailored to their own needs, for example \gls{CAFCA}\cite{guerin_impact_2009} and 
-\gls{COSI}\cite{boucher_cosi_2005,boucher_cosi:_2006,meyer_new_2009,coquelet-pascal_comparison_2011} respectively.
+\gls{COSI}\cite{boucher_cosi_2005,boucher_cosi:_2006,meyer_new_2009,coquelet-pascal_comparison_2011}.
 
@@
 for calculating those metrics vary among simulators. Some model the 
-system of facilities, economics, and materials at static equilibrium. Meanwhile 
-other simulators capture its dynamics.  
+system of facilities, economics, and materials in static equilibrium, while 
+other simulators capture the dynamics of the system.  
 Similarly, while some simulators discretely model material and facilities, 
-others treat materials in streams and facilities in fleets, in an aggregated 
-fashion. Depending on their intended use, simulators often overspecialize, 
+others treat materials as streams and facilities as fleets, in an aggregated 
+fashion. Simulators often overspecialize, 
 modeling a single aspect of the fuel cycle in great detail while neglecting 
@@
 The \Cyclus simulator emerged from a line of tools seeking to break this practice.  
-A \gls{LDRD} project that began at \gls{INL}, 
-\gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006} sought 
+Its precurser, \gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006}, was begun at \gls{LDRD}, began at \gls{INL} and sought 
 to provide generic regional capability.  Based on lessons learned from 
@@
 provide more generality and an extensible interface to facilitate 
-collaboration.  The \Cyclus project, in turn, improved upon the \gls{GENIUSv2} 
+collaboration.  The \Cyclus project then improved upon the \gls{GENIUSv2} 
 effort by implementing increased modularity and encapsulation.  The result is  
@@
 an architecture that permits simulations with multiple and variable levels of 
-fidelity. The simulator's agent-based framework for tracking of 
+fidelity. The simulator's agent-based framework for tracking the 
 transformation and trade of resources between facilities within institutions 
@@
 simulators, the \Cyclus paradigm enables essential capabilities that previous 
-simulators lack. First, its \emph{modular and open architecture}  facilitates 
+simulators lack. Critically, its \emph{modular and open architecture}  facilitates 
 targeted contribution and collaboration within the nuclear fuel cycle analysis 
@@
 of its \emph{\gls{ABM}} paradigm and \emph{discrete, object-oriented approach} 
-emphasizes applicability of the \Cyclus tool across a broader range of 
-fidelities, scales, and applications than other simulators.
+enables \Cyclus to be applicable to a broader range of 
+fidelities, scales, and applications than to other simulators.
 
 \Cyclus separates the problem of modeling a
-physics-dependent supply chain into a simulation kernel and archetypes that
-interact with the kernel during a simulation. The kernel is responsible for the
-deployment and interaction logic of entities in the simulation. Physics
-calculations are constrained to individual archetypes. Accordingly, specialists
+physics-dependent supply chain into two distinct components: a simulation kernel and archetypes that
+interact with the kernel. The kernel is responsible for the
+deployment and interaction logic of entities in the simulation. The archetypes represent 
+individual types of facilities and capture their unique physics.  Accordingly, specialists
 in a given field can utilize their time and resources in modeling a specific
 process associated with the nuclear fuel cycle (e.g., reprocessing and advanced
-fuel fabrication), rather than also modeling the entirety of the cycle.
+fuel fabrication), without having to model the entirety of the cycle.
 
 Furthermore, modeling the evolution of a physics-dependent, international nuclear fuel supply
-chain is a multiscale problem, but existing tools are not sufficiently 
+chain is a multiscale problem, and existing tools are not sufficiently 
 multiscale. Tools have either focused on macro effects, e.g., the fleet-level
-stocks and flows of commodities, or micro effects, e.g., the used fuel
+stocks and flows of commodities, or micro effects, e.g., the used-fuel
 composition of fast reactor fuel. Each focus has driven the
-development of these tools, rendering the task of answering questions between
+development of specialized tools, rendering the task of answering questions between
 the macro and micro levels challenging within a single tool. 
-However, an extensible architecture and discrete object tracking allow 
-the creation and interchangeability of custom \Cyclus archetypes at any level of fidelity.
+In constrast, the extensible architecture and discrete object tracking of \Cyclus allow
+the creation and interchangeability of custom archetypes at any level of fidelity.
 
@@
 
-The architecture within the \Cyclus tool allows developers 
+The architecture of \Cyclus allows developers 
 to define nuclear fuel cycle agents and processes independent of the simulation 
-logic. This `encapsulated,' `plug-in'
-design choice provides two major benefits.
-
-First, analysts across research institutions can take advantage of the 
+logic. This encapsulated `plug-in'
+design choice provides two major benefits. First, analysts across research institutions can take advantage of the 
 simulation logic \gls{API} and archetype ecosystem when they apply \Cyclus to 
-their specific problem. This extensibility, magnified by an open source 
-development process, frees the community of users to contribute desired 
-features, independent from the team of \Cyclus core developers. This 
+their specific problem. This 
 mend-and-extend paradigm, common in modern software development, reduces 
 maintenance overhead and improves code robustness \cite{citation_needed}. 
-The researcher can therefore focus on creating or customizing nuclear 
+The researcher can focus on creating or customizing nuclear 
 facility, institution, resource, and toolkit models within their specific area 
-of technical expertise.
-
+of technical expertise. This extensibility, magnified by an open source 
+development process, frees the community of users to contribute desired 
+features, independent from the team of \Cyclus core developers. 
 % we could use a specific example of Cosi's equivalence method below
@@
 composition for fast reactors. A variety of fuel fabrication archetypes can be 
-developed and interchanged to analyze the effect of each on the 
-simulation output.
-
-There are a number of types of users and developers who will 
-interact with the \Cyclus framework. National laboratory researchers,
-academic researchers, private-industry economic forecasters, and even students 
-in engineering courses may benefit from the ease of development and
-customization provided by the modular architecture of \Cyclus.
+developed and interchanged while keeping the rest of the fuel cycle fixed
+ to compare fuel fabrication designs.
 
@@
 \Cyclus implements an \gls{ABM} paradigm.  \gls{ABM} is modern, sophisticated, 
-true to reality, and it takes advantage of modern computing resources.  
-Furthermore, agent-based modeling provides an analyst a more natural 
-\Cyclus utilizes an \gls{ABM} paradigm.  \gls{ABM} is modern, sophisticated, 
-true to reality, and takes advantage of modern computing resources.  
-Furthermore, \gls{ABM} provides an analyst a more natural 
+true to reality, and it incorporates modern computing resources.  
+Furthermore, \gls{ABM} provides a natural 
 perspective from which to model a given problem. In the nuclear fuel cycle 
-context for example, an analyst can design an agent with reactor-related logic 
-entirely independent from a separate agent with fuel fabrication-related 
+context, for example, an analyst can design an agent with reactor-related logic 
+that is entirely independent from an agent with fuel fabrication-related 
 logic. Defining the behavior of both agents according to the 
 \gls{API} contract is sufficient for them to interact with one another as 
-bona fide actors in the simulation.  The two archetype libraries, therefore, need 
-not have any shared knowledge of one another for them to be building blocks in 
-the same simulation.
+bona fide actors in the simulation.  The two archetype libraries can be used in the same
+simulation without any shared knowledge.
 
+Furthermore, the \gls{ABM} paradigm is easily comparable to system dynamics models.
 System dynamics is a popular approach for modeling nuclear fuel cycles 
-\cite{jacobson_vision_2009,van_den_durpel_daness_2009,guerin_impact_2009,guerin_benchmark_2009}. However, it has been shown in systems analysis literature
-\cite{macal_agent-based_2010} that, formally, the
-set of system dynamics models is a strict subset of agent-based models.
+\cite{jacobson_vision_2009,van_den_durpel_daness_2009,guerin_impact_2009,guerin_benchmark_2009}. 
+Formally however, system dynamics models are simply a strict subset of agent-based models
+\cite{macal_agent-based_2010}.
 That is, any system dynamics model can be translated
-into an agent-based model. Furthermore, agent-based
-techniques can provide a richer model than can system dynamics. To enable the 
-broadest range of simulations in a generic fashion, \gls{ABM} is therefore 
-superior to system dynamics.
+into an agent-based model. Furthermore, because agent-based
+techniques can provide a richer model than can system dynamics, they enable the 
+broadest range of simulations in a generic fashion.
 
@@
 
-This generality specifically permits many use cases that cannot be achieved with 
-fleet-based models. That is, some questions require resolution at the level of 
-individual facilities and materials.  Since fleet-based, 
-lumped-material models do not distinguish between discrete facility entities or 
-materials, many detailed performance metrics cannot be captured with 
-those tools.
+Although some questions require resolution at the level of 
+individual facilities and materials, 
+Fleet-based, lumped-material models do not distinguish between discrete
+facility entities or materials.  As a result, detailed performance 
+metrics cannot be captured with previously existing tools.
+The generality of \Cyclus therefore enables many use cases 
+that cannot be achieved with fleet-based models.
 
-One example use case seeks to capture system vulnerability to nefarious 
-material diversion. This type of analysis requires discrete simulation of a 
+One such example is the use case that seeks to capture system vulnerability to nefarious 
+material diversion. Provenance and trade-history of distinct materials is the fundamental 
+information unit in such studies, and so this type of analysis requires
+ discrete simulation of a 
 target facility and the individual materials modified within it. 
@@
 in the \Cyclus simulator.
+
+There are a number of types of users and developers who will 
+interact with the \Cyclus framework. National laboratory researchers,
+academic researchers, private-industry economic forecasters, and even students 
+in engineering courses may benefit from the ease of development and
+customization provided by the discrete, modular, agent-based architecture of \Cyclus.

### 2014-11-06 fundamentals/impl.tex
more edits and resolution of issues 56 and 57

@@
 build \Cyclus on open source libraries in modern programming languages enables 
-both remote and mutiprocess execution on a number of platforms.
+both remote and mutiprocess execution on a number of platforms. This section begins by 
+describing the general design features that make \Cyclus both flexible and powerful:
+cluster-ready software, dynamic libraries, and interchangeable agents. It then introduces
+the specific framework of \Cyclus: the region-institution-facility hierarchy, handling
+of resources and materials, the Cycamore library of agents, and the experimental toolkit.
+These features provide a solid foundation on which to build an interconnected community 
+of archetype developers with diverse backgrounds and simulation goals.
 
@@
 increases the wall-clock time necessary to conduct parameterized sensitivity 
-analyses and other multi-simulation studies.
-
-\Cyclus, on the other hand, is primarily written in \texttt{C++} and relies on 
-libraries supported by Linux and UNIX (including Ubuntu and OSX) platforms. 
+analyses and other multi-simulation studies. \Cyclus, on the other hand, is 
+primarily written in \texttt{C++} and relies on 
+libraries supported by Linux and UNIX (including Ubuntu and OSX) platforms, 
+which are flexible and support parallelization. 
 Furthermore, the core infrastructure and related archetypes are free and 
@@
 
-Cyclopts (\TODO{cite}), a proof of principle design and implementation of such a
-system, uses UW-Madison's HTCondor \gls{HTC} infrastructure to perform sensitivity
+Cyclopts (\TODO{cite}), a proof of principle design and implementation of \Cyclus on such a large computer system,
+ uses UW-Madison's HTCondor \gls{HTC} infrastructure to perform sensitivity
 studies on \Cyclus' resource exchange optimization solvers. To date, it has been
@@
 % (OO, cpp, xml, backends, inheritances, mixins, generic apis, etc.)
-
-\acrlong{ABM} is inherently object-oriented. Since agents represent 
-discrete, independently acting objects, object-orientation is the natural 
-paradigm in which to conduct \gls{ABM}.
-
-The core of the \Cyclus simulator creates a set of key classes on which agent 
-plug-ins 
-are based. In addition, a set of key tools are also provided to enrich the 
-\gls{API} and supply a robust suite of behaviors for the developer.
 
@@
 
+\acrlong{ABM} is inherently object-oriented because agents represent 
+discrete, independently acting objects.  Figure \ref{fig:framework} illustrates
+the modular nature of \Cyclus archetypes.  The core of the \Cyclus simulator 
+creates a set of key classes on which agent plug-ins 
+are based. In addition, a set of key tools are also provided to enrich the 
+\gls{API} and supply a robust suite of behaviors for the developer. 
 Agent plug-ins utilize the generic core \gls{API} to interact with one another.  For 
-example, agents rely on the dynamic loading and paradigm for clean plug-in 
+example, agents rely on a paradigm of dynamic loading and clean plug-in 
 behavior at the start of the simulation. They also use the resource exchange 
@@
 
-A key innovation in \Cyclus is implementing this generic \gls{API} and modular 
-architecture into a suite of dynamically loadable plug-in libraries.  Though 
+A key innovation is that \Cyclus  implements this generic \gls{API} and modular 
+architecture via a suite of dynamically loadable plug-in libraries.  Though 
 common in modern software architecture, such a plug-in pattern has 
-previously not been implemented in nuclear fuel cycle simulators in the 
-literature.  In \Cyclus, this implementation maximizes the potential of the clean, 
-object-oriented \gls{API} and modern build system already described.
-
-Dynamically loadable libraries are the primary mechanism for extending \Cyclus' capability. 
-This approach provides encapsulation: the core of the code operates
+not previously been implemented in nuclear fuel cycle simulators.  
+Dynamically loadable libraries are the primary mechanism for extending \Cyclus' capability. This approach provides encapsulation: the core of the code operates
 completely independently from the individual plug-in libraries. Thus, any
@@
 explore different levels of complexity within their archetypes, including
-wrapping other simulation tools as loadable libraries within the \Cyclus
-framework.
-
-A secondary benefit is the ability for
-contributors to choose different distribution and licensing strategies
-for their contributions. By allowing models to have varied
-availability, the security concerns of developers can be
-assuaged (See Figure \ref{fig:modifiedopen}).
+wrapping other simulation tools as loadable libraries within \Cyclus.
 
@@
 
+An additional benefit is the ability for
+contributors to choose different distribution and licensing strategies
+for their contributions. By allowing models to have varied
+availability, the security concerns of developers can be
+assuaged (See Figure \ref{fig:modifiedopen}).
 In particular, since the clean plug-in architecture loads libraries without any
 modifications to the \Cyclus kernel, closed-source archetypes can be used with
-the simulator alongside open source archetypes. This architecture
+the simulator alongside open source archetypes without transfer of sensitive information. This architecture
 allows closed-source libraries (e.g., those representing sensitive nuclear
@@
 Due to this plug-in architecture,
-implementations of actors in a given simulation can be easily
+implementations of actors in a given scenario can be easily
 interchanged. Critically, this novel functionality enables the comparison
@@
 agents. For the archetype developer, this interface provides enormous power, 
-very simply. The \gls{API} exposes \Class{Agent} helpful functionality for 
+very simply. The \gls{API} provides the \Class{Agent} with helpful functionality for 
 interacting with the \Cyclus simulation kernel while abstracting away unnecessary 
@@
 \caption{The inheritance in \Cyclus classes, such as the \Class{Agent}, 
-\Class{Facility}, \Class{Institution}, and \Class{Region} classes abstract away 
+\Class{Facility}, \Class{Institution}, and \Class{Region} classes, abstract away 
 unnecessary details while exposing powerful functionality. In the above 
@@
 \Cyclus provides a novel representation of entities in the nuclear fuel cycle 
-which models the reality in international nuclear power production
+that reflects the reality in international nuclear power: production
 encompassing facilities, institutions managing those facilities, and regions. While
@@
 effects, \Cyclus allows for both regions and institutions to be first-class
-actors in simulated fuel cycles.
-
-The fundamental interactions for each entity are implemented in a corresponding
+actors in simulated fuel cycles. The fundamental interactions for each entity are implemented in a corresponding
 archetype class in \Cyclus, i.e., the \Class{Region} class, \Class{Institution}
@@
 provided functionality by inheriting from the appropriate class.
-
 \Cyclus implements a \gls{RIF} relationship through the
@@
 logic regarding building and decommissioning can be obtained by subclassing the
-\Class{Institution} interface. Second, the \Class{Facility} class implmenets the
+\Class{Institution} interface. Second, the \Class{Facility} class implements the
 \Class{Trader} interface, and thus institutions and regions, respectively, can
@@
 
-Although concept of the \gls{RIF} hierarchy is provided, the \Cyclus kernel is
+Although concept of the \gls{RIF} hierarchy is provided explicitly, the \Cyclus kernel is
 designed to handle hierarchies of arbitrary depth.  It is capable of 
@@
 convention, institutions are mainly responsible for facility deployment, but
-any archetype can have access to the \Cyclus agent deployment mechanism.  It easy
+any archetype can have access to the \Cyclus agent deployment mechanism.  It is easy
 to implement agents that deploy copies of themselves, or that schedule their
@@
 All operations performed on every resource object (splitting, combining,
-decay, etc.) are tracked in detail as they are performed.  This information includes 
-the creating
-agent for when resources are newly created and introduced into the simulation.
+decay, etc.) are tracked in detail as they are performed.  This information includes th
+agent that newly created resources are created from  
+when they are introduced into the simulation.
 The parentage of each resource is also tracked. This makes it possible to
@@
 invoke the decay function on them as desired to decay them to the current
-simulation time. \Cyclus can currently operate in 2 decay modes with 2 other
+simulation time. \Cyclus can currently operate in 2 decay modes, with 2 additional
 modes likely to be added in future releases:
@@
 
-    \item "manual" (currently implemented) is the default mode just described
+    \item "manual" (currently implemented) is the default mode 
         where agents decay materials as needed.
@@
 constants that are significant with respect to the time delta for the current
-decay operation.  If all the decay constants are not significant, no decay
+decay operation.  If none of the decay constants are significant, no decay
 calculation is performed and the material remains unchanged.  This error does
@@
 
-\Cyclus has no notion of "tracked" nuclides.  In \Cyclus, a  material's
-composition represents an arbitrarily large list (potentially thousands) of
+\Cyclus has no notion of ``tracked'' versus ``untracked'' nuclides.  In \Cyclus, the composition of a  material
+composition is represented by an arbitrarily large list (potentially thousands) of
 nuclides.  Agents are free to treat nuclides present in materials any way they
@@
 
-In large simulations there may be many material objects changing frequently.
+In large simulations many material objects may be changing frequently.
 Material decay can also contribute significantly to such changes.  In order to
@@
 and users with related simulation and nuclear engineering tasks. The toolkit is
-an activly developed part of \Cyclus, with a primarily forward-looking
+an actively developed part of \Cyclus, with a primarily forward-looking
 focus on supporting interesting \textit{in situ} metric analysis tools.
@@
 facility deployment. Symbolic function representations of linear,
-expontential, and piecewise functions are supported via the
+exponential, and piecewise functions are supported via the
 \Class{SymbFunctionFactory} class. Such functions are used with other toolkit
 classes to determine commodity demand (e.g., power demand) from user input. Four
-mixin classes provide the basis for in-simulation deployment determination:
+mix-in classes provide the basis for in-simulation deployment determination:
 \Class{CommodityProducer}, \Class{CommodityProducerManager}, \Class{Builder},
@@
 \Class{BuildingManager} uses a simple minimum cost algorithm to determine how
-many of each prototype, $y_i$, to build given a demand, $\Phi$, capacities,
-$\phi_i$, and costs, $c_i$.
+many of each prototype, $y_i$, to build given a demand ($\Phi$), capacities
+($\phi_i$), and costs ($c_i$).
 
@@
 
-The \Cyclus toolkit provides two useful interfaces for querying \Class{Material}
-objects regarding physical parameters. First, the \Class{MatQuery} module
+The \Cyclus toolkit provides two useful interfaces for queries referring to physical paramaters of \Class{Material}
+objects. First, the \Class{MatQuery} module
 provides a basic querying \gls{API}, including the atom and mass fractions of
@@
 aggregate nuclides, i.e., a \Class{Composition}, in a material. The
-\Class{enrichment} module provides an \gls{API} for determining enrichment-related
+\Class{Enrichment} module provides an \gls{API} for determining enrichment-related
 parameters of a material, including the separative work units (SWU) and natural
@@
 
-In addition to those that already exist, tools and computational patterns will 
+In addition to those that already exist, new tools and computational patterns will 
 emerge from the archetypes that are developed within the community of 
-developers. As those tools gain adoption between projects and demonstrate their 
+developers. As these tools gain adoption between projects and demonstrate their 
 utility to the developer community, they will be considered for screening and 
@@
 \item economic models
-\item etc.
 \end{itemize}
@@
 repository, provides a fundamental set of agent archetypes for basic simulation 
-functionality within \Cyclus.  Since the \Cyclus framework relies on external 
+functionality within \Cyclus.  Since \Cyclus relies on external 
 archetypes to represent the agents within a simulation, \Cycamore provides the 
@@
 \hline
-Facility & BatchReactor & A reactor model that handles batch refuelling, based on pre-determined recipes of compositions. \\
+Facility & BatchReactor & A reactor model that handles batch refueling, based on pre-determined recipes of compositions. \\
 Facility & Source & This facility generates material of the composition and commodity type specified as input.  \\
@@
 Facility & EnrichmentFacility & This facility enriches uranium at a specified capacity. \\
-Institution & ManagerInst & The manager institution manages production of commodities among its facilities by building new necessary ones. \\
+Institution & ManagerInst & The manager institution manages production of commodities among its facilities by building new ones as needed. \\
 Institution & DeployInst &  This institution deploys specific facilities as defined explicitly in the input file. \\
@@
 
-As future contributions are vetted, the capabilities in \Cycamore may grow. 
-However, the current \Cycamore release provides only 
+The current \Cycamore release provides only 
 basic functionality, enabling simple fuel cycle analyses. 
-\Cycamore is provided so that users can get started quickly with simple 
-analyses.
-
-Figure \ref{fig:simplesim} shows an example of a simple, once-through fuel cycle 
-that can be generated with \Cycamore and \Cyclus alone.
+As illustrated in Figure \ref{fig:simplesim}, \Cycamore provides the tools for users
+to get started quickly with simple 
+once-through fuel cycle scenarios. As future contributions are vetted, the capabilities in \Cycamore may grow.
 

### 2014-11-07 fundamentals/intro.tex

@@
 facility deployment, and material routing. However, most nuclear fuel cycle 
-simulators have not incorporated modern insights into simulation science and 
+simulators have not incorporated modern insights from simulation science and 
 software architecture that can enable more efficient, accurate, robust, and 
@@
 measures of performance can be expressed in terms of these metrics. For example, 
-economic feasibility is often measured in \gls{LCOE}
+economic feasibility is often measured in \gls{LCOE}, requiring calculation of
+lifetime fuel costs and electricity generation, 
 while environmental performance might be measured in spent fuel volume, 
@@
 
-The \Cyclus simulator emerged from a line of tools seeking to break this practice.  
+\Cyclus emerged from a line of tools seeking to break this practice.  
 Its precurser, \gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006}, was begun at \gls{LDRD}, began at \gls{INL} and sought 
 to provide generic regional capability.  Based on lessons learned from 
-\gls{GENIUSv1}, the 
-\gls{GENIUSv2}\cite{oliver_studying_2009,huff_geniusv2_2009} code sought to 
+Version 1, the 
+\acrshort{GENIUSv2} Version 2\cite{oliver_studying_2009,huff_geniusv2_2009} code sought to 
 provide more generality and an extensible interface to facilitate 
-collaboration.  The \Cyclus project then improved upon the \gls{GENIUSv2} 
+collaboration.  The \Cyclus project then improved upon the \acrshort{GENIUSv2} 
 effort by implementing increased modularity and encapsulation.  The result is  
@@
 interact with the kernel. The kernel is responsible for the
-deployment and interaction logic of entities in the simulation. The archetypes represent 
-individual types of facilities and capture their unique physics.  Accordingly, specialists
+deployment and interaction logic of entities in the simulation.  Physics calculations and 
+customized behaviors are implemented within archetypes. Accordingly, specialists
 in a given field can utilize their time and resources in modeling a specific
@@
 microscopic extreme, the model is capable of representing arbitrarily small 
-material objects at isotopic resolution. In this way, the \Cyclus simulator is 
+material objects at isotopic resolution. In this way, \Cyclus is 
 applicable across the full range of modeling extremes.
@@
 Fleet-based, lumped-material models do not distinguish between discrete
-facility entities or materials.  As a result, detailed performance 
+facility entities or materials.  As a result, many detailed performance 
 metrics cannot be captured with previously existing tools.
@@
 
-One such example is the use case that seeks to capture system vulnerability to nefarious 
+One such use case seeks to capture system vulnerability to nefarious 
 material diversion. Provenance and trade-history of distinct materials is the fundamental 
@@
 Material risk analysis, therefore, demands discretely modeled objects like those 
-in the \Cyclus simulator.
+in \Cyclus.
 
 There are a number of types of users and developers who will 
-interact with the \Cyclus framework. National laboratory researchers,
+interact with \Cyclus. National laboratory researchers,
 academic researchers, private-industry economic forecasters, and even students 

### 2014-11-07 fundamentals/examples.tex
edits and some text expansion

--- 2014-11-02 fundamentals/examples.tex
@@
 
+The success of the \Cyclus simulator is illustrated by demonstrations
+of its fundamental simulation capabilities and the feasibility of \Cyclus
+as a community-driven development model.
+%The most compelling are demonstrations of the feasibility of the \Cyclus community-driven development 
+%model and of fundamental simulation capability. 
+Nascent promising growth of the \Cyclus 
 The success of the \Cyclus simulator can be measured in many ways. 
@@
 \item the archetypes provided in the \Cycamore \cite{carlsen_cycamore_2014} 
-repository of additional modules,
-\item the archetypes created by researchers,
-\item isotopic composition data,
-\item historical facility deployment data,
-\item the \Cyclus \gls{GUI} tool Cyclist,
-\item the tools in the \Cyclus toolkit
-\item and other tools for \Cyclus optimization, parallelization, and development.
+repository
+\item the archetypes created by researchers
+\item isotopic composition data
+\item historical facility deployment data
+\item the \Cyclus \gls{GUI} tool Cyclist
+\item fundamental analysis tools in the \Cyclus toolkit
+\item tools for \Cyclus optimization, parallelization, and development
 \end{itemize}
-All together, these form an `ecosystem' of capabilities. Over time, this 
+Taken together, these form an `ecosystem' of capabilities. Over time, this 
 ecosystem will grow as archetype-developers, kernel-developers, and 
@@
 long-term vision for the \Cyclus framework predicts an ever-expanding ecosystem 
-of both general and specialized capability extensions within that ecosystem.
+of both general and specialized capability extensions within the ecosystem.
 
@@
 ecosystem. Table \ref{tab:coretools} lists the tools and projects developed 
-under close integration with the \Cyclus kernel.
+under close integration with the \Cyclus kernel.  These tools are used to ease development
+and simulation design (Cystub, Cycic, Ciclus), data visualization and analysis (Cyclist, Cyan),
+and remote execution (Cloudlus).
+
 \begin{table}[h]
@@
 Cyclist & Interactive data exploration environment & \cite{livnat_cyclist_2014} \\
-Ciclus & Continuous Integration scripts for \Cyclus & \cite{scopatz_ciclus_2014}\\
+Ciclus & Continuous integration scripts for \Cyclus & \cite{scopatz_ciclus_2014}\\
 Cycstub & Skeleton for clean slate module development & \cite{carlsen_cycstub_2014}\\
@@
 \end{tabularx}
-\caption{Many tools outside of the scope of the \Cyclus kernel have been 
-developed for improved user, developer, and analyst experiences with \Cyclus.}
+\caption{Many tools have been developed outside of the scope of the \Cyclus kernel for improved user, developer, and analyst experiences with \Cyclus.}
 \label{tab:coretools}
@@
 
-Many archetypes external to the \Cycamore library  
+Many archetypes external to the \Cycamore library (Table \table{tab:cycamore})  
 have been 
 \cite{huff_streamblender_2014,huff_commodconverter_2014}
-and are being 
+or are being 
 \cite{flanagan_bright-lite_2014,skutnik_nuclear_2014,huff_mktdriveninst_2014} developed for contribution to the 
 \Cyclus ecosystem. These archetypes provide the first examples of 
-developer-contributed capabilities.
+developer-contributed capabilities.  They add to the fundamental \Cycamore
+archetypes by providing physics-based reactors, separation, fabrication, and storage
+facilities, and expanded institutional paradigms.  These contributed archetypes
+illustrate the power of a community-based development approach.
 
@@
 
-Results of some simple recycle scenarios run in \Cyclus follow.  In \Cyclus,
-because material is tracked as discrete objects, single-pass \gls{MOX} 
-recycle is
-easy to implement.  The simulation initially included one provider of fresh
+Results of some simple recycle scenarios run in \Cyclus follow. Beginning with a single
+reactor simulation, open (no recycle), modified open, and closed (infinite-pass recycle) 
+fuel cycles are compared to illustrate the resolution possible with \Cyclus.  The simulation
+is then expanded to include multiple reactors in the same set of fuel cycles to demonstrate
+the system-scale convergance to continuous material flow models.
+
+Because material is tracked as discrete objects, single-pass \gls{MOX} 
+recycle is easy to implement in \Cyclus.  The MOX simulation includes one provider of fresh
 \gls{UOX} fuel, one recycled fuel fabrication facility, one reactor, one separations
-facility, and one repository. The simulation duration was set to 1100 months.
+facility, and one repository. The simulation has a duration of 1100 months and a \TODO{??-month stepsize}.
+
+%** full-system plutonium buildup for open
+(no recycle), modified open, and closed (infinite-pass recycle) variations of
+%the scenario described above (all just a single reactor).  **
 
 The \Class{BatchReactor} archetype from \Cycamore has the ability to accept
-fuel materials from an arbitrary number of different sources delineated by
+fuel materials from an arbitrary number of different sources, delineated by
 commodity. Custom, non-uniform preferences can be set for each different fuel
 commodity.  The dynamic resource exchange makes it easy for a reactor to
-preferrentially accept recycled \gls{MOX} fuel over fresh \gls{UOX} fuel.  The
+preferentially accept recycled \gls{MOX} fuel over fresh \gls{UOX} fuel.  In this
+simulation, the
 \Class{BatchReactor} was configured to run with a 3 batch core on 18 month cycles and
@@
 
-The \Class{Source} and \Class{Sink} archetypes from \Cycamore were also used as a
+The \Class{Source} and \Class{Sink} archetypes from \Cycamore have been used as a
 source of fresh, enriched uranium and a repository respectively. A simple
-custom recycled fuel fabrication facility was used.  This fabrication facility
-mixes fissile and fertile streams to match target fuel compositions as closely
+custom recycled fuel fabrication facility was also used, which mixes fissile 
+and fertile streams to match target fuel compositions as closely
 as possible.  The method used for this matching is approximately the same as
@@
 To switch to a fully closed fuel cycle, all that needs to be done is change
-the output commodity for the \Class{BatchReactor}'s spent \gls{MOX} fuel.  All this
-requires is a one-word change in the input file:
+the output commodity for the spent \gls{MOX} fuel of the \Class{BatchReactor}, 
+requiring only a one-word change in the input file:
 
@@
 fabrication facility 1 cycle longer to accumulate a full batch worth of
-fissile material.  Because facilities are represented individually and
-transact discrete materials as discrete events, realistic non-uniform patterns
-in facility behavior can be observed affecting total system behavior in ways
-that are less commonly observed in fleet-based, continuous material flow
-modeling.
+fissile material.
+
+Because facilities are represented individually and
+transact discrete materials as discrete events, realistic non-uniform patterns in facility behavior
+that affect total system behavior are observed using \Cyclus, which is uncommon 
+for fleet-based, continuous material flow models.
 
@@
 The open, modified open, and closed scenarios can easily be modified to have
-several reactors each with staggered refueling times.  As the number of
+several reactors each with staggered refueling times. The plutonium buildup
+for these three multi-reactor variations is shown in Figure
+\ref{fig:puseriesn}. As the number of
 reactors increases, the behavior of the system approaches a more steady
-average reminiscent of continuous material flow models.  The plutonium buildup
-for these three multi-reactor variations is shown in Figure
-\ref{fig:puseriesn}.
+average reminiscent of continuous material flow models.
 

### 2014-11-07 fundamentals/qa.tex
fixing spelling error and double CI definition in acros.tex
minor edits for QA and one typo in Examples

--- 2014-11-02 fundamentals/qa.tex
@@
 Simulation science - like experimental science - has since the beginning had the 
-problem of identifying trustworthy results from the nonsensical and the noise.
-This is epitomized in the Charles Babbage quote, ``On two occasions I have been asked, 
+problem of identifying trustworthy results from nonsensical results or noise.
+This is epitomized by Charles Babbage, ``On two occasions I have been asked, 
 `Pray, Mr. Babbage, if you put into the machine wrong figures, will the right 
@@
 of ideas that could provoke such a question.'' \cite{babbage_passages_2011}. 
-The \emph{garbage in, garbage out} phenomenon is not the only scenario which a
-simulator must guard against; ensuring correctness is equally important.
+A simulator must both guard against the \emph{garbage in, garbage out} phenomenon, and also assure correctness.
 
-Multiple strategies collectively known as \emph{\gls{QA}} have 
+Multiple strategies, collectively known as \emph{\gls{QA}}, have 
 been invented over the years to mitigate the structural and algorithmic errors
@@
 \cite{sacks_design_1989}, testing, and others. \gls{VV} and \gls{UQ} come from 
-a distinctly computational science background while testing \emph{et al.} come from 
-a software development bent.
+a distinctly computational science background while testing \emph{et al.} come from software development.
 
@@
 \gls{ASME} specification 
-whose latest revision appeared in 2009 \cite{asme_nqa-1a-2009_2009}. This is primarily 
-used for designing reactors. However, it is general enough to apply to 
+whose latest revision appeared in 2009 \cite{asme_nqa-1a-2009_2009}.  
+Although \gls{NQA1} is primarily 
+used for designing reactors, it is general enough to apply to 
 \Cyclus. \Cyclus has adopted an \emph{agile} development process 
@@
 
-\Cyclus acknowledges that quality assurance is an on-going process throughout the 
+Quality assurance is an on-going process throughout the 
 entire life of the code. As a simulator where most modeling decisions are made 
@@
 \gls{QA} is verification. Validation may be impossible and \gls{UQ} is beyond 
-he scope.
+the scope of the kernel.
 
 Verification may be defined as the question, ``Is \Cyclus being built correctly?'' 
-To answer this question we turn to the software development of notions of testing,
+To answer this question, we turn to the software development of notions of testing,
 documentation, version control, style guidelines, and continuous integration. 
 This suite of process controls supplies mechanism for reliable and reproducible 
-software. The impetus to implement these correctly is even stronger in a scientific 
-context because of the emphasis on reproducibility and provenance. These are 
-discussed below individually.
+software. The impetus to implement these controls correctly is particularly strong in a scientific 
+context because of the emphasis on reproducibility and provenance. These verification techniques are 
+discussed individually in the sections that follow.
 
-Validation on the other hand may be defined as the question, 
+Validation, in contrast,  may be defined as the question, 
 ``Is \Cyclus the correct tool?''
 Since \Cyclus is alone in its class as an agent-based fuel cycle simulator, longitudinal 
-validation is not possible. Still code-to-code comparisons with fuel cycle
-simulators with other modeling paradigms are underway, if nascent. However, such 
+validation is not possible. Nonetheless, code-to-code comparisons with fuel cycle
+simulators that use other modeling paradigms are underway, if nascent. However, such 
 exercises are more likely to bring into relief the differences between the modeling
-paradigms than be useful for \gls{QA} and validation.
+paradigms than supply substantial \gls{QA} and validation.
 
 Lastly, \gls{UQ} is a process that is used on specific simulation
-instantiations to statistically determine its quality. Since the \Cyclus 
-kernel requires an input file written by the user, \gls{UQ} is a process that applies 
+instantiations to statistically determine quality. \gls{UQ} is a process that applies 
 to the running of many \Cyclus simulations. The kernel itself, as a generic fuel cycle 
@@
 cycle. Any \gls{UQ} results are applicable only to the scenario that is under 
-analysis. \Cyclus is not a panacea for due dillegence on behalf of the fuel 
+analysis by the user. \Cyclus is not a panacea for due dillegence on behalf of the fuel 
 cycle modeler. Thus, \gls{UQ} is envisioned to be beyond the scope of core development 
@@
 entire answer to the requirements imposed by \gls{NQA1}. Taken together and strictly 
-adhered to they present a fortress through which undesirable code may siege, 
-but never take.
+adhered to, they present a fortress to protect against poorly designed or otherwise undesirable code.
 
@@
 Automated software \emph{testing} is the first line of defense against
-errors in implementation. It also acts as an early warning sign that the
-simulator does or does not work as intended on a new system.
+errors in implementation. It also acts as an early warning sign if the
+simulator does not work as intended on a new system.
 Testing serves a critical role in \gls{QA} because it directly compares the 
@@
 It is important to note that before a proposed
-code change is allowed into \Cyclus, all of the tests must pass
-and the change must be covered by a test, either new or existing. This is 
-matter of policy for the developers. Additionally, test code is equally likely 
-as the code it is testing to contain errors. To prevent an infinite recursion 
-of testing-the-tests, it is assumed that diligence and one level of testing 
-is sufficient to meet the aims of \gls{QA}.
+code change is allowed into \Cyclus,  the change must be covered by a test, either new or existing, and all of the tests must pass.  This is a
+matter of policy for the developers. Of course, test code is 
+just as likely to contain errors as the code it is designed to test. 
+However, it is assumed that diligence and one level of testing 
+is sufficient to meet the aims of \gls{QA} and prevent an infinite recursion
+of testing-the-tests.
 
@@
 
-Unit tests are those which compare the results of the smallest code \emph{unit}, 
+Unit tests compare the results of the smallest code \emph{unit}, 
 typically a single function or a class. What constitutes the smallest code
 unit depends on the context of the specific unit in question. While this is 
-an ambiguous definition, combined with a philosophy of keeping units as small
-as possible it is often clear in practice what needs to be tested.
+an ambiguous definition, when combined with a philosophy of keeping units as small
+as possible, it is often clear in practice what needs to be tested.
 
@@
 tests. Sufficient unit tests are required for any proposed change to the \Cyclus
-code base. Currently \Cyclus implements over 450 unit tests and \Cycamore has 
-85.  These cover approximately 65\% of their respective code bases. This number 
-is expected to grow over time.
+code base. Currently \Cyclus implements over 450 unit tests and \Cycamore implements 
+85.  These cover approximately 65\% of their respective code bases, and their numbers are expected to grow over time.
 
@@
 
-Integration tests are any tests that combine multiple elements of the 
+Integration tests combine multiple elements of the 
 \Cyclus interface and test that they work correctly with each other.  By analogy, 
@@
 simulations and verifying that results are what would be expected ahead of 
-time. Pre-canned input files have thus been constructed. Their results 
-are inspected and compared via nose \cite{pellerin_nose_2007}, a Python test framework.
-Python will run cyclus as a subprocess for each integration test. In this
-way, \Cyclus code units are tested in the full context that they will be
+time. A set of standard input files have thus been constructed. 
+Python is used to run the same set of \Cyclus simulations as a subprocess for each integration test.
+The results are then inspected and compared via Nose \cite{pellerin_nose_2007}, a Python test framework.
+In this way, \Cyclus code units are tested in the full context that they will be
 executed. This category of testing is especially useful for ensuring that 
@@
 
-Regression tests are tests that ensure significant changes do not 
+Regression tests ensure significant changes do not 
 occur over the course of \Cyclus development. Such a change is called a 
@@
 Regression tests are implemented similarly to integration tests.
-Nose is used to execute fully fledged \Cyclus simulations whose results
+Nose is used to execute full \Cyclus simulations whose results
 are then compared. In this category, however, the comparison is done against 
@@
 not care about the contents of a simulation being correct, only whether or not 
-it changed. They thus pick up glaring time-sensitive mistakes that may 
-not appear elsewhere though they do not purport to make claims about the
-quality of the physics modeled. The \Cycamore project is the primary location of
-regression tests. This is because the archetypes here are sophisticated enough
+it changed. They pick up glaring time-sensitive mistakes that may 
+not appear elsewhere, though they do not purport to make claims about the
+quality of the physics modeled. Regression tests are primarily implemented
+in \Cycamore because its archetypes are sophisticated enough
 to make interesting input files. Only a handful ($<10$) of time steps are needed 
@@
 
-All of the public interface (the \gls{API}) must be documented as part of \Cyclus
+All of the public interface (the \gls{API}) must be documented as required by the \Cyclus
 \gls{QA} policy. This certifies that the intention for a code unit is communicated 
 in way that is separate from its implementation. This policy is important 
-because implementations are often wrong; software implementations are unreliable 
-resources about themselves. Truly trustworthy communication about what 
-software should be doing comes from the author explicitly stating the 
+because implementations are often wrong and do not reliably communicate their intent. Truly trustworthy communication about what 
+software should be doing occurs when the author explicitly states the 
 goals of an \gls{API} in prose form. Future development of the code is then able to 
@@
 \cite{brandl_sphinx_2014} 
-tools. These websites are placed online at \url{http://fuelcycle.org}.
+tools, and can be accessed at \url{http://fuelcycle.org}.
 
@@
 term for the collection of all possible histories).
-Though there and many praises and criticisms of git, one 
+Though there are many praises and criticisms of git, one 
 feature that the tool performs exceptionally well is the notion of code branches.
@@
 \cite{kalliamvakou_code-centric_2014} 
-to manage topical branches where individuals develop code, the mainline development
+to manage topical branches where individuals develop code: the mainline development
 branch (simply known as develop), and the stable branch (called master).
-In addition to these rules and delineation, \Cyclus also imposes rules on 
+In addition to these rules and delineations, \Cyclus also imposes rules on 
 when it is acceptable from a quality control standpoint to merge code from 
-the personal topical branches into develop. All software at this stage 
-must have sufficient and passing tests and comprehensive documentation. Without
-these core pieces, proposed changes are not allowed into \Cyclus. A schematic of 
+the personal topical branches into the develop branch. All software at this stage 
+must have sufficient successful tests and comprehensive documentation. Without
+these core pieces, proposed changes are not allowed into \Cyclus. As an example, a schematic of 
 the development stages between reporting a bug and merging the fix is shown in 
@@
 
-The act of proposing a change is known as a \emph{pull request}. The main \Cyclus is 
+The act of proposing a change is known as a \emph{pull request}. The main \Cyclus repository is 
 hosted remotely on the GitHub website \cite{dabbish_social_2012}. The online
 mechanism for pull requests allows for code review by a member of the \Cyclus 
-core team other than the author prior to any change being included. Non-members
+core team, separate from the author, prior to any change being included. Non-members
 of the \Cyclus development team are allowed and encouraged to submit and review 
@@
 In any multi-person software project, there is a tension between how individuals
-wish to write code. Every person tends to have their own custom style. To remedy this
+wish to write code. Every person tends to have their own custom style. To remedy this,
 coding style guides are the software analogy to those for written language,
@@
 
-\emph{\acrfull{CI}} the idea that software should be tested and validated 
+\emph{\acrfull{CI}} is the idea that software should be tested and validated 
 as it is being developed, rather than as a final stage in a longer development 
 cycle.  Under \gls{CI}, every pull request is tested independently immediately after 
-it is proposed. Such tests should be run on all officially supported platforms. 
-\Cyclus uses a \gls{CI} platform called Polyphemus \cite{scopatz_polyphemus_2014}.
-
-Polyphemus serves as an intermediary between GitHub pull requests on the frontend 
+it is proposed. Such tests are run on all officially supported platforms. 
+\Cyclus uses a \gls{CI} platform called Polyphemus \cite{scopatz_polyphemus_2014}. Polyphemus serves as an intermediary between GitHub pull requests on the frontend 
 and temporary \Cyclus servers on the backend. These servers are hosted by 
@@
 actually works. This helps identify build and test problems prior to 
-broken code being allowed into the develop branch.
-
-\gls{CI} has become a necessary but not sufficient addition to the \Cyclus \gls{QA}
-system. Its merit is that it prevents bad code from being implemeted. However, \Cyclus will always
+broken code being allowed into the develop branch. \gls{CI} isa necessary 
+but not sufficient addition to the \Cyclus \gls{QA}
+system. Its merit is that it prevents bad code from being implemented. However, \Cyclus will always
 require human eyes and hands to let good code in.

### 2014-11-07 fundamentals/examples.tex
minor edits for QA and one typo in Examples
minor edits

@@
 The success of the \Cyclus simulator is illustrated by demonstrations
-of its fundamental simulation capabilities and the feasibility of \Cyclus
-as a community-driven development model.
-%The most compelling are demonstrations of the feasibility of the \Cyclus community-driven development 
-%model and of fundamental simulation capability. 
+of its fundamental simulation capabilities and the feasibility the
+ community-driven \Cyclus development model.
 Nascent promising growth of the \Cyclus 
@@
 long-term vision for the \Cyclus framework predicts an ever-expanding ecosystem 
-of both general and specialized capability extensions within the ecosystem.
+of both general and specialized capability extensions.
 
@@
 
-Many archetypes external to the \Cycamore library (Table \table{tab:cycamore})  
+Many archetypes external to the \Cycamore library (Table \ref{tab:cycamore})  
 have been 

### 2014-11-19 fundamentals/impl.tex
small fixes

@@
 studies on \Cyclus' resource exchange optimization solvers. To date, it has been
-used run over $10^4$ jobs, or (\TODO{compute time}) total compute hours, using
+used to run over $10^4$ jobs, or (\TODO{compute time}) total compute hours, using
 the \Cyclus library via its resource exchange \gls{API}.
@@
 
-Interchangeability is accomplished by providing \glspl{API} that define agent-to-agent
+Interchangeability is accomplished by providing \glspl{API} that define canonical agent-to-agent
 interaction and agent-to-environment interaction, primarily through the
@@
 \Class{DetailedReactor} and the other using \Class{SimpleReactor} can therefore 
-be compared directly to determine the impact of using one or the other model.
+be compared directly to determine the whole-simulation impact of using one or the other model.
 This can be done with any agent type, where agents can be ``Regions,'' 
@@
 convention, institutions are mainly responsible for facility deployment, but
-any archetype can have access to the \Cyclus agent deployment mechanism.  It is easy
+all archetypes have access to the agent deployment mechanism.  It is easy
 to implement agents that deploy copies of themselves, or that schedule their
 own decommissioning.  Because regions, institutions, and facilities are all
-agents, they can all be implemented to exercise the full set of features
+just agents, they can all be implemented to exercise the full set of features
 offered by the \Cyclus kernel.
@@
 All operations performed on every resource object (splitting, combining,
-decay, etc.) are tracked in detail as they are performed.  This information includes th
-agent that newly created resources are created from  
-when they are introduced into the simulation.
-The parentage of each resource is also tracked. This makes it possible to
-follow the history of resources as they are transferred
-between agents.  This powerfully impacts the ability to model 
+decay, etc.) are tracked in detail as they are performed.  This information
+includes the agent that created each resource when it was introduced into the
+simulation.  The parentage of each resource is also tracked. This makes it
+possible to follow the history of resources as they are transferred between
+agents.  This powerfully impacts the ability to model
 non-proliferation-related simulation goals.
@@
 In order to avoid excess decay calculations, when decay 
-is invoked, the material checks to see if it contains any nuclides with decay
-constants that are significant with respect to the time delta for the current
+is invoked, a material checks to see if it contains any nuclides with decay
+constants that are significant with respect to the time change since the last
 decay operation.  If none of the decay constants are significant, no decay
@@
 not accumulate because the next time the material's decay function is invoked,
-the time delta will be larger. \TODO{want more detail on this decay shortcut?}
+the time change will be larger. \TODO{want more detail on this decay shortcut?}
 \TODO{describe decay algorithm and how it might be improved}.
@@
 \Cyclus has no notion of ``tracked'' versus ``untracked'' nuclides.  In \Cyclus, the composition of a material
-composition is represented by an arbitrarily large list (potentially thousands) of
+is represented by an arbitrarily large list (potentially thousands) of
 nuclides.  Agents are free to treat nuclides present in materials any way they
@@
 help avoid unnecessary runtime performance and database space impacts,
-compositions in \Cyclus have some special features, such as immutability.
-Immutable compositions allow multiple material objects to all hold
+compositions in \Cyclus have some special features.
+Immutability of compositions allows multiple material objects to all hold
 references to the same composition object safely.  When operations are

### 2014-11-26 fundamentals/impl.tex

@@
 
-\subsection{Cluster-Ready Software}
+\subsection{Modular Architecture}
+% Motivation for encapsulated plug-in architecture 
+% enables ecosystem, ease of contribution across institutions
+% enables myriad levels of simulation fidelity
+% enables FC analyses that can compare ‘apples to apples'
 
-Many fuel cycle simulators rely on \gls{COTS} and Windows-only software that limits 
-performance on resource computing infrastructures. This limitation severely 
-increases the wall-clock time necessary to conduct parameterized sensitivity 
-analyses and other multi-simulation studies. \Cyclus, on the other hand, is 
-primarily written in \texttt{C++} and relies on 
-libraries supported by Linux and UNIX (including Ubuntu and OSX) platforms, 
-which are flexible and support parallelization. 
-Furthermore, the core infrastructure and related archetypes are free and 
-open source, BSD-3-clause licensed. No part of \Cyclus is proprietary or based 
-on \gls{COTS}, Windows-based software. It can be easily deployed 
-on large computer systems, such as \gls{HTC} systems.
+The architecture of \Cyclus allows developers 
+to define nuclear fuel cycle agents and processes independent of the simulation 
+logic. This encapsulated `plug-in'
+design choice provides two major benefits. First, analysts across research institutions can take advantage of the 
+simulation logic \gls{API} and archetype ecosystem when they apply \Cyclus to 
+their specific problem. This 
+mend-and-extend paradigm, common in modern software development, reduces 
+maintenance overhead and improves code robustness \cite{citation_needed}. 
+The researcher can focus on creating or customizing nuclear 
+facility, institution, resource, and toolkit models within their specific area 
+of technical expertise. This extensibility, magnified by an open source 
+development process, frees the community of users to contribute desired 
+features, independent from the team of \Cyclus core developers. 
+% we could use a specific example of Cosi's equivalence method below
+Second, because \Cyclus uses a modular archetype approach, comparing two 
+archetypes is straightforward. Consider a case in which an analyst would like 
+to compare the effect of using different models to determine the input fuel 
+composition for fast reactors. A variety of fuel fabrication archetypes can be 
+developed and interchanged while keeping the rest of the fuel cycle fixed
+ to compare fuel fabrication designs.
 
-Cyclopts (\TODO{cite}), a proof of principle design and implementation of \Cyclus on such a large computer system,
- uses UW-Madison's HTCondor \gls{HTC} infrastructure to perform sensitivity
-studies on \Cyclus' resource exchange optimization solvers. To date, it has been
-used to run over $10^4$ jobs, or (\TODO{compute time}) total compute hours, using
-the \Cyclus library via its resource exchange \gls{API}.
-The \gls{HTC} infrastructure has also been utilized to run and collect
-information from full \Cyclus simulations running in parallel on $10^3$
-machines reliably for order $10^5$ simulations.
-
-\subsection{Framework Structure}
-% (OO, cpp, xml, backends, inheritances, mixins, generic apis, etc.)
-
-\begin{figure}[htbp!]
-\begin{center}
-\includegraphics[width=\textwidth]{./images/framework}
-\end{center}
-\caption{The \Cyclus core provides \gls{API}s that abstract away the details in 
-the kernel and allow the archetypes to be loaded into the simulation in a modular 
-fashion.}
-\label{fig:framework}
-\end{figure}
-
-\acrlong{ABM} is inherently object-oriented because agents represent 
-discrete, independently acting objects.  Figure \ref{fig:framework} illustrates
-the modular nature of \Cyclus archetypes.  The core of the \Cyclus simulator 
-creates a set of key classes on which agent plug-ins 
-are based. In addition, a set of key tools are also provided to enrich the 
-\gls{API} and supply a robust suite of behaviors for the developer. 
-Agent plug-ins utilize the generic core \gls{API} to interact with one another.  For 
-example, agents rely on a paradigm of dynamic loading and clean plug-in 
-behavior at the start of the simulation. They also use the resource exchange 
-paradigm \gls{API} for trading resources with one another.
-
-\subsection{Dynamically Loadable Libraries}
+\subsubsection{Dynamically Loadable Libraries}
 % (diagram)
@@
 
-\subsection{Agent Interchangeability}\label{sec:interchangeability}
+\subsection{Agent-based Paradigm}
+% superior detail in capturing simulation dynamics
+% more flexible control over behavior
+% describe Region/Institution/Facility hierarchy
+% note importance of generic resource exchange paradigm
+
+\Cyclus implements an \gls{ABM} paradigm.  \gls{ABM} is modern, sophisticated, 
+true to reality, and it incorporates modern computing resources.  
+Furthermore, \gls{ABM} provides a natural 
+perspective from which to model a given problem. In the nuclear fuel cycle 
+context, for example, an analyst can design an agent with reactor-related logic 
+that is entirely independent from an agent with fuel fabrication-related 
+logic. Defining the behavior of both agents according to the 
+\gls{API} contract is sufficient for them to interact with one another as 
+bona fide actors in the simulation.  The two archetype libraries can be used in the same
+simulation without any shared knowledge.
+
+Furthermore, the \gls{ABM} paradigm is easily comparable to system dynamics models.
+System dynamics is a popular approach for modeling nuclear fuel cycles 
+\cite{jacobson_vision_2009,van_den_durpel_daness_2009,guerin_impact_2009,guerin_benchmark_2009}. 
+Formally however, system dynamics models are simply a strict subset of agent-based models
+\cite{macal_agent-based_2010}.
+That is, any system dynamics model can be translated
+into an agent-based model. Furthermore, because agent-based
+techniques can provide a richer model than can system dynamics, they enable the 
+broadest range of simulations in a generic fashion.
+
+\subsubsection{Agent Interchangeability}\label{sec:interchangeability}
 
@@
 
-\subsection{Regions, Institutions, and Facilities}
+\subsubsection{Regions, Institutions, and Facilities}
 
@@
 
-\subsection{Resources and Materials}
+\subsection{Discrete Objects}
+% enables more realistic models and metrics
+% material routing metrics
+% shadow fuel cycles
+% etc.
+
+\Cyclus models facilities, institutions, regions, and resources as discrete 
+objects. A discrete resource model allows for a range of modeling granularity. In the
+macroscopic extreme, it is equivalent to time-stepped continuous flow. In the
+microscopic extreme, the model is capable of representing arbitrarily small 
+material objects at isotopic resolution. In this way, \Cyclus is 
+applicable across the full range of modeling extremes.
+
+Although some questions require resolution at the level of 
+individual facilities and materials, 
+Fleet-based, lumped-material models do not distinguish between discrete
+facility entities or materials.  As a result, many detailed performance 
+metrics cannot be captured with previously existing tools.
+The generality of \Cyclus therefore enables many use cases 
+that cannot be achieved with fleet-based models.
+
+One such use case seeks to capture system vulnerability to nefarious 
+material diversion. Provenance and trade-history of distinct materials is the fundamental 
+information unit in such studies, and so this type of analysis requires
+ discrete simulation of a 
+target facility and the individual materials modified within it. 
+Provenance and trade-history of distinct materials is the fundamental 
+information unit in such studies. 
+Material risk analysis, therefore, demands discretely modeled objects like those 
+in \Cyclus.
+
+There are a number of types of users and developers who will 
+interact with \Cyclus. National laboratory researchers,
+academic researchers, private-industry economic forecasters, and even students 
+in engineering courses may benefit from the ease of development and
+customization provided by the discrete, modular, agent-based architecture of \Cyclus.
+
+\subsubsection{Resources and Materials}
 % Resources, Materials (note isotope tracking, decay behavior)
@@
 
-\subsection{Toolkit}
+\subsubsection{Dynamic Resource Exchange}
+
+Placeholder as a reminder to add more detail about this.
+
+\subsection{Software Decisions}
+
+\subsubsection{Cluster-Ready Software}
+
+Many fuel cycle simulators rely on \gls{COTS} and Windows-only software that limits 
+performance on resource computing infrastructures. This limitation severely 
+increases the wall-clock time necessary to conduct parameterized sensitivity 
+analyses and other multi-simulation studies. \Cyclus, on the other hand, is 
+primarily written in \texttt{C++} and relies on 
+libraries supported by Linux and UNIX (including Ubuntu and OSX) platforms, 
+which are flexible and support parallelization. 
+Furthermore, the core infrastructure and related archetypes are free and 
+open source, BSD-3-clause licensed. No part of \Cyclus is proprietary or based 
+on \gls{COTS}, Windows-based software. It can be easily deployed 
+on large computer systems, such as \gls{HTC} systems.
+
+Cyclopts (\TODO{cite}), a proof of principle design and implementation of \Cyclus on such a large computer system,
+ uses UW-Madison's HTCondor \gls{HTC} infrastructure to perform sensitivity
+studies on \Cyclus' resource exchange optimization solvers. To date, it has been
+used to run over $10^4$ jobs, or (\TODO{compute time}) total compute hours, using
+the \Cyclus library via its resource exchange \gls{API}.
+The \gls{HTC} infrastructure has also been utilized to run and collect
+information from full \Cyclus simulations running in parallel on $10^3$
+machines reliably for order $10^5$ simulations.
+
+\subsubsection{Framework Structure}
+% (OO, cpp, xml, backends, inheritances, mixins, generic apis, etc.)
+
+\begin{figure}[htbp!]
+\begin{center}
+\includegraphics[width=\textwidth]{./images/framework}
+\end{center}
+\caption{The \Cyclus core provides \gls{API}s that abstract away the details in 
+the kernel and allow the archetypes to be loaded into the simulation in a modular 
+fashion.}
+\label{fig:framework}
+\end{figure}
+
+\acrlong{ABM} is inherently object-oriented because agents represent 
+discrete, independently acting objects.  Figure \ref{fig:framework} illustrates
+the modular nature of \Cyclus archetypes.  The core of the \Cyclus simulator 
+creates a set of key classes on which agent plug-ins 
+are based. In addition, a set of key tools are also provided to enrich the 
+\gls{API} and supply a robust suite of behaviors for the developer. 
+Agent plug-ins utilize the generic core \gls{API} to interact with one another.  For 
+example, agents rely on a paradigm of dynamic loading and clean plug-in 
+behavior at the start of the simulation. They also use the resource exchange 
+paradigm \gls{API} for trading resources with one another.
+
+\subsection{Simulation Assistance}
+
+\subsubsection{Toolkit}
 
@@
 
-\subsubsection{Simulation Tools}
+\paragraph{Simulation Tools}
 
@@
 
-\subsubsection{Nuclear Engineering Tools}
+\paragraph{Nuclear Engineering Tools}
 
@@
 
-\subsubsection{Toolkit Extensions}
+\paragraph{Toolkit Extensions}
 
@@
 
-\subsection{Cycamore}
+\subsubsection{Cycamore}
 % base modules
@@
 \end{figure}
+
+\subsection{Quality Assurance}
+% Organize this section according to major topics
+% give each topic a section heading in boldface.
+% try to cover the major common points :
+%
+% problem design
+% methods of measurement
+% supporting models
+% supporting data
+% simulations run
+% results
+
+% Just write the section headings for each part and indicate what goes in that
+% section with words :
+%
+% heading
+% figures (with captions)
+% schematics (with captions and footnotes)
+% equations
+% tables
+
+% What does it mean?
+% What did I actually test?
+% What were the results?
+% Did the work yield a new method?
+% Did the work yield new knowledge?
+% What measurements did I make?
+% How were these measurements characterized?
+% What methods were used?
+% What were the results?
+% How were the measurements made and characterized?
+
+Simulation science - like experimental science - has since the beginning had the 
+problem of identifying trustworthy results from nonsensical results or noise.
+This is epitomized by Charles Babbage, ``On two occasions I have been asked, 
+`Pray, Mr. Babbage, if you put into the machine wrong figures, will the right 
+answers come out?' ... I am not able rightly to apprehend the kind of confusion 
+of ideas that could provoke such a question.'' \cite{babbage_passages_2011}. 
+A simulator must both guard against the \emph{garbage in, garbage out} phenomenon, and also assure correctness.
+
+Multiple strategies, collectively known as \emph{\gls{QA}}, have 
+been invented over the years to mitigate the structural and algorithmic errors
+on the part of simulators themselves. These include \emph{\gls{VV}}
+\cite{boehm_software_1989}, \emph{\gls{UQ}} 
+\cite{sacks_design_1989}, testing, and others. \gls{VV} and \gls{UQ} come from 
+a distinctly computational science background while testing \emph{et al.} come from software development.
+
+Nuclear engineering code quality is often governed by \gls{NQA1}, an 
+\gls{ASME} specification 
+whose latest revision appeared in 2009 \cite{asme_nqa-1a-2009_2009}.  
+Although \gls{NQA1} is primarily 
+used for designing reactors, it is general enough to apply to 
+\Cyclus. \Cyclus has adopted an \emph{agile} development process 
+\cite{larman_agile_2004}, 
+interpreting \gls{NQA1} in a manner similar to the process adopted by the 
+\gls{DOE} within \gls{NEAMS} \cite{neams_nuclear_2013} or the 
+PyNE toolkit \cite{biondo_quality_2014}.
+
+Quality assurance is an on-going process throughout the 
+entire life of the code. As a simulator where most modeling decisions are made 
+by third party archetype developers or users, the most important feature of 
+\gls{QA} is verification. Validation may be impossible and \gls{UQ} is beyond 
+the scope of the kernel.
+
+Verification may be defined as the question, ``Is \Cyclus being built correctly?'' 
+To answer this question, we turn to the software development of notions of testing,
+documentation, version control, style guidelines, and continuous integration. 
+This suite of process controls supplies mechanism for reliable and reproducible 
+software. The impetus to implement these controls correctly is particularly strong in a scientific 
+context because of the emphasis on reproducibility and provenance. These verification techniques are 
+discussed individually in the sections that follow.
+
+Validation, in contrast,  may be defined as the question, 
+``Is \Cyclus the correct tool?''
+Since \Cyclus is alone in its class as an agent-based fuel cycle simulator, longitudinal 
+validation is not possible. Nonetheless, code-to-code comparisons with fuel cycle
+simulators that use other modeling paradigms are underway, if nascent. However, such 
+exercises are more likely to bring into relief the differences between the modeling
+paradigms than supply substantial \gls{QA} and validation.
+
+Lastly, \gls{UQ} is a process that is used on specific simulation
+instantiations to statistically determine quality. \gls{UQ} is a process that applies 
+to the running of many \Cyclus simulations. The kernel itself, as a generic fuel cycle 
+simulator, cannot make reliable statements about the uncertainty of a particular fuel 
+cycle. Any \gls{UQ} results are applicable only to the scenario that is under 
+analysis by the user. \Cyclus is not a panacea for due dillegence on behalf of the fuel 
+cycle modeler. Thus, \gls{UQ} is envisioned to be beyond the scope of core development 
+and in the domain of the expert user.
+
+Sections \ref{sec:qa-testing}-\ref{sec:qa-ci} discuss in greater detail the software 
+development components that comprise the \Cyclus verification strategy.
+Each of these on its own is a valuable addition to \gls{QA} but is cannot be the 
+entire answer to the requirements imposed by \gls{NQA1}. Taken together and strictly 
+adhered to, they present a fortress to protect against poorly designed or otherwise undesirable code.
+
+\subsubsection{Testing}
+\label{sec:qa-testing}
+
+Automated software \emph{testing} is the first line of defense against
+errors in implementation. It also acts as an early warning sign if the
+simulator does not work as intended on a new system.
+Testing serves a critical role in \gls{QA} because it directly compares the 
+results of running software versus the expected behavior of the software.
+In \Cyclus, three categories of tests are defined: unit tests, integration 
+tests, and regression tests.
+
+It is important to note that before a proposed
+code change is allowed into \Cyclus,  the change must be covered by a test, either new or existing, and all of the tests must pass.  This is a
+matter of policy for the developers. Of course, test code is 
+just as likely to contain errors as the code it is designed to test. 
+However, it is assumed that diligence and one level of testing 
+is sufficient to meet the aims of \gls{QA} and prevent an infinite recursion
+of testing-the-tests.
+
+\paragraph{Unit Tests}
+
+Unit tests compare the results of the smallest code \emph{unit}, 
+typically a single function or a class. What constitutes the smallest code
+unit depends on the context of the specific unit in question. While this is 
+an ambiguous definition, when combined with a philosophy of keeping units as small
+as possible, it is often clear in practice what needs to be tested.
+
+\Cyclus uses the Google Test framework \cite{inc_googletest_2008} as a harness for running unit 
+tests. Sufficient unit tests are required for any proposed change to the \Cyclus
+code base. Currently \Cyclus implements over 450 unit tests and \Cycamore implements 
+85.  These cover approximately 65\% of their respective code bases, and their numbers are expected to grow over time.
+
+\paragraph{Integration Tests}
+
+Integration tests combine multiple elements of the 
+\Cyclus interface and test that they work correctly with each other.  By analogy, 
+simply because the gears (units) are made correctly does not imply that the 
+clock (integration) will run smoothly, run at all, or give the correct time.
+In \Cyclus and \Cycamore, integration tests are performed by running sample
+simulations and verifying that results are what would be expected ahead of 
+time. A set of standard input files have thus been constructed. 
+Python is used to run the same set of \Cyclus simulations as a subprocess for each integration test.
+The results are then inspected and compared via Nose \cite{pellerin_nose_2007}, a Python test framework.
+In this way, \Cyclus code units are tested in the full context that they will be
+executed. This category of testing is especially useful for ensuring that 
+major \Cyclus components are functioning as expected.
+
+\paragraph{Regression Tests}
+
+Regression tests ensure significant changes do not 
+occur over the course of \Cyclus development. Such a change is called a 
+\emph{regression} because the new version is almost always wrong.
+Regression tests are implemented similarly to integration tests.
+Nose is used to execute full \Cyclus simulations whose results
+are then compared. In this category, however, the comparison is done against 
+the output of the same input file when run with a previous version of \Cyclus, 
+typically the last released version.
+In some sense, regression tests are `dumb' in that they do 
+not care about the contents of a simulation being correct, only whether or not 
+it changed. They pick up glaring time-sensitive mistakes that may 
+not appear elsewhere, though they do not purport to make claims about the
+quality of the physics modeled. Regression tests are primarily implemented
+in \Cycamore because its archetypes are sophisticated enough
+to make interesting input files. Only a handful ($<10$) of time steps are needed 
+for regression testing.
+
+\subsubsection{Documentation}
+
+All of the public interface (the \gls{API}) must be documented as required by the \Cyclus
+\gls{QA} policy. This certifies that the intention for a code unit is communicated 
+in way that is separate from its implementation. This policy is important 
+because implementations are often wrong and do not reliably communicate their intent. Truly trustworthy communication about what 
+software should be doing occurs when the author explicitly states the 
+goals of an \gls{API} in prose form. Future development of the code is then able to 
+compare the implementation versus the documentation to discern whether or not they 
+are in agreement. Documentation is thus a secondary higher-level information 
+stream.  In \Cyclus, this information is aggregated together into static 
+websites with the Doxygen \cite{van_heesch_doxygen:_2008} and Sphinx 
+\cite{brandl_sphinx_2014} 
+tools, and can be accessed at \url{http://fuelcycle.org}.
+
+\subsubsection{Version Control}
+
+Version control is the history-preserving mechanism by which the provenance of 
+a code is recorded. \Cyclus uses a well-established tool called git 
+\cite{software_freedom_conservancy_git_2014}
+for this purpose. Git is currently the most popular utility in the recent wave
+of \emph{distributed version control}. Briefly stated, this means that every 
+user has a complete local copy of the \emph{repository} (the version control
+term for the collection of all possible histories).
+Though there are many praises and criticisms of git, one 
+feature that the tool performs exceptionally well is the notion of code branches.
+These are distinct pathways in the history that branch out of a mainline source
+tree and then may be \emph{merged} back into the mainline. Multiple simultaneous
+branches may exist at all points in time. Every change to the code is recorded
+in the history, along with metadata such as the author, a timestamp, and an 
+accompanying message. Thus 
+it is possible for \Cyclus to accurately replay the entirety of who did what to the
+code when.
+
+\Cyclus uses a strategy known as \emph{git flow} 
+\cite{kalliamvakou_code-centric_2014} 
+to manage topical branches where individuals develop code: the mainline development
+branch (simply known as develop), and the stable branch (called master).
+In addition to these rules and delineations, \Cyclus also imposes rules on 
+when it is acceptable from a quality control standpoint to merge code from 
+the personal topical branches into the develop branch. All software at this stage 
+must have sufficient successful tests and comprehensive documentation. Without
+these core pieces, proposed changes are not allowed into \Cyclus. As an example, a schematic of 
+the development stages between reporting a bug and merging the fix is shown in 
+Figure \ref{fig:gitprocess}.
+
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[height=0.6\textheight]{./images/gitprocess}
+\end{center}
+\caption{A version-control enabled process for finding, reporting, and fixing a bug 
+can take place within an issue tracker alongside multiple stages of code 
+testing and review. In the \Cyclus case, the final review stage includes unit, 
+regression, and integration testing as well as manual code inspection.}
+\label{fig:gitprocess}
+\end{figure}
+
+The act of proposing a change is known as a \emph{pull request}. The main \Cyclus repository is 
+hosted remotely on the GitHub website \cite{dabbish_social_2012}. The online
+mechanism for pull requests allows for code review by a member of the \Cyclus 
+core team, separate from the author, prior to any change being included. Non-members
+of the \Cyclus development team are allowed and encouraged to submit and review 
+pull requests. However, only members of the \Cyclus core team are allowed to 
+merge in any changes and only after the \gls{QA} standards have been met.
+
+\subsubsection{Style Guide}
+
+In any multi-person software project, there is a tension between how individuals
+wish to write code. Every person tends to have their own custom style. To remedy this,
+coding style guides are the software analogy to those for written language,
+such as the Chicago Manual of Style. \Cyclus strictly enforces the use of the 
+Google C++ Style Guide \cite{weinberger_google_2008} for all software contributions.
+This means that all developers of \Cyclus nominally write \Cyclus code in the same 
+way.  This homogenization may be a hurdle to new developers but ultimately 
+improves code legibility. Adoption of a single style guide also settles
+timeless arguments over what style is `the best.' Having only one means that 
+there is a common enemy for all developers to dislike equally.
+
+\subsubsection{Continuous Integration}
+\label{sec:qa-ci}
+
+\emph{\acrfull{CI}} is the idea that software should be tested and validated 
+as it is being developed, rather than as a final stage in a longer development 
+cycle.  Under \gls{CI}, every pull request is tested independently immediately after 
+it is proposed. Such tests are run on all officially supported platforms. 
+\Cyclus uses a \gls{CI} platform called Polyphemus \cite{scopatz_polyphemus_2014}. Polyphemus serves as an intermediary between GitHub pull requests on the frontend 
+and temporary \Cyclus servers on the backend. These servers are hosted by 
+the Build \& Test Laboratory (BaTLab) \cite{uw_batlab_team_batlab_2014} at the University of 
+Wisconsin-Madison. Whenever a pull request is created, Polyphemus performs 
+the following actions:
+
+\begin{enumerate}
+    \item Copies \Cyclus with the pull requested code to BaTLab,
+    \item Initializes Linux and Mac OSX servers,
+    \item Builds \Cyclus on all platforms,
+    \item Runs the complete \Cyclus test suite, 
+    \item Reports back whether the above steps succeeded or not.
+\end{enumerate}
+
+Since these steps are performed for all incoming code, it is easy for the 
+\Cyclus core team to determine whether or not an individual pull request 
+actually works. This helps identify build and test problems prior to 
+broken code being allowed into the develop branch. \gls{CI} is a necessary 
+but not sufficient addition to the \Cyclus \gls{QA}
+system. Its merit is that it prevents bad code from being implemented. However, \Cyclus will always
+require human eyes and hands to let good code in.

### 2014-12-02 fundamentals/intro.tex

@@
 the creation and interchangeability of custom archetypes at any level of fidelity.
-
-\subsubsection{Modular Architecture}
-% Motivation for encapsulated plug-in architecture 
-% enables ecosystem, ease of contribution across institutions
-% enables myriad levels of simulation fidelity
-% enables FC analyses that can compare ‘apples to apples'
-
-The architecture of \Cyclus allows developers 
-to define nuclear fuel cycle agents and processes independent of the simulation 
-logic. This encapsulated `plug-in'
-design choice provides two major benefits. First, analysts across research institutions can take advantage of the 
-simulation logic \gls{API} and archetype ecosystem when they apply \Cyclus to 
-their specific problem. This 
-mend-and-extend paradigm, common in modern software development, reduces 
-maintenance overhead and improves code robustness \cite{citation_needed}. 
-The researcher can focus on creating or customizing nuclear 
-facility, institution, resource, and toolkit models within their specific area 
-of technical expertise. This extensibility, magnified by an open source 
-development process, frees the community of users to contribute desired 
-features, independent from the team of \Cyclus core developers. 
-% we could use a specific example of Cosi's equivalence method below
-Second, because \Cyclus uses a modular archetype approach, comparing two 
-archetypes is straightforward. Consider a case in which an analyst would like 
-to compare the effect of using different models to determine the input fuel 
-composition for fast reactors. A variety of fuel fabrication archetypes can be 
-developed and interchanged while keeping the rest of the fuel cycle fixed
- to compare fuel fabrication designs.
-
-\subsubsection{Agent-based Paradigm}
-% superior detail in capturing simulation dynamics
-% more flexible control over behavior
-% describe Region/Institution/Facility hierarchy
-% note importance of generic resource exchange paradigm
-
-\Cyclus implements an \gls{ABM} paradigm.  \gls{ABM} is modern, sophisticated, 
-true to reality, and it incorporates modern computing resources.  
-Furthermore, \gls{ABM} provides a natural 
-perspective from which to model a given problem. In the nuclear fuel cycle 
-context, for example, an analyst can design an agent with reactor-related logic 
-that is entirely independent from an agent with fuel fabrication-related 
-logic. Defining the behavior of both agents according to the 
-\gls{API} contract is sufficient for them to interact with one another as 
-bona fide actors in the simulation.  The two archetype libraries can be used in the same
-simulation without any shared knowledge.
-
-Furthermore, the \gls{ABM} paradigm is easily comparable to system dynamics models.
-System dynamics is a popular approach for modeling nuclear fuel cycles 
-\cite{jacobson_vision_2009,van_den_durpel_daness_2009,guerin_impact_2009,guerin_benchmark_2009}. 
-Formally however, system dynamics models are simply a strict subset of agent-based models
-\cite{macal_agent-based_2010}.
-That is, any system dynamics model can be translated
-into an agent-based model. Furthermore, because agent-based
-techniques can provide a richer model than can system dynamics, they enable the 
-broadest range of simulations in a generic fashion.
-
-\subsubsection{Discrete Objects}
-% enables more realistic models and metrics
-% material routing metrics
-% shadow fuel cycles
-% etc.
-
-\Cyclus models facilities, institutions, regions, and resources as discrete 
-objects. A discrete resource model allows for a range of modeling granularity. In the
-macroscopic extreme, it is equivalent to time-stepped continuous flow. In the
-microscopic extreme, the model is capable of representing arbitrarily small 
-material objects at isotopic resolution. In this way, \Cyclus is 
-applicable across the full range of modeling extremes.
-
-Although some questions require resolution at the level of 
-individual facilities and materials, 
-Fleet-based, lumped-material models do not distinguish between discrete
-facility entities or materials.  As a result, many detailed performance 
-metrics cannot be captured with previously existing tools.
-The generality of \Cyclus therefore enables many use cases 
-that cannot be achieved with fleet-based models.
-
-One such use case seeks to capture system vulnerability to nefarious 
-material diversion. Provenance and trade-history of distinct materials is the fundamental 
-information unit in such studies, and so this type of analysis requires
- discrete simulation of a 
-target facility and the individual materials modified within it. 
-Provenance and trade-history of distinct materials is the fundamental 
-information unit in such studies. 
-Material risk analysis, therefore, demands discretely modeled objects like those 
-in \Cyclus.
-
-There are a number of types of users and developers who will 
-interact with \Cyclus. National laboratory researchers,
-academic researchers, private-industry economic forecasters, and even students 
-in engineering courses may benefit from the ease of development and
-customization provided by the discrete, modular, agent-based architecture of \Cyclus.

### 2014-12-03 fundamentals/examples.tex
fixes figure label issue
capitalizes f
tiny changes

@@
 
-The success of the \Cyclus simulator is illustrated by demonstrations
+The functionality of the \Cyclus simulator is illustrated by demonstrations
 of its fundamental simulation capabilities and the feasibility the
  community-driven \Cyclus development model.
-Nascent promising growth of the \Cyclus 
 The success of the \Cyclus simulator can be measured in many ways. 
@@
 ecosystem at multiple institutions indicates that a fuel cycle simulator can 
-advance in a community-drive development paradigm. Additionally, simple 
+advance in a community-driven \textbf{collaborative?} development paradigm. Additionally, simple 
 simulations as well as more complex recycling simulations demonstrate that 
-\Cyclus possesses fundamental fuel cycle simulation capabilities.
+\Cyclus possesses fuel cycle simulation capabilities.
 
@@
 \end{itemize}
-Taken together, these form an `ecosystem' of capabilities. Over time, this 
-ecosystem will grow as archetype-developers, kernel-developers, and 
+Taken together, these form an ecosystem of capabilites. Over time, this 
+ecosystem will grow as archetype developers, kernel developers, and 
 even users contribute capabilities developed for their own needs. Indeed, the 
@@
 the ecosystem demonstrate a significant achievement by the \Cyclus framework 
-and provide hope for a community-driven development model.
+and provide the basis for a community-driven development model.
 
@@
 A number of projects and tools outside of the core simulation kernel have been 
-developed which improve the scope and the diversity of the capabilities in the \Cyclus 
+developed to improve the scope and the diversity of the capabilities in the \Cyclus 
 ecosystem. Table \ref{tab:coretools} lists the tools and projects developed 
@@
 developer-contributed capabilities.  They add to the fundamental \Cycamore
-archetypes by providing physics-based reactors, separation, fabrication, and storage
+archetypes by providing physics-based reactors, separation, fabrication, storage
 facilities, and expanded institutional paradigms.  These contributed archetypes
@@
 
-Because material is tracked as discrete objects, single-pass \gls{MOX} 
-recycle is easy to implement in \Cyclus.  The MOX simulation includes one provider of fresh
+Because material is tracked as discrete objects, single-pass recycle using \gls{MOX} 
+fuel is easy to implement in \Cyclus.  The \gls{MOX} simulation includes one provider of fresh
 \gls{UOX} fuel, one recycled fuel fabrication facility, one reactor, one separations
@@
 %** full-system plutonium buildup for open
-(no recycle), modified open, and closed (infinite-pass recycle) variations of
+\TODO{(no recycle), modified open, and closed (infinite-pass recycle)
+variations of}
 %the scenario described above (all just a single reactor).  **
@@
 commodity. Custom, non-uniform preferences can be set for each different fuel
-commodity.  The dynamic resource exchange makes it easy for a reactor to
+commodity.  The dynamic resource exchange \TODO{acro or not?} enables a reactor to
 preferentially accept recycled \gls{MOX} fuel over fresh \gls{UOX} fuel.  In this
@@
 The \Class{Source} and \Class{Sink} archetypes from \Cycamore have been used as a
-source of fresh, enriched uranium and a repository respectively. A simple
+source of fresh, enriched uranium and a repository, respectively. A simple
 custom recycled fuel fabrication facility was also used, which mixes fissile 
@@
 that used by the \gls{COSI} fuel cycle simulator \TODO{cite COSI equivalence
-method}. The material flows for this simulation are shown below in figure
+method}. The material flows for this simulation are shown below in Figure
 \ref{fig:flowmodopen}.
@@
 \begin{figure}[H]
-\label{fig:flowmodopen}
-\caption{Modified open 1-pass \gls{MOX} recycle fuel cycle material flows.}
 \begin{center}
@@
 \end{center}
+\caption{Modified open 1-pass \gls{MOX} recycle fuel cycle material flows.}
+\label{fig:flowmodopen}
 \end{figure}
 
-To switch to a fully closed fuel cycle, all that needs to be done is change
-the output commodity for the spent \gls{MOX} fuel of the \Class{BatchReactor}, 
-requiring only a one-word change in the input file:
+Changing this to a fully closed fuel cycle entails only a one-word change in the input file
+regarding the output commodity for the spent \gls{MOX} fuel of the
+\Class{BatchReactor}:
 
@@
 \end{lstlisting}
-
-This results in new the material flows in Figure \ref{fig:flowclosed}. Note
-that because the \Class{BatchReactor} always transmutes fuel into the same
-composition, the nuclide level flows are not very realistic for the full, 
+This results in the material flows in Figure \ref{fig:flowclosed}. Note
+that the \Class{BatchReactor} always transmutes fuel into the same
+composition, so the nuclide level flows are unrealistic for the full, 
 multi-pass
@@
 \begin{figure}[H]
-\label{fig:flowclosed}
-\caption{Full \gls{MOX} recycle (multi-pass) fuel cycle material flows.}
 \begin{center}
@@
 \end{center}
+\caption{Full \gls{MOX} recycle (multi-pass) fuel cycle material flows.}
+\label{fig:flowclosed}
 \end{figure}
@@
 Figure \ref{fig:puseries1} shows the full-system plutonium buildup for open
-(no recycle), modified open, and closed (infinite-pass recycle) variations of
+(no recycle), modified open, and closed (infinite-pass recycle) \TODO{whats
+the diff btw closed and the multi-pass from above? It's referred to as fully
+closed multi-pass recycle, which is a bit confusing.} variations of
 the scenario described above (all just a single reactor).  The figure was
 generated directly from \Cyclus output data. After several batch cycles (near
-month 300) in the modified open and closed cases, enough separated fissile
+month 300 \TODO{here and below: month or time step?}) in the modified open and closed cases, enough separated fissile
 material accumulates in the fuel fabrication facility to generate a full
@@
 Because the modified open scenario does not re-recycle material, it takes the
-fabrication facility 1 cycle longer to accumulate a full batch worth of
+fabrication facility 1 cycle longer to accumulate a full batch of
 fissile material.
@@
 \end{center}
+\caption{System plutonium buildup with one reactor.}
+\label{fig:puseries1}
 \end{figure}
@@
 The open, modified open, and closed scenarios can easily be modified to have
-several reactors each with staggered refueling times. The plutonium buildup
+several reactors with staggered refueling times. The plutonium buildup
 for these three multi-reactor variations is shown in Figure

### 2014-12-03 fundamentals/intro.tex
tiny changes

@@
 allows cross-institutional collaboration, increases code robustness, and 
-cultivates an ecosystem of calculation options 
+cultivates an ecosystem of modeling and calculation options 
 \cite{softwarecarpentryresource}.  The fundamental concepts of the \Cyclus 
@@
 \Cyclus emerged from a line of tools seeking to break this practice.  
-Its precurser, \gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006}, was begun at \gls{LDRD}, began at \gls{INL} and sought 
+Its precurser,
+\gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006}, began
+at \gls{LDRD} within \gls{INL} and sought 
 to provide generic regional capability.  Based on lessons learned from 

### 2014-12-03 fundamentals/impl.tex
more changes to outline and adding text/TODOs where needed as a result of reorg

@@
 build \Cyclus on open source libraries in modern programming languages enables 
-both remote and mutiprocess execution on a number of platforms. This section begins by 
+both remote and multiprocess execution on a number of platforms. This section begins by 
 describing the general design features that make \Cyclus both flexible and powerful:
-cluster-ready software, dynamic libraries, and interchangeable agents. It then introduces
-the specific framework of \Cyclus: the region-institution-facility hierarchy, handling
-of resources and materials, the Cycamore library of agents, and the experimental toolkit.
+cluster-ready software and dynamic libraries.  Next, the framework using an
+\gls{ABM} paradigm, which provides an expansion in performance beyond typical systems dynamics
+capabilities, is described, focusing on agent interchangeability and the 
+implementation of the region-institution-facility heirarchy. 
+Next, the discrete treatment of objects is discussed in terms of both
+resources and materials and time via the \TODO{DRE}.
+Support for users and developers via the Cycamore library of
+agents \TODO{archetypes?} and the experimental toolkit are also presented.
+Lastly, the methods for quality assurance are outlined.
 These features provide a solid foundation on which to build an interconnected community 
@@
 
-\subsection{Modular Architecture}
+\subsection{Software Architecture}
 % Motivation for encapsulated plug-in architecture 
@@
 Second, because \Cyclus uses a modular archetype approach, comparing two 
-archetypes is straightforward. Consider a case in which an analyst would like 
+archetypes is straightforward. For example, if an analyst would like 
 to compare the effect of using different models to determine the input fuel 
-composition for fast reactors. A variety of fuel fabrication archetypes can be 
+composition for fast reactors, a variety of fuel fabrication archetypes can be 
 developed and interchanged while keeping the rest of the fuel cycle fixed
  to compare fuel fabrication designs.
+
+\subsubsection{Cluster-Ready Software}
+
+Many fuel cycle simulators rely on \gls{COTS} and Windows-only software that limits 
+performance on resource computing infrastructures. This limitation severely 
+increases the wall-clock time necessary to conduct parameterized sensitivity 
+analyses and other multi-simulation studies. \Cyclus, on the other hand, is 
+primarily written in \texttt{C++} and relies on 
+libraries supported by Linux and UNIX (including Ubuntu and OSX) platforms, 
+which are flexible and support parallelization. 
+Furthermore, the core infrastructure and related archetypes are free and 
+open source, BSD-3-clause licensed. No part of \Cyclus is proprietary or based 
+on \gls{COTS}, Windows-based software. It can be easily deployed 
+on large computer systems, such as \gls{HTC} systems.
+
+Cyclopts (\TODO{cite}), a proof of principle design and implementation of \Cyclus on such a large computer system,
+ uses UW-Madison's HTCondor \gls{HTC} infrastructure to perform sensitivity
+studies on \Cyclus' resource exchange optimization solvers. To date, it has been
+used to run over $10^4$ jobs, or (\TODO{compute time}) total compute hours, using
+the \Cyclus library via its resource exchange \gls{API}.
+The \gls{HTC} infrastructure has also been utilized to run and collect
+information from full \Cyclus simulations running in parallel on $10^3$
+machines reliably for order $10^5$ simulations.
 
@@
 
-\Cyclus implements an \gls{ABM} paradigm.  \gls{ABM} is modern, sophisticated, 
+\Cyclus implements an \acrlong{ABM} paradigm.  \gls{ABM} is modern, sophisticated, 
 true to reality, and it incorporates modern computing resources.  
@@
 \subsubsection{Agent Interchangeability}\label{sec:interchangeability}
+
+% (OO, cpp, xml, backends, inheritances, mixins, generic apis, etc.)
+
+\begin{figure}[htbp!]
+\begin{center}
+\includegraphics[width=\textwidth]{./images/framework}
+\end{center}
+\caption{The \Cyclus core provides \gls{API}s that abstract away the details in 
+the kernel and allow the archetypes to be loaded into the simulation in a modular 
+fashion.}
+\label{fig:framework}
+\end{figure}
+
+\gls{ABM} is inherently object-oriented because agents represent 
+discrete, independently acting objects.  Figure \ref{fig:framework} illustrates
+the modular nature of \Cyclus archetypes.  The core of the \Cyclus simulator 
+creates a set of key classes on which agent plug-ins 
+are based. In addition, a set of key tools are also provided to enrich the 
+\gls{API} and supply a robust suite of behaviors for the developer. 
+Agent plug-ins utilize the generic core \gls{API} to interact with one another.  For 
+example, agents rely on a paradigm of dynamic loading and clean plug-in 
+behavior at the start of the simulation. They also use the resource exchange 
+paradigm \gls{API} for trading resources with one another.
 
@@
 
+\TODO{AO Opinion: Move some of the detail from this intro to the main section
+on discrete materials. Then add an intro to the discrete time/DRE as well.}
+
 \subsubsection{Resources and Materials}
@@
 
+\TODO{This is SO for you, Matt Gidden!}
 Placeholder as a reminder to add more detail about this.
 
-\subsection{Software Decisions}
+\subsection{Simulation Assistance}
+\TODO{section intro needed}
+To assist beginner users and developers in accomplishing working simulations
+in the shortest time possible,
 
-\subsubsection{Cluster-Ready Software}
+\subsubsection{Cycamore}
+% base modules
 
-Many fuel cycle simulators rely on \gls{COTS} and Windows-only software that limits 
-performance on resource computing infrastructures. This limitation severely 
-increases the wall-clock time necessary to conduct parameterized sensitivity 
-analyses and other multi-simulation studies. \Cyclus, on the other hand, is 
-primarily written in \texttt{C++} and relies on 
-libraries supported by Linux and UNIX (including Ubuntu and OSX) platforms, 
-which are flexible and support parallelization. 
-Furthermore, the core infrastructure and related archetypes are free and 
-open source, BSD-3-clause licensed. No part of \Cyclus is proprietary or based 
-on \gls{COTS}, Windows-based software. It can be easily deployed 
-on large computer systems, such as \gls{HTC} systems.
+\Cycamore \cite{carlsen_cycamore_2014}, the \Cyclus additional module
+repository, provides a fundamental set of agent archetypes for basic simulation 
+functionality within \Cyclus.  Since \Cyclus relies on external 
+archetypes to represent the agents within a simulation, \Cycamore provides the 
+basic archetypes a new user needs to get started running simple simulations.  
+These archetypes support a minimal set of fuel cycle simulation goals and 
+provide, by example, a guide to new developers who would seek to contribute 
+their own archetypes outside of \Cycamore.
 
-Cyclopts (\TODO{cite}), a proof of principle design and implementation of \Cyclus on such a large computer system,
- uses UW-Madison's HTCondor \gls{HTC} infrastructure to perform sensitivity
-studies on \Cyclus' resource exchange optimization solvers. To date, it has been
-used to run over $10^4$ jobs, or (\TODO{compute time}) total compute hours, using
-the \Cyclus library via its resource exchange \gls{API}.
-The \gls{HTC} infrastructure has also been utilized to run and collect
-information from full \Cyclus simulations running in parallel on $10^3$
-machines reliably for order $10^5$ simulations.
+As of version 1.0, \Cycamore contains four facility archetypes, one region 
+archetype, and two institution archetypes. Short descriptions of these 
+functions can be found in Table \ref{tab:cycamore}.
 
-\subsubsection{Framework Structure}
-% (OO, cpp, xml, backends, inheritances, mixins, generic apis, etc.)
+\begin{table}[h]
+\centering
+\begin{tabularx}{\textwidth}{|r|l|X|}
+\hline
+\textbf{Entity} & \textbf{Archetype} & \textbf{Functionality} \\
+\hline
+Facility & BatchReactor & A reactor model that handles batch refueling, based on pre-determined recipes of compositions. \\
+Facility & Source & This facility generates material of the composition and commodity type specified as input.  \\
+Facility & Sink & This facility is capable of accepting a finite or infinite quantity of some commodity produced in the simulation. \\
+Facility & EnrichmentFacility & This facility enriches uranium at a specified capacity. \\
+Institution & ManagerInst & The manager institution manages production of commodities among its facilities by building new ones as needed. \\
+Institution & DeployInst &  This institution deploys specific facilities as defined explicitly in the input file. \\
+Region & GrowthRegion & This region determines whether there is a need to meet a certain capacity (as defined via input) at each time step. \\
+\hline
+\end{tabularx}
+\caption{The Archetypes in \Cycamore seek to cover a large range of simple simulation use cases.}
+\label{tab:cycamore}
+\end{table}
+
+The current \Cycamore release provides only 
+basic functionality, enabling simple fuel cycle analyses. 
+As illustrated in Figure \ref{fig:simplesim}, \Cycamore provides the tools for users
+to get started quickly with simple 
+once-through fuel cycle scenarios. As future contributions are vetted, the capabilities in \Cycamore may grow.
 
@@
 \begin{center}
-\includegraphics[width=\textwidth]{./images/framework}
+\includegraphics{./images/simplesim}
 \end{center}
-\caption{The \Cyclus core provides \gls{API}s that abstract away the details in 
-the kernel and allow the archetypes to be loaded into the simulation in a modular 
-fashion.}
-\label{fig:framework}
+\caption{Material flows through a simple dynamic simulation created with only the simplest \Cycamore archetypes, \Class{Sink} and \Class{Source}.}
+\label{fig:simplesim}
 \end{figure}
-
-\acrlong{ABM} is inherently object-oriented because agents represent 
-discrete, independently acting objects.  Figure \ref{fig:framework} illustrates
-the modular nature of \Cyclus archetypes.  The core of the \Cyclus simulator 
-creates a set of key classes on which agent plug-ins 
-are based. In addition, a set of key tools are also provided to enrich the 
-\gls{API} and supply a robust suite of behaviors for the developer. 
-Agent plug-ins utilize the generic core \gls{API} to interact with one another.  For 
-example, agents rely on a paradigm of dynamic loading and clean plug-in 
-behavior at the start of the simulation. They also use the resource exchange 
-paradigm \gls{API} for trading resources with one another.
-
-\subsection{Simulation Assistance}
 
@@
 \end{itemize}
-
-\subsubsection{Cycamore}
-% base modules
-
-\Cycamore \cite{carlsen_cycamore_2014}, the \Cyclus additional module
-repository, provides a fundamental set of agent archetypes for basic simulation 
-functionality within \Cyclus.  Since \Cyclus relies on external 
-archetypes to represent the agents within a simulation, \Cycamore provides the 
-basic archetypes a new user needs to get started running simple simulations.  
-These archetypes support a minimal set of fuel cycle simulation goals and 
-provide, by example, a guide to new developers who would seek to contribute 
-their own archetypes outside of \Cycamore.
-
-As of version 1.0, \Cycamore contains four facility archetypes, one region 
-archetype, and two institution archetypes. Short descriptions of these 
-functions can be found in Table \ref{tab:cycamore}.
-
-\begin{table}[h]
-\centering
-\begin{tabularx}{\textwidth}{|r|l|X|}
-\hline
-\textbf{Entity} & \textbf{Archetype} & \textbf{Functionality} \\
-\hline
-Facility & BatchReactor & A reactor model that handles batch refueling, based on pre-determined recipes of compositions. \\
-Facility & Source & This facility generates material of the composition and commodity type specified as input.  \\
-Facility & Sink & This facility is capable of accepting a finite or infinite quantity of some commodity produced in the simulation. \\
-Facility & EnrichmentFacility & This facility enriches uranium at a specified capacity. \\
-Institution & ManagerInst & The manager institution manages production of commodities among its facilities by building new ones as needed. \\
-Institution & DeployInst &  This institution deploys specific facilities as defined explicitly in the input file. \\
-Region & GrowthRegion & This region determines whether there is a need to meet a certain capacity (as defined via input) at each time step. \\
-\hline
-\end{tabularx}
-\caption{The Archetypes in \Cycamore seek to cover a large range of simple simulation use cases.}
-\label{tab:cycamore}
-\end{table}
-
-The current \Cycamore release provides only 
-basic functionality, enabling simple fuel cycle analyses. 
-As illustrated in Figure \ref{fig:simplesim}, \Cycamore provides the tools for users
-to get started quickly with simple 
-once-through fuel cycle scenarios. As future contributions are vetted, the capabilities in \Cycamore may grow.
-
-\begin{figure}[htbp!]
-\begin{center}
-\includegraphics{./images/simplesim}
-\end{center}
-\caption{Material flows through a simple dynamic simulation created with only the simplest \Cycamore archetypes, \Class{Sink} and \Class{Source}.}
-\label{fig:simplesim}
-\end{figure}
 

### 2014-12-04 fundamentals/examples.tex
remove bolded comment

@@
 ecosystem at multiple institutions indicates that a fuel cycle simulator can 
-advance in a community-driven \textbf{collaborative?} development paradigm. Additionally, simple 
+advance in a community-driven development paradigm. Additionally, simple 
 simulations as well as more complex recycling simulations demonstrate that 

### 2014-12-04 fundamentals/impl.tex
adding DRE acronym

@@
 Next, the discrete treatment of objects is discussed in terms of both
-resources and materials and time via the \TODO{DRE}.
+resources and materials and time via the \gls{DRE}.
 Support for users and developers via the Cycamore library of
@@
 the set of capabilities needed to implement an agent-based simulation
-with dynamic resource exchange, a toolkit is provided that assists developers
+with \gls{DRE} a toolkit is provided that assists developers
 and users with related simulation and nuclear engineering tasks. The toolkit is

### 2014-12-04 fundamentals/examples.tex
adding DRE acronym
remove TODO

@@
 commodity. Custom, non-uniform preferences can be set for each different fuel
-commodity.  The dynamic resource exchange \TODO{acro or not?} enables a reactor to
+commodity.  The \gls{DRE} enables a reactor to
 preferentially accept recycled \gls{MOX} fuel over fresh \gls{UOX} fuel.  In this
@@
 generated directly from \Cyclus output data. After several batch cycles (near
-month 300 \TODO{here and below: month or time step?}) in the modified open and closed cases, enough separated fissile
+month 300) in the modified open and closed cases, enough separated fissile
 material accumulates in the fuel fabrication facility to generate a full

### 2015-01-09 fundamentals/intro.tex
intro

@@
 
-As nuclear power expands both domestically and internationally, nuclear fuel cycle
-performance analysis on technical, economic, political, and environmental axes increases 
-in importance. Appropriate nuclear fuel cycle analysis requires calculation of myriad physical, nuclear, 
-chemical, industrial, and political phenomena. Nuclear fuel cycle simulators 
-therefore couple complex systems such as nuclear process physics, 
-facility deployment, and material routing. However, most nuclear fuel cycle 
-simulators have not incorporated modern insights from simulation science and 
-software architecture that can enable more efficient, accurate, robust, and 
-validated analysis.
+As nuclear power expands both domestically and internationally, nuclear fuel
+cycle performance analysis on technical, economic, political, and environmental
+axes increases in importance. Appropriate nuclear fuel cycle analysis requires
+calculation of myriad physical, nuclear, chemical, industrial, and political
+phenomena. Nuclear fuel cycle simulators therefore couple complex systems such
+as nuclear process physics, facility deployment, and material routing.
+However, current fuel cycle simulators rely on closed platforms and inflexible
+architectures which exhibit three main failure modes. First, they discourage
+targeted contribution and collaboration among experts. Next, they hobble
+efforts to directly comparison of modeling methodologies. Finally, they result
+in over-specification, rendering most tools applicable to only a subset of
+desired simulation fidelities, scales, and applications.  A next generation
+fuel cycle simulator is needed which incorporates modern insights from
+simulation science and software architecture to solve these problems. As a
+bonus, many of these methods simultaneously enable more efficient, accurate,
+robust, and validated analysis.
 

### 2015-01-09 fundamentals/intro.tex
spelling and whatnot

--- 2014-12-03 fundamentals/intro.tex
@@
 Historically, the national laboratories have driven development and regulated 
-the use of their own tools: \gls{VISION}\cite{jacobson_verifiable_2010}, 
+the use of their own fuel cycle simulation tools: \gls{VISION}\cite{jacobson_verifiable_2010}, 
+\gls{ORION}\cite{worrall_scenario_2007},
 \gls{DANESS}\cite{van_den_durpel_daness_2009}, 
@@
 ``reinvented the wheel'' by developing tools of their own from scratch and 
-tailored to their own needs, for example \gls{CAFCA}\cite{guerin_impact_2009} and 
+tailored to their own needs, for example 
+\gls{CAFCA}\cite{guerin_impact_2009} and
 \gls{COSI}\cite{boucher_cosi_2005,boucher_cosi:_2006,meyer_new_2009,coquelet-pascal_comparison_2011}.
@@
 \Cyclus emerged from a line of tools seeking to break this practice.  
-Its precurser,
+Its precursor,
 \gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006}, began
 at \gls{LDRD} within \gls{INL} and sought 
+\gls{ORION}\cite{}, and 
 to provide generic regional capability.  Based on lessons learned from 
@@
 the macro and micro levels challenging within a single tool. 
-In constrast, the extensible architecture and discrete object tracking of \Cyclus allow
+In contrast, the extensible architecture and discrete object tracking of \Cyclus allow
 the creation and interchangeability of custom archetypes at any level of fidelity.

### 2015-01-09 fundamentals/impl.tex
renaming section title to include 'Modular'
minor edits to todos
closes #50
compatibility with

@@
 capabilities, is described, focusing on agent interchangeability and the 
-implementation of the region-institution-facility heirarchy. 
+implementation of the region-institution-facility hierarchy. 
 Next, the discrete treatment of objects is discussed in terms of both
 resources and materials and time via the \gls{DRE}.
-Support for users and developers via the Cycamore library of
-agents \TODO{archetypes?} and the experimental toolkit are also presented.
+Support for users and developers via the \Cycamore library of
+archetypes and the experimental toolkit are also presented.
 Lastly, the methods for quality assurance are outlined.
@@
 
-\subsection{Software Architecture}
+\subsection{Modular Software Architecture}
 % Motivation for encapsulated plug-in architecture 
@@
 Many fuel cycle simulators rely on \gls{COTS} and Windows-only software that limits 
-performance on resource computing infrastructures. This limitation severely 
+performance on and compatibility with resource computing infrastructures. This limitation severely 
 increases the wall-clock time necessary to conduct parameterized sensitivity 

### 2015-01-09 fundamentals/impl.tex
code review

@@
 mend-and-extend paradigm, common in modern software development, reduces 
-maintenance overhead and improves code robustness \cite{citation_needed}. 
+maintenance overhead and improves code robustness when combined with code 
+review \cite{cohen_modern_2010}. 
 The researcher can focus on creating or customizing nuclear 
@@
 open source, BSD-3-clause licensed. No part of \Cyclus is proprietary or based 
-on \gls{COTS}, Windows-based software. It can be easily deployed 
+on \gls{COTS}, Windows-only software. \Cyclus can therefore be easily deployed 
 on large computer systems, such as \gls{HTC} systems.

### 2015-01-09 fundamentals/impl.tex
actually,not about review

@@
 mend-and-extend paradigm, common in modern software development, reduces 
-maintenance overhead and improves code robustness when combined with code 
-review \cite{cohen_modern_2010}. 
+maintenance overhead and improves code robustness by protecting the core logic 
+from changes in the extensions. 
 The researcher can focus on creating or customizing nuclear 

### 2015-01-09 fundamentals/impl.tex
overuse of the word 'key'

@@
 Dynamically loadable libraries are the primary mechanism for extending \Cyclus' capability. This approach provides encapsulation: the core of the code operates
-completely independently from the individual plug-in libraries. Thus, any
+independently from the individual plug-in libraries. Thus, any
 customization or extension is implemented only in the loadable
@@
 \Cyclus implements an \acrlong{ABM} paradigm.  \gls{ABM} is modern, sophisticated, 
-true to reality, and it incorporates modern computing resources.  
+true to reality, and incorporates modern computing resources.
 Furthermore, \gls{ABM} provides a natural 
@@
 
-Furthermore, the \gls{ABM} paradigm is easily comparable to system dynamics models.
+Furthermore, the \gls{ABM} paradigm is superior to system dynamics used in 
+current simulators.
 System dynamics is a popular approach for modeling nuclear fuel cycles 
@@
 the modular nature of \Cyclus archetypes.  The core of the \Cyclus simulator 
-creates a set of key classes on which agent plug-ins 
-are based. In addition, a set of key tools are also provided to enrich the 
+creates a set of classes on which agent plug-ins 
+are based. In addition, a set of tools are also provided to enrich the 
 \gls{API} and supply a robust suite of behaviors for the developer. 
@@
 pull requests. However, only members of the \Cyclus core team are allowed to 
-merge in any changes and only after the \gls{QA} standards have been met.
+merge in any changes and only after the \gls{QA} standards have been met. This 
+step has been repeatedly shown to improve code quality \cite{cohen_modern_2010}.
 

### 2015-01-13 fundamentals/impl.tex
cyclopts cited

--- 2015-01-09 fundamentals/impl.tex
@@
 capabilities, is described, focusing on agent interchangeability and the 
-implementation of the region-institution-facility hierarchy. 
+implementation of the region-institution-facility heirarchy. 
 Next, the discrete treatment of objects is discussed in terms of both
 resources and materials and time via the \gls{DRE}.
-Support for users and developers via the \Cycamore library of
-archetypes and the experimental toolkit are also presented.
+Support for users and developers via the Cycamore library of
+agents \TODO{archetypes?} and the experimental toolkit are also presented.
 Lastly, the methods for quality assurance are outlined.
@@
 mend-and-extend paradigm, common in modern software development, reduces 
-maintenance overhead and improves code robustness when combined with code 
-review \cite{cohen_modern_2010}. 
+maintenance overhead and improves code robustness \cite{citation_needed}. 
 The researcher can focus on creating or customizing nuclear 
@@
 Many fuel cycle simulators rely on \gls{COTS} and Windows-only software that limits 
-performance on and compatibility with resource computing infrastructures. This limitation severely 
+performance on resource computing infrastructures. This limitation severely 
 increases the wall-clock time necessary to conduct parameterized sensitivity 
@@
 open source, BSD-3-clause licensed. No part of \Cyclus is proprietary or based 
-on \gls{COTS}, Windows-only software. \Cyclus can therefore be easily deployed 
+on \gls{COTS}, Windows-based software. It can be easily deployed 
 on large computer systems, such as \gls{HTC} systems.
 
-Cyclopts (\TODO{cite}), a proof of principle design and implementation of \Cyclus on such a large computer system,
- uses UW-Madison's HTCondor \gls{HTC} infrastructure to perform sensitivity
-studies on \Cyclus' resource exchange optimization solvers. To date, it has been
-used to run over $10^4$ jobs, or (\TODO{compute time}) total compute hours, using
-the \Cyclus library via its resource exchange \gls{API}.
-The \gls{HTC} infrastructure has also been utilized to run and collect
-information from full \Cyclus simulations running in parallel on $10^3$
-machines reliably for order $10^5$ simulations.
+Cyclopts \cite{gidden_cyclopts_2015}, a proof of principle design and
+implementation of \Cyclus on such a large computer system, uses UW-Madison's
+HTCondor \gls{HTC} infrastructure to perform sensitivity studies on \Cyclus'
+resource exchange optimization solvers. To date, it has been used to run over
+$10^4$ jobs, or (\TODO{compute time}) total compute hours, using the \Cyclus
+library via its resource exchange \gls{API}.  The \gls{HTC} infrastructure has
+also been utilized to run and collect information from full \Cyclus simulations
+running in parallel on $10^3$ machines reliably for order $10^5$ simulations.
 

### 2015-01-14 fundamentals/impl.tex

--- 2015-01-09 fundamentals/impl.tex
@@
 
-Cyclopts (\TODO{cite}), a proof of principle design and implementation of \Cyclus on such a large computer system,
- uses UW-Madison's HTCondor \gls{HTC} infrastructure to perform sensitivity
-studies on \Cyclus' resource exchange optimization solvers. To date, it has been
-used to run over $10^4$ jobs, or (\TODO{compute time}) total compute hours, using
-the \Cyclus library via its resource exchange \gls{API}.
-The \gls{HTC} infrastructure has also been utilized to run and collect
-information from full \Cyclus simulations running in parallel on $10^3$
-machines reliably for order $10^5$ simulations.
+Cyclopts \cite{gidden_cyclopts_2015}, a proof of principle design and
+implementation of \Cyclus on such a large computer system, uses UW-Madison's
+HTCondor \gls{HTC} infrastructure to perform sensitivity studies on \Cyclus'
+resource exchange optimization solvers. To date, it has been used to run over
+$10^4$ jobs, or (\TODO{compute time}) total compute hours, using the \Cyclus
+library via its resource exchange \gls{API}.  The \gls{HTC} infrastructure has
+also been utilized to run and collect information from full \Cyclus simulations
+running in parallel on $10^3$ machines reliably for order $10^5$ simulations.
 

### 2015-01-14 fundamentals/impl.tex
removed canonical

@@
 
-Interchangeability is accomplished by providing \glspl{API} that define canonical agent-to-agent
+Interchangeability is accomplished by providing \glspl{API} that define agent-to-agent
 interaction and agent-to-environment interaction, primarily through the

### 2015-01-14 fundamentals/impl.tex
cite desae"

@@
 choose to \textit{deploy} child agents and \textit{decommission} child
-agents. For the archetype developer, this interface provides enormous power, 
+agents. For the archetype developer, this interface provides enormous power
 very simply. The \gls{API} provides the \Class{Agent} with helpful functionality for 
@@
 encompassing facilities, institutions managing those facilities, and regions. While
-some simulators (\TODO{cite DESAE}) have provided a notion of static regional
+some simulators \cite{adrianova_desae_2008} have provided a notion of static regional
 effects, \Cyclus allows for both regions and institutions to be first-class

### 2015-01-14 fundamentals/impl.tex
intro to simulation assistance. I'm still not sure about the title...

@@
 \subsection{Simulation Assistance}
-\TODO{section intro needed}
-To assist beginner users and developers in accomplishing working simulations
-in the shortest time possible,
+So that users and developers can build working simulations
+in the shortest time possible, the \Cyclus ecosystem provides the fundamental 
+building blocks: basic archetypes and a toolkit of commonly needed functions.
+The \Cycamore library provides a suite of fundamental Region, Institution, and 
+Facility archetypes, while the \Cyclus toolkit provides assistance to 
+developers.
 

### 2015-01-14 fundamentals/impl.tex
he did not epitomize it at all. he expressed it, articulated it, spoke of it. Babbage was neither garbage in nor garbage out
gets rid of overly informal discussion of software nerd debates

@@
 problem of identifying trustworthy results from nonsensical results or noise.
-This is epitomized by Charles Babbage, ``On two occasions I have been asked, 
+Charles Babbage famously articulated this, ``On two occasions I have been asked, 
 `Pray, Mr. Babbage, if you put into the machine wrong figures, will the right 
@@
 way.  This homogenization may be a hurdle to new developers but ultimately 
-improves code legibility. Adoption of a single style guide also settles
-timeless arguments over what style is `the best.' Having only one means that 
-there is a common enemy for all developers to dislike equally.
+improves code legibility and, therefore, robustness \cite{cohen_modern_2010}.
 

### 2015-01-14 fundamentals/impl.tex
simpler text

@@
 as it is being developed, rather than as a final stage in a longer development 
-cycle.  Under \gls{CI}, every pull request is tested independently immediately after 
+cycle.  Under \gls{CI}, every pull request (proposed code change) is tested independently immediately after 
 it is proposed. Such tests are run on all officially supported platforms. 
@@
 \begin{enumerate}
-    \item Copies \Cyclus with the pull requested code to BaTLab,
+    \item Copies \Cyclus with the proposed new code to BaTLab,
     \item Initializes Linux and Mac OSX servers,
@@
     \item Runs the complete \Cyclus test suite, 
-    \item Reports back whether the above steps succeeded or not.
+    \item Reports whether or not the above steps succeeded.
 \end{enumerate}
@@
 but not sufficient addition to the \Cyclus \gls{QA}
-system. Its merit is that it prevents bad code from being implemented. However, \Cyclus will always
+system: it keeps bad code out \Cyclus. However, \Cyclus will always
 require human eyes and hands to let good code in.

### 2015-01-14 fundamentals/examples.tex
simpler words

@@
 
-The functionality of the \Cyclus simulator is illustrated by demonstrations
-of its fundamental simulation capabilities and the feasibility the
+The functionality and feasibility of the \Cyclus simulator is illustrated by demonstrations
+of its fundamental simulation capabilities and growth via its
  community-driven \Cyclus development model.

### 2015-01-14 fundamentals/examples.tex
fixed weird sentence about cyclus having fuel cycle capabilities.. duh. it's an fcs...

@@
 ecosystem at multiple institutions indicates that a fuel cycle simulator can 
-advance in a community-driven development paradigm. Additionally, simple 
-simulations as well as more complex recycling simulations demonstrate that 
-\Cyclus possesses fuel cycle simulation capabilities.
+advance in a community-driven development paradigm. Additionally, simulation 
+results for both once-through and more complex recycling scenarios demonstrate that 
+\Cyclus possesses the fundamental fuel cycle simulation capabilities to 
+contribute to the field.
 
@@
 \end{itemize}
-Taken together, these form an ecosystem of capabilites. Over time, this 
+Taken together, these form an ecosystem of capabilities. Over time, this 
 ecosystem will grow as archetype developers, kernel developers, and 
@@
 is then expanded to include multiple reactors in the same set of fuel cycles to demonstrate
-the system-scale convergance to continuous material flow models.
+the system-scale convergence to continuous material flow models.
 
@@
 \end{lstlisting}
+
 This results in the material flows in Figure \ref{fig:flowclosed}. Note
@@
 Figure \ref{fig:puseries1} shows the full-system plutonium buildup for open
-(no recycle), modified open, and closed (infinite-pass recycle) \TODO{whats
-the diff btw closed and the multi-pass from above? It's referred to as fully
-closed multi-pass recycle, which is a bit confusing.} variations of
-the scenario described above (all just a single reactor).  The figure was
+(no recycle), modified open, and closed (infinite-pass recycle) variations of
+the one-reactor scenario described above. The figure was
 generated directly from \Cyclus output data. After several batch cycles (near

### 2015-01-14 fundamentals/impl.tex

@@
 features, independent from the team of \Cyclus core developers. 
-% we could use a specific example of Cosi's equivalence method below
 Second, because \Cyclus uses a modular archetype approach, comparing two 
@@
 format. It shows how the \Class{Agent} interface
-provides a notion of parent-child hierarchichal relationship, where parents can
+provides a notion of parent-child hierarchical relationship, where parents can
 choose to \textit{deploy} child agents and \textit{decommission} child
@@
 responsible for deploying and decommissioning facilities. Accordingly, advanced
-logic regarding building and decommissioning can be obtained by subclassing the
+logic regarding building and decommissioning can be obtained by inheriting 
+those behaviors from the
 \Class{Institution} interface. Second, the \Class{Facility} class implements the

### 2015-01-14 fundamentals/intro.tex
cohen

@@
 control, without loss of generality \cite{macal_agent-based_2010}. Finally, openness 
-allows cross-institutional collaboration, increases code robustness, and 
-cultivates an ecosystem of modeling and calculation options 
-\cite{softwarecarpentryresource}.  The fundamental concepts of the \Cyclus 
+allows cross-institutional collaboration, increases code robustness \cite{cohen_modern_2010}, and 
+cultivates an ecosystem of modeling and calculation options.  The fundamental concepts of the \Cyclus 
 nuclear fuel cycle simulator capture these modern insights so that challenges 
@@
 \gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006}, began
-at \gls{LDRD} within \gls{INL} and sought 
+as an \gls{LDRD} project within \gls{INL} and sought 
 \gls{ORION}\cite{}, and 

### 2015-01-14 fundamentals/intro.tex
rearrange

--- 2015-01-09 fundamentals/intro.tex
@@
 targeted contribution and collaboration among experts. Next, they hobble
-efforts to directly comparison of modeling methodologies. Finally, they result
-in over-specification, rendering most tools applicable to only a subset of
-desired simulation fidelities, scales, and applications.  A next generation
-fuel cycle simulator is needed which incorporates modern insights from
-simulation science and software architecture to solve these problems. As a
-bonus, many of these methods simultaneously enable more efficient, accurate,
+efforts to directly compare modeling methodologies. Finally, they 
+over-specialize, rendering most tools applicable to only a subset of
+desired simulation fidelities, scales, and applications.
+The \Cyclus nuclear fuel cycle simulator framework and 
+its modeling ecosystem incorporate modern insights from
+simulation science and software architecture to solve these problems. 
+As a bonus, many of these methods simultaneously enable more efficient, accurate,
 robust, and validated analysis.
 
-The \Cyclus nuclear fuel cycle simulator framework and 
-its modeling ecosystem address this need for a next-generation nuclear fuel cycle 
-simulator. This dynamic simulator employs discrete agents, time, and isotopic resolution of materials 
-and supports a range of analysis types, levels of 
-detail, and analyst sophistication.
-Additionally, \Cyclus employs a modular architecture and 
-open development process that supports user access and 
-encourages developer extensions.
+The \Cyclus next-generation fuel cycle simulator is the result of design 
+choices made explicitly to:
+\begin{itemize}
+\item support user access and encourages developer extensions,
+\item enable plug-and-play comparison of modeling methodologies,
+\item and address a range of analysis types, levels of detail, and analyst sophistication.
+\end{itemize}
 
@@
 scientific transparency. 
-
 An alternative to these approaches is a dynamic, agent-based simulator with an 
 open platform and an ecosystem of research-driven capabilities.
-Dynamic nuclear fuel cycle analysis more realistically 
-supports a range of simulation goals than static analysis 
+
+\Cyclus, therefore, is a dynamic, agent-based model, which employs a modular 
+architecture, an open development process, discrete agents, discrete time, and 
+arbitrarily detailed isotopic resolution of materials.  Dynamic nuclear fuel 
+cycle analysis more realistically supports a range of simulation goals than 
+static analysis 
 \cite{piet_dynamic_2011}. Similarly, experience in the broader field of systems 
@@
 
-Historically, the national laboratories have driven development and regulated 
-the use of their own tools: \gls{VISION}\cite{jacobson_verifiable_2010}, 
-\gls{DANESS}\cite{van_den_durpel_daness_2009}, 
-\gls{DYMOND}\cite{yacout_modeling_2005}, and 
-\gls{NFCSim}\cite{schneider_nfcsim:_2005}. 
-Outside the national laboratories, researchers have created new nuclear fuel cycle 
-simulation tools when existing tools were not available or not sufficiently 
-general to calculate their metrics of interest with their method of choice.  
-With limited access to the national laboratory tools and a need to customize 
-them for research purposes, universities and private industry researchers have 
-``reinvented the wheel'' by developing tools of their own from scratch and 
-tailored to their own needs, for example \gls{CAFCA}\cite{guerin_impact_2009} and 
-\gls{COSI}\cite{boucher_cosi_2005,boucher_cosi:_2006,meyer_new_2009,coquelet-pascal_comparison_2011}.
-
-This trend has resulted in a proliferation of specialized
-fuel cycle simulators for the calculation of fuel cycle metrics.  Accordingly, methods 
-for calculating those metrics vary among simulators. Some model the 
+However, methods for calculating those metrics vary among simulators. Some model the 
 system of facilities, economics, and materials in static equilibrium, while 
@@
 neglected.
+
+This overspecialization and fractured community is the result of history. 
+Historically, the national laboratories have driven development and regulated 
+the use of their own tools: \gls{VISION}\cite{jacobson_verifiable_2010}, 
+\gls{DANESS}\cite{van_den_durpel_daness_2009}, 
+\gls{DYMOND}\cite{yacout_modeling_2005}, and 
+\gls{NFCSim}\cite{schneider_nfcsim:_2005}.  Outside the national laboratories, 
+researchers have created new nuclear fuel cycle simulation tools when existing 
+tools were not available or not sufficiently general to calculate their metrics 
+of interest with their method of choice.  With limited access to the national 
+laboratory tools and a need to customize them for research purposes, 
+universities and private industry researchers have ``reinvented the wheel'' by 
+developing tools of their own from scratch and tailored to their own needs, for 
+example \gls{CAFCA}\cite{guerin_impact_2009} and 
+\gls{COSI}\cite{boucher_cosi_2005,boucher_cosi:_2006,meyer_new_2009,coquelet-pascal_comparison_2011}.
 

### 2015-01-14 fundamentals/impl.tex

@@
 encompassing facilities, institutions managing those facilities, and regions. While
-some simulators \cite{adrianova_desae_2008} have provided a notion of static regional
+some simulators \cite{andrianova_desae_2008} have provided a notion of static regional
 effects, \Cyclus allows for both regions and institutions to be first-class

### 2015-01-14 fundamentals/intro.tex

@@
 \Cyclus emerged from a line of tools seeking to break this practice.  
-Its precurser,
+Its precursor,
 \gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006}, began
-at \gls{LDRD} within \gls{INL} and sought 
+as an \gls{LDRD} project within \gls{INL} and sought 
+\gls{ORION}\cite{}, and 
 to provide generic regional capability.  Based on lessons learned from 

### 2015-01-14 fundamentals/impl.tex
got rid of 'assistance' in the simulation assistance title

@@
 Lastly, the methods for quality assurance are outlined.
-These features provide a solid foundation on which to build an interconnected community 
-of archetype developers with diverse backgrounds and simulation goals.
 
@@
 
-\subsection{Simulation Assistance}
+\subsection{Simulation Support}
 So that users and developers can build working simulations

### 2015-01-14 fundamentals/impl.tex
small changes

@@
 
-Many fuel cycle simulators rely on \gls{COTS} and Windows-only software that limits 
+Groundbreaking insights and new classes of problems can be investigated by 
+leveraging modern massive computing resources.
+However, many fuel cycle simulators rely on \gls{COTS} and Windows-only software that limits 
 performance on and compatibility with resource computing infrastructures. This limitation severely 
-increases the wall-clock time necessary to conduct parameterized sensitivity 
+limits the possible scope of simulations and increases the wall-clock time necessary to conduct parameterized sensitivity 
 analyses and other multi-simulation studies. \Cyclus, on the other hand, is 
@@
 \subsubsection{Dynamically Loadable Libraries}
-% (diagram)
 
-A key innovation is that \Cyclus  implements this generic \gls{API} and modular 
-architecture via a suite of dynamically loadable plug-in libraries.  Though 
-common in modern software architecture, such a plug-in pattern has 
-not previously been implemented in nuclear fuel cycle simulators.  
-Dynamically loadable libraries are the primary mechanism for extending \Cyclus' capability. This approach provides encapsulation: the core of the code operates
-independently from the individual plug-in libraries. Thus, any
-customization or extension is implemented only in the loadable
-library.
+The \Cyclus architecture encourages efficient, targeted contribution to the ecosystem of 
+archetype libraries.
+With \Cyclus, a researcher can focus on generating an archetype model within their
+sphere of expertise, while relying on the contributions of others to fill 
+in the other technologies in the simulation.  
+Similarly, individual developers may explore different levels of complexity within their archetypes, including
+wrapping other simulation tools as loadable libraries within \Cyclus.
 
-This approach encourages efficient, targeted contribution to the ecosystem of 
-archetype libraries.  The 
-researcher can focus on generating an archetype model within their
-sphere of expertise, while relying on the contributions of others to fill 
-in the other technologies in the simulation.  This strategy also allows individual developers to
-explore different levels of complexity within their archetypes, including
-wrapping other simulation tools as loadable libraries within \Cyclus.
+\Cyclus acheives this behavior by implementing its generic \gls{API} and 
+modular architecture via a suite of dynamically loadable plug-in libraries.  
+Though common in modern software architecture, such a plug-in pattern has not 
+previously been implemented in nuclear fuel cycle simulators.  Dynamically 
+loadable libraries are the primary mechanism for extending \Cyclus' capability. 
+This approach provides encapsulation: the core of the code operates 
+independently from the individual plug-in libraries. Thus, any customization or 
+extension is implemented only in the loadable library.
 
@@
 Material decay can also contribute significantly to such changes.  In order to
-help avoid unnecessary runtime performance and database space impacts,
+help avoid unnecessary runtime performance and database size impacts,
 compositions in \Cyclus have some special features.
 Immutability of compositions allows multiple material objects to all hold
-references to the same composition object safely.  When operations are
-performed on a material that do not alter the composition, any new resulting
+references to the same composition object safely.  When operations that do not 
+alter the composition are performed on a material, any new resulting
 materials hold a reference to the same, original composition object.

### 2015-01-14 fundamentals/impl.tex
small edits

--- 2015-01-14 fundamentals/impl.tex
@@
 encompassing facilities, institutions managing those facilities, and regions. While
-some simulators \cite{andrianova_desae_2008} have provided a notion of static regional
+some simulators \cite{adrianova_desae_2008} have provided a notion of static regional
 effects, \Cyclus allows for both regions and institutions to be first-class
@@
 
-In large simulations many material objects may be changing frequently.
+In large simulations many material objects may change frequently.
 Material decay can also contribute significantly to such changes.  In order to
@@
 
-\TODO{This is SO for you, Matt Gidden!}
-Placeholder as a reminder to add more detail about this.
+\TODO{Matt Gidden, please fill in}
 

### 2015-01-14 fundamentals/impl.tex
comma
todo cleanup

@@
 
-In large simulations many material objects may change frequently.
+In large simulations, many material objects may change frequently.
 Material decay can also contribute significantly to such changes.  In order to
@@
 
-The \Cyclus toolkit provides two useful interfaces for queries referring to physical paramaters of \Class{Material}
+The \Cyclus toolkit provides two useful interfaces for querying physical paramaters of \Class{Material}
 objects. First, the \Class{MatQuery} module
@@
 In addition to those that already exist, new tools and computational patterns will 
-emerge from the archetypes that are developed within the community of 
+emerge from the archetypes developed within the community of 
 developers. As these tools gain adoption between projects and demonstrate their 

### 2015-01-16 fundamentals/examples.tex
some language to explain why this section is in the demonstration section.

@@
 
-The functionality and feasibility of the \Cyclus simulator is illustrated by demonstrations
-of its fundamental simulation capabilities and growth via its
- community-driven \Cyclus development model.
 The success of the \Cyclus simulator can be measured in many ways. 
@@
 
+The \Cyclus community-driven software development model seeks to break the unproductive cycle proliferating overspecialized simulators and 
+to leverage the collective expertise of fuel cycle researchers. Through the 
+contributions of those researchers, an ecosystem of capabilities should emerge.
 The \Cyclus `Ecosystem' is the collection of tools, calculation libraries, 
@@
 facility, and one repository. The simulation has a duration of 1100 months and a \TODO{??-month stepsize}.
-
-%** full-system plutonium buildup for open
-\TODO{(no recycle), modified open, and closed (infinite-pass recycle)
-variations of}
-%the scenario described above (all just a single reactor).  **
 

### 2015-01-16 fundamentals/examples.tex
more language to tie things in

@@
 
-The \Cyclus community-driven software development model seeks to break the unproductive cycle proliferating overspecialized simulators and 
-to leverage the collective expertise of fuel cycle researchers. Through the 
+The \Cyclus community-driven software development model seeks to break the 
+unproductive proliferation of overspecialized simulators and instead leverages 
+the collective expertise of fuel cycle researchers toward a single, more 
+extensible, tool. Through the targeted
 contributions of those researchers, an ecosystem of capabilities should emerge.
@@
 
-Many archetypes external to the \Cycamore library (Table \ref{tab:cycamore})  
+It is expected that the most common type of contribution to \Cyclus will be 
+contributions of new archetypes. Researchers will be driven to create a new 
+archetype when a need arises to represent a novel reactor type, an innovative 
+reprocessing strategy, or a particular governmental or institutional behavior.  
+The real-world utility of \Cyclus can in part be measured by the breadth and 
+diversity of archetypes being developed in this way.
+
+Early progress has been promising. Many archetypes external to the \Cycamore library (Table \ref{tab:cycamore})  
 have been 
@@
 archetypes by providing physics-based reactors, separation, fabrication, storage
-facilities, and expanded institutional paradigms.  These contributed archetypes
-illustrate the power of a community-based development approach.
+facilities, and expanded institutional paradigms.
 
@@
 \end{table}
+
+The existence and diversity of these contributed archetypes
+illustrate the power and potential of the community-based development approach 
+that \Cyclus has taken.
 

### 2015-01-16 fundamentals/examples.tex
simpler sentence

@@
 The \Cyclus community-driven software development model seeks to break the 
-unproductive proliferation of overspecialized simulators and instead leverages 
+unproductive proliferation of overspecialized simulators. It instead leverages 
 the collective expertise of fuel cycle researchers toward a single, more 

### 2015-01-21 fundamentals/intro.tex

@@
 simulators, the \Cyclus paradigm enables essential capabilities that previous 
-simulators lack. Critically, its \emph{modular and open architecture}  facilitates 
-targeted contribution and collaboration within the nuclear fuel cycle analysis 
-community.  Additionally, \emph{agent interchangeability} facilitates direct 
-comparison of modeling methodologies. Finally, the flexibility and generality 
+simulators lack. Critically, targeted contribution and collaboration within the nuclear fuel cycle analysis 
+community are assisted by the \emph{modular and open architecture} of \Cyclus.
+Additionally, \Cyclus facilitates direct comparison of modeling methodologies with 
+\emph{agent interchangeability}.
+Finally, \Cyclus is applicable to a broader range of 
+fidelities, scales, and applications than other simulators. 
+due to the flexibility and generality 
 of its \emph{\gls{ABM}} paradigm and \emph{discrete, object-oriented approach}
-enables \Cyclus to be applicable to a broader range of 
-fidelities, scales, and applications than to other simulators.
 
-\Cyclus separates the problem of modeling a
+Specialists in a given field should utilize their time and resources in 
+modeling the specific processes associated with their area of expertise within 
+thenuclear fuel cycle (e.g., reprocessing and advanced
+fuel fabrication), without having to model the entirety of the cycle.
+\Cyclus supports them by separating the problem of modeling a
 physics-dependent supply chain into two distinct components: a simulation kernel and archetypes that
@@
 deployment and interaction logic of entities in the simulation.  Physics calculations and 
-customized behaviors are implemented within archetypes. Accordingly, specialists
-in a given field can utilize their time and resources in modeling a specific
-process associated with the nuclear fuel cycle (e.g., reprocessing and advanced
-fuel fabrication), without having to model the entirety of the cycle.
+customized behaviors are implemented within archetypes.
 

### 2015-02-05 fundamentals/examples.tex
more details about example simulation.

@@
 
-Results of some simple recycle scenarios run in \Cyclus follow. Beginning with a single
-reactor simulation, open (no recycle), modified open, and closed (infinite-pass recycle) 
-fuel cycles are compared to illustrate the resolution possible with \Cyclus.  The simulation
-is then expanded to include multiple reactors in the same set of fuel cycles to demonstrate
-the system-scale convergence to continuous material flow models.
+This section will discuss the creation and results of a few simple fuel cycle
+simulations to help illustrate the flexibility of \Cyclus. These simulations
+are designed to illustrate Cyclus' capability.  Many simplifying assumptions
+have been made with respect to material compositions, fuel transmutation, and
+others. The three fuel cycles examined are:
 
-Because material is tracked as discrete objects, single-pass recycle using \gls{MOX} 
-fuel is easy to implement in \Cyclus.  The \gls{MOX} simulation includes one provider of fresh
-\gls{UOX} fuel, one recycled fuel fabrication facility, one reactor, one separations
-facility, and one repository. The simulation has a duration of 1100 months and a \TODO{??-month stepsize}.
+\begin{enumerate}
+    \item Once through (no recycle) 
+    \item Modified open (1-pass recycle)
+    \item closed (infinite-pass recycle)
+\end{enumerate}
 
-The \Class{BatchReactor} archetype from \Cycamore has the ability to accept
-fuel materials from an arbitrary number of different sources, delineated by
-commodity. Custom, non-uniform preferences can be set for each different fuel
-commodity.  The \gls{DRE} enables a reactor to
-preferentially accept recycled \gls{MOX} fuel over fresh \gls{UOX} fuel.  In this
-simulation, the
-\Class{BatchReactor} was configured to run with a 3 batch core on 18 month cycles and
-a 2-month refueling period.  Adjusting and setting parameters such as these is
-as simple as editing numbers in an input file such as:
+For each of these fuel cycles, a 1,100 month \Cyclus simulation with only a
+single reactor is run in addition to a simulation with 10 reactors with
+staggered refueling times.  As the number of staggered-cycle reactors
+increases the system converges toward continuous material flow results.
+\Cyclus flexibility allows this transition to be examined.  The facilities
+used in these simulations are:
 
-\begin{lstlisting}[language=xml]
-  ...
-  <BatchReactor>
-      ...
-      <processtime>18</processtime>
-      <nbatches>3</nbatches>
-      <batchsize>20000</batchsize>
-      <refueltime>2</refueltime>
-      ...
-  </BatchReactor>
-  ...
-\end{lstlisting}
+\begin{itemize}
 
-The \Class{Source} and \Class{Sink} archetypes from \Cycamore have been used as a
-source of fresh, enriched uranium and a repository, respectively. A simple
-custom recycled fuel fabrication facility was also used, which mixes fissile 
-and fertile streams to match target fuel compositions as closely
-as possible.  The method used for this matching is approximately the same as
-that used by the \gls{COSI} fuel cycle simulator \TODO{cite COSI equivalence
-method}. The material flows for this simulation are shown below in Figure
-\ref{fig:flowmodopen}.
+    \item \textbf{Reactor} (\Class{cycamore::Reactor}): This is a reactor
+        model that requests any number of input fuel types and uses static
+        compositions to transmute them to after they are burnt and discharged
+        from the core.  Due to the static spent fuel compositions spent fuel
+        compositions become "incorrect" as the input fuel diverges from the
+        fixed, expected input composition. The reactor was configured to model
+        a light water reactor with a 3 batch core (20,000 kg HM per batch)
+        operating on an 18 month cycle with a 2 month refuel time.  The
+        reactor was also configured to take in either enriched UOX fuel or
+        recycled MOX fuel - preferring the latter if available.
+
+    \item \textbf{Recycled Fuel Fabrication} (\Class{cycamore::Fab}): This
+        facility requests depleted uranium and separated fissile material and
+        mixes them together into recycled MOX fuel that it offers to
+        requesters.  The streams are mixed using a D-factors approach
+        \TODO{add D-factors citation} in an attempt to match simple neutronics
+        properties of an ideal target fuel composition.
+
+    \item \textbf{Separations} (\Class{cycamore::Separations}): This facility
+        takes in all kinds of spent fuel and separates it into plutonium and
+        waste streams with some efficiency (0.99 was used for these
+        simulations).  Up to 60,000 kg of Pu can be separated per month.
+
+    \item \textbf{Repository} (\Class{cycamore::Sink}): This is an
+        infinite-capacity facility that can take in all types of material
+        including separations waste streams and spent reactor fuel.
+
+    \item \textbf{UOX Fabrication} (\Class{cycamore::Source}): This facility
+        provides enriched UOX fuel as requested with infinite capacity.
+
+    \item \textbf{DU Source} (\Class{cycamore::Source}): This facility provides
+        depleted uranium as requested with infinite capacity.
+
+\end{itemize}
+
+For the once through case, the \Class{Reactor} was set to offer all spent fuel
+as waste.  For the modified open case, the \Class{Reactor} offerred spent UOX
+into a spent fuel market where it is preferrentially sent to separations, but
+spent MOX is still offerred as waste.  In the closed case, the \Class{Reactor}
+offers all spent fuel into a spent fuel market. Because the separations
+facility requests spent fuel with a higher preference than the repository, it
+is sent there if possible.  All these preferences are easy to adjust and
+\Cyclus will dynamically handle supply constraints and non-uniform preference
+resolution.  It is notable that separations and recycle fuel fabrication
+capacity is deployed identically in all simulations.  In the once-through
+case, the recycling loop never acquires material, and so reactors always
+receive fresh UOX fuel.  In the modified open case, the recycle loop only
+acquires spent UOX.  The \gls{DRE} ensures everything operates smoothly in all
+cases.
+
+Cyclus' discrete materials make single-pass recycle easy to implement.  The
+reactors keep track of fuel as discrete batches. A reactor remembers where it
+received each batch from.  If a batch was received from the recycled fuel
+fabrication facility, it does not offer it to separations and instead sends it
+to the repository directly.  The material flows for the modified open case are
+shown in Figure \ref{fig:flowmodopen}.
 
@@
 \end{center}
-\caption{Modified open 1-pass \gls{MOX} recycle fuel cycle material flows.}
+\caption{Modified open 1-pass \gls{MOX} recycle scenario material flows.}
 \label{fig:flowmodopen}
@@
 
-Changing this to a fully closed fuel cycle entails only a one-word change in the input file
-regarding the output commodity for the spent \gls{MOX} fuel of the
-\Class{BatchReactor}:
+Changing the scenario from a modified open fuel cycle to a closed fuel cycle
+requires only a one-word change in the input file regarding the output
+commodity for the spent \gls{MOX} fuel of the \Class{Reactor}:
 
 \begin{lstlisting}[language=diff]
-  --- mod-open-1.xml	2014-10-08 08:31:33.892523173 -0500
-  +++ closed-1.xml	2014-10-08 08:31:33.892523173 -0500
-  @@ -108,7 +108,7 @@
      <fuel>         
-             <incommodity>mox_fuel</incommodity>
-             <inrecipe>lwr_mox_fuel</inrecipe>
-  -          <outcommodity>spent_mox</outcommodity>
+       <incommodity>mox</incommodity>
+  -    <outcommodity>waste</outcommodity>
   +    <outcommodity>spent_fuel</outcommodity>
+       <inrecipe>mox_resh_fuel</inrecipe>
        <outrecipe>mox_spent_fuel</outrecipe>
@@
 
-This results in the material flows in Figure \ref{fig:flowclosed}. Note
-that the \Class{BatchReactor} always transmutes fuel into the same
-composition, so the nuclide level flows are unrealistic for the full, 
-multi-pass
-recycle case.
+This results in the material flows in Figure \ref{fig:flowclosed}.  A
+similarly trivial change was used to switch from the once through to a
+modified open fuel cycle.  Note that the \Class{Reactor} always transmutes
+fuel into fixed compositions, so nuclide-specific flows become
+somewhat unrealistic in the fully closed cycle case.
 
@@
 (no recycle), modified open, and closed (infinite-pass recycle) variations of
-the one-reactor scenario described above. The figure was
-generated directly from \Cyclus output data. After several batch cycles (near
-month 300) in the modified open and closed cases, enough separated fissile
-material accumulates in the fuel fabrication facility to generate a full
-recycled batch.  When this batch is transmuted, more plutonium is burned than
-created.  This results in a drop in the total fuel cycle system plutonium
-inventory.  This pattern repeats roughly every 10 cycles (200 months) for the
-modified open case and every 9 cycles (180 months) for the closed case.
-Because the modified open scenario does not re-recycle material, it takes the
-fabrication facility 1 cycle longer to accumulate a full batch of
-fissile material.
+the one-reactor scenario described above. The figure was generated directly
+from \Cyclus output data. After several batch cycles (near month 300) in the
+modified open and closed cases, enough separated fissile material accumulates
+in the fuel fabrication facility to generate a full recycled batch.  When this
+batch is transmuted, more plutonium is burned than created.  This results in a
+drop in the total fuel cycle system plutonium inventory.  This pattern repeats
+roughly every 10 cycles (200 months) for the modified open case and every 9
+cycles (180 months) for the closed case.  Because the modified open scenario
+does not re-recycle material, it takes the fabrication facility 1 cycle longer
+to accumulate a full batch of fissile material.
 
-Because facilities are represented individually and
-transact discrete materials as discrete events, realistic non-uniform patterns in facility behavior
-that affect total system behavior are observed using \Cyclus, which is uncommon 
-for fleet-based, continuous material flow models.
+Because facilities are represented individually and transact discrete
+materials as discrete events, realistic non-uniform patterns in facility
+behavior that affect total system behavior are observed using \Cyclus.
 
@@
 
-The open, modified open, and closed scenarios can easily be modified to have
-several reactors with staggered refueling times. The plutonium buildup
-for these three multi-reactor variations is shown in Figure
-\ref{fig:puseriesn}. As the number of
-reactors increases, the behavior of the system approaches a more steady
-average reminiscent of continuous material flow models.
+Figure \ref{fig:puseriesn} shows plutonium buildup for the 10-reactor
+simulations of the open, modified open, and closed scenarios.  As the number
+of reactors (with staggered refueling) increases, the behavior of the system
+approaches a more steady average reminiscent of continuous material flow
+models.
 

### 2015-02-05 fundamentals/examples.tex
minor edits

@@
 cycles (180 months) for the closed case.  Because the modified open scenario
-does not re-recycle material, it takes the fabrication facility 1 cycle longer
+does not re-recycle material, it takes the fabrication facility 2 cycles longer
 to accumulate a full batch of fissile material.

### 2015-02-06 fundamentals/examples.tex
improve graphs - address many of katy's comments

--- 2015-02-05 fundamentals/examples.tex
@@
     \item Once through (no recycle) 
-    \item Modified open (1-pass recycle)
-    \item closed (infinite-pass recycle)
+    \item 1-pass MOX recycle
+    \item Infinite-pass MOX recycle
 \end{enumerate}
 
-For each of these fuel cycles, a 1,100 month \Cyclus simulation with only a
-single reactor is run in addition to a simulation with 10 reactors with
-staggered refueling times.  As the number of staggered-cycle reactors
-increases the system converges toward continuous material flow results.
-\Cyclus flexibility allows this transition to be examined.  The facilities
-used in these simulations are:
+For each of these fuel cycles, a 1,100 month single-reactor \Cyclus simulation
+was run in addition to a 10-reactor simulation with staggered refueling times.
+As the number of staggered-cycle reactors increases the system converges
+toward continuous material flow results.  \Cyclus flexibility allows this
+transition to be examined.  The facilities used in these simulations are:
 
@@
     \item \textbf{Reactor} (\Class{cycamore::Reactor}): This is a reactor
-        model that requests any number of input fuel types and uses static
-        compositions to transmute them to after they are burnt and discharged
-        from the core.  Due to the static spent fuel compositions spent fuel
-        compositions become "incorrect" as the input fuel diverges from the
-        fixed, expected input composition. The reactor was configured to model
-        a light water reactor with a 3 batch core (20,000 kg HM per batch)
-        operating on an 18 month cycle with a 2 month refuel time.  The
-        reactor was also configured to take in either enriched UOX fuel or
-        recycled MOX fuel - preferring the latter if available.
+        model that requests any number of input fuel types and transmutes them
+        to static compositions when they are burnt and discharged from the
+        core.  . The reactor was configured to model a light water reactor
+        with a 3 batch core (20,000 kg HM per batch) operating on an 18 month
+        cycle with a 2 month refuel time.  The reactor was also configured to
+        take in either enriched UOX fuel or recycled MOX fuel - preferring the
+        latter if available.
 
@@
         mixes them together into recycled MOX fuel that it offers to
-        requesters.  The streams are mixed using a D-factors approach
-        \TODO{add D-factors citation} in an attempt to match simple neutronics
-        properties of an ideal target fuel composition.
+        requesters.  The two streams are mixed in a ratio in order to match
+        simple neutronics properties of the target fuel as closely as
+        possible.  The method used is based on a variation "equivalence
+        method" originally developed by Baker and Ross
+        \cite{baker1963comparison}.  This technique has also been used in the
+        Commelini-Sicart (COSI) fuel cycle simulator developed by the French
+        Commissariat \`{a} l'\'{e}nergie atomique (CEA).
 
@@
     \item \textbf{UOX Fabrication} (\Class{cycamore::Source}): This facility
-        provides enriched UOX fuel as requested with infinite capacity.
+        provides enriched UOX fuel as requested.  This facility has infinite
+        production capacity.
 
-    \item \textbf{DU Source} (\Class{cycamore::Source}): This facility provides
-        depleted uranium as requested with infinite capacity.
+    \item \textbf{DU Source} (\Class{cycamore::Source}): This facility
+        provides depleted uranium as requested. This facility has infinite
+        production capacity.
 
@@
 For the once through case, the \Class{Reactor} was set to offer all spent fuel
-as waste.  For the modified open case, the \Class{Reactor} offerred spent UOX
-into a spent fuel market where it is preferrentially sent to separations, but
-spent MOX is still offerred as waste.  In the closed case, the \Class{Reactor}
-offers all spent fuel into a spent fuel market. Because the separations
-facility requests spent fuel with a higher preference than the repository, it
-is sent there if possible.  All these preferences are easy to adjust and
-\Cyclus will dynamically handle supply constraints and non-uniform preference
-resolution.  It is notable that separations and recycle fuel fabrication
-capacity is deployed identically in all simulations.  In the once-through
-case, the recycling loop never acquires material, and so reactors always
-receive fresh UOX fuel.  In the modified open case, the recycle loop only
-acquires spent UOX.  The \gls{DRE} ensures everything operates smoothly in all
-cases.
+as waste.  For the 1-pass recycle case, the \Class{Reactor} offered spent UOX
+into a spent fuel market where it is preferentially sent to separations, but
+spent MOX is still offered as waste.  In the infinite-pass recycle case, the
+\Class{Reactor} offers all spent fuel into a spent fuel market. Because the
+separations facility requests spent fuel with a higher preference than the
+repository, it is sent there if possible.  All these preferences are easy to
+adjust and \Cyclus will dynamically handle supply constraints and non-uniform
+preference resolution.  It is notable that separations and recycle fuel
+fabrication capacity is deployed identically in all simulations.  In the
+once-through case, the recycling loop never acquires material, and so reactors
+always receive fresh UOX fuel.  In the 1-pass recycle case, the recycle loop
+only acquires spent UOX.  The \gls{DRE} ensures everything operates smoothly
+in all cases.
 
@@
 fabrication facility, it does not offer it to separations and instead sends it
-to the repository directly.  The material flows for the modified open case are
+to the repository directly.  The material flows for the 1-pass recycle case are
 shown in Figure \ref{fig:flowmodopen}.
@@
 \end{center}
-\caption{Modified open 1-pass \gls{MOX} recycle scenario material flows.}
+\caption{1-pass \gls{MOX} recycle scenario material flows.}
 \label{fig:flowmodopen}
@@
 
-Changing the scenario from a modified open fuel cycle to a closed fuel cycle
+Changing the scenario from a 1-pass fuel cycle to an infinite-pass fuel cycle
 requires only a one-word change in the input file regarding the output
@@
   +    <outcommodity>spent_fuel</outcommodity>
-       <inrecipe>mox_resh_fuel</inrecipe>
+       <inrecipe>mox_fresh_fuel</inrecipe>
        <outrecipe>mox_spent_fuel</outrecipe>
@@
 This results in the material flows in Figure \ref{fig:flowclosed}.  A
-similarly trivial change was used to switch from the once through to a
-modified open fuel cycle.  Note that the \Class{Reactor} always transmutes
-fuel into fixed compositions, so nuclide-specific flows become
-somewhat unrealistic in the fully closed cycle case.
+similarly trivial change was used to switch from the once through to a 1-pass
+fuel cycle.  Note that the \Class{Reactor} always transmutes fuel into fixed
+compositions, the error in isotopic compositions is larger in the
+infinite-pass recycle case.
 
@@
 
-Figure \ref{fig:puseries1} shows the full-system plutonium buildup for open
-(no recycle), modified open, and closed (infinite-pass recycle) variations of
+Figure \ref{fig:puseries1} shows the full-system plutonium buildup for once
+through (no recycle), 1-pass recycle, and infinite-pass recycle variations of
 the one-reactor scenario described above. The figure was generated directly
 from \Cyclus output data. After several batch cycles (near month 300) in the
-modified open and closed cases, enough separated fissile material accumulates
+1-pass and inifinite-pass cases, enough separated fissile material accumulates
 in the fuel fabrication facility to generate a full recycled batch.  When this
@@
 drop in the total fuel cycle system plutonium inventory.  This pattern repeats
-roughly every 10 cycles (200 months) for the modified open case and every 9
-cycles (180 months) for the closed case.  Because the modified open scenario
-does not re-recycle material, it takes the fabrication facility 1 cycle longer
-to accumulate a full batch of fissile material.
+roughly every 10 cycles (200 months) for the 1-pass recycle case and every 9
+cycles (180 months) for the infinite-pass recycle case.  Because the 1-pass
+recycle scenario does not re-recycle material, it takes the fabrication
+facility 2 cycles longer to accumulate a full batch of fissile material.
 
@@
 Figure \ref{fig:puseriesn} shows plutonium buildup for the 10-reactor
-simulations of the open, modified open, and closed scenarios.  As the number
-of reactors (with staggered refueling) increases, the behavior of the system
-approaches a more steady average reminiscent of continuous material flow
-models.
+simulations of the once through, 1-pass recycle, and infinite-pass recycle
+scenarios.  As the number of reactors (with staggered refueling) increases,
+the behavior of the system approaches a more steady average reminiscent of
+continuous material flow models.
 

### 2015-02-06 fundamentals/examples.tex
reword big paragraph

@@
         cycle with a 2 month refuel time.  The reactor was also configured to
-        take in either enriched UOX fuel or recycled MOX fuel - preferring the
-        latter if available.
+        take in either enriched UOX fuel or recycled MOX fuel.
 
@@
 
-For the once through case, the \Class{Reactor} was set to offer all spent fuel
-as waste.  For the 1-pass recycle case, the \Class{Reactor} offered spent UOX
-into a spent fuel market where it is preferentially sent to separations, but
-spent MOX is still offered as waste.  In the infinite-pass recycle case, the
-\Class{Reactor} offers all spent fuel into a spent fuel market. Because the
+Modifying the input file specification to model each of the 3 fuel cycles was
+done by making simple adjustments to the commodities and trade preferences for
+each of the facilities.  The reactor was configured to request recycled MOX
+fuel with a higher preference then new UOX fuel. For the once through case,
+the \Class{Reactor} was set to offer all spent fuel as waste.  For the 1-pass
+recycle case, the \Class{Reactor} offered spent UOX into a spent fuel market,
+but spent MOX is still offered as waste.  In the infinite-pass recycle case,
+the \Class{Reactor} offers all burned fuel into a spent fuel market. The
 separations facility requests spent fuel with a higher preference than the
-repository, it is sent there if possible.  All these preferences are easy to
-adjust and \Cyclus will dynamically handle supply constraints and non-uniform
+repository resulting in preferential recycle.  All these preferences are easy
+to adjust and \Cyclus dynamically handles supply constraints and non-uniform
 preference resolution.  It is notable that separations and recycle fuel
-fabrication capacity is deployed identically in all simulations.  In the
-once-through case, the recycling loop never acquires material, and so reactors
-always receive fresh UOX fuel.  In the 1-pass recycle case, the recycle loop
-only acquires spent UOX.  The \gls{DRE} ensures everything operates smoothly
-in all cases.
+fabrication capacity are deployed identically in all simulations.  In the once
+through case, the recycling loop never acquires material, and so reactors
+always receive fresh UOX fuel.  The \gls{DRE} ensures everything operates
+smoothly in all cases.
 
@@
 received each batch from.  If a batch was received from the recycled fuel
-fabrication facility, it does not offer it to separations and instead sends it
-to the repository directly.  The material flows for the 1-pass recycle case are
-shown in Figure \ref{fig:flowmodopen}.
+fabrication facility, it does not offer it to separations and instead offers
+it as a waste commodity which is only requested by the repository.  The
+material flows for the 1-pass recycle case are shown in Figure
+\ref{fig:flowmodopen}.
 
@@
 similarly trivial change was used to switch from the once through to a 1-pass
-fuel cycle.  Note that the \Class{Reactor} always transmutes fuel into fixed
-compositions, the error in isotopic compositions is larger in the
+fuel cycle.  Note that because the reactors always transmute fuel into fixed
+compositions, the error in isotopic compositions is larger for the
 infinite-pass recycle case.

### 2015-02-09 fundamentals/intro.tex
fixes erroneous double add of baker paper and adds paper by Flicker and Schneider on evaluation criteria.

@@
 
-As nuclear power expands both domestically and internationally, nuclear fuel
-cycle performance analysis on technical, economic, political, and environmental
-axes increases in importance. Appropriate nuclear fuel cycle analysis requires
-calculation of myriad physical, nuclear, chemical, industrial, and political
-phenomena. Nuclear fuel cycle simulators therefore couple complex systems such
-as nuclear process physics, facility deployment, and material routing.
+As nuclear power expands, technical, economic, political, and environmental analyses of nuclear fuel
+cycles by simulators increases in importance.
+The merit of advanced nuclear technologies and the fuel cycles they comprise is shaped by myriad physical, nuclear, chemical, industrial, and political factors.
+Nuclear fuel cycle simulators must therefore couple complex models of
+nuclear process physics, facility deployment, and material routing.
 However, current fuel cycle simulators rely on closed platforms and inflexible
@@
 simulation science and software architecture to solve these problems.
-As a bonus, many of these methods simultaneously enable more efficient, accurate,
+These modern methods simultaneously enable more efficient, accurate,
 robust, and validated analysis.
@@
 The \Cyclus next-generation fuel cycle simulator is the result of design
-choices made explicitly to:
+choices made to:
 \begin{itemize}
-\item support user access and encourages developer extensions,
+\item support access to the tool by fuel cycle analysts and other users,
+\item encourage developer extensions,
 \item enable plug-and-play comparison of modeling methodologies,
@@
 \end{itemize}
-
-Historically, nuclear fuel cycle simulators have estimated 
-nuclear fuel cycle performance using software 
+Historically, nuclear fuel cycle simulators have calculated
+fuel cycle mass balances and performance metrics derived from them using software
 ranging from ad hoc spreadsheet-driven flow calculators to highly specialized
-system dynamics
-proprietary models. To date, current tools are either static, fleet-based, 
+system dynamics modeling platforms. To date, current tools are either static, fleet-based,
 privately distributed, or all of the above. Each of these qualities presents a
-severe challenge to modeling fidelity, generality, efficiency, robustness, and 
+challenge to modeling fidelity, generality, efficiency, robustness, and
 scientific transparency.
-An alternative to these approaches is a dynamic, agent-based simulator with an 
-open platform and an ecosystem of research-driven capabilities.
 
@@
 allows cross-institutional collaboration, increases code robustness \cite{cohen_modern_2010}, and
-cultivates an ecosystem of modeling and calculation options.  The fundamental concepts of the \Cyclus 
+cultivates an ecosystem of modeling and calculation options.
+Comprising flexible, interchangeable models of fuel cycle components with varying scope, depth and fidelity, this ecosystem allows users and developers to customise \Cyclus to analyze the cases that are of interest to them, rather than those the simulator was originally developed to address.
+The fundamental concepts of the \Cyclus
 nuclear fuel cycle simulator capture these modern insights so that challenges
@@
 quantitative measures of performance that
-can be compared among fuel cycle options. The feasibility of technology 
-strategies, dynamics of transitions between fuel cycles, and many other 
+can be compared among fuel cycle options. The feasibility of the technology development and deployment
+strategies which comprise a fuel cycle option, the dynamics of transitions between fuel cycles, and many other
 measures of performance can be expressed in terms of these metrics. For example,
-economic feasibility is often measured in \gls{LCOE}, requiring calculation of
+economic feasibility is often measured in levelized cost of electricity (\gls{LCOE}), requiring calculation of
 lifetime fuel costs and electricity generation,
-while environmental performance might be measured in spent fuel volume, 
+while environmental performance might be measured by spent fuel volume,
   toxicity, or mined uranium.
+A meta-analysis of fuel cycle systems studies identified over two dozen unique quantitative metrics spanning economics and cost, environmental stainability and waste management impacts, safety, security and nonproliferation, resource adequacy and utilization, among others.
+With few exceptions, these metrics are derived from mass balances calculated by a fuel cycle simulator.
+*** shameless plug for some of our work!
+:)  Citation: Flicker, M.
+E., Schneider, E.
+A.
+and P.
+Campbell, "Evaluation Criteria for Analyses of Nuclear Fuel Cycles," Trans.
+Am.
+Nucl.
+Soc.
+111, November 2014 ***
 
@@
 other simulators capture the dynamics of the system.
-Similarly, while some simulators discretely model material and facilities, 
-others treat materials as streams and facilities as fleets, in an aggregated 
-fashion. Simulators often overspecialize, 
-modeling a single aspect of the fuel cycle in great detail while neglecting 
+Similarly, while some simulators discretely model batches of material and individual facilities,
+others aggregate facilities into fleets and materials into streams.
+Simulators can *** deleted overspecialization here and below since it struck me as a judgment call rather than objective statement ***
+model a single aspect of the fuel cycle in great detail while neglecting
 others. For example, a simulator created for policy modeling might have excellent
-capability in economics while material isotopics and transmutation detail are 
-neglected.
+capability in economics while models affecting transformations in material isotopics or the effects of isotopics on technology performance are
+neglected.   *** would be useful to give an example here of a simulator that suffers from overspecification ***
 
-This overspecialization and fractured community is the result of history. 
 Historically, the national laboratories have driven development and regulated
@@
 tools were not available or not sufficiently general to calculate their metrics
-of interest with their method of choice.  With limited access to the national 
+of interest.  With limited access to the national
 laboratory tools and a need to customize them for research purposes,
@@
 \gls{COSI}\cite{boucher_cosi_2005,boucher_cosi:_2006,meyer_new_2009,coquelet-pascal_comparison_2011}.
+*** I would put COSI into the first category of lab tools, to which you could add ORION.
+Nothing else springs to mind here, but I'm sure a quick lit review would reveal some university developed models that were used for a few specific tasks, then forgotten ***
 
@@
 Its precursor,
-\gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006}, began
-as an \gls{LDRD} project within \gls{INL} and sought 
-\gls{ORION}\cite{}, and 
+\gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006}, originated within \gls{INL} and sought
+\gls{ORION}\cite{}, *** lost me here... sought ORION? Also the next sentence seems abrupt... which lessons learned? ***  and
 to provide generic regional capability.  Based on lessons learned from
@@
 a dynamic simulator that treats both materials and facilities discretely, with
-an architecture that permits simulations with multiple and variable levels of 
+an architecture that permits multiple and variable levels of
 fidelity. The simulator's agent-based framework for tracking the
-transformation and trade of resources between facilities within institutions 
-and regions greatly improves upon the existing fuel cycle simulators.
+transformation and trade of resources between autonomous entities with customizable behavior and objectives is an innovation not pursued by any existing fuel cycle simulator.
+*** changed 'greatly improves upon' because it's subjective, also removed mention of institutions, regions here as the meaning of those terms in Cyclus has not yet been defined ***
 
@@
 % \Cyclus, a hero, came in to fill that gap.
+*** I'm inspired to crank up the Bonnie Tyler :)  'I need a hero!' ***
 
-In addition to providing the fundamental features expected in fuel cycle 
-simulators, the \Cyclus paradigm enables essential capabilities that previous 
-simulators lack. Critically, targeted contribution and collaboration within the nuclear fuel cycle analysis 
-community are assisted by the \emph{modular and open architecture} of \Cyclus.
+The \Cyclus paradigm enables targeted contribution and collaboration within the nuclear fuel cycle analysis community.
+This essential capability, absent in previous simulators where user customization and extensibility were not design objectives, comes about through the \emph{modular and open architecture} of \Cyclus.
 Additionally, \Cyclus facilitates direct comparison of modeling methodologies with
@@
 
-Specialists in a given field should utilize their time and resources in 
-modeling the specific processes associated with their area of expertise within 
-thenuclear fuel cycle (e.g., reprocessing and advanced
-fuel fabrication), without having to model the entirety of the cycle.
+This structure recognizes that specialists should utilize their time and resources in
+modeling the specific process associated with their area of expertise (e.g., reprocessing and advanced
+fuel fabrication), without having to create a model of the entire fuel cycle to serve as its host.
 \Cyclus supports them by separating the problem of modeling a
@@
 Furthermore, modeling the evolution of a physics-dependent, international nuclear fuel supply
-chain is a multiscale problem, and existing tools are not sufficiently 
-multiscale. Tools have either focused on macro effects, e.g., the fleet-level
+chain is a multiscale problem which existing tools cannot support. They have either focused on macro effects, e.g., the fleet-level
 stocks and flows of commodities, or micro effects, e.g., the used-fuel

### 2015-02-10 fundamentals/intro.tex

@@
 
-As nuclear power expands, technical, economic, political, and environmental analyses of nuclear fuel
-cycles by simulators increases in importance.
-The merit of advanced nuclear technologies and the fuel cycles they comprise is shaped by myriad physical, nuclear, chemical, industrial, and political factors.
-Nuclear fuel cycle simulators must therefore couple complex models of
-nuclear process physics, facility deployment, and material routing.
-However, current fuel cycle simulators rely on closed platforms and inflexible
+As nuclear power expands, technical, economic, political, and environmental
+analyses of nuclear fuel cycles by simulators increases in importance. The
+merit of advanced nuclear technologies and the fuel cycles they comprise is
+shaped by myriad physical, nuclear, chemical, industrial, and political
+factors. Nuclear fuel cycle simulators must therefore couple complex models of
+nuclear process physics, facility deployment, and material routing.  However,
+current fuel cycle simulators rely on closed platforms and inflexible
 architectures which exhibit three main failure modes. First, they discourage
@@
 efforts to directly compare modeling methodologies. Finally, they
-over-specialize, rendering most tools applicable to only a subset of
-desired simulation fidelities, scales, and applications.
-The \Cyclus nuclear fuel cycle simulator framework and
-its modeling ecosystem incorporate modern insights from
-simulation science and software architecture to solve these problems.
-These modern methods simultaneously enable more efficient, accurate,
+over-specialize, rendering most tools applicable to only a subset of desired
+simulation fidelities, scales, and applications.  The \Cyclus nuclear fuel
+cycle simulator framework and its modeling ecosystem incorporate modern
+insights from simulation science and software architecture to solve these
+problems.  These modern methods simultaneously enable more efficient, accurate,
 robust, and validated analysis.
@@
 \end{itemize}
+
 Historically, nuclear fuel cycle simulators have calculated
@@
 cycle analysis more realistically supports a range of simulation goals than
-static analysis
-\cite{piet_dynamic_2011}. Similarly, experience in the broader field of systems
-analysis indicates that agent-based modeling enables more flexible simulation
-control, without loss of generality \cite{macal_agent-based_2010}. Finally, openness
-allows cross-institutional collaboration, increases code robustness \cite{cohen_modern_2010}, and
-cultivates an ecosystem of modeling and calculation options.
-Comprising flexible, interchangeable models of fuel cycle components with varying scope, depth and fidelity, this ecosystem allows users and developers to customise \Cyclus to analyze the cases that are of interest to them, rather than those the simulator was originally developed to address.
-The fundamental concepts of the \Cyclus
-nuclear fuel cycle simulator capture these modern insights so that challenges
-in nuclear fuel cycle analysis can be better addressed.
+static analysis \cite{piet_dynamic_2011}. Similarly, experience in the broader
+field of systems analysis indicates that agent-based modeling enables more
+flexible simulation control, without loss of generality
+\cite{macal_agent-based_2010}. Finally, openness allows cross-institutional
+collaboration, increases code robustness \cite{cohen_modern_2010}, and
+cultivates an ecosystem of modeling and calculation options.  Comprising
+flexible, interchangeable models of fuel cycle components with varying scope,
+depth and fidelity, this ecosystem allows users and developers to customise
+\Cyclus to analyze the cases that are of interest to them, rather than those
+the simulator was originally developed to address.  The fundamental concepts of
+the \Cyclus nuclear fuel cycle simulator capture these modern insights so that
+challenges in nuclear fuel cycle analysis can be better addressed.
 
@@
 Nuclear fuel cycle simulators drive \gls{RDD} by calculating `metrics',
-quantitative measures of performance that
-can be compared among fuel cycle options. The feasibility of the technology development and deployment
-strategies which comprise a fuel cycle option, the dynamics of transitions between fuel cycles, and many other
-measures of performance can be expressed in terms of these metrics. For example,
-economic feasibility is often measured in levelized cost of electricity (\gls{LCOE}), requiring calculation of
-lifetime fuel costs and electricity generation,
-while environmental performance might be measured by spent fuel volume,
-  toxicity, or mined uranium.
-A meta-analysis of fuel cycle systems studies identified over two dozen unique quantitative metrics spanning economics and cost, environmental stainability and waste management impacts, safety, security and nonproliferation, resource adequacy and utilization, among others.
-With few exceptions, these metrics are derived from mass balances calculated by a fuel cycle simulator.
-*** shameless plug for some of our work!
-:)  Citation: Flicker, M.
-E., Schneider, E.
-A.
-and P.
-Campbell, "Evaluation Criteria for Analyses of Nuclear Fuel Cycles," Trans.
-Am.
-Nucl.
-Soc.
-111, November 2014 ***
+quantitative measures of performance that can be compared among fuel cycle
+options. The feasibility of the technology development and deployment
+strategies which comprise a fuel cycle option, the dynamics of transitions
+between fuel cycles, and many other measures of performance can be expressed in
+terms of these metrics. For example, economic feasibility is often measured in
+levelized cost of electricity (\gls{LCOE}), requiring calculation of lifetime
+fuel costs and electricity generation, while environmental performance might be
+measured by spent fuel volume, toxicity, or mined uranium.  A meta-analysis of
+fuel cycle systems studies identified over two dozen unique quantitative
+metrics spanning economics and cost, environmental stainability and waste
+management impacts, safety, security and nonproliferation, resource adequacy
+and utilization, among others. With few exceptions, these metrics are derived
+from mass balances calculated by a fuel cycle simulator.
+\cite{flicker_evaluation_2014}.
 
-However, methods for calculating those metrics vary among simulators. Some model the
-system of facilities, economics, and materials in static equilibrium, while
-other simulators capture the dynamics of the system.
-Similarly, while some simulators discretely model batches of material and individual facilities,
-others aggregate facilities into fleets and materials into streams.
-Simulators can *** deleted overspecialization here and below since it struck me as a judgment call rather than objective statement ***
-model a single aspect of the fuel cycle in great detail while neglecting
-others. For example, a simulator created for policy modeling might have excellent
-capability in economics while models affecting transformations in material isotopics or the effects of isotopics on technology performance are
-neglected.   *** would be useful to give an example here of a simulator that suffers from overspecification ***
+However, methods for calculating those metrics vary among simulators. Some
+model the system of facilities, economics, and materials in static equilibrium,
+while other simulators capture the dynamics of the system.  Similarly, while
+some simulators discretely model batches of material and individual facilities,
+others aggregate facilities into fleets and materials into streams. Simulators
+can model a single aspect of the fuel cycle in great detail while neglecting
+others. For example, a simulator created for policy modeling might have
+excellent capability in economics while models affecting transformations in
+material isotopics or the effects of isotopics on technology performance are
+neglected.  The \gls{CAFCA}\cite{guerin_impact_2009} code is problem-oriented
+in this way.
 
-Historically, the national laboratories have driven development and regulated
+Historically, domestic national laboratories have driven development and regulated
 the use of their own tools: \gls{VISION}\cite{jacobson_verifiable_2010},
@@
 \gls{DYMOND}\cite{yacout_modeling_2005}, and
-\gls{NFCSim}\cite{schneider_nfcsim:_2005}.  Outside the national laboratories,
+\gls{NFCSim}\cite{schneider_nfcsim:_2005}.
+Internationally, other laboratories have created their own as well, such as
+\gls{COSI}\cite{boucher_cosi_2005,boucher_cosi:_2006,meyer_new_2009,coquelet-pascal_comparison_2011}
+and
+\gls{ORION}\cite{worrall_scenario_2007}.
+Outside the national laboratories,
 researchers have created new nuclear fuel cycle simulation tools when existing
@@
 developing tools of their own from scratch and tailored to their own needs, for
-example \gls{CAFCA}\cite{guerin_impact_2009} and
-\gls{COSI}\cite{boucher_cosi_2005,boucher_cosi:_2006,meyer_new_2009,coquelet-pascal_comparison_2011}.
-*** I would put COSI into the first category of lab tools, to which you could add ORION.
-Nothing else springs to mind here, but I'm sure a quick lit review would reveal some university developed models that were used for a few specific tasks, then forgotten ***
+example \gls{CAFCA}\cite{guerin_impact_2009}.
 
-\Cyclus emerged from a line of tools seeking to break this practice.
-Its precursor,
-\gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006}, originated within \gls{INL} and sought
-\gls{ORION}\cite{}, *** lost me here... sought ORION? Also the next sentence seems abrupt... which lessons learned? ***  and
-to provide generic regional capability.  Based on lessons learned from
-Version 1, the
-\acrshort{GENIUSv2} Version 2\cite{oliver_studying_2009,huff_geniusv2_2009} code sought to
-provide more generality and an extensible interface to facilitate
-collaboration.  The \Cyclus project then improved upon the \acrshort{GENIUSv2}
-effort by implementing increased modularity and encapsulation.  The result is
-a dynamic simulator that treats both materials and facilities discretely, with
-an architecture that permits multiple and variable levels of
-fidelity. The simulator's agent-based framework for tracking the
-transformation and trade of resources between autonomous entities with customizable behavior and objectives is an innovation not pursued by any existing fuel cycle simulator.
-*** changed 'greatly improves upon' because it's subjective, also removed mention of institutions, regions here as the meaning of those terms in Cyclus has not yet been defined ***
+\Cyclus emerged from a line of tools seeking to break this practice.  Its
+precursor,
+\gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006},
+originated within \gls{INL} and sought to provide generic regional capability.
+Based on lessons learned from Version 1, the \acrshort{GENIUSv2} Version
+2\cite{oliver_studying_2009,huff_geniusv2_2009} code sought to provide more
+generality and an extensible interface to facilitate collaboration.  The
+\Cyclus project then improved upon the \acrshort{GENIUSv2} effort by
+implementing increased modularity and encapsulation.  The result is a dynamic
+simulator that treats both materials and facilities discretely, with an
+architecture that permits multiple and variable levels of fidelity. The
+simulator's agent-based framework for tracking the transformation and trade of
+resources between autonomous regional and institutional entities with
+customizable behavior and objectives is an innovation not pursued by any
+existing fuel cycle simulator.
 
@@
 % \Cyclus, a hero, came in to fill that gap.
-*** I'm inspired to crank up the Bonnie Tyler :)  'I need a hero!' ***
 
-The \Cyclus paradigm enables targeted contribution and collaboration within the nuclear fuel cycle analysis community.
-This essential capability, absent in previous simulators where user customization and extensibility were not design objectives, comes about through the \emph{modular and open architecture} of \Cyclus.
-Additionally, \Cyclus facilitates direct comparison of modeling methodologies with
-\emph{agent interchangeability}.
-Finally, \Cyclus is applicable to a broader range of
-fidelities, scales, and applications than other simulators.
-due to the flexibility and generality
-of its \emph{\gls{ABM}} paradigm and \emph{discrete, object-oriented approach}
+The \Cyclus paradigm enables targeted contribution and collaboration within the
+nuclear fuel cycle analysis community. This essential capability, absent in
+previous simulators where user customization and extensibility were not design
+objectives, comes about through the \emph{modular and open architecture} of
+\Cyclus.  Additionally, \Cyclus facilitates direct comparison of modeling
+methodologies with \emph{agent interchangeability}.  Finally, \Cyclus is
+applicable to a broader range of fidelities, scales, and applications than
+other simulators.  due to the flexibility and generality of its
+\emph{\gls{ABM}} paradigm and \emph{discrete, object-oriented approach}.
 
-This structure recognizes that specialists should utilize their time and resources in
-modeling the specific process associated with their area of expertise (e.g., reprocessing and advanced
-fuel fabrication), without having to create a model of the entire fuel cycle to serve as its host.
-\Cyclus supports them by separating the problem of modeling a
-physics-dependent supply chain into two distinct components: a simulation kernel and archetypes that
-interact with the kernel. The kernel is responsible for the
-deployment and interaction logic of entities in the simulation.  Physics calculations and
-customized behaviors are implemented within archetypes.
+This structure recognizes that specialists should utilize their time and
+resources in modeling the specific process associated with their area of
+expertise (e.g., reprocessing and advanced fuel fabrication), without having to
+create a model of the entire fuel cycle to serve as its host.  \Cyclus supports
+them by separating the problem of modeling a physics-dependent supply chain
+into two distinct components: a simulation kernel and archetypes that interact
+with the kernel. The kernel is responsible for the deployment and interaction
+logic of entities in the simulation.  Physics calculations and customized
+behaviors are implemented within archetypes.
 
-Furthermore, modeling the evolution of a physics-dependent, international nuclear fuel supply
-chain is a multiscale problem which existing tools cannot support. They have either focused on macro effects, e.g., the fleet-level
+Furthermore, modeling the evolution of a physics-dependent, international
+nuclear fuel supply chain is a multiscale problem which existing tools cannot
+support. They have either focused on macro effects, e.g., the fleet-level
 stocks and flows of commodities, or micro effects, e.g., the used-fuel
-composition of fast reactor fuel. Each focus has driven the
-development of specialized tools, rendering the task of answering questions between
-the macro and micro levels challenging within a single tool.
-In contrast, the extensible architecture and discrete object tracking of \Cyclus allow
-the creation and interchangeability of custom archetypes at any level of fidelity.
+composition of fast reactor fuel. Each focus has driven the development of
+specialized tools, rendering the task of answering questions between the macro
+and micro levels challenging within a single tool.  In contrast, the extensible
+architecture and discrete object tracking of \Cyclus allow the creation and
+interchangeability of custom archetypes at any level of fidelity.

### 2015-02-10 fundamentals/examples.tex
adds a wrapup paragraph to @rwcarlsen examples section.

@@
         method" originally developed by Baker and Ross
-        \cite{baker1963comparison}.  This technique has also been used in the
+        \cite{baker_comparison_1963}.  This technique has also been used in the
         Commelini-Sicart (COSI) fuel cycle simulator developed by the French
@@
 from \Cyclus output data. After several batch cycles (near month 300) in the
-1-pass and inifinite-pass cases, enough separated fissile material accumulates
+1-pass and infinite-pass cases, enough separated fissile material accumulates
 in the fuel fabrication facility to generate a full recycled batch.  When this
@@
 \end{figure}
+
+The fundamental capabilities of demonstrated in these simulations qualify
+\Cyclus and its ecosystem to model the breadth of scenario types expected of
+nuclear fuel cycle simulator tools. These examples further show the flexibility
+provided by the material routing logic within the \Cyclus framework and provide
+an example of the resolution made possible by discrete-facility and
+discrete-material modeling in fuel cycle simulation.

### 2015-02-11 fundamentals/intro.tex
lcoe should not be repeated

@@
 As nuclear power expands, technical, economic, political, and environmental
-analyses of nuclear fuel cycles by simulators increases in importance. The
+analyses of nuclear fuel cycles by simulators increases in importance. NucleThe
 merit of advanced nuclear technologies and the fuel cycles they comprise is
@@
 terms of these metrics. For example, economic feasibility is often measured in
-levelized cost of electricity (\gls{LCOE}), requiring calculation of lifetime
+\gls{LCOE}, requiring calculation of lifetime
 fuel costs and electricity generation, while environmental performance might be
@@
 example \gls{CAFCA}\cite{guerin_impact_2009}.
+
+\input{fcsreqs}
 

### 2015-02-11 fundamentals/fcsreqs.tex
adding some text about previous simulators that borrows heavily from the NGFCS functions and requirements document

Many fuel cycle phenomena have aggregate system-level effects which can only be captured by discrete material tracking \cite{huff_functions_2010}.  \Cyclus tracks materials as discrete objects. Some current fuel cycle simulation tools such as \gls{COSI6}, \gls{DESAE2.1}, \gls{FAMILY21}, \gls{GENIUS} versions 1 and 2, and \gls{NFCSim} also possess the ability to model discrete materials.

Similarly, the ability to model disruptions (i.e. facility shutdowns due to insufficient feed material or insufficient processing and storage capacity) is most readily captured by software capable of tracking the operations status of discrete facilities \cite{huff_functions_2010}.
Fleet-based models (i.e. \gls{VISION}) are unable to capture this gracefully. All of the software capable of discrete materials have a notion of discrete facilities, however not all handle disruption in the same manner. \gls{DESAE}, for example, does not allow shutdown due to insufficient feedstock, though \Cyclus does. In the event of insufficient fissile material during reprocessing, \gls{DESAE} borrows material from storage, leaving a negative value \macarthy_benchmark_2012}.

The proprietary concerns of research institutions and security constraints of data within fuel cycle codes often restrict code access. A code's use is therefore often limited to its institution of origin, necessitating effort duplication at other institutions and thereby squandering broader human resources. License agreements and institutional approval are required for most current codes (i.e. \gls{COSI}6, \gls{DANESS}, \gls{DESAE}, \gls{EVOLCODE}, \gls{FAMILY}, and \gls{NFCSIM})\cite{juchau_modeling_2010}. However, \Cyclus and the MIT code, \gls{CAFCA}, provides fully free and open access to all users and developers, foreign and domestic.

Uncertainty and Sensitivity Automation
While uncertainty and sensitivity analysis of input parameters can be conducted at a medium-fidelity level by manual parametric sampling with almost any fuel cycle code [26] [33], automated sampling and propagation of uncertainties and parametric sensitivity has not been achieved by any of the fuel cycle codes discussed here. Furthermore, uncertainty distributions for included data and propagation algorithms are lacking. Many of the missions that the FCS seeks to support would be facilitated by such a capability and this need constitutes a driving factor in the development of the FCS concept.

Unconventional Reactor Modeling
Much fuel cycle simulation focus in the recent decade has been driven by specific fuel cycle policy goals. As a result, most fuel cycle models have neglected to model myriad unconventional fuel cycles and reactor models on the research stage today. \Cyclus seeks to offer unconstrained modeling freedom for researchers interested in the impact of unconventional transmutation technologies and uses of reactor heat production on fuel cycle metrics. Such unconventional models may include advanced designs such as small modular reactors and travelling wave reactors.

Dynamic Feedback for Economic Analysis
In addition to recording cost information about deployment and material movements, \Cyclus simulation logic relies on a market paradigm that enables simulation of the dynamic responses within the system to pricing, availability, and other institutional preferences. This capability is an advanced functionality and does not exist in a flexible manner for other fuel cycle simulators.

### 2015-02-12 fundamentals/intro.tex
adds erich definition of fcs

@@
 
-Historically, nuclear fuel cycle simulators have calculated
-fuel cycle mass balances and performance metrics derived from them using software
-ranging from ad hoc spreadsheet-driven flow calculators to highly specialized
-system dynamics modeling platforms. To date, current tools are either static, fleet-based,
-privately distributed, or all of the above. Each of these qualities presents a
-challenge to modeling fidelity, generality, efficiency, robustness, and
-scientific transparency.
+The cardinal purpose of a nuclear fuel cycle simulator is to calculate the
+time- and facility-dependent mass flow through all or part the fuel cycle. Many
+architecture choices are discussed in \ref{sec:litrev}.  Historically, nuclear
+fuel cycle simulators have calculated fuel cycle mass balances and performance
+metrics derived from them using software ranging from ad hoc spreadsheet-driven
+flow calculators to highly specialized system dynamics modeling platforms. To
+date, current tools are often static rather than dynamic, rigid rather than
+flexible, fleet-based rather than discrete, or privately distributed rather
+than open source. Each of these choices presents a challenge to modeling
+fidelity, generality, efficiency, robustness, and scientific transparency.
 
@@
 
-\input{fcsreqs}
-
 \Cyclus emerged from a line of tools seeking to break this practice.  Its
@@
 existing fuel cycle simulator.
+
+\input{fcsreqs}
 

### 2015-02-12 fundamentals/fcsreqs.tex
this attemps to provide a stronger literature review of existing simulators. It was based heavily on the functions and requirements, for obvious reasons... that document drove our devlopment.

@@
-Many fuel cycle phenomena have aggregate system-level effects which can only be captured by discrete material tracking \cite{huff_functions_2010}.
-\Cyclus tracks materials as discrete objects.
-Some current fuel cycle simulation tools such as \gls{COSI6}, \gls{DESAE2.1}, \gls{FAMILY21}, \gls{GENIUS} versions 1 and 2, and \gls{NFCSim} also possess the ability to model discrete materials.
+\subsubsection{Discrete Facilities and Materials}
 
-Similarly, the ability to model disruptions (i.e.
-facility shutdowns due to insufficient feed material or insufficient processing and storage capacity) is most readily captured by software capable of tracking the operations status of discrete facilities \cite{huff_functions_2010}.
-Fleet-based models (i.e.
-\gls{VISION}) are unable to capture this gracefully.
-All of the software capable of discrete materials have a notion of discrete facilities, however not all handle disruption in the same manner.
-\gls{DESAE}, for example, does not allow shutdown due to insufficient feedstock, though \Cyclus does.
-In the event of insufficient fissile material during reprocessing, \gls{DESAE} borrows material from storage, leaving a negative value \macarthy_benchmark_2012}.
+Many fuel cycle phenomena have aggregate system-level effects which can only be
+captured by discrete material tracking \cite{huff_functions_2010}.  \Cyclus
+tracks materials as discrete objects. Some current fuel cycle simulation tools
+such as \gls{COSI6}, \gls{DESAE2.1}, \gls{FAMILY21}, \gls{GENIUS} versions 1
+and 2, and \gls{NFCSim} also possess the ability to model discrete materials.
 
-The proprietary concerns of research institutions and security constraints of data within fuel cycle codes often restrict code access.
-A code's use is therefore often limited to its institution of origin, necessitating effort duplication at other institutions and thereby squandering broader human resources.
-License agreements and institutional approval are required for most current codes (i.e.
-\gls{COSI}6, \gls{DANESS}, \gls{DESAE}, \gls{EVOLCODE}, \gls{FAMILY}, and \gls{NFCSIM})\cite{juchau_modeling_2010}.
-However, \Cyclus and the MIT code, \gls{CAFCA}, provides fully free and open access to all users and developers, foreign and domestic.
+Similarly, the ability to model disruptions (i.e. facility shutdowns due to
+insufficient feed material or insufficient processing and storage capacity) is
+most readily captured by software capable of tracking the operations status of
+discrete facilities \cite{huff_functions_2010}.  Fleet-based models (i.e.
+\gls{VISION}) are unable to capture this gracefully.  All of the software
+capable of discrete materials have a notion of discrete facilities, however not
+all handle disruption in the same manner. \gls{DESAE}, for example, does not
+allow shutdown due to insufficient feedstock, though \Cyclus does. In the event
+of insufficient fissile material during reprocessing, \gls{DESAE} borrows
+material from storage, leaving a negative value \cite{macarthy_benchmark_2012}.
 
-Uncertainty and Sensitivity Automation
-While uncertainty and sensitivity analysis of input parameters can be conducted at a medium-fidelity level by manual parametric sampling with almost any fuel cycle code [26] [33], automated sampling and propagation of uncertainties and parametric sensitivity has not been achieved by any of the fuel cycle codes discussed here.
-Furthermore, uncertainty distributions for included data and propagation algorithms are lacking.
-Many of the missions that the FCS seeks to support would be facilitated by such a capability and this need constitutes a driving factor in the development of the FCS concept.
+\subsubsection{Open Access}
 
-Unconventional Reactor Modeling
-Much fuel cycle simulation focus in the recent decade has been driven by specific fuel cycle policy goals.
-As a result, most fuel cycle models have neglected to model myriad unconventional fuel cycles and reactor models on the research stage today.
-\Cyclus seeks to offer unconstrained modeling freedom for researchers interested in the impact of unconventional transmutation technologies and uses of reactor heat production on fuel cycle metrics.
-Such unconventional models may include advanced designs such as small modular reactors and travelling wave reactors.
+The proprietary concerns of research institutions and security constraints of
+data within fuel cycle codes often restrict code access. A code's use is
+therefore often limited to its institution of origin, necessitating effort
+duplication at other institutions and thereby squandering broader human
+resources. License agreements and institutional approval are required for most
+current codes (i.e. \gls{COSI}6, \gls{DANESS}, \gls{DESAE}, \gls{EVOLCODE},
+\gls{FAMILY}, and \gls{NFCSIM})\cite{juchau_modeling_2010}.  Even when, as in
+the case of the MIT \gls{CAFCA} software, the source code is unrestricted, the
+platform on which it relies is oftenrestricted or commercial.  However, \Cyclus
+provide fully free and open access to all users
+and developers, foreign and domestic.
 
-Dynamic Feedback for Economic Analysis
-In addition to recording cost information about deployment and material movements, \Cyclus simulation logic relies on a market paradigm that enables simulation of the dynamic responses within the system to pricing, availability, and other institutional preferences.
-This capability is an advanced functionality and does not exist in a flexible manner for other fuel cycle simulators.
+\subsubsection{Flexibility and Extensibility}
+
+In addition to being inaccessible, the vast majority of fuel cycle simulators
+are, effectively, inextensible. Typical fuel cycle simulator evelopment teams are insular, in
+part due to accessiblity issues. Also, however, their frameworks contain
+heuristics and assumptions that constrain developer additions.
+
+For example, where most other simulators describe a finite set of acceptable
+cycle constructions (once through, single-pass, multi-pass), the \Cyclus
+simulation logic relies on a market paradigm that can be easily directed to
+create novel material and economic paths. The simulation of the dynamic
+responses within the system to pricing, availability, and other institutional
+preferences in \Cyclus is an advanced capability and does not exist in a
+flexible manner for other fuel cycle simulators.

### 2015-02-12 fundamentals/intro.tex
this attemps to provide a stronger literature review of existing simulators. It was based heavily on the functions and requirements, for obvious reasons... that document drove our devlopment.

@@
 universities and private industry researchers have ``reinvented the wheel'' by
-developing tools of their own from scratch and tailored to their own needs, for
-example \gls{CAFCA}\cite{guerin_impact_2009}.
+developing tools of their own from scratch and tailored to their own needs.
 

### 2015-02-12 fundamentals/fcsreqs.tex
fixin some bib issues

@@
 Many fuel cycle phenomena have aggregate system-level effects which can only be
-captured by discrete material tracking \cite{huff_functions_2010}.  \Cyclus
+captured by discrete material tracking \cite{huff_next_2010}.  \Cyclus
 tracks materials as discrete objects. Some current fuel cycle simulation tools
-such as \gls{COSI6}, \gls{DESAE2.1}, \gls{FAMILY21}, \gls{GENIUS} versions 1
-and 2, and \gls{NFCSim} also possess the ability to model discrete materials.
+such as \gls{COSI}
+\cite{mccarthy_benchmark_2012,grasso_nea-wpfc/fcts_2009,guerin_benchmark_2009},
+\gls{DESAE}
+\cite{andrianova_desae_2008}, FAMILY21\cite{mccarthy_benchmark_2012},
+\gls{GENIUSv1}, \gls{GENIUSv2}, and \gls{NFCSim} also possess the ability to
+model discrete materials.
 
@@
 most readily captured by software capable of tracking the operations status of
-discrete facilities \cite{huff_functions_2010}.  Fleet-based models (i.e.
+discrete facilities \cite{huff_next_2010}.  Fleet-based models (i.e.
 \gls{VISION}) are unable to capture this gracefully.  All of the software
@@
 of insufficient fissile material during reprocessing, \gls{DESAE} borrows
-material from storage, leaving a negative value \cite{macarthy_benchmark_2012}.
+material from storage, leaving a negative value \cite{mccarthy_benchmark_2012}.
 
@@
 resources. License agreements and institutional approval are required for most
-current codes (i.e. \gls{COSI}6, \gls{DANESS}, \gls{DESAE}, \gls{EVOLCODE},
-\gls{FAMILY}, and \gls{NFCSIM})\cite{juchau_modeling_2010}.  Even when, as in
+current codes (i.e. \gls{COSI}6, \gls{DANESS}, \gls{DESAE}, EVOLCODE,
+FAMILY21, \gls{NFCSim})\cite{juchau_modeling_2010}, ORION, and VISION.  Even when, as in
 the case of the MIT \gls{CAFCA} software, the source code is unrestricted, the

### 2015-02-13 fundamentals/impl.tex
adds api def
first rough draft of a dre section

@@
 to define nuclear fuel cycle agents and processes independent of the simulation 
-logic. This encapsulated `plug-in'
+logic. To achieve this, agents are developed using the \Cyclus framework \gls{API}, a set of functions and protocols
+which 
+assist in agent development and specify how agents should be defined. 
+This encapsulated `plug-in'
 design choice provides two major benefits. First, analysts across research institutions can take advantage of the 
@@
 
-\TODO{Matt Gidden, please fill in}
+Dynamic Resource Exchange (DRE) is the critical resource-related process on
+which \Cyclus simulations are built. It defines the resource interaction
+mechanisms and methodologies for all agents. As the \Cyclus supply-demand
+resolution framework, the DRE must be able to support arbitrary
+facilities. Supporting the general \Cyclus philosophy, facilities are treated as
+black boxes and a clear supply-demand communication framework is defined.
+
+The DRE consists of three steps: supply-demand information gathering, resource
+exchange solution, and trade execution. Importantly, each step is agnostic with
+respect to the exchange of resources in question, i.e., the same procedure is
+used for both Materials and Products. The information-gathering step consists of
+three phases. First, consumers of commodities denote both the quantity of a
+commodity they need to consume as well as the target isotopics, or quality, by
+posting their demand to the market exchange as a series of \textit{requests}. An
+optional collection of demand constraints are associated with each collection of
+requests. Collections of requests may be grouped together, denoting
+\textit{mutual} requests that represent demand for some common purpose. For
+example, a reactor may request UOX and MOX fuel mutually, indicating that either
+will satisfy its demand for fuel. Suppliers then respond to the series of
+requests with a \textit{bid}. A bid supplies a notion of the quantity and
+quality of a resource to match a request. Suppliers may add an arbitrary number
+of constraints to accomany bids. For example, an enriched UOX supplier may
+supply both a natural Uranium and SWU constraint. Any potential resource
+transfer may be denoted as \textit{exclusive}. An exclusive transfer must either
+be met fully or not at all in order to support concepts such as the the trading
+of individual reactor assemblies. Finally, requesting facilities, institutions
+and regions may apply \textit{preferences} to each potential request-bid pairing
+based on the proposed resource transfer. Therefore, an institution can apply a
+higher preference to a partner to which it is congenial; similarly, a region may
+negate any transfers of material which have a higher Uranium enrichment than is
+allowable.
+
+The DRE may be solved either optimally by a mathematical program or
+approximately by a simulation-based heuristic \TODO{cite}. If any trade is
+denoted as exclusive, e.g., if an analyst desires an assembly-fidelity model,
+then either a heuristic must be used or exchanges must be respresented as
+Mixed-Integer Nonlinear Programs (MILP). If no exclusive trades exist, a Linear
+Programming (LP) model may be used. In practice, LPs solve much faster than
+MILPs. However, the capability to model both exists in \Cyclus in order to
+provide users with the desired level of fidelity.
+
+Trades are initiated by the \Cyclus kernel after a solution to the DRE is
+found. The DRE is executed at each time step. Therefore, if a facility's request
+for a resource is not met at a given time step, it may offer a request in the
+proceeding time step.
 

### 2015-02-14 fundamentals/impl.tex
spell checked

@@
 quality of a resource to match a request. Suppliers may add an arbitrary number
-of constraints to accomany bids. For example, an enriched UOX supplier may
+of constraints to accompany bids. For example, an enriched UOX supplier may
 supply both a natural Uranium and SWU constraint. Any potential resource
@@
 denoted as exclusive, e.g., if an analyst desires an assembly-fidelity model,
-then either a heuristic must be used or exchanges must be respresented as
+then either a heuristic must be used or exchanges must be represented as
 Mixed-Integer Nonlinear Programs (MILP). If no exclusive trades exist, a Linear

### 2015-02-14 fundamentals/impl.tex
no more the the
using gls package

@@
 
-Dynamic Resource Exchange (DRE) is the critical resource-related process on
-which \Cyclus simulations are built. It defines the resource interaction
-mechanisms and methodologies for all agents. As the \Cyclus supply-demand
-resolution framework, the DRE must be able to support arbitrary
-facilities. Supporting the general \Cyclus philosophy, facilities are treated as
-black boxes and a clear supply-demand communication framework is defined.
+The \gls{DRE} is the critical resource-related process on which \Cyclus
+simulations are built. It defines the resource interaction mechanisms and
+methodologies for all agents. As the \Cyclus supply-demand resolution framework,
+the DRE must be able to support arbitrary facilities. Supporting the general
+\Cyclus philosophy, facilities are treated as black boxes and a clear
+supply-demand communication framework is defined.
 
-The DRE consists of three steps: supply-demand information gathering, resource
-exchange solution, and trade execution. Importantly, each step is agnostic with
-respect to the exchange of resources in question, i.e., the same procedure is
-used for both Materials and Products. The information-gathering step consists of
-three phases. First, consumers of commodities denote both the quantity of a
-commodity they need to consume as well as the target isotopics, or quality, by
-posting their demand to the market exchange as a series of \textit{requests}. An
-optional collection of demand constraints are associated with each collection of
-requests. Collections of requests may be grouped together, denoting
-\textit{mutual} requests that represent demand for some common purpose. For
-example, a reactor may request UOX and MOX fuel mutually, indicating that either
-will satisfy its demand for fuel. Suppliers then respond to the series of
-requests with a \textit{bid}. A bid supplies a notion of the quantity and
-quality of a resource to match a request. Suppliers may add an arbitrary number
-of constraints to accompany bids. For example, an enriched UOX supplier may
-supply both a natural Uranium and SWU constraint. Any potential resource
-transfer may be denoted as \textit{exclusive}. An exclusive transfer must either
-be met fully or not at all in order to support concepts such as the the trading
-of individual reactor assemblies. Finally, requesting facilities, institutions
-and regions may apply \textit{preferences} to each potential request-bid pairing
-based on the proposed resource transfer. Therefore, an institution can apply a
-higher preference to a partner to which it is congenial; similarly, a region may
-negate any transfers of material which have a higher Uranium enrichment than is
-allowable.
+The \gls{DRE} consists of three steps: supply-demand information gathering,
+resource exchange solution, and trade execution. Importantly, each step is
+agnostic with respect to the exchange of resources in question, i.e., the same
+procedure is used for both Materials and Products. The information-gathering
+step consists of three phases. First, consumers of commodities denote both the
+quantity of a commodity they need to consume as well as the target isotopics, or
+quality, by posting their demand to the market exchange as a series of
+\textit{requests}. An optional collection of demand constraints are associated
+with each collection of requests. Collections of requests may be grouped
+together, denoting \textit{mutual} requests that represent demand for some
+common purpose. For example, a reactor may request UOX and MOX fuel mutually,
+indicating that either will satisfy its demand for fuel. Suppliers then respond
+to the series of requests with a \textit{bid}. A bid supplies a notion of the
+quantity and quality of a resource to match a request. Suppliers may add an
+arbitrary number of constraints to accompany bids. For example, an enriched UOX
+supplier may supply both a natural Uranium and SWU constraint. Any potential
+resource transfer may be denoted as \textit{exclusive}. An exclusive transfer
+must either be met fully or not at all in order to support concepts such as the
+trading of individual reactor assemblies. Finally, requesting facilities,
+institutions and regions may apply \textit{preferences} to each potential
+request-bid pairing based on the proposed resource transfer. Therefore, an
+institution can apply a higher preference to a partner to which it is congenial;
+similarly, a region may negate any transfers of material which have a higher
+Uranium enrichment than is allowable.
 
-The DRE may be solved either optimally by a mathematical program or
+The \gls{DRE} may be solved either optimally by a mathematical program or
 approximately by a simulation-based heuristic \TODO{cite}. If any trade is
 denoted as exclusive, e.g., if an analyst desires an assembly-fidelity model,
-then either a heuristic must be used or exchanges must be represented as
-Mixed-Integer Nonlinear Programs (MILP). If no exclusive trades exist, a Linear
-Programming (LP) model may be used. In practice, LPs solve much faster than
-MILPs. However, the capability to model both exists in \Cyclus in order to
-provide users with the desired level of fidelity.
+then either a heuristic must be used or exchanges must be represented as a
+\gls{MILP}. If no exclusive trades exist, a \gls{LP} model may be used. In
+practice, LPs solve much faster than \gls{MILP}s. However, the capability to
+model both exists in \Cyclus in order to provide users with the desired level of
+fidelity.
 
-Trades are initiated by the \Cyclus kernel after a solution to the DRE is
-found. The DRE is executed at each time step. Therefore, if a facility's request
-for a resource is not met at a given time step, it may offer a request in the
-proceeding time step.
+Trades are initiated by the \Cyclus kernel after a solution to the \gls{DRE} is
+found. The \gls{DRE} is executed at each time step. Therefore, if a facility's
+request for a resource is not met at a given time step, it may offer a request
+in the proceeding time step.
 

### 2015-02-14 fundamentals/impl.tex
added prelim citation
split up information-gathering paragraph

@@
 
-The \gls{DRE} consists of three steps: supply-demand information gathering,
-resource exchange solution, and trade execution. Importantly, each step is
-agnostic with respect to the exchange of resources in question, i.e., the same
-procedure is used for both Materials and Products. The information-gathering
-step consists of three phases. First, consumers of commodities denote both the
-quantity of a commodity they need to consume as well as the target isotopics, or
-quality, by posting their demand to the market exchange as a series of
-\textit{requests}. An optional collection of demand constraints are associated
-with each collection of requests. Collections of requests may be grouped
-together, denoting \textit{mutual} requests that represent demand for some
-common purpose. For example, a reactor may request UOX and MOX fuel mutually,
-indicating that either will satisfy its demand for fuel. Suppliers then respond
-to the series of requests with a \textit{bid}. A bid supplies a notion of the
-quantity and quality of a resource to match a request. Suppliers may add an
-arbitrary number of constraints to accompany bids. For example, an enriched UOX
-supplier may supply both a natural Uranium and SWU constraint. Any potential
-resource transfer may be denoted as \textit{exclusive}. An exclusive transfer
-must either be met fully or not at all in order to support concepts such as the
-trading of individual reactor assemblies. Finally, requesting facilities,
-institutions and regions may apply \textit{preferences} to each potential
-request-bid pairing based on the proposed resource transfer. Therefore, an
-institution can apply a higher preference to a partner to which it is congenial;
-similarly, a region may negate any transfers of material which have a higher
-Uranium enrichment than is allowable.
+The \gls{DRE} consists of three steps: supply-demand information
+gathering, resource exchange solution, and trade execution. Importantly, each
+step is agnostic with respect to the exchange of resources in question, i.e.,
+the same procedure is used for both Materials and Products.
 
-The \gls{DRE} may be solved either optimally by a mathematical program or
-approximately by a simulation-based heuristic \TODO{cite}. If any trade is
-denoted as exclusive, e.g., if an analyst desires an assembly-fidelity model,
-then either a heuristic must be used or exchanges must be represented as a
-\gls{MILP}. If no exclusive trades exist, a \gls{LP} model may be used. In
-practice, LPs solve much faster than \gls{MILP}s. However, the capability to
-model both exists in \Cyclus in order to provide users with the desired level of
-fidelity.
+The information-gathering step begins by polling potential consumers. Agents
+denote both the quantity of a commodity they need to consume as well as the
+target isotopics, or quality, by posting their demand to the market exchange as
+a series of \textit{requests}. An optional collection of demand constraints are
+associated with each collection of requests. Collections of requests may be
+grouped together, denoting \textit{mutual} requests that represent demand for
+some common purpose. For example, a reactor may request UOX and MOX fuel
+mutually, indicating that either will satisfy its demand for fuel.
+
+Suppliers then respond to the series of requests with a \textit{bid}. A bid
+supplies a notion of the quantity and quality of a resource to match a
+request. Suppliers may add an arbitrary number of constraints to accompany
+bids. For example, an enriched UOX supplier may supply both a natural Uranium
+and SWU constraint. Any potential resource transfer may be denoted as
+\textit{exclusive}. An exclusive transfer must either be met fully or not at all
+in order to support concepts such as the trading of individual reactor
+assemblies.
+
+Finally, requesting facilities, institutions and regions may apply
+\textit{preferences} to each potential request-bid pairing based on the proposed
+resource transfer. Therefore, an institution can apply a higher preference to a
+partner to which it is congenial; similarly, a region may negate any transfers
+of material which have a higher Uranium enrichment than is allowable.
+
+Given a full definition of supply and demand, the \gls{DRE} may be solved either
+optimally using a mathematical program or approximately by a simulation-based
+heuristic \cite{Gidden2014}. If any trade is denoted as exclusive, e.g., if an
+analyst desires an assembly-fidelity model, then either a heuristic must be used
+or exchanges must be represented as a \gls{MILP}. If no exclusive trades exist,
+a \gls{LP} model may be used. In practice, LPs solve much faster than
+\gls{MILP}s. However, the capability to model both exists in \Cyclus in order to
+provide users with the desired level of fidelity.
 

### 2015-02-15 fundamentals/impl.tex

@@
 
-Trades are initiated by the \Cyclus kernel after a solution to the \gls{DRE} is
-found. The \gls{DRE} is executed at each time step. Therefore, if a facility's
-request for a resource is not met at a given time step, it may offer a request
-in the proceeding time step.
+Trades between agents are initiated by the \Cyclus kernel after a solution to
+the \gls{DRE} is found. For each trade, the supplying agent is notified of its
+matched request and provides an associated resource to the exchange. All
+supplied resources are then sent to the corresponding requesting agents.
+
+In \Cyclus, the \gls{DRE} is executed at each time step. Therefore, if a
+facility's request for a resource is not met at a given time step, it may offer
+a request in the proceeding time step. Because agent behavior may change
+arbitrarily, the exchange executed at any given time step may be unique in a
+simulation.
+
+The \gls{DRE} is a novel simulation concept in the nuclear fuel cycle domain. It
+provides a flexible supply-demand infrastructure, supporting dynamic flows of
+resources between agents. Trading between agents can be affected by both the
+proposed quality of a resource and agent relationships through the use of
+cardinal preferences. Accordingly, a wide range of possible effects can be
+modeled, from capacitated fuel supply to international trade agreements.
 

### 2015-02-18 fundamentals/intro.tex
typo in intro

@@
 As nuclear power expands, technical, economic, political, and environmental
-analyses of nuclear fuel cycles by simulators increases in importance. NucleThe
-merit of advanced nuclear technologies and the fuel cycles they comprise is
+analyses of nuclear fuel cycles by simulators increases in importance. The
+merits of advanced nuclear technologies and fuel cycles are
 shaped by myriad physical, nuclear, chemical, industrial, and political
@@
 \gls{DYMOND}\cite{yacout_modeling_2005}, and
-\gls{NFCSim}\cite{schneider_nfcsim:_2005}.
+\gls{NFCSim}\cite{schneider_nfcsim:_2005,allan_guidance_2008}.
 Internationally, other laboratories have created their own as well, such as
@@
 developing tools of their own from scratch and tailored to their own needs.
+Examples include \gls{CAFCA}\cite{guerin_benchmark_2009} and
+\gls{DESAE}\cite{andrianova_desae_2008,mccarthy_benchmark_2012,allan_guidance_2008}.
 

### 2015-02-18 fundamentals/intro.tex
typo in intro
fixing intro stuff

@@
 As nuclear power expands, technical, economic, political, and environmental
-analyses of nuclear fuel cycles by simulators increases in importance. The
+analyses of nuclear fuel cycles by simulators increase in importance. The
 merits of advanced nuclear technologies and fuel cycles are
@@
 over-specialize, rendering most tools applicable to only a subset of desired
-simulation fidelities, scales, and applications.  The \Cyclus nuclear fuel
-cycle simulator framework and its modeling ecosystem incorporate modern
-insights from simulation science and software architecture to solve these
-problems.  These modern methods simultaneously enable more efficient, accurate,
-robust, and validated analysis.
+simulation fidelities, scales, and applications.
 
-The \Cyclus next-generation fuel cycle simulator is the result of design
-choices made to:
+The \Cyclus nuclear fuel cycle simulator framework and its modeling ecosystem
+incorporate modern insights from simulation science and software architecture
+to solve these problems.  These modern methods simultaneously enable more
+efficient, accurate, robust, and validated analysis.  This next-generation fuel
+cycle simulator is the result of design choices made to:
+
 \begin{itemize}
@@
 The cardinal purpose of a nuclear fuel cycle simulator is to calculate the
-time- and facility-dependent mass flow through all or part the fuel cycle. Many
-architecture choices are discussed in \ref{sec:litrev}.  Historically, nuclear
-fuel cycle simulators have calculated fuel cycle mass balances and performance
-metrics derived from them using software ranging from ad hoc spreadsheet-driven
-flow calculators to highly specialized system dynamics modeling platforms. To
-date, current tools are often static rather than dynamic, rigid rather than
-flexible, fleet-based rather than discrete, or privately distributed rather
-than open source. Each of these choices presents a challenge to modeling
-fidelity, generality, efficiency, robustness, and scientific transparency.
+time- and facility-dependent mass flow through all or part the fuel cycle.
+Historically, nuclear fuel cycle simulators have calculated fuel cycle mass
+balances and performance metrics derived from them using software ranging from
+ad hoc spreadsheet-driven flow calculators to highly specialized system
+dynamics modeling platforms. To date, current tools are often static rather
+than dynamic, rigid rather than flexible, fleet-based rather than discrete, or
+privately distributed rather than open source. Each of these choices presents a
+challenge to modeling fidelity, generality, efficiency, robustness, and
+scientific transparency.
 

### 2015-02-18 fundamentals/examples.tex
spell check and trailing whitespaces

@@
         \cite{baker_comparison_1963}.  This technique has also been used in the
-        Commelini-Sicart (COSI) fuel cycle simulator developed by the French
-        Commissariat \`{a} l'\'{e}nergie atomique (CEA).
+        \gls{COSI} fuel cycle simulator developed by the French \gls{CEA}.
 
@@
     \item \textbf{UOX Fabrication} (\Class{cycamore::Source}): This facility
-        provides enriched UOX fuel as requested.  This facility has infinite
+        provides enriched \gls{UOX} fuel as requested.  This facility has infinite
         production capacity.
@@
 each of the facilities.  The reactor was configured to request recycled MOX
-fuel with a higher preference then new UOX fuel. For the once through case,
+fuel with a higher preference then new \gls{UOX} fuel. For the once through case,
 the \Class{Reactor} was set to offer all spent fuel as waste.  For the 1-pass
-recycle case, the \Class{Reactor} offered spent UOX into a spent fuel market,
+recycle case, the \Class{Reactor} offered spent \gls{UOX into a spent fuel market,
 but spent MOX is still offered as waste.  In the infinite-pass recycle case,
@@
 through case, the recycling loop never acquires material, and so reactors
-always receive fresh UOX fuel.  The \gls{DRE} ensures everything operates
+always receive fresh \gls{UOX} fuel.  The \gls{DRE} ensures everything operates
 smoothly in all cases.

### 2015-02-18 fundamentals/fcsreqs.tex
spell check and trailing whitespaces

@@
 the case of the MIT \gls{CAFCA} software, the source code is unrestricted, the
-platform on which it relies is oftenrestricted or commercial.  However, \Cyclus
+platform on which it relies is often restricted or commercial.  However, \Cyclus
 provide fully free and open access to all users
@@
 In addition to being inaccessible, the vast majority of fuel cycle simulators
-are, effectively, inextensible. Typical fuel cycle simulator evelopment teams are insular, in
-part due to accessiblity issues. Also, however, their frameworks contain
+are, effectively, inextensible. Typical fuel cycle simulator development teams are insular, in
+part due to accessibility issues. Also, however, their frameworks contain
 heuristics and assumptions that constrain developer additions.

### 2015-02-18 fundamentals/impl.tex
spell check and trailing whitespaces

@@
 cycle. Any \gls{UQ} results are applicable only to the scenario that is under
-analysis by the user. \Cyclus is not a panacea for due dillegence on behalf of the fuel 
+analysis by the user. \Cyclus is not a panacea for due diligence on behalf of the fuel
 cycle modeler. Thus, \gls{UQ} is envisioned to be beyond the scope of core development
@@
 it is proposed. Such tests are run on all officially supported platforms.
-\Cyclus uses a \gls{CI} platform called Polyphemus \cite{scopatz_polyphemus_2014}. Polyphemus serves as an intermediary between GitHub pull requests on the frontend 
-and temporary \Cyclus servers on the backend. These servers are hosted by 
+\Cyclus uses a \gls{CI} platform called Polyphemus
+\cite{scopatz_polyphemus_2014}. Polyphemus serves as an intermediary between GitHub pull requests on the front-end
+and temporary \Cyclus servers on the back-end. These servers are hosted by
 the Build \& Test Laboratory (BaTLab) \cite{uw_batlab_team_batlab_2014} at the University of

### 2015-02-18 fundamentals/intro.tex
spell check and trailing whitespaces

@@
 fuel cycle systems studies identified over two dozen unique quantitative
-metrics spanning economics and cost, environmental stainability and waste
+metrics spanning economics and cost, environmental sustainability and waste
 management impacts, safety, security and nonproliferation, resource adequacy
@@
 Furthermore, modeling the evolution of a physics-dependent, international
-nuclear fuel supply chain is a multiscale problem which existing tools cannot
+nuclear fuel supply chain is a multi-scale problem which existing tools cannot
 support. They have either focused on macro effects, e.g., the fleet-level

### 2015-02-18 fundamentals/conclusion.tex
tiny changes
spell check and trailing whitespaces
the word code is not appropriate when we mean software or simulator. that is, it doesn't make the best noun.

@@
 The \Cyclus nuclear fuel cycle framework presents a more generic and flexible
-alternative to existing fuel cycle simulators.
-
-Where previous nuclear fuel cycle simulators have had limited distribution, 
+alternative to existing fuel cycle simulators. Where previous nuclear fuel cycle simulators have had limited distribution,
 uncertain provenance, and restricted customizability, \Cyclus emphasizes an
@@
 
-The object-oriented \acrlong{ABM} simulation paradigm ensures more generic 
+The object-oriented \gls{ABM} simulation paradigm ensures more generic
 simulation capability. It allows \Cyclus to address common analyses in a more
 flexible fashion and enables analyses that are impossible with system dynamics
-codes.
+simulators.
 

### 2015-02-18 fundamentals/fcsreqs.tex
the word code is not appropriate when we mean software or simulator. that is, it doesn't make the best noun.

@@
 The proprietary concerns of research institutions and security constraints of
-data within fuel cycle codes often restrict code access. A code's use is
+data within fuel cycle simulators often restrict access. Use of a simulator is
 therefore often limited to its institution of origin, necessitating effort
@@
 resources. License agreements and institutional approval are required for most
-current codes (i.e. \gls{COSI}6, \gls{DANESS}, \gls{DESAE}, EVOLCODE,
+current simulators (i.e. \gls{COSI}6, \gls{DANESS}, \gls{DESAE}, EVOLCODE,
 FAMILY21, \gls{NFCSim})\cite{juchau_modeling_2010}, ORION, and VISION.  Even when, as in
@@
 platform on which it relies is often restricted or commercial.  However, \Cyclus
-provide fully free and open access to all users
+provides fully free and open access to all users
 and developers, foreign and domestic.

### 2015-02-18 fundamentals/impl.tex
the word code is not appropriate when we mean software or simulator. that is, it doesn't make the best noun.

@@
 mend-and-extend paradigm, common in modern software development, reduces
-maintenance overhead and improves code robustness by protecting the core logic
+maintenance overhead and improves software robustness by protecting the core logic
 from changes in the extensions.
@@
 loadable libraries are the primary mechanism for extending \Cyclus' capability.
-This approach provides encapsulation: the core of the code operates
+This approach provides encapsulation: the core framework operates
 independently from the individual plug-in libraries. Thus, any customization or
@@
 
-Nuclear engineering code quality is often governed by \gls{NQA1}, an
+Nuclear engineering software quality is often governed by \gls{NQA1}, an
 \gls{ASME} specification
@@
 Quality assurance is an on-going process throughout the
-entire life of the code. As a simulator where most modeling decisions are made
+entire life of the software. As a simulator where most modeling decisions are made
 by third party archetype developers or users, the most important feature of
@@
 software should be doing occurs when the author explicitly states the
-goals of an \gls{API} in prose form. Future development of the code is then able to
-compare the implementation versus the documentation to discern whether or not they
-are in agreement. Documentation is thus a secondary higher-level information
+goals of an \gls{API} in prose form. Future developers are then able to
+compare the implementation versus the documentation to discern whether or not
+these are in agreement. Documentation is thus a secondary higher-level information
 stream.  In \Cyclus, this information is aggregated together into static
@@
 
-Version control is the history-preserving mechanism by which the provenance of
-a code is recorded. \Cyclus uses a well-established tool called git
+Version control preserves the development history, or \emph{provenance}, of
+source code files. \Cyclus uses a well-established tool called git
 \cite{software_freedom_conservancy_git_2014}
@@
 term for the collection of all possible histories).
-Though there are many praises and criticisms of git, one
-feature that the tool performs exceptionally well is the notion of code branches.
-These are distinct pathways in the history that branch out of a mainline source
+One feature that git performs exceptionally well is \emph{branching}.
+Branches are distinct pathways in the history that diverge from a mainline source
 tree and then may be \emph{merged} back into the mainline. Multiple simultaneous
@@
 \caption{A version-control enabled process for finding, reporting, and fixing a bug
-can take place within an issue tracker alongside multiple stages of code
+can take place within an issue tracker alongside multiple stages of software
 testing and review. In the \Cyclus case, the final review stage includes unit,

### 2015-02-18 fundamentals/intro.tex
the word code is not appropriate when we mean software or simulator. that is, it doesn't make the best noun.

@@
 \cite{macal_agent-based_2010}. Finally, openness allows cross-institutional
-collaboration, increases code robustness \cite{cohen_modern_2010}, and
+collaboration, increases software robustness \cite{cohen_modern_2010}, and
 cultivates an ecosystem of modeling and calculation options.  Comprising
@@
 material isotopics or the effects of isotopics on technology performance are
-neglected.  The \gls{CAFCA}\cite{guerin_impact_2009} code is problem-oriented
+neglected.  The \gls{CAFCA}\cite{guerin_impact_2009} simulator is problem-oriented
 in this way.
@@
 Based on lessons learned from Version 1, the \acrshort{GENIUSv2} Version
-2\cite{oliver_studying_2009,huff_geniusv2_2009} code sought to provide more
+2\cite{oliver_studying_2009,huff_geniusv2_2009} simulator sought to provide more
 generality and an extensible interface to facilitate collaboration.  The

### 2015-02-18 fundamentals/acros.tex
minor revisions
fixing spelling error and double CI definition in acros.tex
adding DRE acronym
lcoe should not be repeated
fixin some bib issues
the genius acronym should just encapsulate the acronym.

@@
 \newacronym{DOE}{DOE}{Department of Energy}
-\newacronym{GENIUSv1}{GENIUS}{Global Evaluation of Nuclear Infrastructure 
-Utilization Scenarios, Version 1}
-\newacronym{GENIUSv2}{GENIUS}{Global Evaluation of Nuclear Infrastructure Utilization Scenarios, Version 2}
+\newacronym{GENIUS}{GENIUS}{Global Evaluation of Nuclear Infrastructure Utilization Scenarios}
+\newacronym{GENIUSv1}{GENIUSv1}{Global Evaluation of Nuclear Infrastructure Utilization Scenarios, Version 1}
+\newacronym{GENIUSv2}{GENIUSv2}{Global Evaluation of Nuclear Infrastructure Utilization Scenarios, Version 2}
 \newacronym{CNERG}{CNERG}{Computational Nuclear Engineering Research Group}
@@
 \newacronym{CAFCA}{CAFCA}{ Code for Advanced Fuel Cycles Assessment }
-\newacronym{ORION}{ORION}{O..}
+\newacronym{ORION}{ORION}{ORION}
 \newacronym{NFCSim}{NFCSim}{Nuclear Fuel Cycle Simulator}
@@
 \newacronym{DAG}{DAG}{Directed Acyclic Graph}
+\newacronym{MOX}{MOX}{Mixed Oxide}
+\newacronym{UOX}{UOX}{Uranium Oxide}
 \newacronym{QA}{QA}{Quality Assurance}
@@
 \newacronym{CI}{CI}{Continuous Integration}
+\newacronym{DRE}{DRE}{Dynamic Resource Exchange}
+\newacronym{DESAE}{DESAE}{Dynamic Analysis of Nuclear Energy Systems Strategies}
+\newacronym{MILP}{MILP}{Mixed-Integer Linear Program}
+\newacronym{LP}{LP}{Linear Program}
 %\newacronym{<++>}{<++>}{<++>}

### 2015-02-18 fundamentals/intro.tex
the genius acronym should just encapsulate the acronym.

@@
 precursor,
-\gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006},
+\gls{GENIUS} Version 1 \cite{dunzik-gougar_global_2007,jain_transitioning_2006},
 originated within \gls{INL} and sought to provide generic regional capability.
-Based on lessons learned from Version 1, the \acrshort{GENIUSv2} Version
-2\cite{oliver_studying_2009,huff_geniusv2_2009} simulator sought to provide more
+Based on lessons learned from \gls{GENIUS} Version 1, the \gls{GENIUS} Version
+2 \cite{oliver_studying_2009,huff_geniusv2_2009} simulator sought to provide more
 generality and an extensible interface to facilitate collaboration.  The
-\Cyclus project then improved upon the \acrshort{GENIUSv2} effort by
+\Cyclus project then improved upon the \gls{GENIUS} effort by
 implementing increased modularity and encapsulation.  The result is a dynamic
@@
 architecture that permits multiple and variable levels of fidelity. The
-simulator's agent-based framework for tracking the transformation and trade of
+simulator's agent-based framework for tracking the transformation and tradef
 resources between autonomous regional and institutional entities with

### 2015-02-18 fundamentals/examples.tex
using the glossary

@@
     \item Once through (no recycle)
-    \item 1-pass MOX recycle
-    \item Infinite-pass MOX recycle
+    \item 1-pass \gls{MOX} recycle
+    \item Infinite-pass \gls{MOX} recycle
 \end{enumerate}
@@
         cycle with a 2 month refuel time.  The reactor was also configured to
-        take in either enriched UOX fuel or recycled MOX fuel.
+        take in either enriched \gls{UOX} fuel or recycled \gls{MOX} fuel.
 
@@
         facility requests depleted uranium and separated fissile material and
-        mixes them together into recycled MOX fuel that it offers to
+        mixes them together into recycled \gls{MOX} fuel that it offers to
         requesters.  The two streams are mixed in a ratio in order to match
@@
 done by making simple adjustments to the commodities and trade preferences for
-each of the facilities.  The reactor was configured to request recycled MOX
+each of the facilities.  The reactor was configured to request recycled \gls{MOX}
 fuel with a higher preference then new \gls{UOX} fuel. For the once through case,
 the \Class{Reactor} was set to offer all spent fuel as waste.  For the 1-pass
-recycle case, the \Class{Reactor} offered spent \gls{UOX into a spent fuel market,
-but spent MOX is still offered as waste.  In the infinite-pass recycle case,
+recycle case, the \Class{Reactor} offered spent \gls{UOX} into a spent fuel market,
+but spent \gls{MOX} is still offered as waste.  In the infinite-pass recycle case,
 the \Class{Reactor} offers all burned fuel into a spent fuel market. The

### 2015-02-18 fundamentals/impl.tex
using the glossary

@@
 grouped together, denoting \textit{mutual} requests that represent demand for
-some common purpose. For example, a reactor may request UOX and MOX fuel
+some common purpose. For example, a reactor may request \gls{UOX} and \gls{MOX} fuel
 mutually, indicating that either will satisfy its demand for fuel.
@@
 request. Suppliers may add an arbitrary number of constraints to accompany
-bids. For example, an enriched UOX supplier may supply both a natural Uranium
+bids. For example, an enriched \gls{UOX} supplier may supply both a natural Uranium
 and SWU constraint. Any potential resource transfer may be denoted as

### 2015-02-19 fundamentals/fcsreqs.tex
the genius acronym should just encapsulate the acronym.
cleanup, fcsreqs

@@
 \cite{andrianova_desae_2008}, FAMILY21\cite{mccarthy_benchmark_2012},
-\gls{GENIUSv1}, \gls{GENIUSv2}, and \gls{NFCSim} also possess the ability to
+\gls{GENIUS} version 1, \gls{GENIUS} version 2, and \gls{NFCSim} also possess the ability to
 model discrete materials.
@@
 all handle disruption in the same manner. \gls{DESAE}, for example, does not
-allow shutdown due to insufficient feedstock, though \Cyclus does. In the event
+allow shutdown due to insufficient feedstock. In the event
 of insufficient fissile material during reprocessing, \gls{DESAE} borrows
 material from storage, leaving a negative value \cite{mccarthy_benchmark_2012}.
+The \Cyclus framework does not dictate such heuristics. Rather, it provides a
+flexible framework on which either method is possible.
 
@@
 are, effectively, inextensible. Typical fuel cycle simulator development teams are insular, in
-part due to accessibility issues. Also, however, their frameworks contain
-heuristics and assumptions that constrain developer additions.
+part due to aforementioned accessibility issues. Accordingly, their frameworks
+typically contain heuristics and assumptions that constrain developer additions.
 
-For example, where most other simulators describe a finite set of acceptable
-cycle constructions (once through, single-pass, multi-pass), the \Cyclus
-simulation logic relies on a market paradigm that can be easily directed to
-create novel material and economic paths. The simulation of the dynamic
-responses within the system to pricing, availability, and other institutional
-preferences in \Cyclus is an advanced capability and does not exist in a
-flexible manner for other fuel cycle simulators.
+For example, most current simulators describe a finite set of acceptable
+cycle constructions (once through, single-pass, multi-pass). That limits the
+capability to create novel material flows and economic scenarios. The \Cyclus
+simulation logic relies on a market paradigm, parameterized by the user, which
+flexibly simulates dynamic responses to pricing, availability, and other
+institutional preferences. This is an advanced level of flexibility that does
+not exist in other fuel cycle simulators.

### 2015-02-19 fundamentals/impl.tex
cleanup, fcsreqs

@@
 
-Although some questions require resolution at the level of
-individual facilities and materials,
 Fleet-based, lumped-material models do not distinguish between discrete
-facility entities or materials.  As a result, many detailed performance
-metrics cannot be captured with previously existing tools.
-The generality of \Cyclus therefore enables many use cases
-that cannot be achieved with fleet-based models.
+facility entities or materials. However, some questions require resolution at the level of
+individual facilities and materials.
+As a result, many detailed performance
+metrics cannot be captured with previously existing fleet-based models.
 
@@
 customization provided by the discrete, modular, agent-based architecture of \Cyclus.
-
-\TODO{AO Opinion: Move some of the detail from this intro to the main section
-on discrete materials. Then add an intro to the discrete time/DRE as well.}
 

### 2015-02-19 fundamentals/intro.tex
cleanup, fcsreqs

@@
 
+The cardinal purpose of a nuclear fuel cycle simulator is to calculate the
+time- and facility-dependent mass flow through all or part the fuel cycle.
+Historically, nuclear fuel cycle simulators have calculated fuel cycle mass
+balances and performance metrics derived from them using software ranging from
+ad hoc spreadsheet-driven flow calculators to highly specialized system
+dynamics modeling platforms. To date, current tools are often static rather
+than dynamic, rigid rather than flexible, fleet-based rather than discrete, or
+privately distributed rather than open source. Each of these choices presents a
+challenge to modeling fidelity, generality, efficiency, robustness, and
+scientific transparency.
+
 The \Cyclus nuclear fuel cycle simulator framework and its modeling ecosystem
@@
 
-The cardinal purpose of a nuclear fuel cycle simulator is to calculate the
-time- and facility-dependent mass flow through all or part the fuel cycle.
-Historically, nuclear fuel cycle simulators have calculated fuel cycle mass
-balances and performance metrics derived from them using software ranging from
-ad hoc spreadsheet-driven flow calculators to highly specialized system
-dynamics modeling platforms. To date, current tools are often static rather
-than dynamic, rigid rather than flexible, fleet-based rather than discrete, or
-privately distributed rather than open source. Each of these choices presents a
-challenge to modeling fidelity, generality, efficiency, robustness, and
-scientific transparency.
-
 \Cyclus, therefore, is a dynamic, agent-based model, which employs a modular
@@
 collaboration, increases software robustness \cite{cohen_modern_2010}, and
-cultivates an ecosystem of modeling and calculation options.  Comprising
+cultivates an ecosystem of modeling and calculation options. Comprised of
 flexible, interchangeable models of fuel cycle components with varying scope,
@@
 the \Cyclus nuclear fuel cycle simulator capture these modern insights so that
-challenges in nuclear fuel cycle analysis can be better addressed.
+novel challenges in nuclear fuel cycle analysis can be better addressed.
 
@@
 others. For example, a simulator created for policy modeling might have
-excellent capability in economics while models affecting transformations in
-material isotopics or the effects of isotopics on technology performance are
+excellent capability in economics while capabailities for tracking transformations in
+material isotopics and the effects of isotopics on technology performance are
 neglected.  The \gls{CAFCA}\cite{guerin_impact_2009} simulator is problem-oriented
-in this way.
+in this way, having elected to neglect isotopic resolution in favor of
+integral effects.
 

### 2015-02-19 fundamentals/intro.tex
moved fcsreqs stuff out of the intro

@@
 
-\input{fcsreqs}
-
 \subsection{Motivation}
@@
 The \Cyclus paradigm enables targeted contribution and collaboration within the
-nuclear fuel cycle analysis community. This essential capability, absent in
+nuclear fuel cycle analysis community. This essential capability is absent in
 previous simulators where user customization and extensibility were not design
-objectives, comes about through the \emph{modular and open architecture} of
+objectives, and was attained by the \emph{modular and open architecture} of
 \Cyclus.  Additionally, \Cyclus facilitates direct comparison of modeling
@@
 
-Furthermore, modeling the evolution of a physics-dependent, international
+Ultimately, modeling the evolution of a physics-dependent, international
 nuclear fuel supply chain is a multi-scale problem which existing tools cannot
@@
 specialized tools, rendering the task of answering questions between the macro
-and micro levels challenging within a single tool.  In contrast, the extensible
+and micro levels challenging within a single tool.  In contrast, the open, extensible
 architecture and discrete object tracking of \Cyclus allow the creation and
-interchangeability of custom archetypes at any level of fidelity.
+interchangeability of custom archetypes at any level of fidelity and by any
+fuel cycle analyst.
+
+\input{fcsreqs}

### 2015-02-19 fundamentals/impl.tex
cleanup

@@
 
-A modular, agent-based approach is ideal for solving complex, coupled,
+A modular, \acrfull{ABM} approach is ideal for solving complex, coupled,
 physics-dependent supply chain problems involving material routing, facility
@@
 describing the general design features that make \Cyclus both flexible and powerful:
-cluster-ready software and dynamic libraries.  Next, the framework using an
-\gls{ABM} paradigm, which provides an expansion in performance beyond typical systems dynamics
+cluster-ready software and dynamic libraries.  Next, the framework has an
+\gls{ABM} paradigm, which provides an expansion in performance beyond typical system dynamics
 capabilities, is described, focusing on agent interchangeability and the

### 2015-02-20 fundamentals/impl.tex
simplifying language in implementation

@@
 However, many fuel cycle simulators rely on \gls{COTS} and Windows-only software that limits
-performance on and compatibility with resource computing infrastructures. This limitation severely
-limits the possible scope of simulations and increases the wall-clock time necessary to conduct parameterized sensitivity
+performance on and compatibility with resource computing infrastructures. This
+severely constrains the possible scope of simulations and increases the wall-clock time necessary to conduct parameterized sensitivity
 analyses and other multi-simulation studies. \Cyclus, on the other hand, is
@@
 With \Cyclus, a researcher can focus on generating an archetype model within their
-sphere of expertise, while relying on the contributions of others to fill
+sphere of expertise while relying on the contributions of others to fill
 in the other technologies in the simulation.
@@
 \Cyclus acheives this behavior by implementing its generic \gls{API} and
-modular architecture via a suite of dynamically loadable plug-in libraries.
+modular architecture via a suite of dynamically loadable plug-in libraries, as
+pictured in Figure \ref{fig:framework}.
 Though common in modern software architecture, such a plug-in pattern has not
-previously been implemented in nuclear fuel cycle simulators.  Dynamically
+previously been implemented in a nuclear fuel cycle simulator. Dynamically
 loadable libraries are the primary mechanism for extending \Cyclus' capability.
@@
 \begin{center}
-\includegraphics{./images/modifiedopen.eps}
+\includegraphics[width=\textwidth]{./images/framework}
 \end{center}
-\caption{The \Cyclus framework enables fully open, partially open, and fully
-closed collaborations\cite{carlsen_cyclus_2014}.}
-\label{fig:modifiedopen}
+\caption{The \Cyclus core provides \gls{API}s that abstract away the details in
+the kernel and allow the archetypes to be loaded into the simulation in a modular
+fashion.}
+\label{fig:framework}
 \end{figure}
@@
 
+\begin{figure}[htbp!]
+\begin{center}
+\includegraphics{./images/modifiedopen.eps}
+\end{center}
+\caption{The \Cyclus framework enables fully open, partially open, and fully
+closed collaborations\cite{carlsen_cyclus_2014}.}
+\label{fig:modifiedopen}
+\end{figure}
+
 This last benefit of dynamically loadable libraries addresses
@@
 questions as well as users focused on more detailed, technical
-analyses. They merely choose their preferred level of fidelity from the
-available libraries.
+analyses. They merely choose their preferred level of fidelity from among the
+available libraries in the ecosystem.
 
@@
 perspective from which to model a given problem. In the nuclear fuel cycle
-context, for example, an analyst can design an agent with reactor-related logic
-that is entirely independent from an agent with fuel fabrication-related
-logic. Defining the behavior of both agents according to the
+context, for example, an analyst can design a reactor agent
+that is entirely independent from a fuel fabrication agent. Defining the behavior of both agents according to the
 \gls{API} contract is sufficient for them to interact with one another as
@@
 % (OO, cpp, xml, backends, inheritances, mixins, generic apis, etc.)
-
-\begin{figure}[htbp!]
-\begin{center}
-\includegraphics[width=\textwidth]{./images/framework}
-\end{center}
-\caption{The \Cyclus core provides \gls{API}s that abstract away the details in
-the kernel and allow the archetypes to be loaded into the simulation in a modular
-fashion.}
-\label{fig:framework}
-\end{figure}
 

### 2015-02-20 fundamentals/impl.tex
citing juchau

@@
 encompassing facilities, institutions managing those facilities, and regions. While
-some simulators \cite{andrianova_desae_2008} have provided a notion of static regional
-effects, \Cyclus allows for both regions and institutions to be first-class
+few simulators have provided any notion of static regional
+effects \cite{huff_next_2010,juchau_modeling_2010}, \Cyclus allows for both regions and institutions to be first-class
 actors in simulated fuel cycles. The fundamental interactions for each entity are implemented in a corresponding

### 2015-02-20 fundamentals/impl.tex
elements are common nouns

@@
 \subsection{Agent-based Paradigm}
+\label{sec:abm}
 % superior detail in capturing simulation dynamics
@@
 convention, institutions are mainly responsible for facility deployment, but
-all archetypes have access to the agent deployment mechanism.  It is easy
-to implement agents that deploy copies of themselves, or that schedule their
-own decommissioning.  Because regions, institutions, and facilities are all
-just agents, they can all be implemented to exercise the full set of features
-offered by the \Cyclus kernel.
+all archetypes have access to the agent deployment mechanism. \Cyclus enables
+the developer to to implement agents that deploy copies of themselves, or that
+schedule their own decommissioning.  Because regions, institutions, and
+facilities are all just agents, they can all be implemented to exercise the
+full set of features offered by the \Cyclus kernel.
 
@@
 
+\subsubsection{Resources and Materials}
+% Resources, Materials (note isotope tracking, decay behavior)
+
+For all of the reasons that the \gls{ABM} paradigm in \ref{sec:abm} enables
+novel simulations, multiple use cases require that these agents, such as the
+regions, institutions, and facilities in \Cyclus, must be represented as
+discrete objects. Furthermore, important use cases are enabled when materials
+and resources are tracked as discrete objects alongside those agents.
+
 One such use case seeks to capture system vulnerability to nefarious
@@
 information unit in such studies.
-Material risk analysis, therefore, demands discretely modeled objects like those
-in \Cyclus.
+Material risk analysis, therefore, demands that both facilities and materials
+should be discretely modeled objects like those in \Cyclus.
 
-There are a number of types of users and developers who will
-interact with \Cyclus. National laboratory researchers,
-academic researchers, private-industry economic forecasters, and even students
-in engineering courses may benefit from the ease of development and
-customization provided by the discrete, modular, agent-based architecture of \Cyclus.
-
-\subsubsection{Resources and Materials}
-% Resources, Materials (note isotope tracking, decay behavior)
-
-\TODO{add blurb about discrete agent/facility tracking.}
-
-In \Cyclus, agents can transfer discrete resource objects between each other.
+In \Cyclus, agents can transfer discrete resource objects among one another.
 Cyclus currently supports two types of resources:
@@
 not accumulate because the next time the material's decay function is invoked,
-the time change will be larger. \TODO{want more detail on this decay shortcut?}
-\TODO{describe decay algorithm and how it might be improved}.
+the time change will be larger.
 
@@
 object is only recorded in the database once, significant space savings also
-occurs. \TODO{do we want a diagram helping show this composition caching?}
+occurs.
+\TODO{do we want a diagram helping show this composition caching?}
 
@@
 
-The \gls{DRE} is the critical resource-related process on which \Cyclus
-simulations are built. It defines the resource interaction mechanisms and
-methodologies for all agents. As the \Cyclus supply-demand resolution framework,
+Since the \Cyclus simulation paradigm involves both discrete agents and
+discrete resources, the logic engine defining resource interaction mechanisms
+among agents is crucial. The \gls{DRE} is that critical logic engine on which \Cyclus
+simulations are built.
+As the \Cyclus supply-demand resolution framework,
 the DRE must be able to support arbitrary facilities. Supporting the general
@@
 The information-gathering step begins by polling potential consumers. Agents
-denote both the quantity of a commodity they need to consume as well as the
+define both the quantity of a commodity they need to consume as well as the
 target isotopics, or quality, by posting their demand to the market exchange as
-a series of \textit{requests}. An optional collection of demand constraints are
-associated with each collection of requests. Collections of requests may be
-grouped together, denoting \textit{mutual} requests that represent demand for
+a series of \textit{requests}. Users may optionally parameterize the agent to
+associate a collection of demand constraints with each collection of requests.
+Collections of requests may be grouped together, denoting \textit{mutual}
+requests that represent demand for
 some common purpose. For example, a reactor may request \gls{UOX} and \gls{MOX} fuel
@@
 request. Suppliers may add an arbitrary number of constraints to accompany
-bids. For example, an enriched \gls{UOX} supplier may supply both a natural Uranium
+bids. For example, an enriched \gls{UOX} supplier may supply both a natural uranium
 and SWU constraint. Any potential resource transfer may be denoted as
@@
 partner to which it is congenial; similarly, a region may negate any transfers
-of material which have a higher Uranium enrichment than is allowable.
+of material which have a higher uranium enrichment than is allowable.
 

### 2015-02-20 fundamentals/impl.tex
simpler words for simple minds (like katys).

@@
 a \gls{LP} model may be used. In practice, LPs solve much faster than
-\gls{MILP}s. However, the capability to model both exists in \Cyclus in order to
+\gls{MILP}s. However, both capabilities exist in \Cyclus in order to
 provide users with the desired level of fidelity.
@@
 proposed quality of a resource and agent relationships through the use of
-cardinal preferences. Accordingly, a wide range of possible effects can be
-modeled, from capacitated fuel supply to international trade agreements.
+preferences. Accordingly, a wide range of possible effects can be
+modeled, from capacitaty-limited fuel supply to international trade agreements.
 

### 2015-02-20 fundamentals/impl.tex
redundant sentence

@@
 \end{tabularx}
-\caption{The Archetypes in \Cycamore seek to cover a large range of simple simulation use cases.}
+\caption{The Archetypes in \Cycamore seek to cover a large range of simple simulation use cases \cite{carlsen_cycamore_2014}.}
 \label{tab:cycamore}
@@
 
-The current \Cycamore release provides only
-basic functionality, enabling simple fuel cycle analyses.
-As illustrated in Figure \ref{fig:simplesim}, \Cycamore provides the tools for users
-to get started quickly with simple
-once-through fuel cycle scenarios. As future contributions are vetted, the capabilities in \Cycamore may grow.
+The current \Cycamore release provide basic functionality, As illustrated in
+Figure \ref{fig:simplesim}, the current \Cycamore release provides basic
+functionality enabling simple fuel cycle analyses  As future contributions are
+vetted, the capabilities in \Cycamore may grow.
 

### 2015-02-20 fundamentals/impl.tex
list punctuation

@@
 the set of capabilities needed to implement an agent-based simulation
-with \gls{DRE} a toolkit is provided that assists developers
+with \gls{DRE}, a toolkit is provided that assists developers
 and users with related simulation and nuclear engineering tasks. The toolkit is
@@
 utility to the developer community, they will be considered for screening and
-adoption into the kernel as toolkit extensions. Likely extensions include:
+adoption into the kernel as toolkit extensions. Likely extensions include
 
 \begin{itemize}
-\item fuel cycle metrics calculators
-\item supportive data tables
-\item policy models
-\item economic models
+\item fuel cycle metrics calculators,
+\item supportive data tables,
+\item policy models,
+\item and economic models.
 \end{itemize}

### 2015-02-20 fundamentals/impl.tex
misisng .

@@
 Figure \ref{fig:simplesim}, the current \Cycamore release provides basic
-functionality enabling simple fuel cycle analyses  As future contributions are
+functionality enabling simple fuel cycle analyses. As future contributions are
 vetted, the capabilities in \Cycamore may grow.

### 2015-02-20 fundamentals/impl.tex
for example

@@
 the set of capabilities needed to implement an agent-based simulation
-with \gls{DRE}, a toolkit is provided that assists developers
+with \gls{DRE}, a toolkit is provided to assist developers
 and users with related simulation and nuclear engineering tasks. The toolkit is
@@
 A series of utility classes are provided to support demand-constrained agent
-facility deployment. Symbolic function representations of linear,
+facility deployment. For example, symbolic function representations of linear,
 exponential, and piecewise functions are supported via the

### 2015-02-20 fundamentals/impl.tex
more brevity

@@
 
-Simulation science - like experimental science - has since the beginning had the
-problem of identifying trustworthy results from nonsensical results or noise.
+Simulation science - like experimental science - must identify trustworthy
+results from nonsensical results or noise.
 Charles Babbage famously articulated this, ``On two occasions I have been asked,
@@
 of ideas that could provoke such a question.'' \cite{babbage_passages_2011}.
-A simulator must both guard against the \emph{garbage in, garbage out} phenomenon, and also assure correctness.
+A simulator must assure correctness and guard against the \emph{garbage
+in, garbage out} phenomenon.
 

### 2015-02-20 fundamentals/impl.tex
weird sentence pain
sentence getting more readable
simplicity is beauty

@@
 
-Simulation science - like experimental science - must identify trustworthy
-results from nonsensical results or noise.
+Simulation science - like experimental science - must distinguish trustworthy
+results from untrustworthy ones.
 Charles Babbage famously articulated this, ``On two occasions I have been asked,
@@
 Multiple strategies, collectively known as \emph{\gls{QA}}, have
-been invented over the years to mitigate the structural and algorithmic errors
-on the part of simulators themselves. These include \emph{\gls{VV}}
+been invented to mitigate the structural and algorithmic errors
+in software. These include \emph{\gls{VV}}
 \cite{boehm_software_1989}, \emph{\gls{UQ}}
@@
 
-Quality assurance is an on-going process throughout the
-entire life of the software. As a simulator where most modeling decisions are made
+Quality assurance is an on-going process throughout the entire life of the software. As a simulator where most modeling decisions are made
 by third party archetype developers or users, the most important feature of

### 2015-02-20 fundamentals/impl.tex
for brevity

@@
 Multiple strategies, collectively known as \emph{\gls{QA}}, have
-been invented to mitigate the structural and algorithmic errors
+been invented to mitigate structural and algorithmic errors
 in software. These include \emph{\gls{VV}}
 \cite{boehm_software_1989}, \emph{\gls{UQ}}
-\cite{sacks_design_1989}, testing, and others. \gls{VV} and \gls{UQ} come from
-a distinctly computational science background while testing \emph{et al.} come from software development.
+\cite{sacks_design_1989}, testing, and others.
 

### 2015-02-20 fundamentals/impl.tex
for brevity
nonsense sentence

@@
 whose latest revision appeared in 2009 \cite{asme_nqa-1a-2009_2009}.
-Although \gls{NQA1} is primarily
-used for designing reactors, it is general enough to apply to
-\Cyclus. \Cyclus has adopted an \emph{agile} development process
+\Cyclus has adopted an \emph{agile} development process
 \cite{larman_agile_2004},
 interpreting \gls{NQA1} in a manner similar to the process adopted by the
-\gls{DOE} within \gls{NEAMS} \cite{neams_nuclear_2013} or the
-PyNE toolkit \cite{biondo_quality_2014}.
+\gls{DOE} within \gls{NEAMS} \cite{neams_nuclear_2013} or by the PyNE toolkit
+\cite{biondo_quality_2014}.
 
-Quality assurance is an on-going process throughout the entire life of the software. As a simulator where most modeling decisions are made
+Quality assurance is an on-going process throughout the entire life of the
+software. Since \Cyclus modeling decisions are made
 by third party archetype developers or users, the most important feature of

### 2015-02-20 fundamentals/impl.tex
deleted confusing, out of place sentence
weird grammar

@@
 
-Quality assurance is an on-going process throughout the entire life of the
-software. Since \Cyclus modeling decisions are made
+Since \Cyclus modeling decisions are made
 by third party archetype developers or users, the most important feature of
@@
 Verification may be defined as the question, ``Is \Cyclus being built correctly?''
-To answer this question, we turn to the software development of notions of testing,
+To answer this question, \Cyclsu relies on software development best practices
+such as testing,
 documentation, version control, style guidelines, and continuous integration.

### 2015-02-20 fundamentals/impl.tex
another unnecessary sentence

@@
 Verification may be defined as the question, ``Is \Cyclus being built correctly?''
-To answer this question, \Cyclsu relies on software development best practices
+To answer this question, \Cyclus relies on software development best practices
 such as testing,
-documentation, version control, style guidelines, and continuous integration.
-This suite of process controls supplies mechanism for reliable and reproducible
-software. The impetus to implement these controls correctly is particularly strong in a scientific
-context because of the emphasis on reproducibility and provenance. These verification techniques are
+documentation, version control, style guidelines, and continuous integration to
+ensure reliability and reproducibility. These verification techniques are
 discussed individually in the sections that follow.

### 2015-02-20 fundamentals/impl.tex
cite ans paper
significant changes are good. regression tests warn against unexpected, usually backwards incompatible changes

@@
 optimally using a mathematical program or approximately by a simulation-based
-heuristic \cite{Gidden2014}. If any trade is denoted as exclusive, e.g., if an
+heuristic \cite{gidden_agent-based_2014}. If any trade is denoted as exclusive, e.g., if an
 analyst desires an assembly-fidelity model, then either a heuristic must be used
@@
 validation is not possible. Nonetheless, code-to-code comparisons with fuel cycle
-simulators that use other modeling paradigms are underway, if nascent. However, such
+simulators that use other modeling paradigms are underway
+\cite{huff_extensions_2014}. However, such
 exercises are more likely to bring into relief the differences between the modeling
@@
 to the running of many \Cyclus simulations. The kernel itself, as a generic fuel cycle
-simulator, cannot make reliable statements about the uncertainty of a particular fuel
+simulator, cannot make reliable statements about the uncertainty of metrics for a particular fuel
 cycle. Any \gls{UQ} results are applicable only to the scenario that is under
-analysis by the user. \Cyclus is not a panacea for due diligence on behalf of the fuel
+analysis by the user. \Cyclus is not a substitute for due diligence on behalf of the fuel
 cycle modeler. Thus, \gls{UQ} is envisioned to be beyond the scope of core development
@@
 tests. Sufficient unit tests are required for any proposed change to the \Cyclus
-code base. Currently \Cyclus implements over 450 unit tests and \Cycamore implements
-85.  These cover approximately 65\% of their respective code bases, and their numbers are expected to grow over time.
+code base. Currently, \Cyclus implements over 450 unit tests and \Cycamore implements
+85.  These cover approximately 65\% of their respective code bases, and these numbers are expected to grow over time.
 
@@
 
-Regression tests ensure significant changes do not
+Regression tests ensure unexpected backwards-incompatible changes do not
 occur over the course of \Cyclus development. Such a change is called a

### 2015-02-20 fundamentals/impl.tex
simplification

@@
 in \Cycamore because its archetypes are sophisticated enough
-to make interesting input files. Only a handful ($<10$) of time steps are needed
-for regression testing.
+to make interesting simulations.
 

### 2015-02-20 fundamentals/impl.tex
grammar and brevity

@@
 Version control preserves the development history, or \emph{provenance}, of
-source code files. \Cyclus uses a well-established tool called git
-\cite{software_freedom_conservancy_git_2014}
-for this purpose. Git is currently the most popular utility in the recent wave
-of \emph{distributed version control}. Briefly stated, this means that every
-user has a complete local copy of the \emph{repository} (the version control
+source code files. \Cyclus uses a well-established \emph{distributed version
+control} tool called git \cite{software_freedom_conservancy_git_2014} for this
+purpose.  Distributed version control allows every
+user to have complete local copy of the \emph{repository} (the version control
 term for the collection of all possible histories).

### 2015-02-20 fundamentals/impl.tex
missing of

@@
 Branches are distinct pathways in the history that diverge from a mainline source
-tree and then may be \emph{merged} back into the mainline. Multiple simultaneous
+tree and then may be \emph{merged} back in. Multiple simultaneous
 branches may exist at all points in time. Every change to the code is recorded
 in the history, along with metadata such as the author, a timestamp, and an
-accompanying message. Thus
+accompanying message. Thus,
 it is possible for \Cyclus to accurately replay the entirety of who did what to the
@@
 
-Since these steps are performed for all incoming code, it is easy for the
+Since these steps are performed for all incoming code, it is easyi for the
 \Cyclus core team to determine whether or not an individual pull request
@@
 but not sufficient addition to the \Cyclus \gls{QA}
-system: it keeps bad code out \Cyclus. However, \Cyclus will always
+system: it keeps bad code out of \Cyclus. However, \Cyclus will always
 require human eyes and hands to let good code in.

### 2015-02-20 fundamentals/examples.tex
missing of
nouns

@@
 ecosystem at multiple institutions indicates that a fuel cycle simulator can
-advance in a community-driven development paradigm. Additionally, simulation
+advance in this community-driven development paradigm. Additionally, simulation
 results for both once-through and more complex recycling scenarios demonstrate that
@@
 developer-contributed capabilities.  They add to the fundamental \Cycamore
-archetypes by providing physics-based reactors, separation, fabrication, storage
-facilities, and expanded institutional paradigms.
+archetypes by providing physics-based reactors, separations logic, fuel
+fabrication processing, storage facilities, and expanded institutional paradigms.
 
@@
 
-Cyclus' discrete materials make single-pass recycle easy to implement.  The
+Cyclus' discrete materials make single-pass recycle straightforward to implement.  The
 reactors keep track of fuel as discrete batches. A reactor remembers where it

### 2015-02-20 fundamentals/examples.tex
acks

@@
 nuclear fuel cycle simulator tools. These examples further show the flexibility
-provided by the material routing logic within the \Cyclus framework and provide
+provided by the \gls{DRE} logic within the \Cyclus framework and provide
 an example of the resolution made possible by discrete-facility and

### 2015-02-20 fundamentals/abs.tex
forgot abs

As nuclear power expands both domestically and internationally, nuclear fuel cycle
performance analysis on technical, economic, political, and environmental axes increases
in importance. Appropriate nuclear fuel cycle analysis requires calculation of myriad physical, nuclear,
chemical, industrial, and political phenomena. Nuclear fuel cycle simulators
therefore couple complex systems such as nuclear process physics,
facility deployment, and material routing. However, most nuclear fuel cycle
simulators have not incorporated modern insights in simulation science and
software architecture that can enable more efficient, accurate, robust, and
validated analysis.

An alternative to these approaches is a dynamic, agent-based simulator with an
open platform and an ecosystem of research-driven capabilities.  Modern
insight indicates that dynamic nuclear fuel cycle analysis more realistically
supports a broader range of simulation goals than static analysis
\cite{piet_dynamic_2011}. Similarly, experience in the broader field of systems
analysis indicates that agent-based modeling enables more flexible simulation
control, without loss of generality \cite{macal_agent-based_2010}. Finally, openness
allows cross-institutional collaboration, increases software robustness, and
enables the cultivation of an ecosystem of calculation options
\cite{softwarecarpentryresource}.  The fundamental concepts of the \Cyclus
nuclear fuel cycle simulator capture these modern insights so that challenges
in nuclear fuel cycle analysis can be better addressed. A summary of the
motivating use cases, an overview of the software architecture, and several
representative solutions built on the framework are presented.

### 2015-02-22 fundamentals/intro.tex
Fix a couple of typos

@@
 architecture that permits multiple and variable levels of fidelity. The
-simulator's agent-based framework for tracking the transformation and tradef
+simulator's agent-based framework for tracking the transformation and trade of
 resources between autonomous regional and institutional entities with
@@
 applicable to a broader range of fidelities, scales, and applications than
-other simulators.  due to the flexibility and generality of its
+other simulators, due to the flexibility and generality of its
 \emph{\gls{ABM}} paradigm and \emph{discrete, object-oriented approach}.

### 2015-02-22 fundamentals/fcsreqs.tex
Two small changes: * hedge on definition of not handling disruptions gracefully * criticize commercial platforms for being costly, rather than just commercial

@@
 discrete facilities \cite{huff_next_2010}.  Fleet-based models (i.e.
-\gls{VISION}) are unable to capture this gracefully.  All of the software
+\gls{VISION}) are unable to capture this gracefully, perhaps representing it as 
+a reduction in the capacity of the whole fleet.  All of the software
 capable of discrete materials have a notion of discrete facilities, however not
@@
 the case of the MIT \gls{CAFCA} software, the source code is unrestricted, the
-platform on which it relies is often restricted or commercial.  However, \Cyclus
+platform on which it relies is often restricted or costly.  However, \Cyclus
 provides fully free and open access to all users

### 2015-02-22 fundamentals/impl.tex
A variety of separate changes: * some typos, repeated phrases and grammar glitches * clarfiy inheritance for institutions wrt deploy/decommission * change framing of non-RIF operation - suggest footnote * strengthen language about the need for the DRE:     basically uncertainty in every angle: archetype defintion, agent entry/exit, resource quality * improve language connecting mathematical constraints to real-world constraints * introduce role of facilities in preference setting * small clarifications for integration and regression tests

--- 2015-02-20 fundamentals/impl.tex
@@
 describing the general design features that make \Cyclus both flexible and powerful:
-cluster-ready software and dynamic libraries.  Next, the framework has an
+cluster-ready software and dynamic libraries.  Next, the framework's
 \gls{ABM} paradigm, which provides an expansion in performance beyond typical system dynamics
@@
 responsible for deploying and decommissioning facilities. Accordingly, advanced
-logic regarding building and decommissioning can be obtained by inheriting
-those behaviors from the
+logic regarding building and decommissioning can be implemented on top of  
+those behaviors inherited from the
 \Class{Institution} interface. Second, the \Class{Facility} class implements the
@@
 
-Although concept of the \gls{RIF} hierarchy is provided explicitly, the \Cyclus kernel is
-designed to handle hierarchies of arbitrary depth.  It is capable of
+% the paragraph below muddies the concept of the RIF hierarchy
+% (perhaps an extended footnote?)
+% Either way, I prefer something other than ``provided explicitly''.
+
+Although the \Cyclus kernel is designed around the concept of the \gls{RIF} hierarchy, 
+it can handle hierarchies of arbitrary depth.  It is capable of
 running a simulation without regions and institutions (i.e.  only facilities)
@@
 target facility and the individual materials modified within it.
-Provenance and trade-history of distinct materials is the fundamental
-information unit in such studies.
 Material risk analysis, therefore, demands that both facilities and materials
@@
 
-\subsubsection{Dynamic Resource Exchange}
+% although this abbreviation is provided by the glossary capability, I think
+% the DRE is so important that it should be redefined here.
 
-Since the \Cyclus simulation paradigm involves both discrete agents and
-discrete resources, the logic engine defining resource interaction mechanisms
+\subsubsection{Dynamic Resource Exchange (DRE)}
+
+Since the \Cyclus simulation paradigm allows discrete agents, based on archetypes
+about which the kernel has no knowledge, to enter 
+the simulation at arbitrary times and
+trade in discrete resources that are not defined \textit{a priori}, 
+the logic engine defining resource interaction mechanisms
 among agents is crucial. The \gls{DRE} is that critical logic engine on which \Cyclus
@@
 request. Suppliers may add an arbitrary number of constraints to accompany
-bids. For example, an enriched \gls{UOX} supplier may supply both a natural uranium
-and SWU constraint. Any potential resource transfer may be denoted as
+bids. For example, an enriched \gls{UOX} supplier may be constrained by its current
+inventory of natural uranium or its total capacity to provide enrichment (SWUs), and
+attach such constraints to its bids. Any potential resource transfer may be denoted as
 \textit{exclusive}. An exclusive transfer must either be met fully or not at all
@@
 \textit{preferences} to each potential request-bid pairing based on the proposed
-resource transfer. Therefore, an institution can apply a higher preference to a
+resource transfer. Facilities can apply arbitrary complex logic to rank the bids 
+that they have received, whether based on the quantity available in each bid or
+on the quality of each bid, and the consequent implications of the physics behavior
+of that facility. In addition, an institution can apply a higher preference to a
 partner to which it is congenial; similarly, a region may negate any transfers
@@
 optimally using a mathematical program or approximately by a simulation-based
-heuristic \cite{gidden_agent-based_2014}. If any trade is denoted as exclusive, e.g., if an
+heuristic \cite{Gidden2014}. If any trade is denoted as exclusive, e.g., if an
 analyst desires an assembly-fidelity model, then either a heuristic must be used
@@
 provides a flexible supply-demand infrastructure, supporting dynamic flows of
-resources between agents. Trading between agents can be affected by both the
+resources between agents, even as those agents enter and leave the simulation, and 
+even when those agents are defined by archetypes of arbitrary complexity. Trading 
+between agents can be affected by both the
 proposed quality of a resource and agent relationships through the use of
@@
 
-The current \Cycamore release provide basic functionality, As illustrated in
+As illustrated in
 Figure \ref{fig:simplesim}, the current \Cycamore release provides basic
-functionality enabling simple fuel cycle analyses. As future contributions are
+functionality enabling simple fuel cycle analyses  As future contributions are
 vetted, the capabilities in \Cycamore may grow.
@@
 the set of capabilities needed to implement an agent-based simulation
-with \gls{DRE}, a toolkit is provided to assist developers
+with \gls{DRE}, a toolkit is provided that assists developers
 and users with related simulation and nuclear engineering tasks. The toolkit is
@@
 A series of utility classes are provided to support demand-constrained agent
-facility deployment. For example, symbolic function representations of linear,
+facility deployment. Symbolic function representations of linear,
 exponential, and piecewise functions are supported via the
@@
 
-Simulation science - like experimental science - must distinguish trustworthy
-results from untrustworthy ones.
+Simulation science - like experimental science - has since the beginning had the
+problem of identifying trustworthy results from nonsensical results or noise.
 Charles Babbage famously articulated this, ``On two occasions I have been asked,
@@
 of ideas that could provoke such a question.'' \cite{babbage_passages_2011}.
-A simulator must assure correctness and guard against the \emph{garbage
-in, garbage out} phenomenon.
+A simulator must both guard against the \emph{garbage in, garbage out} phenomenon, and also assure correctness.
 
 Multiple strategies, collectively known as \emph{\gls{QA}}, have
-been invented to mitigate structural and algorithmic errors
-in software. These include \emph{\gls{VV}}
+been invented over the years to mitigate the structural and algorithmic errors
+on the part of simulators themselves. These include \emph{\gls{VV}}
 \cite{boehm_software_1989}, \emph{\gls{UQ}}
-\cite{sacks_design_1989}, testing, and others.
+\cite{sacks_design_1989}, testing, and others. \gls{VV} and \gls{UQ} come from
+a distinctly computational science background while testing \emph{et al.} come from software development.
 
@@
 whose latest revision appeared in 2009 \cite{asme_nqa-1a-2009_2009}.
-\Cyclus has adopted an \emph{agile} development process
+Although \gls{NQA1} is primarily
+used for designing reactors, it is general enough to apply to
+\Cyclus. \Cyclus has adopted an \emph{agile} development process
 \cite{larman_agile_2004},
 interpreting \gls{NQA1} in a manner similar to the process adopted by the
-\gls{DOE} within \gls{NEAMS} \cite{neams_nuclear_2013} or by the PyNE toolkit
-\cite{biondo_quality_2014}.
+\gls{DOE} within \gls{NEAMS} \cite{neams_nuclear_2013} or the
+PyNE toolkit \cite{biondo_quality_2014}.
 
-Since \Cyclus modeling decisions are made
+Quality assurance is an on-going process throughout the
+entire life of the software. As a simulator where most modeling decisions are made
 by third party archetype developers or users, the most important feature of
@@
 Verification may be defined as the question, ``Is \Cyclus being built correctly?''
-To answer this question, \Cyclus relies on software development best practices
-such as testing,
-documentation, version control, style guidelines, and continuous integration to
-ensure reliability and reproducibility. These verification techniques are
+To answer this question, we turn to the software development of notions of testing,
+documentation, version control, style guidelines, and continuous integration.
+This suite of process controls supplies mechanism for reliable and reproducible
+software. The impetus to implement these controls correctly is particularly strong in a scientific
+context because of the emphasis on reproducibility and provenance. These verification techniques are
 discussed individually in the sections that follow.
@@
 validation is not possible. Nonetheless, code-to-code comparisons with fuel cycle
-simulators that use other modeling paradigms are underway
-\cite{huff_extensions_2014}. However, such
+simulators that use other modeling paradigms are underway, if nascent. However, such
 exercises are more likely to bring into relief the differences between the modeling
@@
 to the running of many \Cyclus simulations. The kernel itself, as a generic fuel cycle
-simulator, cannot make reliable statements about the uncertainty of metrics for a particular fuel
+simulator, cannot make reliable statements about the uncertainty of a particular fuel
 cycle. Any \gls{UQ} results are applicable only to the scenario that is under
-analysis by the user. \Cyclus is not a substitute for due diligence on behalf of the fuel
+analysis by the user. \Cyclus is not a panacea for due diligence on behalf of the fuel
 cycle modeler. Thus, \gls{UQ} is envisioned to be beyond the scope of core development
@@
 tests. Sufficient unit tests are required for any proposed change to the \Cyclus
-code base. Currently, \Cyclus implements over 450 unit tests and \Cycamore implements
-85.  These cover approximately 65\% of their respective code bases, and these numbers are expected to grow over time.
+code base. Currently \Cyclus implements over 450 unit tests and \Cycamore implements
+85.  These cover approximately 65\% of their respective code bases, and their numbers are expected to grow over time.
 
@@
 In \Cyclus and \Cycamore, integration tests are performed by running sample
-simulations and verifying that results are what would be expected ahead of
-time. A set of standard input files have thus been constructed.
+simulations for scenarios that are sufficiently simple to predict the results and verifying 
+that results match those predictions. A set of standard input files have thus been constructed.
 Python is used to run the same set of \Cyclus simulations as a subprocess for each integration test. 
@@
 
-Regression tests ensure unexpected backwards-incompatible changes do not
+Regression tests ensure significant unintended changes do not
 occur over the course of \Cyclus development. Such a change is called a
@@
 in \Cycamore because its archetypes are sophisticated enough
-to make interesting simulations.
+to make interesting input files. Only a handful ($<10$) of time steps are needed
+for regression testing.
 

### 2015-02-22 fundamentals/examples.tex
Expand list of reasons for introducing new archetypes to include fidelity.

--- 2015-02-18 fundamentals/examples.tex
@@
 contributions of new archetypes. Researchers will be driven to create a new
-archetype when a need arises to represent a novel reactor type, an innovative
+archetype when a need arises, such as to improve the fidelity of simulation, 
+or to represent a novel reactor type, an innovative
 reprocessing strategy, or a particular governmental or institutional behavior.

### 2015-02-22 fundamentals/impl.tex
reduced intro to mod software. specifically, this section was being a bit editorial

@@
 describing the general design features that make \Cyclus both flexible and powerful:
-cluster-ready software and dynamic libraries.  Next, the framework's
+cluster-ready software and dynamic libraries.  Next, the framework has an
 \gls{ABM} paradigm, which provides an expansion in performance beyond typical system dynamics
@@
 
-The architecture of \Cyclus allows developers
-to define nuclear fuel cycle agents and processes independent of the simulation
-logic. To achieve this, agents are developed using the \Cyclus framework \gls{API}, a set of functions and protocols
-which
-assist in agent development and specify how agents should be defined.
-This encapsulated `plug-in'
-design choice provides two major benefits. First, analysts across research institutions can take advantage of the
+The architecture of \Cyclus allows developers to define nuclear fuel cycle
+agents and processes independent of the simulation logic. To achieve this,
+agents are developed using the \Cyclus framework \gls{API}, a set of functions
+and protocols which assist in agent development and specify how agents should be
+defined.  This encapsulated `plug-in' design choice provides two major
+benefits. First, analysts across research institutions can take advantage of the
 simulation logic \gls{API} and archetype ecosystem when they apply \Cyclus to
-their specific problem. This
-mend-and-extend paradigm, common in modern software development, reduces
-maintenance overhead and improves software robustness by protecting the core logic
-from changes in the extensions.
-The researcher can focus on creating or customizing nuclear
-facility, institution, resource, and toolkit models within their specific area
-of technical expertise. This extensibility, magnified by an open source
-development process, frees the community of users to contribute desired
-features, independent from the team of \Cyclus core developers.
-Second, because \Cyclus uses a modular archetype approach, comparing two
-archetypes is straightforward. For example, if an analyst would like
-to compare the effect of using different models to determine the input fuel
-composition for fast reactors, a variety of fuel fabrication archetypes can be
-developed and interchanged while keeping the rest of the fuel cycle fixed
- to compare fuel fabrication designs.
+their specific problem.  A researcher can focus on creating or customizing
+nuclear facility, institution, resource, and toolkit models within their
+specific area of technical expertise. Second, because \Cyclus uses a modular
+archetype approach, comparing two archetypes is straightforward. For example, if
+an analyst would like to compare the effect of using different models to
+determine the input fuel composition for fast reactors, a variety of fuel
+fabrication archetypes can be developed and interchanged while keeping the rest
+of the fuel cycle fixed to compare fuel fabrication designs.
 
@@
 responsible for deploying and decommissioning facilities. Accordingly, advanced
-logic regarding building and decommissioning can be implemented on top of  
-those behaviors inherited from the
+logic regarding building and decommissioning can be obtained by inheriting
+those behaviors from the
 \Class{Institution} interface. Second, the \Class{Facility} class implements the
@@
 
-% the paragraph below muddies the concept of the RIF hierarchy
-% (perhaps an extended footnote?)
-% Either way, I prefer something other than ``provided explicitly''.
-
-Although the \Cyclus kernel is designed around the concept of the \gls{RIF} hierarchy, 
-it can handle hierarchies of arbitrary depth.  It is capable of
+Although concept of the \gls{RIF} hierarchy is provided explicitly, the \Cyclus kernel is
+designed to handle hierarchies of arbitrary depth.  It is capable of
 running a simulation without regions and institutions (i.e.  only facilities)
@@
 target facility and the individual materials modified within it.
+Provenance and trade-history of distinct materials is the fundamental
+information unit in such studies.
 Material risk analysis, therefore, demands that both facilities and materials
@@
 
-% although this abbreviation is provided by the glossary capability, I think
-% the DRE is so important that it should be redefined here.
+\subsubsection{Dynamic Resource Exchange}
 
-\subsubsection{Dynamic Resource Exchange (DRE)}
-
-Since the \Cyclus simulation paradigm allows discrete agents, based on archetypes
-about which the kernel has no knowledge, to enter 
-the simulation at arbitrary times and
-trade in discrete resources that are not defined \textit{a priori}, 
-the logic engine defining resource interaction mechanisms
+Since the \Cyclus simulation paradigm involves both discrete agents and
+discrete resources, the logic engine defining resource interaction mechanisms
 among agents is crucial. The \gls{DRE} is that critical logic engine on which \Cyclus
@@
 request. Suppliers may add an arbitrary number of constraints to accompany
-bids. For example, an enriched \gls{UOX} supplier may be constrained by its current
-inventory of natural uranium or its total capacity to provide enrichment (SWUs), and
-attach such constraints to its bids. Any potential resource transfer may be denoted as
+bids. For example, an enriched \gls{UOX} supplier may supply both a natural uranium
+and SWU constraint. Any potential resource transfer may be denoted as
 \textit{exclusive}. An exclusive transfer must either be met fully or not at all
@@
 \textit{preferences} to each potential request-bid pairing based on the proposed
-resource transfer. Facilities can apply arbitrary complex logic to rank the bids 
-that they have received, whether based on the quantity available in each bid or
-on the quality of each bid, and the consequent implications of the physics behavior
-of that facility. In addition, an institution can apply a higher preference to a
+resource transfer. Therefore, an institution can apply a higher preference to a
 partner to which it is congenial; similarly, a region may negate any transfers
@@
 provides a flexible supply-demand infrastructure, supporting dynamic flows of
-resources between agents, even as those agents enter and leave the simulation, and 
-even when those agents are defined by archetypes of arbitrary complexity. Trading 
-between agents can be affected by both the
+resources between agents. Trading between agents can be affected by both the
 proposed quality of a resource and agent relationships through the use of
@@
 
-As illustrated in
+The current \Cycamore release provide basic functionality, As illustrated in
 Figure \ref{fig:simplesim}, the current \Cycamore release provides basic
@@
 In \Cyclus and \Cycamore, integration tests are performed by running sample
-simulations for scenarios that are sufficiently simple to predict the results and verifying 
-that results match those predictions. A set of standard input files have thus been constructed.
+simulations and verifying that results are what would be expected ahead of
+time. A set of standard input files have thus been constructed.
 Python is used to run the same set of \Cyclus simulations as a subprocess for each integration test.
@@
 
-Regression tests ensure significant unintended changes do not
+Regression tests ensure significant changes do not
 occur over the course of \Cyclus development. Such a change is called a

### 2015-02-22 fundamentals/impl.tex
don't need to harp
rm'd paragraph about trader interface. this is implementation detail, but could still be considered important. happy to revert this.

@@
 Furthermore, the core infrastructure and related archetypes are free and
-open source, BSD-3-clause licensed. No part of \Cyclus is proprietary or based
-on \gls{COTS}, Windows-only software. \Cyclus can therefore be easily deployed
+open source, BSD-3-clause licensed.  \Cyclus can therefore be easily deployed
 on large computer systems, such as \gls{HTC} systems.
@@
 \end{figure}
-
-In a similar fashion, the \Class{Trader} interface allows agent-agent interaction through the
-trading of \Class{Resource}s. Archetypes in a \Cyclus simulation must
-implement the \Class{Agent} interface and may optionally implement the
-\Class{Trader} interface. For example, a \Class{Region} implements only the
-\Class{Agent} interface, whereas a \Class{Facility} implements both the
-\Class{Agent} and \Class{Trader} interface, allowing any \Class{Facility} to
-trade with another \Class{Facility}.
 

### 2015-02-22 fundamentals/impl.tex
removed long paragraph about composition caching. this is very much an implementation detail. can revert, but I think this should at least be stripped down to a few sentences.

@@
 developers to choose how to handle potentially full-fidelity compositions.
-
-In large simulations, many material objects may change frequently.
-Material decay can also contribute significantly to such changes.  In order to
-help avoid unnecessary runtime performance and database size impacts,
-compositions in \Cyclus have some special features.
-Immutability of compositions allows multiple material objects to all hold
-references to the same composition object safely.  When operations that do not
-alter the composition are performed on a material, any new resulting
-materials hold a reference to the same, original composition object.
-Although the decay operation generates a new, separate composition (preserving
-immutability), a reference to the new composition is placed in a cache shared
-by the new and original compositions. The next time the original
-composition is decayed, this cache will be checked for a prior calculation
-with the same cumulative decay time.  If one exists, the cached composition is
-used.  This cache is shared by all compositions that transitively come from
-the same origin.  Composition immutability in concert with decay history
-caching help eliminate many redundant decay calculations in addition to
-reducing the total number of composition objects.  Since each composition
-object is only recorded in the database once, significant space savings also
-occurs.
-\TODO{do we want a diagram helping show this composition caching?}
 

### 2015-02-22 fundamentals/impl.tex
removed git flow section and figure. this seemed like getting a bit too much into the weeds for me. happy to revert, but if reverted, i think it should be reduced to one or two sentences.

@@
 
-\Cyclus uses a strategy known as \emph{git flow}
-\cite{kalliamvakou_code-centric_2014}
-to manage topical branches where individuals develop code: the mainline development
-branch (simply known as develop), and the stable branch (called master).
-In addition to these rules and delineations, \Cyclus also imposes rules on
-when it is acceptable from a quality control standpoint to merge code from
-the personal topical branches into the develop branch. All software at this stage
-must have sufficient successful tests and comprehensive documentation. Without
-these core pieces, proposed changes are not allowed into \Cyclus. As an example, a schematic of
-the development stages between reporting a bug and merging the fix is shown in
-Figure \ref{fig:gitprocess}.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[height=0.6\textheight]{./images/gitprocess}
-\end{center}
-\caption{A version-control enabled process for finding, reporting, and fixing a bug
-can take place within an issue tracker alongside multiple stages of software
-testing and review. In the \Cyclus case, the final review stage includes unit,
-regression, and integration testing as well as manual code inspection.}
-\label{fig:gitprocess}
-\end{figure}
-
 The act of proposing a change is known as a \emph{pull request}. The main \Cyclus repository is

### 2015-02-22 fundamentals/fcsreqs.tex
Overhaul motivation and fcsreqs

@@
+\subsubsection{Open Access and Development Practices}
+
+The proprietary concerns of research institutions and security constraints of
+data within fuel cycle simulators often restrict access. Use of a simulator is
+therefore often limited to its institution of origin, necessitating effort
+duplication at other institutions and thereby squandering broader human
+resources. License agreements and institutional approval are required for most
+current simulators (i.e. \gls{COSI}6, \gls{DANESS}, \gls{DESAE}, EVOLCODE,
+FAMILY21, \gls{NFCSim})\cite{juchau_modeling_2010}, ORION, and VISION.  Even when, as in
+the case of the MIT \gls{CAFCA} software, the source code is unrestricted, the
+platform on which it relies is often restricted or costly.  However, \Cyclus
+provides fully free and open access to all users
+and developers, foreign and domestic.
+
+Moreover, both technical and institutional aspects of the software development
+practices employed by the \Cyclus community faciltate collaboration.
+Technically, \Cyclus employs a set of tools commonly used collaborative
+software development that reduce the effort required to comment on, test and
+ultimately merge individual contributions into the main development path.  
+For many of the simulation platforms adopted by previous simulators, there were
+technical obstacles that impeded this kind of collaboration.
+Institutionally, \Cyclus invites all participants to propose, discuss and
+provide input to the final decision making for all important changes.
+
+\subsubsection{Modularity and Extensibility}
+
+Modularity is a key enabler of extending the scope of fuel cycle analysis
+within the \Cyclus framework.  Changes that are required to improve the
+fidelity of modeling a paticular agent, or to introduce entirely new agents,
+are narrowly confined and place no new requirements on the \Cyclus kernel.
+Furthermore, there are very few assumptions or heuristics that would otherwise
+restrict the algorithmic complexity that can be used to model the behavior of
+such agents.
+
+For example, most current simulators describe a finite set of acceptable cycle
+constructions (once through, single-pass, multi-pass). That limits the
+capability to create novel material flows and economic scenarios. The \Cyclus
+simulation logic relies on a market paradigm, parameterized by the user, which
+flexibly simulates dynamic responses to pricing, availability, and other
+institutional preferences.
+
+This minimal set of mutual dependencies between the kernel and the agents is
+expressed through the \gls{DRE} that provides a level of flexibility that does
+not exist in other fuel cycle simulators.  It creates the potential for novel
+agent archetypes to interact with existing archetypes as they enter and leave
+the simulation over time and seek to trade materials whose specific
+composition may not be known \textit{a priori}.
+
 \subsubsection{Discrete Facilities and Materials}
@@
 flexible framework on which either method is possible.
-
-\subsubsection{Open Access}
-
-The proprietary concerns of research institutions and security constraints of
-data within fuel cycle simulators often restrict access. Use of a simulator is
-therefore often limited to its institution of origin, necessitating effort
-duplication at other institutions and thereby squandering broader human
-resources. License agreements and institutional approval are required for most
-current simulators (i.e. \gls{COSI}6, \gls{DANESS}, \gls{DESAE}, EVOLCODE,
-FAMILY21, \gls{NFCSim})\cite{juchau_modeling_2010}, ORION, and VISION.  Even when, as in
-the case of the MIT \gls{CAFCA} software, the source code is unrestricted, the
-platform on which it relies is often restricted or costly.  However, \Cyclus
-provides fully free and open access to all users
-and developers, foreign and domestic.
-
-\subsubsection{Flexibility and Extensibility}
-
-In addition to being inaccessible, the vast majority of fuel cycle simulators
-are, effectively, inextensible. Typical fuel cycle simulator development teams are insular, in
-part due to aforementioned accessibility issues. Accordingly, their frameworks
-typically contain heuristics and assumptions that constrain developer additions.
-
-For example, most current simulators describe a finite set of acceptable
-cycle constructions (once through, single-pass, multi-pass). That limits the
-capability to create novel material flows and economic scenarios. The \Cyclus
-simulation logic relies on a market paradigm, parameterized by the user, which
-flexibly simulates dynamic responses to pricing, availability, and other
-institutional preferences. This is an advanced level of flexibility that does
-not exist in other fuel cycle simulators.

### 2015-02-22 fundamentals/intro.tex
Overhaul motivation and fcsreqs

@@
 The \Cyclus paradigm enables targeted contribution and collaboration within the
-nuclear fuel cycle analysis community. This essential capability is absent in
+nuclear fuel cycle analysis community to achieve two important goals: lower the
+barrier for innvoative nuclear technologies to be included in fuel cycle analysis 
+while improving the ability to compare simulations with and without those innovative
+concepts.  This essential capability is absent in
 previous simulators where user customization and extensibility were not design
-objectives, and was attained by the \emph{modular and open architecture} of
-\Cyclus.  Additionally, \Cyclus facilitates direct comparison of modeling
-methodologies with \emph{agent interchangeability}.  Finally, \Cyclus is
+objectives.  While the \emph{modular and open architecture} of
+\Cyclus is necessary to meet these goals, it is not sufficient.  
+\emph{Agent interchangeability} is required to facilitates direct comparison 
+of alternative modeling methodologies and facility concepts.  Finally, \Cyclus is
 applicable to a broader range of fidelities, scales, and applications than

### 2015-02-22 fundamentals/impl.tex
reduced some extra wordiness. it's important information, but likely too far into the weeds

--- 2015-02-22 fundamentals/impl.tex
@@
 developers to choose how to handle potentially full-fidelity compositions.
+
+In large simulations, many material objects may change frequently.  Material
+decay can also contribute significantly to such changes.  In order to help
+avoid unnecessary runtime performance and database size impacts, compositions
+in \Cyclus have some special features.  In particular, compositions are stored
+immutably in the database so that multiple material objects can hold references
+to the same composition safely.  Additionally, when transmutation and decay
+result in new compositions, those are cached for additional avoidance of
+redundancy.Composition immutability in concert with decay history caching help
+eliminate many redundant decay calculations in addition to reducing the total
+number of composition objects recorded in the database.
+\TODO{do we want a diagram helping show this composition caching?}
 

### 2015-02-22 fundamentals/impl.tex
reduces come git flow text that got into the weeds

@@
 \Cyclus uses a strategy known as \emph{git flow}
-\cite{kalliamvakou_code-centric_2014}
-to manage topical branches where individuals develop code: the mainline development
-branch (simply known as develop), and the stable branch (called master).
-In addition to these rules and delineations, \Cyclus also imposes rules on
-when it is acceptable from a quality control standpoint to merge code from
-the personal topical branches into the develop branch. All software at this stage
-must have sufficient successful tests and comprehensive documentation. Without
-these core pieces, proposed changes are not allowed into \Cyclus. As an example, a schematic of
+\cite{kalliamvakou_code-centric_2014} to manage topical branches where
+individuals develop code in parallel and changes are only merged into the
+mainline branch after when it is acceptable from a quality control standpoint
+All software at this stage must have sufficient successful tests and
+comprehensive documentation.  Proposed changes must be sufficiently documented
+and tested before they are allowed into \Cyclus.  As an example, a schematic of
 the development stages between reporting a bug and merging the fix is shown in

### 2015-02-22 fundamentals/impl.tex
more reduction of excess verbage. Aiming for brevity.

@@
 \cite{kalliamvakou_code-centric_2014} to manage topical branches where
-individuals develop code in parallel and changes are only merged into the
-mainline branch after when it is acceptable from a quality control standpoint
-All software at this stage must have sufficient successful tests and
-comprehensive documentation.  Proposed changes must be sufficiently documented
-and tested before they are allowed into \Cyclus.  As an example, a schematic of
-the development stages between reporting a bug and merging the fix is shown in
+individuals develop code in parallel. All proposed software changes from
+topical branches must have sufficient successful tests and comprehensive
+documentation to be allowed into \Cyclus.  As an example, a schematic of the
+development stages between reporting a bug and merging the fix is shown in
 Figure \ref{fig:gitprocess}.

### 2015-02-22 fundamentals/impl.tex

@@
 
-Simulation science - like experimental science - has since the beginning had the
-problem of identifying trustworthy results from nonsensical results or noise.
+Simulation science - like experimental science - must distinguish trustworthy
+results from untrustworthy ones.
 Charles Babbage famously articulated this, ``On two occasions I have been asked,
@@
 of ideas that could provoke such a question.'' \cite{babbage_passages_2011}.
-A simulator must both guard against the \emph{garbage in, garbage out} phenomenon, and also assure correctness.
+A simulator must assure correctness and guard against the \emph{garbage
+in, garbage out} phenomenon.
 
 Multiple strategies, collectively known as \emph{\gls{QA}}, have
-been invented over the years to mitigate the structural and algorithmic errors
-on the part of simulators themselves. These include \emph{\gls{VV}}
+been invented to mitigate structural and algorithmic errors
+in software. These include \emph{\gls{VV}}
 \cite{boehm_software_1989}, \emph{\gls{UQ}}
-\cite{sacks_design_1989}, testing, and others. \gls{VV} and \gls{UQ} come from
-a distinctly computational science background while testing \emph{et al.} come from software development.
+\cite{sacks_design_1989}, testing, and others.
 
@@
 whose latest revision appeared in 2009 \cite{asme_nqa-1a-2009_2009}.
-Although \gls{NQA1} is primarily
-used for designing reactors, it is general enough to apply to
-\Cyclus. \Cyclus has adopted an \emph{agile} development process
+\Cyclus has adopted an \emph{agile} development process
 \cite{larman_agile_2004},
 interpreting \gls{NQA1} in a manner similar to the process adopted by the
-\gls{DOE} within \gls{NEAMS} \cite{neams_nuclear_2013} or the
-PyNE toolkit \cite{biondo_quality_2014}.
+\gls{DOE} within \gls{NEAMS} \cite{neams_nuclear_2013} or by the PyNE toolkit
+\cite{biondo_quality_2014}.
 
-Quality assurance is an on-going process throughout the
-entire life of the software. As a simulator where most modeling decisions are made
+Since \Cyclus modeling decisions are made
 by third party archetype developers or users, the most important feature of
@@
 Verification may be defined as the question, ``Is \Cyclus being built correctly?''
-To answer this question, we turn to the software development of notions of testing,
-documentation, version control, style guidelines, and continuous integration.
-This suite of process controls supplies mechanism for reliable and reproducible
-software. The impetus to implement these controls correctly is particularly strong in a scientific
-context because of the emphasis on reproducibility and provenance. These verification techniques are
+To answer this question, \Cyclus relies on software development best practices
+such as testing,
+documentation, version control, style guidelines, and continuous integration to
+ensure reliability and reproducibility. These verification techniques are
 discussed individually in the sections that follow.

### 2015-02-22 fundamentals/impl.tex

@@
 responsible for deploying and decommissioning facilities. Accordingly, advanced
-logic regarding building and decommissioning can be obtained by inheriting
-those behaviors from the
+logic regarding building and decommissioning can be implemented on top of
+those behaviors inherited from the
 \Class{Institution} interface. Second, the \Class{Facility} class implements the
@@
 
-Although concept of the \gls{RIF} hierarchy is provided explicitly, the \Cyclus kernel is
-designed to handle hierarchies of arbitrary depth.  It is capable of
+% the paragraph below muddies the concept of the RIF hierarchy
+% (perhaps an extended footnote?)
+% Either way, I prefer something other than ``provided explicitly''.
+
+Although the \Cyclus kernel is designed around the concept of the \gls{RIF} hierarchy,
+it can handle hierarchies of arbitrary depth.  It is capable of
 running a simulation without regions and institutions (i.e.  only facilities)
@@
 
-\subsubsection{Dynamic Resource Exchange}
+% although this abbreviation is provided by the glossary capability, I think
+% the DRE is so important that it should be redefined here.
 
-Since the \Cyclus simulation paradigm involves both discrete agents and
-discrete resources, the logic engine defining resource interaction mechanisms
+\subsubsection{Dynamic Resource Exchange (DRE)}
+
+Since the \Cyclus simulation paradigm allows discrete agents, based on archetypes
+about which the kernel has no knowledge, to enter
+the simulation at arbitrary times and
+trade in discrete resources that are not defined \textit{a priori},
+the logic engine defining resource interaction mechanisms
 among agents is crucial. The \gls{DRE} is that critical logic engine on which \Cyclus
@@
 \textit{preferences} to each potential request-bid pairing based on the proposed
-resource transfer. Therefore, an institution can apply a higher preference to a
+resource transfer. Facilities can apply arbitrary complex logic to rank the bids
+that they have received, whether based on the quantity available in each bid or
+on the quality of each bid, and the consequent implications of the physics behavior
+of that facility. In addition, an institution can apply a higher preference to a
 partner to which it is congenial; similarly, a region may negate any transfers
@@
 provides a flexible supply-demand infrastructure, supporting dynamic flows of
-resources between agents. Trading between agents can be affected by both the
+resources between agents, even as those agents enter and leave the simulation, and
+even when those agents are defined by archetypes of arbitrary complexity. Trading
+between agents can be affected by both the
 proposed quality of a resource and agent relationships through the use of
@@
 
-The current \Cycamore release provide basic functionality, As illustrated in
+As illustrated in
 Figure \ref{fig:simplesim}, the current \Cycamore release provides basic
@@
 In \Cyclus and \Cycamore, integration tests are performed by running sample
-simulations and verifying that results are what would be expected ahead of
-time. A set of standard input files have thus been constructed.
+simulations for scenarios that are sufficiently simple to predict the results and verifying
+        that results match those predictions. A set of standard input files have thus been constructed.
 Python is used to run the same set of \Cyclus simulations as a subprocess for each integration test.

### 2015-02-22 fundamentals/conclusion.tex
Comments on things we say about VISION, et al

@@
 
+% gonuke: I am sensitive to making the implication that VISION (or others) has
+%         ``uncertain provenance''.  It's not that I disagree with that
+%         sentiments, but this can imagine this being perceived as a pretty
+%         strong accusation and we better be prepared to back it up, or reword
+%         it slightly.
+
 The \Cyclus nuclear fuel cycle framework presents a more generic and flexible
 alternative to existing fuel cycle simulators. Where previous nuclear fuel cycle simulators have had limited distribution,
-uncertain provenance, and restricted customizability, \Cyclus emphasizes an
+constrained simulation capabilities, and restricted customizability, \Cyclus emphasizes an
 open access and development strategy.  Open development, with transparent

### 2015-02-22 fundamentals/acros.tex

@@
 \newacronym{FCO}{FCO}{Fuel Cycle Options}
-\newacronym{RDD}{RD\&D}{Research Development and Design}
+\newacronym{RDD}{RD\&D}{research development and design}
 \newacronym{WIPP}{WIPP}{Waste Isolation Pilot Plant}
@@
 \newacronym{CUBIT}{CUBIT}{CUBIT Geometry and Mesh Generation Toolkit}
-\newacronym{CSNF}{CSNF}{Commercial Spent Nuclear Fuel}
-\newacronym{DSNF}{DSNF}{DOE Spent Nuclear Fuel}
-\newacronym{MTHM}{MTHM}{Metric Ton of Heavy Metal}
-\newacronym{HTGR}{HTGR}{High Temperature Gas Reactor}
+\newacronym{CSNF}{CSNF}{commercial spent nuclear fuel}
+\newacronym{DSNF}{DSNF}{DOE spent nuclear fuel}
+\newacronym{MTHM}{MTHM}{metric ton of heavy metal}
+\newacronym{HTGR}{HTGR}{high temperature gas reactor}
 \newacronym{TRISO}{TRISO}{Tristructural Isotropic}
-\newacronym{MA}{MA}{Minor Actinide}
+\newacronym{MA}{MA}{minor actinide}
 \newacronym{CEA}{CEA}{Commissariat a l'Energie Atomique et aux Energies Alternatives}
@@
 \newacronym{SINDAG}{SINDA{\textbackslash}G}{Systems Improved Numerical Differencing Analyzer $\backslash$ Gaski}
-\newacronym{STC}{STC}{Specific Temperature Change}
-\newacronym{LDRD}{LDRD}{Laboratory Directed Research and Development}
-\newacronym{LCOE}{LCOE}{Levelized Cost of Electricity}
-\newacronym{ABM}{ABM}{Agent-Based Modeling}
-\newacronym{COTS}{COTS}{Commercial, Off-The-Shelf}
-\newacronym{API}{API}{Application Programming Interface}
+\newacronym{STC}{STC}{specific temperature change}
+\newacronym{LDRD}{LDRD}{laboratory directed research and development}
+\newacronym{LCOE}{LCOE}{levelized cost of electricity}
+\newacronym{ABM}{ABM}{agent-based modeling}
+\newacronym{COTS}{COTS}{commercial, off-the-shelf}
+\newacronym{API}{API}{application programming interface}
 \newacronym{RIF}{RIF}{Region-Institution-Facility}
-\newacronym{GUI}{GUI}{Graphical User Interface}
-\newacronym{HPC}{HPC}{High-Performance Computing}
-\newacronym{HTC}{HTC}{High-Throughput Computing}
+\newacronym{GUI}{GUI}{graphical user interface}
+\newacronym{HPC}{HPC}{high-performance computing}
+\newacronym{HTC}{HTC}{high-throughput computing}
 \newacronym{UML}{UML}{Unified Modeling Language}
-\newacronym{DAG}{DAG}{Directed Acyclic Graph}
-\newacronym{MOX}{MOX}{Mixed Oxide}
-\newacronym{UOX}{UOX}{Uranium Oxide}
-\newacronym{QA}{QA}{Quality Assurance}
+\newacronym{DAG}{DAG}{directed acyclic graph}
+\newacronym{MOX}{MOX}{mixed oxide}
+\newacronym{UOX}{UOX}{uranium oxide}
+\newacronym{QA}{QA}{quality assurance}
 \newacronym{NQA1}{NQA-1}{Nuclear Quality Assurance - 1}
-\newacronym{VV}{V\&V}{Verification and Validation}
-\newacronym{UQ}{UQ}{Uncertainty Quantification}
+\newacronym{VV}{V\&V}{verification and validation}
+\newacronym{UQ}{UQ}{uncertainty quantification}
 \newacronym{ASME}{ASME}{American Society of Mechanical Engineers}
 \newacronym{NEAMS}{NEAMS}{Nuclear Engineering Advanced Modeling and Simulation}
-\newacronym{CI}{CI}{Continuous Integration}
-\newacronym{DRE}{DRE}{Dynamic Resource Exchange}
+\newacronym{CI}{CI}{continuous integration}
+\newacronym{DRE}{DRE}{dynamic resource exchange}
 \newacronym{DESAE}{DESAE}{Dynamic Analysis of Nuclear Energy Systems Strategies}
-\newacronym{MILP}{MILP}{Mixed-Integer Linear Program}
-\newacronym{LP}{LP}{Linear Program}
+\newacronym{MILP}{MILP}{mixed-integer linear program}
+\newacronym{LP}{LP}{linear program}
 %\newacronym{<++>}{<++>}{<++>}

### 2015-02-22 fundamentals/intro.tex
updates language between dynamic and static simulators. now all language points to dynamic as in time-stepping, facilities, etc.

@@
 
-The cardinal purpose of a nuclear fuel cycle simulator is to calculate the
-time- and facility-dependent mass flow through all or part the fuel cycle.
-Historically, nuclear fuel cycle simulators have calculated fuel cycle mass
-balances and performance metrics derived from them using software ranging from
-ad hoc spreadsheet-driven flow calculators to highly specialized system
-dynamics modeling platforms. To date, current tools are often static rather
-than dynamic, rigid rather than flexible, fleet-based rather than discrete, or
-privately distributed rather than open source. Each of these choices presents a
-challenge to modeling fidelity, generality, efficiency, robustness, and
-scientific transparency.
+The cardinal purpose of a dyamic nuclear fuel cycle simulator is to calculate
+the time- and facility-dependent mass flow through all or part the fuel cycle.
+Dynamic nuclear fuel cycle analysis more realistically supports a range of
+simulation goals than static analysis \cite{piet_dynamic_2011}. Historically,
+dynamic nuclear fuel cycle simulators have calculated fuel cycle mass balances
+and performance metrics derived from them using software ranging from ad hoc
+spreadsheet-driven flow calculators to highly specialized system dynamics
+modeling platforms. To date, current tools are often rigid rather than flexible,
+fleet-based rather than discrete, or privately distributed rather than open
+source. Each of these choices presents a challenge to modeling fidelity,
+generality, efficiency, robustness, and scientific transparency.
 
@@
 architecture, an open development process, discrete agents, discrete time, and
-arbitrarily detailed isotopic resolution of materials. Dynamic nuclear fuel
-cycle analysis more realistically supports a range of simulation goals than
-static analysis \cite{piet_dynamic_2011}. Similarly, experience in the broader
+arbitrarily detailed isotopic resolution of materials. Experience in the broader
 field of systems analysis indicates that agent-based modeling enables more
 flexible simulation control, without loss of generality
-\cite{macal_agent-based_2010}. Finally, openness allows cross-institutional
+\cite{macal_agent-based_2010}. Furthermore, openness allows cross-institutional
 collaboration, increases software robustness \cite{cohen_modern_2010}, and
@@
 depth and fidelity, this ecosystem allows users and developers to customise
-\Cyclus to analyze the cases that are of interest to them, rather than those
-the simulator was originally developed to address.  The fundamental concepts of
-the \Cyclus nuclear fuel cycle simulator capture these modern insights so that
-novel challenges in nuclear fuel cycle analysis can be better addressed.
+\Cyclus to analyze the cases that are of interest to them, rather than those the
+simulator was originally developed to address.  The fundamental concepts of the
+\Cyclus nuclear fuel cycle simulator capture these modern insights so that novel
+challenges in nuclear fuel cycle analysis can be better addressed.
 

### 2015-02-22 fundamentals/intro.tex
intro intro adjustments

@@
 
-\Cyclus, therefore, is a dynamic, agent-based model, which employs a modular
-architecture, an open development process, discrete agents, discrete time, and
-arbitrarily detailed isotopic resolution of materials. Experience in the broader
-field of systems analysis indicates that agent-based modeling enables more
-flexible simulation control, without loss of generality
+\Cyclus, is a dynamic, agent-based model, which employs a modular architecture,
+an open development process, discrete agents, discrete time, and arbitrarily
+detailed isotopic resolution of materials. Experience in the broader field of
+systems analysis indicates that agent-based modeling enables more flexible
+simulation control, without loss of generality
 \cite{macal_agent-based_2010}. Furthermore, openness allows cross-institutional
 collaboration, increases software robustness \cite{cohen_modern_2010}, and
-cultivates an ecosystem of modeling and calculation options. Comprised of
-flexible, interchangeable models of fuel cycle components with varying scope,
-depth and fidelity, this ecosystem allows users and developers to customise
+cultivates an ecosystem of modeling and calculation options. This ecosystem is
+comprised of flexible, interchangeable models of fuel cycle components with
+varying scope, depth, and fidelity. It allows users and developers to customise
 \Cyclus to analyze the cases that are of interest to them, rather than those the

### 2015-02-22 fundamentals/intro.tex
cleaned up last sentence of IA

@@
 \Cyclus emerged from a line of tools seeking to break this practice.  Its
-precursor,
-\gls{GENIUS} Version 1 \cite{dunzik-gougar_global_2007,jain_transitioning_2006},
-originated within \gls{INL} and sought to provide generic regional capability.
-Based on lessons learned from \gls{GENIUS} Version 1, the \gls{GENIUS} Version
-2 \cite{oliver_studying_2009,huff_geniusv2_2009} simulator sought to provide more
-generality and an extensible interface to facilitate collaboration.  The
-\Cyclus project then improved upon the \gls{GENIUS} effort by
-implementing increased modularity and encapsulation.  The result is a dynamic
-simulator that treats both materials and facilities discretely, with an
-architecture that permits multiple and variable levels of fidelity. The
-simulator's agent-based framework for tracking the transformation and trade of
-resources between autonomous regional and institutional entities with
-customizable behavior and objectives is an innovation not pursued by any
-existing fuel cycle simulator.
+precursor, \gls{GENIUS} Version 1
+\cite{dunzik-gougar_global_2007,jain_transitioning_2006}, originated within
+\gls{INL} and sought to provide generic regional capability.  Based on lessons
+learned from \gls{GENIUS} Version 1, the \gls{GENIUS} Version 2
+\cite{oliver_studying_2009,huff_geniusv2_2009} simulator sought to provide more
+generality and an extensible interface to facilitate collaboration.  The \Cyclus
+project then improved upon the \gls{GENIUS} effort by implementing increased
+modularity and encapsulation.  The result is a dynamic simulator that treats
+both materials and facilities discretely, with an architecture that permits
+multiple and variable levels of fidelity. Using an agent-based framework, the
+simulator tracks the transformation and trade of resources between autonomous
+regional and institutional entities with customizable behavior and
+objectives. This capability is an innovation not pursued by any existing fuel
+cycle simulator.
 

### 2015-02-22 fundamentals/fcsreqs.tex
Comments on things we say about VISION, et al
Put VISION in gls{}
tried to clean up the citation listing in IBi

@@
 resources. License agreements and institutional approval are required for most
-current simulators (i.e. \gls{COSI}6, \gls{DANESS}, \gls{DESAE}, EVOLCODE,
-FAMILY21, \gls{NFCSim})\cite{juchau_modeling_2010}, ORION, and VISION.  Even when, as in
-the case of the MIT \gls{CAFCA} software, the source code is unrestricted, the
-platform on which it relies is often restricted or costly.  However, \Cyclus
-provides fully free and open access to all users
-and developers, foreign and domestic.
+current simulators (e.g., \gls{COSI}6, \gls{DANESS}, \gls{DESAE}, EVOLCODE,
+FAMILY21, \gls{NFCSim})\cite{juchau_modeling_2010}, including ORION,
+and \gls{VISION}.  Even when, as in the case of the MIT \gls{CAFCA} software,
+the source code is unrestricted, the platform on which it relies is often
+restricted or costly.  However, \Cyclus provides fully free and open access to
+all users and developers, foreign and domestic.
 

### 2015-02-22 fundamentals/fcsreqs.tex
fixed ie/eg

--- 2015-02-22 fundamentals/fcsreqs.tex
@@
 resources. License agreements and institutional approval are required for most
-current simulators (i.e. \gls{COSI}6, \gls{DANESS}, \gls{DESAE}, EVOLCODE,
-FAMILY21, \gls{NFCSim})\cite{juchau_modeling_2010}, ORION, and VISION.  Even when, as in
-the case of the MIT \gls{CAFCA} software, the source code is unrestricted, the
-platform on which it relies is often restricted or costly.  However, \Cyclus
-provides fully free and open access to all users
-and developers, foreign and domestic.
+current simulators (e.g. \gls{COSI}6, \gls{DANESS}, \gls{DESAE}, EVOLCODE,
+FAMILY21, \gls{NFCSim})\cite{juchau_modeling_2010}, including ORION,
+and \gls{VISION}.  Even when, as in the case of the MIT \gls{CAFCA} software,
+the source code is unrestricted, the platform on which it relies is often
+restricted or costly.  However, \Cyclus provides fully free and open access to
+all users and developers, foreign and domestic.
 
@@
 most readily captured by software capable of tracking the operations status of
-discrete facilities \cite{huff_next_2010}.  Fleet-based models (i.e.
+discrete facilities \cite{huff_next_2010}.  Fleet-based models (e.g.
 \gls{VISION}) are unable to capture this gracefully, perhaps representing it as

### 2015-02-22 fundamentals/impl.tex
Add comment about UML diagram
cleaned up intro to II

@@
 physics-dependent supply chain problems involving material routing, facility
-deployment, and regional and institutional hierarchies. Additionally, the choice to
-build \Cyclus on open source libraries in modern programming languages enables
-both remote and multiprocess execution on a number of platforms. This section begins by
-describing the general design features that make \Cyclus both flexible and powerful:
-cluster-ready software and dynamic libraries.  Next, the framework's
-\gls{ABM} paradigm, which provides an expansion in performance beyond typical system dynamics
-capabilities, is described, focusing on agent interchangeability and the
-implementation of the region-institution-facility hierarchy.
-Next, the discrete treatment of objects is discussed in terms of both
-resources and materials and time via the \gls{DRE}.
-Support for users and developers via the \Cycamore library of
-archetypes and the experimental toolkit are also presented.
-Lastly, the methods for quality assurance are outlined.
+deployment, and regional and institutional hierarchies. Additionally, the choice
+to build \Cyclus on open source libraries in modern programming languages
+enables both remote and multiprocess execution on a number of platforms. This
+section begins by describing the general design features that make \Cyclus both
+flexible and powerful: cluster-ready software and dynamic libraries.  The
+\gls{ABM} framework is then described, focusing on how \gls{ABM} is implemented
+in a fuel cycle context and the relative benefits thereof. A discussion of the
+time-dependent treatement of discrete resources follow, focusing on the
+\gls{DRE}. Support for users and developers via the \Cycamore library of
+archetypes and the experimental toolkit are also presented.  Lastly, the methods
+for quality assurance are outlined.
 

### 2015-02-22 fundamentals/impl.tex
updated cyclopts mention

@@
 Cyclopts \cite{gidden_cyclopts_2015}, a proof of principle design and
-implementation of \Cyclus on such a large computer system, uses UW-Madison's
-HTCondor \gls{HTC} infrastructure to perform sensitivity studies on \Cyclus'
-resource exchange optimization solvers. To date, it has been used to run over
-$10^4$ jobs, or (\TODO{compute time}) total compute hours, using the \Cyclus
-library via its resource exchange \gls{API}.  The \gls{HTC} infrastructure has
-also been utilized to run and collect information from full \Cyclus simulations
-running in parallel on $10^3$ machines reliably for order $10^5$ simulations.
+implementation of a \Cyclus-enabled application on such a large computer system,
+uses UW-Madison's HTCondor \gls{HTC} infrastructure to perform sensitivity
+studies on \Cyclus' resource exchange optimization solvers. To date, it has been
+used to run over $10^5$ jobs, comprising more than 60,000 total compute hours,
+using the \Cyclus library via its resource exchange \gls{API}.  The \gls{HTC}
+infrastructure has separately been utilized to run and collect information from
+full \Cyclus simulations running in parallel on $10^3$ machines reliably for
+order $10^5$ simulations.
 

### 2015-02-22 fundamentals/impl.tex
cleaned up interchange ex

@@
 
-\gls{ABM} is inherently object-oriented because agents represent
-discrete, independently acting objects.  Figure \ref{fig:framework} illustrates
-the modular nature of \Cyclus archetypes.  The core of the \Cyclus simulator
-creates a set of classes on which agent plug-ins
-are based. In addition, a set of tools are also provided to enrich the
-\gls{API} and supply a robust suite of behaviors for the developer.
-Agent plug-ins utilize the generic core \gls{API} to interact with one another.  For
-example, agents rely on a paradigm of dynamic loading and clean plug-in
-behavior at the start of the simulation. They also use the resource exchange
-paradigm \gls{API} for trading resources with one another.
+\gls{ABM} is inherently object-oriented because agents represent discrete,
+independently acting objects.  Figure \ref{fig:framework} illustrates the
+modular nature of \Cyclus archetypes.  The core of the \Cyclus simulator creates
+a set of classes on which agent plug-ins are based. In addition, a set of tools
+are also provided to enrich the \gls{API} and supply a robust suite of behaviors
+for the developer.  Agent plug-ins utilize the generic core \gls{API} to
+interact with one another.  For example, they use the resource exchange paradigm
+\gls{API} for trading resources with one another.
 

### 2015-02-22 fundamentals/impl.tex
extremes->fidelity
moved first paragraph up into IIC intro. it mentions both faciliteis and resources
clean up decay sentence

@@
 material objects at isotopic resolution. In this way, \Cyclus is
-applicable across the full range of modeling extremes.
+applicable across the full range of modeling fidelity.
 
-Fleet-based, lumped-material models do not distinguish between discrete
-facility entities or materials. However, some questions require resolution at the level of
-individual facilities and materials.
-As a result, many detailed performance
-metrics cannot be captured with previously existing fleet-based models.
+Fleet-based, lumped-material models do not distinguish between discrete facility
+entities or materials. However, some questions require resolution at the level
+of individual facilities and materials.  As a result, many detailed performance
+metrics cannot be captured with previously existing fleet-based models. For all
+of the reasons that the \gls{ABM} paradigm in \ref{sec:abm} enables novel
+simulations, multiple use cases require that these agents, such as the regions,
+institutions, and facilities in \Cyclus, must be represented as discrete
+objects. Furthermore, important use cases are enabled when materials and
+resources are tracked as discrete objects alongside those agents.
 
@@
 % Resources, Materials (note isotope tracking, decay behavior)
-
-For all of the reasons that the \gls{ABM} paradigm in \ref{sec:abm} enables
-novel simulations, multiple use cases require that these agents, such as the
-regions, institutions, and facilities in \Cyclus, must be represented as
-discrete objects. Furthermore, important use cases are enabled when materials
-and resources are tracked as discrete objects alongside those agents.
 
@@
 
-In order to avoid excess decay calculations, when decay
-is invoked, a material checks to see if it contains any nuclides with decay
-constants that are significant with respect to the time change since the last
-decay operation.  If none of the decay constants are significant, no decay
+When decay is invoked, A material checks to see if it contains any nuclides with
+decay constants that are significant with respect to the time change since the
+last decay operation.  If none of the decay constants are significant, no decay
 calculation is performed and the material remains unchanged.  This error does

### 2015-02-22 fundamentals/impl.tex
space after period

@@
 result in new compositions, those are cached for additional avoidance of
-redundancy.Composition immutability in concert with decay history caching help
+redundancy. Composition immutability in concert with decay history caching help
 eliminate many redundant decay calculations in addition to reducing the total

### 2015-02-22 fundamentals/impl.tex
cleaned up the dre intro a bit

@@
 
-Since the \Cyclus simulation paradigm allows discrete agents, based on archetypes
-about which the kernel has no knowledge, to enter
-the simulation at arbitrary times and
-trade in discrete resources that are not defined \textit{a priori},
-the logic engine defining resource interaction mechanisms
-among agents is crucial. The \gls{DRE} is that critical logic engine on which \Cyclus
-simulations are built.
-As the \Cyclus supply-demand resolution framework,
-the DRE must be able to support arbitrary facilities. Supporting the general
-\Cyclus philosophy, facilities are treated as black boxes and a clear
+The \Cyclus simulation paradigm allows discrete agents, based on archetypes
+about which the kernel has no knowledge, to enter the simulation at arbitrary
+times and trade in discrete resources. These resources are not defined \textit{a
+  priori}. Therefore, the logic engine defining resource interaction mechanisms
+among agents is crucial. The \gls{DRE} is that critical logic engine on which
+\Cyclus simulations are built.  As the \Cyclus supply-demand resolution
+framework, the DRE must be able to support arbitrary facilities. Supporting the
+general \Cyclus philosophy, facilities are treated as black boxes and a clear
 supply-demand communication framework is defined.

### 2015-02-22 fundamentals/impl.tex
the new intro sentence already made the arbitrary facility comment
the removed... too picky?

@@
 among agents is crucial. The \gls{DRE} is that critical logic engine on which
-\Cyclus simulations are built.  As the \Cyclus supply-demand resolution
-framework, the DRE must be able to support arbitrary facilities. Supporting the
-general \Cyclus philosophy, facilities are treated as black boxes and a clear
-supply-demand communication framework is defined.
+\Cyclus simulations are built.  Supporting the general \Cyclus philosophy,
+facilities are treated as black boxes and a clear supply-demand communication
+framework is defined.
 
@@
 \subsection{Simulation Support}
-So that users and developers can build working simulations
-in the shortest time possible, the \Cyclus ecosystem provides the fundamental
-building blocks: basic archetypes and a toolkit of commonly needed functions.
-The \Cycamore library provides a suite of fundamental Region, Institution, and
-Facility archetypes, while the \Cyclus toolkit provides assistance to
-developers.
+So that users and developers can build working simulations in the shortest time
+possible, the \Cyclus ecosystem provides fundamental building blocks: basic
+archetypes and a toolkit of commonly needed functions.  The \Cycamore library
+provides a suite of fundamental Region, Institution, and Facility archetypes,
+while the \Cyclus toolkit provides assistance to developers.
 

### 2015-02-22 fundamentals/examples.tex
swap capability and ecosystem in III

@@
 
-The success of the \Cyclus simulator can be measured in many ways.
-The most compelling are demonstrations of the feasibility of the \Cyclus community-driven development
-model and of fundamental simulation capability. Nascent promising growth of the \Cyclus
-ecosystem at multiple institutions indicates that a fuel cycle simulator can
-advance in this community-driven development paradigm. Additionally, simulation
-results for both once-through and more complex recycling scenarios demonstrate that
-\Cyclus possesses the fundamental fuel cycle simulation capabilities to
-contribute to the field.
+The success of the \Cyclus simulator can be measured in many ways.  The most
+compelling are demonstrations of fundamental simulation capability and of the
+feasibility of the \Cyclus community-driven development model. Nascent promising
+growth of the \Cyclus ecosystem at multiple institutions indicates that a fuel
+cycle simulator can advance in this community-driven development
+paradigm. Additionally, simulation results for both once-through and more
+complex recycling scenarios demonstrate that \Cyclus possesses the fundamental
+fuel cycle simulation capabilities to contribute to the field.
 

### 2015-02-22 fundamentals/examples.tex
cycstub typo

@@
 A number of projects and tools outside of the core simulation kernel have been
-developed to improve the scope and the diversity of the capabilities in the \Cyclus
-ecosystem. Table \ref{tab:coretools} lists the tools and projects developed
-under close integration with the \Cyclus kernel.  These tools are used to ease development
-and simulation design (Cystub, Cycic, Ciclus), data visualization and analysis (Cyclist, Cyan),
-and remote execution (Cloudlus).
+developed to improve the scope and the diversity of the capabilities in the
+\Cyclus ecosystem. Table \ref{tab:coretools} lists the tools and projects
+developed under close integration with the \Cyclus kernel.  These tools are used
+to ease development and simulation design (Cycstub, Cycic, Ciclus), data
+visualization and analysis (Cyclist, Cyan), and remote execution (Cloudlus).
 

### 2015-02-22 fundamentals/examples.tex
added single sentence paragraph to its neighbor
and -> among

@@
 
-Early progress has been promising. Many archetypes external to the \Cycamore library (Table \ref{tab:cycamore})
-have been
-\cite{huff_streamblender_2014,huff_commodconverter_2014}
-or are being
-\cite{flanagan_bright-lite_2014,skutnik_nuclear_2014,huff_mktdriveninst_2014} developed for contribution to the
-\Cyclus ecosystem. These archetypes provide the first examples of
-developer-contributed capabilities.  They add to the fundamental \Cycamore
-archetypes by providing physics-based reactors, separations logic, fuel
-fabrication processing, storage facilities, and expanded institutional paradigms.
+Early progress has been promising. Many archetypes external to the \Cycamore
+library (Table \ref{tab:cycamore}) have been
+\cite{huff_streamblender_2014,huff_commodconverter_2014} or are being
+\cite{flanagan_bright-lite_2014,skutnik_nuclear_2014,huff_mktdriveninst_2014}
+developed for contribution to the \Cyclus ecosystem. These archetypes provide
+the first examples of developer-contributed capabilities.  They add to the
+fundamental \Cycamore archetypes by providing physics-based reactors,
+separations logic, fuel fabrication processing, storage facilities, and expanded
+institutional paradigms.  The existence and diversity of these contributed
+archetypes illustrate the power and potential of the community-based development
+approach that \Cyclus has taken.
 
@@
 
-The existence and diversity of these contributed archetypes
-illustrate the power and potential of the community-based development approach
-that \Cyclus has taken.
-
 \subsection{Simulations}
@@
 This section will discuss the creation and results of a few simple fuel cycle
-simulations to help illustrate the flexibility of \Cyclus. These simulations
-are designed to illustrate Cyclus' capability.  Many simplifying assumptions
-have been made with respect to material compositions, fuel transmutation, and
+simulations to help illustrate the flexibility of \Cyclus. These simulations are
+designed to illustrate Cyclus' capability.  Many simplifying assumptions have
+been made with respect to material compositions, fuel transmutation, among
 others. The three fuel cycles examined are:

### 2015-02-23 fundamentals/impl.tex
cycamore listing now in rif order
consistent notation
made exclusive its own paragraph, closes #89

@@
 inventory of natural uranium or its total capacity to provide enrichment (SWUs), and
-attach such constraints to its bids. Any potential resource transfer may be denoted as
+attach such constraints to its bids.
+
+Any potential resource transfer, i.e., a bid or a request, may be denoted as
 \textit{exclusive}. An exclusive transfer must either be met fully or not at all
 in order to support concepts such as the trading of individual reactor
-assemblies.
+assemblies. In combination with the notion of mutual requests, complex instances
+of supply and demand are enabled.
 
@@
 
-As of version 1.0, \Cycamore contains four facility archetypes, one region
-archetype, and two institution archetypes. Short descriptions of these
-functions can be found in Table \ref{tab:cycamore}.
+As of version 1.0, \Cycamore contains one region archetype, two institution
+archetypes, and four facility archetypes. Short descriptions of these functions
+can be found in Table \ref{tab:cycamore}.
 
@@
  s.t. & \sum_{i=1}^{N}\phi_i y_i \ge \Phi \\
-      & n_i \in [0,\infty) \:\: \forall i \in I, \:\: y_i \:\: \text{integer}
+      & y_i \in [0,\infty) \:\: \forall i \in I, \:\: y_i \:\: \text{integer}
 \end{aligned}

### 2015-02-23 fundamentals/impl.tex

@@
 
-When decay is invoked, A material checks to see if it contains any nuclides with
+When decay is invoked, a material checks to see if it contains any nuclides with
 decay constants that are significant with respect to the time change since the

### 2015-02-23 fundamentals/intro.tex
kernel responsible for *supporting* deployment
daness is now used in industry by bcbva

@@
 
-Historically, domestic national laboratories have driven development and regulated
-the use of their own tools: \gls{VISION}\cite{jacobson_verifiable_2010},
-\gls{DANESS}\cite{van_den_durpel_daness_2009},
+Historically, domestic national laboratories have driven development and
+regulated the use of their own tools:
+\gls{VISION}\cite{jacobson_verifiable_2010},
 \gls{DYMOND}\cite{yacout_modeling_2005}, and
-\gls{NFCSim}\cite{schneider_nfcsim:_2005,allan_guidance_2008}.
-Internationally, other laboratories have created their own as well, such as
+\gls{NFCSim}\cite{schneider_nfcsim:_2005,allan_guidance_2008}.  Internationally,
+other laboratories have created their own as well, such as
 \gls{COSI}\cite{boucher_cosi_2005,boucher_cosi:_2006,meyer_new_2009,coquelet-pascal_comparison_2011}
-and
-\gls{ORION}\cite{worrall_scenario_2007}.
-Outside the national laboratories,
+and \gls{ORION}\cite{worrall_scenario_2007}.  Finally, some simulators initiated in a national lab setting have
+been continued as propriety, industry-based simulators, such as
+\gls{DANESS}\cite{van_den_durpel_daness_2009}.  Outside the national laboratories,
 researchers have created new nuclear fuel cycle simulation tools when existing
 tools were not available or not sufficiently general to calculate their metrics
-of interest.  With limited access to the national
-laboratory tools and a need to customize them for research purposes,
+of interest.  With limited access to the
+national laboratory tools and a need to customize them for research purposes,
 universities and private industry researchers have ``reinvented the wheel'' by
@@
 create a model of the entire fuel cycle to serve as its host.  \Cyclus supports
-them by separating the problem of modeling a physics-dependent supply chain
-into two distinct components: a simulation kernel and archetypes that interact
-with the kernel. The kernel is responsible for the deployment and interaction
-logic of entities in the simulation.  Physics calculations and customized
-behaviors are implemented within archetypes.
+them by separating the problem of modeling a physics-dependent supply chain into
+two distinct components: a simulation kernel and archetypes that interact with
+the kernel. The kernel is responsible for supporting the deployment and
+interaction logic of entities in the simulation.  Physics calculations and
+customized behaviors are implemented within archetypes.
 

### 2015-02-23 fundamentals/intro.tex
rm'd cafca example. it doesn't have great economic capability

@@
 can model a single aspect of the fuel cycle in great detail while neglecting
-others. For example, a simulator created for policy modeling might have
-excellent capability in economics while capabailities for tracking transformations in
-material isotopics and the effects of isotopics on technology performance are
-neglected.  The \gls{CAFCA}\cite{guerin_impact_2009} simulator is problem-oriented
-in this way, having elected to neglect isotopic resolution in favor of
-integral effects.
+others.
 

### 2015-02-23 fundamentals/impl.tex
tmp

@@
 
+    \item "lazy" (currently implemented) decays any material whenever its
+        composition is observed (e.g. when an agent queries information about
+        a material's $^{239}$Pu content).
+
     \item "periodic" (future) automatically decays all materials in a
         simulation with some fixed frequency.
-
-    \item "lazy" (future) decays any material whenever its composition is
-        viewed (e.g. when an agent queries information about a material's
-        $^{239}$Pu content).
 
@@
 
-\Cyclus has no notion of ``tracked'' versus ``untracked'' nuclides.  In \Cyclus, the composition of a material
-is represented by an arbitrarily large list (potentially thousands) of
-nuclides.  Agents are free to treat nuclides present in materials any way they
-please - including ignoring them.  It is the responsibility of archetype
-developers to choose how to handle potentially full-fidelity compositions.
+\Cyclus has no notion of ``tracked'' versus ``untracked'' nuclides.  In
+\Cyclus, the composition of a material is represented by an arbitrarily large
+list (potentially thousands) of nuclides.  Agents are free to treat nuclides
+present in materials any way they please - including ignoring them.  It is the
+responsibility of archetype developers to choose how to handle potentially
+full-fidelity compositions.
 
@@
 number of composition objects recorded in the database.
+
 \TODO{do we want a diagram helping show this composition caching?}

### 2015-02-23 fundamentals/impl.tex
add decay line cache figure and discussion

@@
 avoid unnecessary runtime performance and database size impacts, compositions
-in \Cyclus have some special features.  In particular, compositions are stored
-immutably in the database so that multiple material objects can hold references
-to the same composition safely.  Additionally, when transmutation and decay
-result in new compositions, those are cached for additional avoidance of
-redundancy. Composition immutability in concert with decay history caching help
-eliminate many redundant decay calculations in addition to reducing the total
-number of composition objects recorded in the database.
+in \Cyclus have some special features.  In particular, compositions are
+immutable once created.  This allows multiple material objects to hold
+references to the same composition safely.  Additionally, new compositions
+resulting from decay are cached and used to avoid redundant decay
+calculations.  Composition immutability in concert with decay history caching
+help eliminate many redundant calculations in addition to reducing the
+total number of composition entries recorded in the database.
 
-\TODO{do we want a diagram helping show this composition caching?}
+Figure \ref{fig:compositions} shows a set of four compositions A, B, C, and a
+yet-uncomputed decayed composition D.  B comes from decaying A 1 time step.  C
+comes from decaying B 2 time steps, etc.  Black represents the decay history
+cache for this particular composition chain. Blue represents decay
+calculations that are satisfied by cache lookups.   If A needs to be decayed 1
+time step (A +1), a lookup is performed on the decay line and B is found and
+returned - no decay calculation is performed and no new compositions need to
+be created or recorded.  Decaying B 3 time steps requires a decay calculation
+to compute D, but subsequent requests such as decaying A 4 time steps will not
+require any recalculation.
+
+\begin{figure}[htbp!]
+\begin{center}
+\includegraphics{./images/compositions}
+\end{center}
+\caption{Composition decay history chain helps avoid redundant decay calculations and reduce duplication in the database.}
+\label{fig:composition}
+\end{figure}
 

### 2015-02-23 fundamentals/impl.tex
move more into caption

@@
 resulting from decay are cached and used to avoid redundant decay
-calculations.  Composition immutability in concert with decay history caching
-help eliminate many redundant calculations in addition to reducing the
+calculations.  Figure \ref{fig:compositions} illustrates how this decay
+history cache works. Composition immutability in concert with decay history
+caching help eliminate many redundant calculations in addition to reducing the
 total number of composition entries recorded in the database.
-
-Figure \ref{fig:compositions} shows a set of four compositions A, B, C, and a
-yet-uncomputed decayed composition D.  B comes from decaying A 1 time step.  C
-comes from decaying B 2 time steps, etc.  Black represents the decay history
-cache for this particular composition chain. Blue represents decay
-calculations that are satisfied by cache lookups.   If A needs to be decayed 1
-time step (A +1), a lookup is performed on the decay line and B is found and
-returned - no decay calculation is performed and no new compositions need to
-be created or recorded.  Decaying B 3 time steps requires a decay calculation
-to compute D, but subsequent requests such as decaying A 4 time steps will not
-require any recalculation.
 
@@
 \end{center}
-\caption{Composition decay history chain helps avoid redundant decay calculations and reduce duplication in the database.}
-\label{fig:composition}
+\caption{
+A simple decay line cache holding compositions A, B, C, and a
+yet-uncomputed composition D.  B comes from decaying A 1 time step.  C comes
+from decaying B 2 time steps, etc.  Black represents the cache for this
+particular composition chain. Blue indicates decay operations that can be
+satisfied by cache lookups.   If A needs to be decayed 1 time step (A +1), a
+quick lookup returns the previously computed B.  Decaying B 3 time steps
+requires a decay calculation to compute a new composition D, but subsequent
+requests such as decaying A 4 time steps will not require any recalculation.
+}
+\label{fig:compositions}
 \end{figure}

### 2015-02-27 fundamentals/examples.tex
double period
then->than
some edits

@@
 compelling are demonstrations of fundamental simulation capability and of the
-feasibility of the \Cyclus community-driven development model. Nascent promising
+feasibility of the \Cyclus community-driven development model. Promising
 growth of the \Cyclus ecosystem at multiple institutions indicates that a fuel
@@
 The \Cyclus community-driven software development model seeks to break the
-unproductive proliferation of overspecialized simulators. It instead leverages
+proliferation of specialized simulators. It instead leverages
 the collective expertise of fuel cycle researchers toward a single, more
@@
         to static compositions when they are burnt and discharged from the
-        core.  . The reactor was configured to model a light water reactor
+        core. The reactor was configured to model a light water reactor
         with a 3 batch core (20,000 kg HM per batch) operating on an 18 month
@@
 each of the facilities.  The reactor was configured to request recycled \gls{MOX}
-fuel with a higher preference then new \gls{UOX} fuel. For the once through case,
+fuel with a higher preference than new \gls{UOX} fuel. For the once through case,
 the \Class{Reactor} was set to offer all spent fuel as waste.  For the 1-pass

### 2015-02-27 fundamentals/intro.tex
ORION isn't an acronym?
some edits

--- 2015-02-23 fundamentals/intro.tex
@@
 dynamic nuclear fuel cycle simulators have calculated fuel cycle mass balances
-and performance metrics derived from them using software ranging from ad hoc
+and performance metrics derived from them using software ranging from 
 spreadsheet-driven flow calculators to highly specialized system dynamics
-modeling platforms. To date, current tools are often rigid rather than flexible,
-fleet-based rather than discrete, or privately distributed rather than open
-source. Each of these choices presents a challenge to modeling fidelity,
+modeling platforms. To date, current tools are often rigid,
+fleet-based, or privately distributed. Each of these choices presents a challenge to modeling fidelity,
 generality, efficiency, robustness, and scientific transparency.
@@
 collaboration, increases software robustness \cite{cohen_modern_2010}, and
-cultivates an ecosystem of modeling and calculation options. This ecosystem is
+cultivates an ecosystem of modeling options. This ecosystem is
 comprised of flexible, interchangeable models of fuel cycle components with
@@
 \gls{COSI}\cite{boucher_cosi_2005,boucher_cosi:_2006,meyer_new_2009,coquelet-pascal_comparison_2011}
-and \gls{ORION}\cite{worrall_scenario_2007}.  Finally, some simulators initiated in a national lab setting have
+and ORION\cite{worrall_scenario_2007}.  Finally, some simulators initiated in a national lab setting have
 been continued as propriety, industry-based simulators, such as

### 2015-03-01 fundamentals/impl.tex
fix discussion of decay modes
Flanagan edits

@@
 in a fuel cycle context and the relative benefits thereof. A discussion of the
-time-dependent treatement of discrete resources follow, focusing on the
+time-dependent treatement of discrete resources follows, focusing on the
 \gls{DRE}. Support for users and developers via the \Cycamore library of
@@
 invoke the decay function on them as desired to decay them to the current
-simulation time. \Cyclus can currently operate in 2 decay modes, with 2 additional
-modes likely to be added in future releases:
+simulation time. \Cyclus can currently operate in 3 decay modes, with 1 additional
+mode likely to be added in a future release:
 

### 2015-03-02 fundamentals/conclusion.tex
To clarify phrasing as suggested by @flanflanagan

--- 2015-02-18 fundamentals/conclusion.tex
@@
 alternative to existing fuel cycle simulators. Where previous nuclear fuel cycle simulators have had limited distribution,
-uncertain provenance, and restricted customizability, \Cyclus emphasizes an
-open access and development strategy.  Open development, with transparent
+constrained simulation capabilities, and restricted customizability, \Cyclus emphasizes an
+open strategy for access and development.  This open strategy, with transparent
 publication of the source code, not only provides much-needed accessibility,

### 2015-03-02 fundamentals/conclusion.tex
less redundancy, as suggested by @flanflanagan
more clarity, as suggested by @flanflanagan

@@
 The \Cyclus nuclear fuel cycle framework presents a more generic and flexible
-alternative to existing fuel cycle simulators. Where previous nuclear fuel cycle simulators have had limited distribution,
-constrained simulation capabilities, and restricted customizability, \Cyclus emphasizes an
-open strategy for access and development.  This open strategy, with transparent
-publication of the source code, not only provides much-needed accessibility,
-but also enables transparency and community oversight.
+alternative to existing fuel cycle simulators. Where previous nuclear fuel
+cycle simulators have had limited distribution, constrained simulation
+capabilities, and restricted customizability, \Cyclus emphasizes an open
+strategy for access and development.  This open strategy not only improves
+accessibility, but also enables transparency and community oversight.
 
@@
 
-Similarly, discrete, fidelity-agnostic object tracking facilitates simulations
+Similarly the fidelity-agnostic modular architecture facilitates simulations
 at every level of detail. Simulations relying on arbitrarily complex isotopic

### 2015-03-02 fundamentals/intro.tex
clarifying archetype definition, as suggested by @flanflanagan

--- 2015-02-23 fundamentals/intro.tex
@@
 two distinct components: a simulation kernel and archetypes that interact with
-the kernel. The kernel is responsible for supporting the deployment and
+it. The kernel is responsible for supporting the deployment and
 interaction logic of entities in the simulation.  Physics calculations and
-customized behaviors are implemented within archetypes.
+customized behaviors of those entities are implemented within \emph{archetype}
+classes.
 

### 2015-03-02 fundamentals/intro.tex
spellcheck

@@
 
-The cardinal purpose of a dyamic nuclear fuel cycle simulator is to calculate
+The cardinal purpose of a dynamic nuclear fuel cycle simulator is to calculate
 the time- and facility-dependent mass flow through all or part the fuel cycle.
@@
 others. For example, a simulator created for policy modeling might have
-excellent capability in economics while capabailities for tracking transformations in
+excellent capability in economics while capabilities for tracking transformations in
 material isotopics and the effects of isotopics on technology performance are
@@
 nuclear fuel cycle analysis community to achieve two important goals: lower the
-barrier for innvoative nuclear technologies to be included in fuel cycle analysis
+barrier for innovative nuclear technologies to be included in fuel cycle analysis
 while improving the ability to compare simulations with and without those innovative

### 2015-03-02 fundamentals/impl.tex

@@
 
-A modular, \acrfull{ABM} approach is ideal for solving complex, coupled,
+A modular, \acrfull{ABM} approach is ideal for solving the coupled,
 physics-dependent supply chain problems involving material routing, facility
-deployment, and regional and institutional hierarchies. Additionally, the choice
+deployment, and regional and institutional hierarchies which arise in \Cyclus. Additionally, the choice
 to build \Cyclus on open source libraries in modern programming languages
@@
 flexible and powerful: cluster-ready software and dynamic libraries.  The
-\gls{ABM} framework is then described, focusing on how \gls{ABM} is implemented
-in a fuel cycle context and the relative benefits thereof. A discussion of the
-time-dependent treatement of discrete resources follows, focusing on the
+\gls{ABM} framework is then described, focusing on its implementation and benefits
+in a fuel cycle context. A discussion of the
+time-dependent treatment of discrete resources follows, focusing on the
 \gls{DRE}. Support for users and developers via the \Cycamore library of
@@
 defined.  This encapsulated `plug-in' design choice provides two major
-benefits. First, analysts across research institutions can take advantage of the
+benefits. First, analysts can take advantage of the
 simulation logic \gls{API} and archetype ecosystem when they apply \Cyclus to
-their specific problem.  A researcher can focus on creating or customizing
+their specific problem.  A modeler can focus on creating or customizing
 nuclear facility, institution, resource, and toolkit models within their
@@
 an analyst would like to compare the effect of using different models to
-determine the input fuel composition for fast reactors, a variety of fuel
+determine the input fuel composition for fast reactors, fuel
 fabrication archetypes can be developed and interchanged while keeping the rest
-of the fuel cycle fixed to compare fuel fabrication designs.
+of the models used in the simulation fixed.
 
@@
 
-Groundbreaking insights and new classes of problems can be investigated by
-leveraging modern massive computing resources.
+Innovative approaches to designing and optimizing robust fuel cycle strategies can become available by leveraging modern parallel computing resources.
+For example, large scale sensitivity analyses to quantify the dependence of fuel cycle outcomes on potentially hundreds of uncertain parameters would only be feasible in a massively parallelized environment.
 However, many fuel cycle simulators rely on \gls{COTS} and Windows-only software that limits
 performance on and compatibility with resource computing infrastructures. This
-severely constrains the possible scope of simulations and increases the wall-clock time necessary to conduct parameterized sensitivity
+constrains the possible scope of simulations and increases the wall-clock time necessary to conduct parameterized sensitivity
 analyses and other multi-simulation studies. \Cyclus, on the other hand, is
@@
 uses UW-Madison's HTCondor \gls{HTC} infrastructure to perform sensitivity
-studies on \Cyclus' resource exchange optimization solvers. To date, it has been
-used to run over $10^5$ jobs, comprising more than 60,000 total compute hours,
+studies on \Cyclus' resource exchange optimization solvers. Cyclopts has run over $10^5$ jobs, comprising more than 60,000 total compute hours,
 using the \Cyclus library via its resource exchange \gls{API}.  The \gls{HTC}
@@
 
-\Cyclus acheives this behavior by implementing its generic \gls{API} and
-modular architecture via a suite of dynamically loadable plug-in libraries, as
+\Cyclus achieves this behavior by implementing its generic \gls{API} and
+modular architecture via a suite of dynamically loadable plug-in libraries as
 pictured in Figure \ref{fig:framework}.
-Though common in modern software architecture, such a plug-in pattern has not
+Though common in modern software architecture, such a plug-in paradigm has not
 previously been implemented in a nuclear fuel cycle simulator. Dynamically
 loadable libraries are the primary mechanism for extending \Cyclus' capability.
-This approach provides encapsulation: the core framework operates
-independently from the individual plug-in libraries. Thus, any customization or
-extension is implemented only in the loadable library.
+The core framework operates
+independently from the plug-in libraries, and the APIs are designed to provide archetype developers with the tools needed to collect inputs required by their archetype as well as return outputs.
+Hence the libraries enable customization and extension of \Cyclus' capabilities independent of the core.
 
@@
 contributors to choose different distribution and licensing strategies
-for their contributions. By allowing models to have varied
-availability, the security concerns of developers can be
-assuaged (See Figure \ref{fig:modifiedopen}).
+for their contributions. Users and modelers control the accessibility of their archetypes and data sets (See Figure \ref{fig:modifiedopen}).
 In particular, since the clean plug-in architecture loads libraries without any
@@
 
-This last benefit of dynamically loadable libraries addresses
-another goal of \Cyclus: ubiquity amongst its potential user base. By
-engineering \Cyclus to easily handle varying levels of complexity, a single
+Finally, dynamically loadable libraries enable \Cyclus to easily handle varying levels of simulation complexity. Hence a single
 simulation engine can be used by both users interested in big-picture policy
-questions as well as users focused on more detailed, technical
-analyses. They merely choose their preferred level of fidelity from among the
+questions as well as users focused on detailed technical
+analyses. They merely choose their preferred level of modeling depth from among the
 available libraries in the ecosystem.
@@
 
-\Cyclus implements an \acrlong{ABM} paradigm.  \gls{ABM} is modern, sophisticated,
-true to reality, and incorporates modern computing resources.
-Furthermore, \gls{ABM} provides a natural
+\Cyclus implements an \acrlong{ABM} paradigm.  \gls{ABM} provides a natural
 perspective from which to model a given problem. In the nuclear fuel cycle
@@
 
-Furthermore, the \gls{ABM} paradigm is superior to system dynamics used in
+Furthermore, the \gls{ABM} paradigm is superior to the system dynamic approach used in
 current simulators.
@@
 Due to this plug-in architecture,
-implementations of actors in a given scenario can be easily
+implementations of agents in a given scenario can be easily
 interchanged. Critically, this novel functionality enables the comparison
@@
 In this way, a researcher can directly compare two different reactor modeling
-implementations (perhaps \Class{DetailedReactor} and \Class{SimpleReactor})
+implementations (perhaps the imaginary classes \Class{DetailedReactor} and \Class{SimpleReactor})
 simply by exchanging the two corresponding archetypes. That is, two reactor
 archetypes both inheriting from the \Class{Facility} class are indistinguishable
-from a simulation perspective. Two simulations, one using
-\Class{DetailedReactor} and the other using \Class{SimpleReactor} can therefore
-be compared directly to determine the whole-simulation impact of using one or the other model.
-This can be done with any agent type, where agents can be ``Regions,''
-``Institutions,'' or ``Facilities.''
+from a simulation perspective.  This can be done with any agent type, where agents can be ``Regions,'' ``Institutions,'' or ``Facilities.''
 
@@
 \Cyclus provides a novel representation of entities in the nuclear fuel cycle
-that reflects the reality in international nuclear power: production
-encompassing facilities, institutions managing those facilities, and regions. While
+that reflects the reality in international nuclear power: facilities implementing individual fuel cycle technologies, institutions managing those facilities, and regions providing geographical and political context for institutions and facilities.
+While
 few simulators have provided any notion of static regional
@@
 Two primary consequences arise from this structure. First, institutions are
-nominally
-responsible for deploying and decommissioning facilities. Accordingly, advanced
+nominally responsible for deploying and decommissioning facilities. Accordingly, advanced
 logic regarding building and decommissioning can be implemented on top of
@@
 all archetypes have access to the agent deployment mechanism. \Cyclus enables
-the developer to to implement agents that deploy copies of themselves, or that
+the developer to implement agents that deploy copies of themselves or
 schedule their own decommissioning.  Because regions, institutions, and
@@
 institutions, and facilities in \Cyclus, must be represented as discrete
-objects. Furthermore, important use cases are enabled when materials and
-resources are tracked as discrete objects alongside those agents.
+objects. For instance, tracking of individual shipments is only viable if materials and
+resources are tracked as discrete objects.
 
@@
 
-One such use case seeks to capture system vulnerability to nefarious
+Another such use case seeks to capture system vulnerability to
 material diversion. Provenance and trade-history of distinct materials is the fundamental
@@
 In \Cyclus, agents can transfer discrete resource objects among one another.
-Cyclus currently supports two types of resources:
+Cyclus supports two types of resources:
 
@@
 
-  \item Materials: These represent typical nuclear materials with
-      nuclide compositions.
+  \item materials: these represent typical nuclear materials with
+      nuclide compositions;
 
-  \item Products: These can represent any user-defined measure - e.g. carbon
-      credits, build permits, employees, etc.
+  \item products: these can represent any user-defined measure: carbon
+      credits, build permits, employees, etc..
 
@@
 possible to follow the history of resources as they are transferred between
-agents.  This powerfully impacts the ability to model
-non-proliferation-related simulation goals.
+agents.
 
@@
     \item "manual" (currently implemented) is the default mode
-        where agents decay materials as needed.
+        where agents decay materials as needed,
 
     \item "never" (currently implemented) globally turns off all decay.
-        The Material decay function does nothing.
+        The Material decay function does nothing,
 
@@
         composition is observed (e.g. when an agent queries information about
-        a material's $^{239}$Pu content).
-
+        a material's $^{239}$Pu content),
     \item "periodic" (future) automatically decays all materials in a
@@
 \Cyclus simulations are built.  Supporting the general \Cyclus philosophy,
-facilities are treated as black boxes and a clear supply-demand communication
+facilities are treated as black boxes and a supply-demand communication
 framework is defined.
@@
 facility's request for a resource is not met at a given time step, it may offer
-a request in the proceeding time step. Because agent behavior may change
+a request in the following time step. Because agent behavior may change
 arbitrarily, the exchange executed at any given time step may be unique in a
@@
 preferences. Accordingly, a wide range of possible effects can be
-modeled, from capacitaty-limited fuel supply to international trade agreements.
+modeled, from capacity-limited fuel supply to international trade agreements.
 
@@
 interface for querying the \textit{prototypes} which have the
-capacity to produce a given commdity. The \Class{CommodityProducerManager}
+capacity to produce a given commodity. The \Class{CommodityProducerManager}
 provides an interface for registering \Class{CommodityProducer}s and querying
@@
 ($\phi_i$), and costs ($c_i$).
+Here $i$ indexes $I$ available prototypes which perform a similar function, and the demand, capacity and cost carry prototype-specific units which are defined by the developer.
 
@@
 
-The \Cyclus toolkit provides two useful interfaces for querying physical paramaters of \Class{Material}
+The \Cyclus toolkit provides two useful interfaces for querying physical parameters of \Class{Material}
 objects. First, the \Class{MatQuery} module
@@
 
-In addition to those that already exist, new tools and computational patterns will
-emerge from the archetypes developed within the community of
-developers. As these tools gain adoption between projects and demonstrate their
+In addition to those that already exist, new tools will
+emerge from the archetypes developed by the community. As these tools gain adoption between projects and demonstrate their
 utility to the developer community, they will be considered for screening and
@@
 by third party archetype developers or users, the most important feature of
-\gls{QA} is verification. Validation may be impossible and \gls{UQ} is beyond
-the scope of the kernel.
+\gls{QA} is verification.
+Validation of the \Cyclus core in a general sense is infeasible as it is contingent on the archetypes comprising a simulation, and to be meaningful \gls{UQ} must likewise extend beyond the kernel.
 
@@
 It is important to note that before a proposed
-code change is allowed into \Cyclus,  the change must be covered by a test, either new or existing, and all of the tests must pass.  This is a
-matter of policy for the developers. Of course, test code is
+code change is allowed into \Cyclus,  the change must be covered by a test, either new or existing, and all tests must pass.  Of course, test code is
 just as likely to contain errors as the code it is designed to test.
@@
 
-Since these steps are performed for all incoming code, it is easyi for the
+Since these steps are performed for all incoming code, it is easy for the
 \Cyclus core team to determine whether or not an individual pull request

### 2015-03-02 fundamentals/impl.tex
addresses the concern that agents were not defined clearly before that vocabulary began to be used. The comment was 'readers may be confused by the meaning of 'agent' and 'process' in connection with the NFC and Cyclus.  Would it be possible to offer concise definitions?'

@@
 The architecture of \Cyclus allows developers to define nuclear fuel cycle
-agents and processes independent of the simulation logic. To achieve this,
-agents are developed using the \Cyclus framework \gls{API}, a set of functions
-and protocols which assist in agent development and specify how agents should be
-defined.  This encapsulated `plug-in' design choice provides two major
-benefits. First, analysts can take advantage of the
+processes independent of the simulation logic. To achieve this, agents are
+developed to represent facilities, institutions, and regions comprising the
+nuclear fuel cycle. These agents are created using the \Cyclus framework
+\gls{API}, a set of functions and protocols which assist in agent development
+and specify how agents should be defined.  This encapsulated `plug-in' design
+choice provides two major benefits. First, analysts can take advantage of the
 simulation logic \gls{API} and archetype ecosystem when they apply \Cyclus to

### 2015-03-02 fundamentals/impl.tex
addresses the concern that mention of the resource exchange may blindside readers. This was suggested by Erich Schneider. The original comment was ' This may blindside readers, as the resource exchange has not yet been introduced.  Maybe this level of information need not be provided here'

@@
 The architecture of \Cyclus allows developers to define nuclear fuel cycle
-processes independent of the simulation logic. To achieve this, agents are
-developed to represent facilities, institutions, and regions comprising the
+processes independent of the simulation logic. To achieve this, \emph{agents} are
+developed which represent facilities, institutions, and regions comprising the
 nuclear fuel cycle. These agents are created using the \Cyclus framework
@@
 uses UW-Madison's HTCondor \gls{HTC} infrastructure to perform sensitivity
-studies on \Cyclus' resource exchange optimization solvers. Cyclopts has run over $10^5$ jobs, comprising more than 60,000 total compute hours,
-using the \Cyclus library via its resource exchange \gls{API}.  The \gls{HTC}
-infrastructure has separately been utilized to run and collect information from
-full \Cyclus simulations running in parallel on $10^3$ machines reliably for
-order $10^5$ simulations.
+studies. Cyclopts has run over $10^5$ jobs, comprising more than 60,000 total
+compute hours. The \gls{HTC} infrastructure has separately been utilized to
+run and collect information from full \Cyclus simulations running in parallel
+on $10^3$ machines reliably for order $10^5$ simulations.
 

### 2015-03-02 fundamentals/impl.tex
addresses the concern that the ABM section intro was confusing. The comment from Erich was "Im still struggling with how to open this section. What is meant by the natural perspective"
addresses the comment from Erich 'what is the advantage of this?  Maybe the point is that these two agents can each be given different sets of rules governing how they will interact with the simulation.  Assumedly they're acting in their own best interest according to a simple, rational set of rules... but that's really up to the archetype modeler :)'

@@
 
-\Cyclus implements an \acrlong{ABM} paradigm.  \gls{ABM} provides a natural
-perspective from which to model a given problem. In the nuclear fuel cycle
-context, for example, an analyst can design a reactor agent
-that is entirely independent from a fuel fabrication agent. Defining the behavior of both agents according to the
+\Cyclus implements an \acrlong{ABM} paradigm. \gls{ABM} enables model
+development to take place at an agent level rather than a system level. In the
+nuclear fuel cycle context, for example, an analyst can design a reactor agent
+that is entirely independent from a fuel fabrication agent. Defining the
+behavior of both agents according to the
 \gls{API} contract is sufficient for them to interact with one another as
-bona fide actors in the simulation.  The two archetype libraries can be used in the same
-simulation without any shared knowledge.
+bona fide actors in the simulation.  The two archetype libraries can be used in
+the same simulation without any shared knowledge, allowing modelers to
+construct a simulation from building blocks of many types and origins.
 

### 2015-03-02 fundamentals/impl.tex
addresses the comment from Erich ' it feels like the APIs are important and more should be said about them.  Specifically to communicate to readers that Cyclus makes it easy to pass needed information from/to the rest of the simulation, and that the possible classes of needed information have been anticipated.'

@@
 
-\Cyclus achieves this behavior by implementing its generic \gls{API} and
-modular architecture via a suite of dynamically loadable plug-in libraries as
-pictured in Figure \ref{fig:framework}.
+\Cyclus achieves this behavior by implementing generic \glspl{API} and a
+modular architecture via a suite of dynamically loadable plug-in libraries
+(pictured in Figure \ref{fig:framework}). By anticipating the possible classes of
+information required by the simulation kernel, the \Cyclus \glspl{API}
+facilitate information passing between the plug-in agents and the core
+framework.
 Though common in modern software architecture, such a plug-in paradigm has not
-previously been implemented in a nuclear fuel cycle simulator. Dynamically
-loadable libraries are the primary mechanism for extending \Cyclus' capability.
-The core framework operates
-independently from the plug-in libraries, and the APIs are designed to provide archetype developers with the tools needed to collect inputs required by their archetype as well as return outputs.
-Hence the libraries enable customization and extension of \Cyclus' capabilities independent of the core.
+previously been implemented in a nuclear fuel cycle simulator.
+It allows the core \Cyclus framework to operate independently from the plug-in libraries, and the
+dynamically loadable plug-ins to be the primary mechanism for extending \Cyclus'
+capabilities independent of the core.
 

### 2015-03-02 fundamentals/impl.tex
addresses concern from Erich ' is there a distinction between agents and actors?  Using both terminologies may confuse people'

@@
 \gls{API} contract is sufficient for them to interact with one another as
-bona fide actors in the simulation.  The two archetype libraries can be used in
+bona fide agents in the simulation.  The two archetype libraries can be used in
 the same simulation without any shared knowledge, allowing modelers to
@@
 effects \cite{huff_next_2010,juchau_modeling_2010}, \Cyclus allows for both regions and institutions to be first-class
-actors in simulated fuel cycles. The fundamental interactions for each entity are implemented in a corresponding
+agents in simulated fuel cycles. The fundamental interactions for each entity are implemented in a corresponding
 archetype class in \Cyclus, i.e., the \Class{Region} class, \Class{Institution}

### 2015-03-02 fundamentals/impl.tex
Both @ Erich and @gonuke wanted to see this paragraph removed or de-emphasized because it muddies the RIF hierarchy concept as soon as it is introduced. It has therefore been deleted.

@@
 (e.g., long-term contracts).
-
-% the paragraph below muddies the concept of the RIF hierarchy
-% (perhaps an extended footnote?)
-% Either way, I prefer something other than ``provided explicitly''.
-
-Although the \Cyclus kernel is designed around the concept of the \gls{RIF} hierarchy,
-it can handle hierarchies of arbitrary depth.  It is capable of
-running a simulation without regions and institutions (i.e.  only facilities)
-or a simulation having archetypes that are the parents of regions. By
-convention, institutions are mainly responsible for facility deployment, but
-all archetypes have access to the agent deployment mechanism. \Cyclus enables
-the developer to implement agents that deploy copies of themselves or
-schedule their own decommissioning.  Because regions, institutions, and
-facilities are all just agents, they can all be implemented to exercise the
-full set of features offered by the \Cyclus kernel.
 

### 2015-03-02 fundamentals/impl.tex
addresses Erich's comment that ' difference between manual and lazy is not clear to me.  Specifically, what's the difference between 'decay as needed' and 'decay whenever queried'?'

@@
 \begin{itemize}
-
     \item "manual" (currently implemented) is the default mode
-        where agents decay materials as needed,
-
+        where agents decay materials when requested by an archetype,
     \item "never" (currently implemented) globally turns off all decay.
         The Material decay function does nothing,
-
-    \item "lazy" (currently implemented) decays any material whenever its
-        composition is observed (e.g. when an agent queries information about
-        a material's $^{239}$Pu content),
+    \item "lazy" (currently implemented) decays material automatically whenever
+         its composition is observed (e.g. when an agent queries information
+         about a material's $^{239}$Pu content),
     \item "periodic" (future) automatically decays all materials in a
         simulation with some fixed frequency.
-
 \end{itemize}

### 2015-03-02 fundamentals/impl.tex
addresses the concern by Erich: ' exclusive of what?  this isn't clear'

@@
 Any potential resource transfer, i.e., a bid or a request, may be denoted as
-\textit{exclusive}. An exclusive transfer must either be met fully or not at all
-in order to support concepts such as the trading of individual reactor
-assemblies.  In combination with the notion of mutual requests, complex instances
+\textit{exclusive}. An exclusive transfer excludes partial fulfilment; it must
+either be met fully or not at all. This mode supports concepts such as the
+trading of individual reactor assemblies.  In combination with the notion of
+mutual requests, complex instances
 of supply and demand are enabled.
@@
 or exchanges must be represented as a \gls{MILP}. If no exclusive trades exist,
-a \gls{LP} model may be used. In practice, LPs solve much faster than
-\gls{MILP}s. However, both capabilities exist in \Cyclus in order to
+a \gls{LP} model may be used. In practice, \glspl{LP} solve much faster than
+\glspl{MILP}. However, both capabilities exist in \Cyclus in order to
 provide users with the desired level of fidelity.

### 2015-03-02 fundamentals/impl.tex
addresses confusion about aggregate nuclides by deleting the phrase."

@@
 provides a basic querying \gls{API}, including the atom and mass fractions of
-nuclides, the number of moles of a nuclide in a material, and also the amount of
-aggregate nuclides, i.e., a \Class{Composition}, in a material. The
+nuclides, the number of moles of a nuclide in a material, etc. (i.e., a
+\Class{Composition}), in a material. The
 \Class{Enrichment} module provides an \gls{API} for determining enrichment-related

### 2015-03-02 fundamentals/impl.tex
gets rid of vague tools comment

@@
 modular nature of \Cyclus archetypes.  The core of the \Cyclus simulator creates
-a set of classes on which agent plug-ins are based. In addition, a set of tools
-are also provided to enrich the \gls{API} and supply a robust suite of behaviors
-for the developer. Agent plug-ins utilize the generic core \gls{API} to
-interact with one another.  For example, they use the resource exchange paradigm
-\gls{API} for trading resources with one another.
+a set of classes on which agent plug-ins are based.  Agent plug-ins utilize the
+generic core \gls{API} to interact with one another.  For example, they use the
+resource exchange paradigm \gls{API} for trading resources with one another.
 

### 2015-03-02 fundamentals/acks.tex
Adds acknowldegements draft. Still may need some explicit legal language for NEUP, NRC etc. Acknowledges @rakhimov and @zwelchWI, which fixes #45 and fixes #43

\section{Acknowledgements}
This work has been supported by a number of people. The authors
would like to thank software contributors Zach Welch and Olzhas Rakhimov.
Additionally, the authors are grateful to the many enthusiastic members of the
\Cyclus community and our \gls{NEUP} collaboration partners at the University
of Texas, University of Utah, and University of Idaho.

This work has received institutional support from \gls{ANL}, the \gls{NEUP},
the \gls{NRC}, the \gls{NSF}, and the \gls{UW}.

### 2015-03-02 fundamentals/impl.tex
removes paragraph about extra need for UQ and v&v because of external developers. This statement is true, but doesn't directly contribute to the purpose of this section: to convince readers that Cyclus has exceptional qa

@@
 That is, any system dynamics model can be translated
-into an agent-based model. Furthermore, because agent-based
-techniques can provide a richer model than can system dynamics, they enable the
-broadest range of simulations in a generic fashion.
+into an agent-based model.
+\gls{ABM} techniques therefore enable a broader range of simulations in a more
+generic fashion.
 
@@
 
-Since \Cyclus modeling decisions are made
-by third party archetype developers or users, the most important feature of
-\gls{QA} is verification.
-Validation of the \Cyclus core in a general sense is infeasible as it is contingent on the archetypes comprising a simulation, and to be meaningful \gls{UQ} must likewise extend beyond the kernel.
-
 Verification may be defined as the question, ``Is \Cyclus being built correctly?''

### 2015-03-02 fundamentals/impl.tex
since we only refer to UQ in order to say we don't do it, mentioning uq doesn't directly contribute to the purpose of this section: to convince readers that Cyclus has exceptional qa

@@
 in software. These include \emph{\gls{VV}}
-\cite{boehm_software_1989}, \emph{\gls{UQ}}
-\cite{sacks_design_1989}, testing, and others.
+\cite{boehm_software_1989}, testing, and others.
 
@@
 paradigms than supply substantial \gls{QA} and validation.
-
-Lastly, \gls{UQ} is a process that is used on specific simulation
-instantiations to statistically determine quality. \gls{UQ} is a process that applies
-to the running of many \Cyclus simulations. The kernel itself, as a generic fuel cycle
-simulator, cannot make reliable statements about the uncertainty of metrics for a particular fuel
-cycle. Any \gls{UQ} results are applicable only to the scenario that is under
-analysis by the user. \Cyclus is not a substitute for due diligence on behalf of the fuel
-cycle modeler. Thus, \gls{UQ} is envisioned to be beyond the scope of core development
-and in the domain of the expert user.
 

### 2015-03-02 fundamentals/impl.tex
removing sentences about testing the tests. I do think this is a very important point about QA and testing in general, but a bit too far into the weeds for this particular discussion, which needs to concisely focus on how cyclus has exceptional qa.
removing philosophical aside about how big a unit is. I do think this is well spoken and makes an important point about QA and testing in general, but again, I think it distracts somewhat from the focus on how cyclus has exceptional qa.

@@
 In \Cyclus, three categories of tests are defined: unit tests, integration
-tests, and regression tests.
-
-It is important to note that before a proposed
-code change is allowed into \Cyclus,  the change must be covered by a test, either new or existing, and all tests must pass.  Of course, test code is
-just as likely to contain errors as the code it is designed to test.
-However, it is assumed that diligence and one level of testing
-is sufficient to meet the aims of \gls{QA} and prevent an infinite recursion
-of testing-the-tests.
+tests, and regression tests.  It is important to note that before a proposed
+code change is allowed into \Cyclus,  the change must be covered by a test, either new or existing, and all tests must pass.
 
@@
 
-Unit tests compare the results of the smallest code \emph{unit},
-typically a single function or a class. What constitutes the smallest code
-unit depends on the context of the specific unit in question. While this is
-an ambiguous definition, when combined with a philosophy of keeping units as small
-as possible, it is often clear in practice what needs to be tested.
-
-\Cyclus uses the Google Test framework \cite{inc_googletest_2008} as a harness for running unit
-tests. Sufficient unit tests are required for any proposed change to the \Cyclus
-code base. Currently, \Cyclus implements over 450 unit tests and \Cycamore implements
-85.  These cover approximately 65\% of their respective code bases, and these numbers are expected to grow over time.
+Unit tests compare the results of the smallest code \emph{unit}, typically a
+single function or a class.  \Cyclus uses the Google Test framework
+\cite{inc_googletest_2008} as a harness for running unit tests. Sufficient unit
+tests are required for any proposed change to the \Cyclus code base. Currently,
+\Cyclus implements over 450 unit tests and \Cycamore implements 85.  These
+cover approximately 65\% of their respective code bases, and these numbers are
+expected to grow over time.
 

### 2015-03-02 fundamentals/impl.tex
reducing the length of sentence about subprocess tests. Keeps to the point: we use nose to do the comparison for each input file.

@@
 In \Cyclus and \Cycamore, integration tests are performed by running sample
-simulations for scenarios that are sufficiently simple to predict the results and verifying
-        that results match those predictions. A set of standard input files have thus been constructed.
-Python is used to run the same set of \Cyclus simulations as a subprocess for each integration test.
- The results are then inspected and compared via Nose \cite{pellerin_nose_2007}, a Python test framework.
-In this way, \Cyclus code units are tested in the full context that they will be
+simulations for scenarios that are sufficiently simple to predict the results
+and verifying that results match those predictions. A set of standard input
+files are run, then the output is inspected and compared via Nose
+\cite{pellerin_nose_2007}, a Python test framework.  In this way, \Cyclus code
+units are tested in the full context that they will be
 executed. This category of testing is especially useful for ensuring that

### 2015-03-02 fundamentals/impl.tex
removes redundant sentence about nose, for brevity
removes aside about the implementation of regression tests, for brevity

@@
 Regression tests are implemented similarly to integration tests.
-Nose is used to execute full \Cyclus simulations whose results
-are then compared. In this category, however, the comparison is done against
+In this category, however, the comparison is done against
 the output of the same input file when run with a previous version of \Cyclus,
@@
 not care about the contents of a simulation being correct, only whether or not
-it changed. They pick up glaring time-sensitive mistakes that may
-not appear elsewhere, though they do not purport to make claims about the
-quality of the physics modeled. Regression tests are primarily implemented
-in \Cycamore because its archetypes are sophisticated enough
-to make interesting simulations.
+it changed.
 

### 2015-03-02 fundamentals/impl.tex
simplifies sentences about documentation, reducing the number of generally-known facts about documentation.

@@
 All of the public interface (the \gls{API}) must be documented as required by the \Cyclus
-\gls{QA} policy. This certifies that the intention for a code unit is communicated
-in way that is separate from its implementation. This policy is important
-because implementations are often wrong and do not reliably communicate their intent. Truly trustworthy communication about what
-software should be doing occurs when the author explicitly states the
-goals of an \gls{API} in prose form. Future developers are then able to
+\gls{QA} policy. This certifies that the intended goals of an \gls{API} are communicated
+explicity by the author in prose form. Future developers are then able to
 compare the implementation versus the documentation to discern whether or not

### 2015-03-02 fundamentals/impl.tex
Well-written, but unnecessary platitude about documentation being deleted for brevity
Again, for brevity

@@
 
-All of the public interface (the \gls{API}) must be documented as required by the \Cyclus
-\gls{QA} policy. This certifies that the intended goals of an \gls{API} are communicated
-explicity by the author in prose form. Future developers are then able to
-compare the implementation versus the documentation to discern whether or not
-these are in agreement. Documentation is thus a secondary higher-level information
-stream.  In \Cyclus, this information is aggregated together into static
-websites with the Doxygen \cite{van_heesch_doxygen:_2008} and Sphinx
-\cite{brandl_sphinx_2014}
-tools, and can be accessed at \url{http://fuelcycle.org}.
+All of the public interface (the \gls{API}) must be documented as required by
+the \Cyclus \gls{QA} policy. This certifies that the intended goals of an
+\gls{API} are communicated explicity by the author in prose form.  In \Cyclus,
+this information is aggregated together into static websites with the Doxygen
+\cite{van_heesch_doxygen:_2008} and Sphinx \cite{brandl_sphinx_2014} tools, and
+can be accessed at \url{http://fuelcycle.org}.
 

### 2015-03-02 fundamentals/impl.tex
since the lowercasing of acronyms, it's hard to use their full form at the start of a sentence. I hackily have done this manually for CI in this case..

@@
 
-\emph{\acrfull{CI}} is the idea that software should be tested and validated
+\emph{Continuous integration (CI)} is the idea that software should be tested and validated
 as it is being developed, rather than as a final stage in a longer development

### 2015-03-02 fundamentals/impl.tex
spellcheck
I think this solves #85 with the 'changing all the text' strategy.

--- 2015-03-02 fundamentals/impl.tex
@@
 
-Interchangeability is accomplished by providing \glspl{API} that define agent-to-agent
-interaction and agent-to-environment interaction, primarily through the
-\Class{Agent} and \Class{Trader} interfaces. Figure \ref{fig:agent_uml} shows
-the ``inheritance'' structure of the \Class{Agent} class in a \gls{UML} diagram
-format. It shows how the \Class{Agent} interface
-provides a notion of parent-child hierarchical relationship, where parents can
-choose to \textit{deploy} child agents and \textit{decommission} child
-agents. For the archetype developer, this interface provides enormous power
-very simply. The \gls{API} provides the \Class{Agent} with helpful functionality for
-interacting with the \Cyclus simulation kernel while abstracting away unnecessary
-detail.
+Interchangeability is accomplished by providing inheritable \glspl{API} that define agent-to-agent
+interaction and agent-to-environment interaction. For example,
+an archetype that inherits the \Class{Region} interface, as in Figure
+\ref{fig:agent_uml}, is interchangeable with any other Region agent.
+For the archetype developer, this interface provides enormous power
+very simply. The \gls{API} abstracts away unnecessary detail while providing
+all necessary functionality for interacting with the \Cyclus simulation kernel.
 
@@
 in software. These include \emph{\gls{VV}}
-\cite{boehm_software_1989}, testing, and others.
+\cite{boehm_software_1989}, \emph{\gls{UQ}}
+\cite{sacks_design_1989}, testing, and others.
 
@@
 \cite{biondo_quality_2014}.
+
+Since \Cyclus modeling decisions are made
+by third party archetype developers or users, the most important feature of
+\gls{QA} is verification.
+Validation of the \Cyclus core in a general sense is infeasible as it is contingent on the archetypes comprising a simulation, and to be meaningful \gls{UQ} must likewise extend beyond the kernel.
 
@@
 
+Lastly, \gls{UQ} is a process that is used on specific simulation
+instantiations to statistically determine quality. \gls{UQ} is a process that applies
+to the running of many \Cyclus simulations. The kernel itself, as a generic fuel cycle
+simulator, cannot make reliable statements about the uncertainty of metrics for a particular fuel
+cycle. Any \gls{UQ} results are applicable only to the scenario that is under
+analysis by the user. \Cyclus is not a substitute for due diligence on behalf of the fuel
+cycle modeler. Thus, \gls{UQ} is envisioned to be beyond the scope of core development
+and in the domain of the expert user.
+
 Sections \ref{sec:qa-testing}-\ref{sec:qa-ci} discuss in greater detail the software
@@
 In \Cyclus, three categories of tests are defined: unit tests, integration
-tests, and regression tests.  It is important to note that before a proposed
-code change is allowed into \Cyclus,  the change must be covered by a test, either new or existing, and all tests must pass.
+tests, and regression tests.
+
+It is important to note that before a proposed
+code change is allowed into \Cyclus,  the change must be covered by a test, either new or existing, and all tests must pass.  Of course, test code is
+just as likely to contain errors as the code it is designed to test.
+However, it is assumed that diligence and one level of testing
+is sufficient to meet the aims of \gls{QA} and prevent an infinite recursion
+of testing-the-tests.
 
@@
 
-Unit tests compare the results of the smallest code \emph{unit}, typically a
-single function or a class.  \Cyclus uses the Google Test framework
-\cite{inc_googletest_2008} as a harness for running unit tests. Sufficient unit
-tests are required for any proposed change to the \Cyclus code base. Currently,
-\Cyclus implements over 450 unit tests and \Cycamore implements 85.  These
-cover approximately 65\% of their respective code bases, and these numbers are
-expected to grow over time.
+Unit tests compare the results of the smallest code \emph{unit},
+typically a single function or a class. What constitutes the smallest code
+unit depends on the context of the specific unit in question. While this is
+an ambiguous definition, when combined with a philosophy of keeping units as small
+as possible, it is often clear in practice what needs to be tested.
+
+\Cyclus uses the Google Test framework \cite{inc_googletest_2008} as a harness for running unit
+tests. Sufficient unit tests are required for any proposed change to the \Cyclus
+code base. Currently, \Cyclus implements over 450 unit tests and \Cycamore implements
+85.  These cover approximately 65\% of their respective code bases, and these numbers are expected to grow over time.
 
@@
 In \Cyclus and \Cycamore, integration tests are performed by running sample
-simulations for scenarios that are sufficiently simple to predict the results
-and verifying that results match those predictions. A set of standard input
-files are run, then the output is inspected and compared via Nose
-\cite{pellerin_nose_2007}, a Python test framework.  In this way, \Cyclus code
-units are tested in the full context that they will be
+simulations for scenarios that are sufficiently simple to predict the results and verifying
+        that results match those predictions. A set of standard input files have thus been constructed.
+Python is used to run the same set of \Cyclus simulations as a subprocess for each integration test.
+ The results are then inspected and compared via Nose \cite{pellerin_nose_2007}, a Python test framework.
+In this way, \Cyclus code units are tested in the full context that they will be
 executed. This category of testing is especially useful for ensuring that
@@
 Regression tests are implemented similarly to integration tests.
-In this category, however, the comparison is done against
+Nose is used to execute full \Cyclus simulations whose results
+are then compared. In this category, however, the comparison is done against
 the output of the same input file when run with a previous version of \Cyclus,
@@
 not care about the contents of a simulation being correct, only whether or not
-it changed.
+it changed. They pick up glaring time-sensitive mistakes that may
+not appear elsewhere, though they do not purport to make claims about the
+quality of the physics modeled. Regression tests are primarily implemented
+in \Cycamore because its archetypes are sophisticated enough
+to make interesting simulations.
 
@@
 All of the public interface (the \gls{API}) must be documented as required by the \Cyclus
-\gls{QA} policy. This certifies that the intended goals of an \gls{API} are communicated
-explicity by the author in prose form. Future developers are then able to
+\gls{QA} policy. This certifies that the intention for a code unit is communicated
+in way that is separate from its implementation. This policy is important
+because implementations are often wrong and do not reliably communicate their intent. Truly trustworthy communication about what
+software should be doing occurs when the author explicitly states the
+goals of an \gls{API} in prose form. Future developers are then able to
 compare the implementation versus the documentation to discern whether or not

### 2015-03-02 fundamentals/impl.tex
cleanup

@@
 \end{center}
-\caption{The \Cyclus core provides \gls{API}s that abstract away the details in
+\caption{The \Cyclus core provides \glspl{API} that abstract away the details in
 the kernel and allow the archetypes to be loaded into the simulation in a modular
@@
 \end{center}
-\caption{The inheritance in \Cyclus classes, such as the \Class{Agent},
-\Class{Facility}, \Class{Institution}, and \Class{Region} classes, abstract away
+\caption{Inheriting \Cyclus class interfaces, such as the \Class{Agent},
+\Class{Facility}, \Class{Institution}, and \Class{Region} classes, abstracts away
 unnecessary details while exposing powerful functionality. In the above

### 2015-03-02 fundamentals/impl.tex
fixes #94 with the 'just delete it' strategy. I cited the example given in the Simulations section instead

--- 2015-03-02 fundamentals/impl.tex
@@
 
-Interchangeability is accomplished by providing inheritable \glspl{API} that define agent-to-agent
-interaction and agent-to-environment interaction. For example,
-an archetype that inherits the \Class{Region} interface, as in Figure
-\ref{fig:agent_uml}, is interchangeable with any other Region agent.
-For the archetype developer, this interface provides enormous power
-very simply. The \gls{API} abstracts away unnecessary detail while providing
-all necessary functionality for interacting with the \Cyclus simulation kernel.
+Interchangeability is accomplished by providing \glspl{API} that define agent-to-agent
+interaction and agent-to-environment interaction, primarily through the
+\Class{Agent} and \Class{Trader} interfaces. Figure \ref{fig:agent_uml} shows
+the ``inheritance'' structure of the \Class{Agent} class in a \gls{UML} diagram
+format. It shows how the \Class{Agent} interface
+provides a notion of parent-child hierarchical relationship, where parents can
+choose to \textit{deploy} child agents and \textit{decommission} child
+agents. For the archetype developer, this interface provides enormous power
+very simply. The \gls{API} provides the \Class{Agent} with helpful functionality for
+interacting with the \Cyclus simulation kernel while abstracting away unnecessary
+detail.
 
@@
 
-As illustrated in
-Figure \ref{fig:simplesim}, the current \Cycamore release provides basic
-functionality enabling simple fuel cycle analyses. As future contributions are
-vetted, the capabilities in \Cycamore may grow.
-
-\begin{figure}[htbp!]
-\begin{center}
-\includegraphics{./images/simplesim}
-\end{center}
-\caption{Material flows through a simple dynamic simulation created with only the simplest \Cycamore archetypes, \Class{Sink} and \Class{Source}.}
-\label{fig:simplesim}
-\end{figure}
+Section \ref{sec:simulations} will demonstrate how the current \Cycamore
+release provides basic functionality enabling simple fuel cycle analyses. As
+future contributions are vetted, the capabilities in \Cycamore may grow.
 

### 2015-03-02 fundamentals/impl.tex
this fixes #95 by assuming that these facilities will appear in Cycamore 1.3

--- 2015-03-02 fundamentals/impl.tex
@@
 Facility & BatchReactor & A reactor model that handles batch refueling, based on pre-determined recipes of compositions. \\
+Facility & EnrichmentFacility & This facility enriches uranium at a specified capacity. \\
+Facility & Fab & This facility fabricates fuel material based on separated streams. \\
+Facility & Reactor & This facility, based on BatchReactor, requests any number of input fuel types and transmutes them to static compositions upon discharge.\\
+Facility & Separations & This facility separates an incoming material into specified streams. \\
+Facility & Sink & This facility is capable of accepting a finite or infinite quantity of some commodity produced in the simulation. \\
 Facility & Source & This facility generates material of the composition and commodity type specified as input.  \\
-Facility & Sink & This facility is capable of accepting a finite or infinite quantity of some commodity produced in the simulation. \\
-Facility & EnrichmentFacility & This facility enriches uranium at a specified capacity. \\
 Institution & ManagerInst & The manager institution manages production of commodities among its facilities by building new ones as needed. \\

### 2015-03-02 fundamentals/impl.tex
adds asterisk

--- 2015-03-02 fundamentals/impl.tex
@@
 As of version 1.0, \Cycamore contains one region archetype, two institution
-archetypes, and four facility archetypes. Short descriptions of these functions
-can be found in Table \ref{tab:cycamore}.
+archetypes, and four facility archetypes. Three additional facilities were
+added in version 1.3 . Short descriptions of these functions can be found in
+Table \ref{tab:cycamore}.
 
@@
 Facility & BatchReactor & A reactor model that handles batch refueling, based on pre-determined recipes of compositions. \\
+Facility & EnrichmentFacility & This facility enriches uranium at a specified capacity. \\
+Facility & Fab$^*$ & This facility fabricates fuel material based on separated streams. \\
+Facility & Reactor$^*$ & This facility, based on BatchReactor, requests any number of input fuel types and transmutes them to static compositions upon discharge.\\
+Facility & Separations$^*$ & This facility separates an incoming material into specified streams. \\
+Facility & Sink & This facility is capable of accepting a finite or infinite quantity of some commodity produced in the simulation. \\
 Facility & Source & This facility generates material of the composition and commodity type specified as input.  \\
-Facility & Sink & This facility is capable of accepting a finite or infinite quantity of some commodity produced in the simulation. \\
-Facility & EnrichmentFacility & This facility enriches uranium at a specified capacity. \\
 Institution & ManagerInst & The manager institution manages production of commodities among its facilities by building new ones as needed. \\
@@
 \end{tabularx}
-\caption{The Archetypes in \Cycamore seek to cover a large range of simple simulation use cases \cite{carlsen_cycamore_2014}.}
+\caption{The Archetypes in \Cycamore seek to cover a large range of simple
+simulation use cases \cite{carlsen_cycamore_2014}. Facilities added in version
+1.3 are marked with $^*$.}
 \label{tab:cycamore}

### 2015-03-02 fundamentals/impl.tex

@@
 \cite{biondo_quality_2014}.
-
-Since \Cyclus modeling decisions are made
-by third party archetype developers or users, the most important feature of
-\gls{QA} is verification.
-Validation of the \Cyclus core in a general sense is infeasible as it is contingent on the archetypes comprising a simulation, and to be meaningful \gls{UQ} must likewise extend beyond the kernel.
 
@@
 
-Lastly, \gls{UQ} is a process that is used on specific simulation
-instantiations to statistically determine quality. \gls{UQ} is a process that applies
-to the running of many \Cyclus simulations. The kernel itself, as a generic fuel cycle
-simulator, cannot make reliable statements about the uncertainty of metrics for a particular fuel
-cycle. Any \gls{UQ} results are applicable only to the scenario that is under
-analysis by the user. \Cyclus is not a substitute for due diligence on behalf of the fuel
-cycle modeler. Thus, \gls{UQ} is envisioned to be beyond the scope of core development
-and in the domain of the expert user.
-
 Sections \ref{sec:qa-testing}-\ref{sec:qa-ci} discuss in greater detail the software
@@
 
-All of the public interface (the \gls{API}) must be documented as required by the \Cyclus
-\gls{QA} policy. This certifies that the intention for a code unit is communicated
-in way that is separate from its implementation. This policy is important
-because implementations are often wrong and do not reliably communicate their intent. Truly trustworthy communication about what
-software should be doing occurs when the author explicitly states the
-goals of an \gls{API} in prose form. Future developers are then able to
-compare the implementation versus the documentation to discern whether or not
-these are in agreement. Documentation is thus a secondary higher-level information
-stream.  In \Cyclus, this information is aggregated together into static
-websites with the Doxygen \cite{van_heesch_doxygen:_2008} and Sphinx
-\cite{brandl_sphinx_2014}
-tools, and can be accessed at \url{http://fuelcycle.org}.
+All of the public interface (the \gls{API}) must be documented as required by
+the \Cyclus \gls{QA} policy. This certifies that the intended goals of an
+\gls{API} are communicated explicitly by the author in prose form.  In \Cyclus,
+this information is aggregated together into static websites with the Doxygen
+\cite{van_heesch_doxygen:_2008} and Sphinx \cite{brandl_sphinx_2014} tools, and
+can be accessed at \url{http://fuelcycle.org}.
 

### 2015-03-05 fundamentals/acks.tex
Massage the acknoledgements

@@
 
-This work has received institutional support from \gls{ANL}, the \gls{NEUP},
-the \gls{NRC}, the \gls{NSF}, and the \gls{UW}.
+Direct support for the \Cyclus project has been received from the \gls{NRC}
+Faculty Development program, the \gls{NEUP} Research \& Development Program,
+the \gls{NNSA} Consortium for Verification Technology, and the \gls{UW}.  In
+addition students contributing to \Cyclus have received fellowship support
+from the \gls{ANL} Lab Grad program, the \gls{NEUP} Fellowship program, the
+\gls{NSF} Graduate Fellowship program, and the \gls{DHS} Nuclear Forensics
+Graduate Fellowship program.

### 2015-03-11 fundamentals/abs.tex
takes out abs
adjusts abstract

@@
-As nuclear power expands both domestically and internationally, nuclear fuel cycle
-performance analysis on technical, economic, political, and environmental axes increases
-in importance. Appropriate nuclear fuel cycle analysis requires calculation of myriad physical, nuclear,
-chemical, industrial, and political phenomena. Nuclear fuel cycle simulators
-therefore couple complex systems such as nuclear process physics,
-facility deployment, and material routing. However, most nuclear fuel cycle
-simulators have not incorporated modern insights in simulation science and
-software architecture that can enable more efficient, accurate, robust, and
-validated analysis.
-
-An alternative to these approaches is a dynamic, agent-based simulator with an
-open platform and an ecosystem of research-driven capabilities.  Modern
-insight indicates that dynamic nuclear fuel cycle analysis more realistically
-supports a broader range of simulation goals than static analysis
-\cite{piet_dynamic_2011}. Similarly, experience in the broader field of systems
-analysis indicates that agent-based modeling enables more flexible simulation
-control, without loss of generality \cite{macal_agent-based_2010}. Finally, openness
-allows cross-institutional collaboration, increases software robustness, and
-enables the cultivation of an ecosystem of calculation options
-\cite{softwarecarpentryresource}.  The fundamental concepts of the \Cyclus
-nuclear fuel cycle simulator capture these modern insights so that challenges
-in nuclear fuel cycle analysis can be better addressed. A summary of the
-motivating use cases, an overview of the software architecture, and several
-representative solutions built on the framework are presented.
+The \Cyclus fuel cycle simulation framework and its modeling ecosystem are
+presented. This tool incorporates modeling methodologies to enable flexible
+simulation fidelity as well as contribution and collaboration among experts. To
+date, current tools are often rigid rather than flexible, fleet-based rather
+than discrete, or privately distributed rather than open source. Each of these
+choices presents a challenge to modeling fidelity, generality, efficiency,
+robustness, and scientific transparency.  \Cyclus incorporates modern insights
+from simulation science and software architecture to solve these problems so
+that challenges in nuclear fuel cycle analysis can be better addressed.
+Implementation of these insights in the \Cyclus framework and its modeling
+ecosystem is described. Finally, the current capabilities of \Cyclus are
+demonstrated for both an open and closed fuel cycle.

### 2015-03-11 fundamentals/abs.tex
embeds abstract

--- 2015-02-20 fundamentals/abs.tex
@@
+\begin{abstract}
 As nuclear power expands both domestically and internationally, nuclear fuel cycle
@@
 representative solutions built on the framework are presented.
+
+\end{abstract}

### 2015-03-11 fundamentals/abs.tex
abstract adjustment

--- 2015-03-11 fundamentals/abs.tex
@@
-The \Cyclus fuel cycle simulation framework and its modeling ecosystem are
-presented. This tool incorporates modeling methodologies to enable flexible
-simulation fidelity as well as contribution and collaboration among experts. To
-date, current tools are often rigid rather than flexible, fleet-based rather
+\begin{abstract}
+As nuclear power expands, technical, economic, political, and environmental
+analyses of nuclear fuel cycles by simulators increase in importance.  To date,
+however, current tools are often rigid rather than flexible, fleet-based rather
 than discrete, or privately distributed rather than open source. Each of these
 choices presents a challenge to modeling fidelity, generality, efficiency,
-robustness, and scientific transparency.  \Cyclus incorporates modern insights
-from simulation science and software architecture to solve these problems so
-that challenges in nuclear fuel cycle analysis can be better addressed.
-Implementation of these insights in the \Cyclus framework and its modeling
-ecosystem is described. Finally, the current capabilities of \Cyclus are
-demonstrated for both an open and closed fuel cycle.
+robustness, and scientific transparency.  The Cyclus nuclear fuel cycle
+simulator framework and its modeling ecosystem incorporate modern insights from
+simulation science and software architecture to solve these problems so that
+challenges in nuclear fuel cycle analysis can be better addressed.  A summary
+of the Cyclus fuel cycle simulator framework and its modeling ecosystem are
+presented. Additionally, implementation of each is discussed in the context of
+their motivating challenges in nuclear fuel cycle simulation.  Finally, the
+current capabilities of Cyclus are demonstrated for both an open and a closed
+fuel cycle.
+\end{abstract}

### 2015-03-11 fundamentals/examples.tex
adds label to simulation section}
fixes links and stuff in bib.

@@
 \cite{huff_streamblender_2014,huff_commodconverter_2014} or are being
-\cite{flanagan_bright-lite_2014,skutnik_nuclear_2014,huff_mktdriveninst_2014}
+\cite{flanagan_bright-lite_2014,skutnik_development_2015,huff_mktdriveninst_2014}
 developed for contribution to the \Cyclus ecosystem. These archetypes provide
@@
 Bright-lite & A physics-based reactor archetype and fuel fabrication archetype & \cite{flanagan_bright-lite_2014} \\
-Nuclear Fuel Inventory Model & A flexible, ORIGEN-based, reactor analysis module & \cite{skutnik_nuclear_2014} \\
+Nuclear Fuel Inventory Model & A flexible, ORIGEN-based, reactor analysis module & \cite{skutnik_development_2015} \\
 CommodConverter & A simple commodity converting storage facility archetype  & \cite{huff_commodconverter_2014} \\
@@
 \subsection{Simulations}
+\label{ref:simulation}
 %Inpro example (is this still running or did we deprecate it with 1.0?)

### 2015-03-11 cover_letter/cover_letter.tex
adds cover letter

% Plain Cover Letter
% LaTeX Template
%
% This template has been downloaded from:
% http://www.latextemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%       PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{letter} % Default font size of the document, change to 10pt to fit more text
\usepackage{graphicx}
%\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font
%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=10in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
%\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
%\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

%\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right
%\usepackage{wallpaper}
%\ULCornerWallPaper{0.97}{bk_logo.eps}

\begin{document}

%----------------------------------------------------------------------------------------
%       ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{N. Tsoulfanidis and A. Klein\\
Editors\\
Nuclear Technology}

%----------------------------------------------------------------------------------------
%       YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\begin{center}
\includegraphics[width=\textwidth]{bk_logo.eps}
\end{center}

\address{Department of Nuclear Engineering\\
4155 Etcheverry Hall\\
MC 1730\\
University of California, Berkeley\\
Berkeley, CA 94720-1730}

\name{\vspace{5mm}
Kathryn Huff\\
Postdoctoral Scholar\\
huff@berkeley.edu}

%----------------------------------------------------------------------------------------
%       LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{Dear Dr. Klein and Dr. Tsoulfanidis:}

Please find enclosed a manuscript entitled: ``Fundamental Concepts in the
Cyclus Fuel Cycle Simulator Framework and Modeling Ecosystem'' which I am
submitting for exclusive consideration of publication as a research article in
Nuclear Technology.

This manuscript describes the fundamental concepts in the Cyclus fuel cycle
simulator framework and its modeling ecosystem. These concepts and their
implementations are described in the context of motivating challenges in
nuclear fuel cycle simulation. Additionally, the current capabilities of Cyclus
are demonstrated for both an open and a closed fuel cycle.

We request that this manuscript be considered for joint publication alongside
Scopatz et al., ``Cyclus Archetypes.'' These two papers are complementary, and we
believe it would be ideal for both manuscripts to be published together in the
same issue of Nuclear Technology.

Thank you for your consideration of this work. I expect it will be of interest
to a broad readership concerned with nuclear fuel cycle simulation and
computational methods. Please address all correspondence concerning this
manuscript to me at UC Berkeley and feel free to correspond with me by e-mail.

\closing{Sincere regards,%
\\
\vspace{-20mm}\includegraphics[height=1.5cm]{signature.eps}
}
%----------------------------------------------------------------------------------------

\end{letter}

\end{document}

### 2015-03-11 fundamentals/abs.tex
plurality
make the abstract appear on a new page.
uses cyclus macro in abstract

@@
+\newpage
 \begin{abstract}
@@
 choices presents a challenge to modeling fidelity, generality, efficiency,
-robustness, and scientific transparency.  The Cyclus nuclear fuel cycle
+robustness, and scientific transparency.  The \Cyclus nuclear fuel cycle
 simulator framework and its modeling ecosystem incorporate modern insights from
@@
 challenges in nuclear fuel cycle analysis can be better addressed.  A summary
-of the Cyclus fuel cycle simulator framework and its modeling ecosystem are
-presented. Additionally, implementation of each is discussed in the context of
-their motivating challenges in nuclear fuel cycle simulation.  Finally, the
-current capabilities of Cyclus are demonstrated for both an open and a closed
+of the \Cyclus fuel cycle simulator framework and its modeling ecosystem are
+presented. Additionally, the implementation of each is discussed in the context
+of motivating challenges in nuclear fuel cycle simulation.  Finally, the
+current capabilities of \Cyclus are demonstrated for both an open and a closed
 fuel cycle.

### 2015-05-08 fundamentals/fcsreqs.tex
reviewer 2:page 6: typing errors: ...facilitate... ...particular agent

@@
 Moreover, both technical and institutional aspects of the software development
-practices employed by the \Cyclus community faciltate collaboration.
+practices employed by the \Cyclus community facilitate collaboration.
 Technically, \Cyclus employs a set of tools commonly used collaborative
@@
 within the \Cyclus framework.  Changes that are required to improve the
-fidelity of modeling a paticular agent, or to introduce entirely new agents,
+fidelity of modeling a particular agent, or to introduce entirely new agents,
 are narrowly confined and place no new requirements on the \Cyclus kernel.
@@
 \subsubsection{Discrete Facilities and Materials}
-
 Many fuel cycle phenomena have aggregate system-level effects which can only be
@@
 \cite{mccarthy_benchmark_2012,grasso_nea-wpfc/fcts_2009,guerin_benchmark_2009},
-\gls{DESAE}
-\cite{andrianova_desae_2008}, FAMILY21\cite{mccarthy_benchmark_2012},
+\DIFdelbegin 
+\DIFdel{\mbox{%DIFAUXCMD
+\gls{DESAE} \cite{andrianova_desae_2008}
+}%DIFAUXCMD
+, }\DIFdelend FAMILY21\cite{mccarthy_benchmark_2012},
 \gls{GENIUS} version 1, \gls{GENIUS} version 2, and \gls{NFCSim} also possess the ability to

### 2015-05-08 fundamentals/fcsreqs.tex
reviewer 2:page 6: typing errors: ...facilitate... ...particular agent

@@
 \subsubsection{Discrete Facilities and Materials}
+
 Many fuel cycle phenomena have aggregate system-level effects which can only be
@@
 \cite{mccarthy_benchmark_2012,grasso_nea-wpfc/fcts_2009,guerin_benchmark_2009},
-\DIFdelbegin 
-\DIFdel{\mbox{%DIFAUXCMD
-\gls{DESAE} \cite{andrianova_desae_2008}
-}%DIFAUXCMD
-, }\DIFdelend FAMILY21\cite{mccarthy_benchmark_2012},
+\gls{DESAE}
+\cite{andrianova_desae_2008}, FAMILY21\cite{mccarthy_benchmark_2012},
 \gls{GENIUS} version 1, \gls{GENIUS} version 2, and \gls{NFCSim} also possess the ability to

### 2015-05-08 fundamentals/intro.tex
restoring sentence with pairs.
Reviewer 2: page 3 (Background): With few exceptions, these metrics are derived from mass balances calculated by a fuel cycle simulator. [4]. : It would be nice to illustrate what are the few exceptions. Please read C. Poinssot, S. Bourg, N. Ouvrier, N. Combernoux, C. Rostaing, M. Vargas-Gonzalez et J. Bruno, Assessment of the environmental footprint of nuclear energy systems. Comparison between closed and open fuel cycles., Energy, n1In Press, pp. 1-13, 2014

@@
 spreadsheet-driven flow calculators to highly specialized system dynamics
-modeling platforms. To date, current tools are often rigid,
-fleet-based, or privately distributed. Each of these choices presents a challenge to modeling fidelity,
-generality, efficiency, robustness, and scientific transparency.
+modeling platforms. To date, current tools are often rigid rather than
+flexible, fleet-based rather than discrete, or privately distributed rather
+than open source. Each of these choices presents a challenge to modeling
+fidelity, generality, efficiency, robustness, and scientific transparency.
 
@@
 management impacts, safety, security and nonproliferation, resource adequacy
-and utilization, among others. With few exceptions, these metrics are derived
+and utilization, among others. With few exceptions (e.g. 
+\cite{poinssot_assessment_2014}, these metrics are derived
 from mass balances calculated by a fuel cycle simulator.

### 2015-05-08 fundamentals/impl.tex
Reviewer 2: page 18: SWUs please give a complete list of acronyms: here Separate Work Units

@@
 bids. For example, an enriched \gls{UOX} supplier may be constrained by its current
-inventory of natural uranium or its total capacity to provide enrichment (SWUs), and
-attach such constraints to its bids.
+inventory of natural uranium or its total capacity to provide enrichment 
+in \glspl{SWU}. It attaches such constraints to its bids.
 
@@
 \Class{Enrichment} module provides an \gls{API} for determining enrichment-related
-parameters of a material, including the separative work units (SWU) and natural
+parameters of a material, including the \gls{SWU} and natural
 uranium required to enrich a material provided knowledge of feed, product, and tails

### 2015-05-08 fundamentals/impl.tex
reviewer 2:page 23: typing error: and it cannot... but is cannot -> but it cannot
reviewer 2: page 20: What is BatchReactor?

@@
 \hline
-Facility & BatchReactor & A reactor model that handles batch refueling, based on pre-determined recipes of compositions. \\
+Facility & BatchReactor$^{**}$ & A reactor model that handles batch refueling, based on pre-determined recipes of compositions.\\
 Facility & EnrichmentFacility & This facility enriches uranium at a specified capacity. \\
 Facility & Fab$^*$ & This facility fabricates fuel material based on separated streams. \\
-Facility & Reactor$^*$ & This facility, based on BatchReactor, requests any number of input fuel types and transmutes them to static compositions upon discharge.\\
+Facility & Reactor$^*$ & This facility has capabilities of BatchReactor (above), and requests any number of input fuel types and transmutes them to static compositions upon discharge.\\
 Facility & Separations$^*$ & This facility separates an incoming material into specified streams. \\
@@
 simulation use cases \cite{carlsen_cycamore_2014}. Facilities added in version
-1.3 are marked with $^*$.}
+1.3 are marked with $^*$. Facilities deprecated in version 1.3 are marked with 
+$^{**}$.}
 \label{tab:cycamore}
@@
 development components that comprise the \Cyclus verification strategy.
-Each of these on its own is a valuable addition to \gls{QA} but is cannot be the
+Each of these on its own is a valuable addition to \gls{QA} but it cannot be the
 entire answer to the requirements imposed by \gls{NQA1}. Taken together and strictly

### 2015-05-08 fundamentals/intro.tex
Reviewer 2: The manuscript has the following title: Fundamental Concepts in the Cyclus Fuel Cycle Simulator Framework and Modeling Ecosystem. It is not clear to me what and Modeling Ecosystem refers to.. Adds phrase to explain modeling ecosystem on first mention.

@@
 
-The \Cyclus nuclear fuel cycle simulator framework and its modeling ecosystem
+The \Cyclus nuclear fuel cycle simulator framework and its modeling ecosystem, 
+the suite of agents and other physics plugins compatible with it,
 incorporate modern insights from simulation science and software architecture

### 2015-05-08 fundamentals/intro.tex
fixes hanging paren

@@
 management impacts, safety, security and nonproliferation, resource adequacy
-and utilization, among others. With few exceptions (e.g. 
-\cite{poinssot_assessment_2014}, these metrics are derived
+and utilization, among others \cite{flicker_evaluation_2014}. With few 
+exceptions (e.g.  \cite{poinssot_assessment_2014}), these metrics are derived 
 from mass balances calculated by a fuel cycle simulator.
-\cite{flicker_evaluation_2014}.
 

### 2015-05-08 fundamentals/intro.tex
Reviewer 1: IA: would be good to mention that such simulators can be used both for questions addressing operational facets of nuclear energy systems, e.g. interim UNF storage optimisation,as well as 'strategic' questions allowing to address R&D-options assessment.

@@
 options.  The feasibility of the technology development and deployment
-strategies which comprise a fuel cycle option, the dynamics of transitions
-between fuel cycles, and many other measures of performance can be expressed in
-terms of these metrics. For example, economic feasibility is often measured in
-\gls{LCOE}, requiring calculation of lifetime
-fuel costs and electricity generation, while environmental performance might be
-measured by spent fuel volume, toxicity, or mined uranium.  A meta-analysis of
-fuel cycle systems studies identified over two dozen unique quantitative
-metrics spanning economics and cost, environmental sustainability and waste
-management impacts, safety, security and nonproliferation, resource adequacy
-and utilization, among others \cite{flicker_evaluation_2014}. With few 
-exceptions (e.g.  \cite{poinssot_assessment_2014}), these metrics are derived 
-from mass balances calculated by a fuel cycle simulator.
+strategies which comprise a fuel cycle option, the operational features of
+nuclear energy systems, the dynamics of transitions between fuel cycles, and
+many other measures of performance can be expressed in terms of these metrics.
+For example, economic feasibility is often measured in \gls{LCOE}, requiring
+calculation of lifetime fuel costs and electricity generation, while
+environmental performance might be measured by spent fuel volume, toxicity, or
+mined uranium.  A meta-analysis of fuel cycle systems studies identified over
+two dozen unique quantitative metrics spanning economics and cost,
+environmental sustainability and waste management impacts, safety, security and
+nonproliferation, resource adequacy and utilization, among others
+\cite{flicker_evaluation_2014}. With few exceptions (e.g.
+\cite{poinssot_assessment_2014}), these metrics are derived from mass balances
+calculated by a fuel cycle simulator.
 

### 2015-05-11 fundamentals/impl.tex
updates prelim citation to thesis. closes #78

--- 2015-03-02 fundamentals/impl.tex
@@
 optimally using a mathematical program or approximately by a simulation-based
-heuristic \cite{gidden_agent-based_2014}. If any trade is denoted as exclusive, e.g., if an
+heuristic \cite{gidden_agent-based_2015}. If any trade is denoted as exclusive, e.g., if an
 analyst desires an assembly-fidelity model, then either a heuristic must be used

### 2015-05-12 fundamentals/impl.tex
1.3

--- 2015-05-08 fundamentals/impl.tex
@@
 \hline
-Facility & BatchReactor$^{**}$ & A reactor model that handles batch refueling, based on pre-determined recipes of compositions.\\
 Facility & EnrichmentFacility & This facility enriches uranium at a specified capacity. \\
 Facility & Fab$^*$ & This facility fabricates fuel material based on separated streams. \\
-Facility & Reactor$^*$ & This facility has capabilities of BatchReactor (above), and requests any number of input fuel types and transmutes them to static compositions upon discharge.\\
+Facility & Reactor$^*$ & A reactor model that handles batch refueling, based on pre-determined recipes of compositions.
+It requests any number of input fuel types and transmutes them to static compositions upon discharge.\\
 Facility & Separations$^*$ & This facility separates an incoming material into specified streams. \\

### 2015-05-26 fundamentals/fcsreqs.tex
Reviewer 1: "IB.iii: The simulation codes with discrete materials tracking are: COSI, FAMILY21, GENIUS 1 and 2, DANESS, NFCSim and ORION. DESAE doesn't. Not clear about VISION. DYMOND didn't neither." Removes DESAE.

@@
 \cite{mccarthy_benchmark_2012,grasso_nea-wpfc/fcts_2009,guerin_benchmark_2009},
-\gls{DESAE}
-\cite{andrianova_desae_2008}, FAMILY21\cite{mccarthy_benchmark_2012},
-\gls{GENIUS} version 1, \gls{GENIUS} version 2, and \gls{NFCSim} also possess the ability to
-model discrete materials.
+FAMILY21\cite{mccarthy_benchmark_2012},
+\gls{GENIUS} version 1, \gls{GENIUS} version 2, \gls{NFCSim}, and ORION also 
+possess the ability to model discrete materials.
 

### 2015-05-26 fundamentals/intro.tex
Thanks @gidden

@@
 nonproliferation, resource adequacy and utilization, among others
-\cite{flicker_evaluation_2014}. With few exceptions (e.g.
-\cite{poinssot_assessment_2014}), these metrics are derived from mass balances
-calculated by a fuel cycle simulator.
+\cite{flicker_evaluation_2014}. With few exceptions these metrics are derived from 
+mass balances and facility operation history calculated by a fuel cycle 
+simulator. For example, where nuclear waste repository burden is derived from 
+ejected fuel masses, water pollution or land use can be derived from facility 
+operational histories (as in \cite{poinssot_assessment_2014}).
 

### 2015-07-13 fundamentals/intro.tex
fixes #124

--- 2015-05-08 fundamentals/intro.tex
@@
 spreadsheet-driven flow calculators to highly specialized system dynamics
-modeling platforms. To date, current tools are often rigid rather than
-flexible, fleet-based rather than discrete, or privately distributed rather
-than open source. Each of these choices presents a challenge to modeling
-fidelity, generality, efficiency, robustness, and scientific transparency.
+modeling platforms. To date, current tools are often fleet-based rather than
+discrete and privately distributed rather than open source. These choices both
+present challenges to modeling fidelity, generality, efficiency, robustness,
+and scientific transparency.
 
-The \Cyclus nuclear fuel cycle simulator framework and its modeling ecosystem, 
-the suite of agents and other physics plugins compatible with it,
+The \Cyclus nuclear fuel cycle simulator framework and its modeling ecosystem
 incorporate modern insights from simulation science and software architecture
@@
 management impacts, safety, security and nonproliferation, resource adequacy
-and utilization, among others \cite{flicker_evaluation_2014}. With few 
-exceptions (e.g.  \cite{poinssot_assessment_2014}), these metrics are derived 
+and utilization, among others. With few exceptions, these metrics are derived
 from mass balances calculated by a fuel cycle simulator.
+\cite{flicker_evaluation_2014}.
 

### 2015-07-13 fundamentals/impl.tex
version 1.3"

@@
 simulation use cases \cite{carlsen_cycamore_2014}. Facilities added in version
-1.3 are marked with $^*$. Facilities deprecated in version 1.3 are marked with 
-$^{**}$.}
+1.3 are marked with $^*$. 
 \label{tab:cycamore}

### 2015-07-13 fundamentals/intro.tex

--- 2015-05-26 fundamentals/intro.tex
@@
 spreadsheet-driven flow calculators to highly specialized system dynamics
-modeling platforms. To date, current tools are often rigid rather than
-flexible, fleet-based rather than discrete, or privately distributed rather
-than open source. Each of these choices presents a challenge to modeling
-fidelity, generality, efficiency, robustness, and scientific transparency.
+modeling platforms. To date, current tools are often fleet-based rather than
+discrete and privately distributed rather than open source. These choices both
+present challenges to modeling fidelity, generality, efficiency, robustness,
+and scientific transparency.
 

### 2015-07-13 fundamentals/examples.tex
reviewer 2: page 20: bad reference for:  Section ??
fixes #121 according to suggestion given by @gidden"

@@
 \subsection{Simulations}
-\label{ref:simulation}
+\label{ref:simulations}
 %Inpro example (is this still running or did we deprecate it with 1.0?)
@@
 This section will discuss the creation and results of a few simple fuel cycle
-simulations to help illustrate the flexibility of \Cyclus. These simulations are
-designed to illustrate Cyclus' capability.  Many simplifying assumptions have
-been made with respect to material compositions, fuel transmutation, among
-others. The three fuel cycles examined are:
+simulations to help illustrate the flexibility of \Cyclus. These examples are
+not the limit of \Cyclus' capabilities, which are extended with each new
+addition to the ecosystem, as discussed above.  Rather, these simulations are
+designed to illustrate that \Cyclus has capabilities matching those of any
+recipe-based simulator.  Accordingly, many simplifying assumptions have been
+made with respect to material compositions, fuel transmutation, among others.
+The three fuel cycles examined are:
 

### 2015-07-14 fundamentals/intro.tex
toward a solution to #116, I add more description of fleet-based on first mention. Additional description of fleet based and the challenges presented can be discussed.

@@
 spreadsheet-driven flow calculators to highly specialized system dynamics
-modeling platforms. To date, current tools are often fleet-based rather than
-discrete and privately distributed rather than open source. These choices both
-present challenges to modeling fidelity, generality, efficiency, robustness,
-and scientific transparency.
+modeling platforms. To date, current tools are typically privately distributed
+rather than open source and most acheive only fleet-level resolution of
+facilities and materials rather than discrete resolution of those agents and
+objects. Both choices present challenges to modeling fidelity, generality,
+efficiency, robustness, and scientific transparency.
 

### 2015-07-14 fundamentals/fcsreqs.tex
Fixes #116, using comments from @rwcarlsen

@@
 possess the ability to model discrete materials.
+However, even among these, the ability to model reactor facilities individually is not equivalent to the ability to model distinct activities.
+\gls{COSI}, for example,
+has some support for modeling reactors individually, but according to a recent benchmark \cite{oecd_benchmark_2012}, it models many reactors operating in sync.
+That is, refuelling and discharging occur simultaneously for all reactors.
+While \Cyclus allows this type of fleet-based aggregation of reactor behavior, \Cyclus also enables operations in each facility to vary independently of any others in the simulation.
 
@@
 discrete facilities \cite{huff_next_2010}.  Fleet-based models (e.g.
-\gls{VISION}) are unable to capture this gracefully, perhaps representing it as
-a reduction in the capacity of the whole fleet.  All of the software
-capable of discrete materials have a notion of discrete facilities, however not
-all handle disruption in the same manner. \gls{DESAE}, for example, does not
-allow shutdown due to insufficient feedstock. In the event
-of insufficient fissile material during reprocessing, \gls{DESAE} borrows
-material from storage, leaving a negative value \cite{mccarthy_benchmark_2012}.
-The \Cyclus framework does not dictate such heuristics. Rather, it provides a
+\gls{VISION}) are unable to capture this gracefully, since supply disruptions
+are modeled as a reduction in the capacity of the whole fleet.  All of the
+software capable of discrete materials have a notion of discrete facilities,
+however not all handle disruption in the same manner. \gls{DESAE}, for example,
+does not allow shutdown due to insufficient feedstock. In the event of
+insufficient fissile material during reprocessing, \gls{DESAE} borrows material
+from storage, leaving a negative value \cite{mccarthy_benchmark_2012}.  The
+\Cyclus framework does not dictate such heuristics. Rather, it provides a
 flexible framework on which either method is possible.
+
+A final benefit of the discreteness of facilities and materials is their power
+when combined. The ability to track a material's history as it moves from one
+facility to another is unique to \Cyclus. While some current simulators track
+materials in chunks, they do not necessarily preserve chunk identity as the
+materials move around the fuel cycle. When coupled with \Cyclus' individual
+facility modeling, this capacity becomes distinct from what other fuel cycle
+simulators are able to do. So, while FAMILY21 and \gls{COSI} can identify
+whether a batch being discharged from a reactor originated in \gls{MOX}
+fabrication rather than fresh \gls{UOX} fabrication, \Cyclus can go further,
+tracking which of the fresh batches contained material from a particular
+discharged batch. By extension, \Cyclus can also report which individual
+facilities the batch passed through and in which it originated. The
+nonproliferation-related applications of this analysis capability are
+significant - allowing \Cyclus to answer questions that previous simulators
+have been unable to ask.

### 2015-07-15 fundamentals/intro.tex
helps with #116

--- 2015-07-13 fundamentals/intro.tex
@@
 factors. Nuclear fuel cycle simulators must therefore couple complex models of
-nuclear process physics, facility deployment, and material routing. However,
-current fuel cycle simulators rely on closed platforms and inflexible
-architectures which exhibit three main failure modes. First, they discourage
-targeted contribution and collaboration among experts. Next, they hobble
-efforts to directly compare modeling methodologies. Finally, they
-over-specialize, rendering most tools applicable to only a subset of desired
-simulation fidelities, scales, and applications.
+nuclear process physics, facility deployment, and material routing.
 
-The cardinal purpose of a dynamic nuclear fuel cycle simulator is to calculate
+Indeed, the cardinal purpose of a dynamic nuclear fuel cycle simulator is to calculate
 the time- and facility-dependent mass flow through all or part the fuel cycle.
@@
 spreadsheet-driven flow calculators to highly specialized system dynamics
-modeling platforms. To date, current tools are often fleet-based rather than
-discrete and privately distributed rather than open source. These choices both
-present challenges to modeling fidelity, generality, efficiency, robustness,
-and scientific transparency.
+modeling platforms.
 
-The \Cyclus nuclear fuel cycle simulator framework and its modeling ecosystem, 
-the suite of agents and other physics plugins compatible with it,
+To date, current tools are typically privately distributed rather than open
+source, having been developed in industrial contexts.  Additionally, having
+often been developed for customized applications, many possess inflexible
+architectures. Finally, many model only fleet-level dynamics of facilities and
+materials rather than discrete resolution of those individual agents and
+objects.  Those software choices exhibit three main failure modes which present
+significant challenges to modeling fidelity, generality, efficiency,
+robustness, and scientific transparency. First, they discourage targeted
+contribution and collaboration among experts. Next, they hobble efforts to
+directly compare modeling methodologies. Finally, they over-specialize,
+rendering most tools applicable to only a subset of desired simulation
+fidelities, scales, and applications.
+
+The \Cyclus nuclear fuel cycle simulator framework and its \emph{modeling
+ecosystem}, the suite of agents and other physics plugins compatible with it,
 incorporate modern insights from simulation science and software architecture
@@
 
-\Cyclus, is a dynamic, agent-based model, which employs a modular architecture,
+\Cyclus is a dynamic, agent-based model, which employs a modular architecture,
 an open development process, discrete agents, discrete time, and arbitrarily

### 2015-07-15 fundamentals/intro.tex
helps with #120

@@
 collaboration, increases software robustness \cite{cohen_modern_2010}, and
-cultivates an ecosystem of modeling options. This ecosystem is
-comprised of flexible, interchangeable models of fuel cycle components with
-varying scope, depth, and fidelity. It allows users and developers to customise
-\Cyclus to analyze the cases that are of interest to them, rather than those the
-simulator was originally developed to address.  The fundamental concepts of the
-\Cyclus nuclear fuel cycle simulator capture these modern insights so that novel
+cultivates an ecosystem of modeling options. This ecosystem is \emph{modular},
+being comprised of flexible, interchangeable models of fuel cycle component
+process physics that vary in their scope, depth, and fidelity. This modularity
+allows users and developers to customise \Cyclus to analyze the cases that are
+of interest to them, rather than any custom applicaiton the simulator was
+originally developed to address.  The fundamental concepts of the \Cyclus
+nuclear fuel cycle simulator capture these modern insights so that novel
 challenges in nuclear fuel cycle analysis can be better addressed.

### 2015-07-15 fundamentals/impl.tex
fixes build error from missing curly brace
used some emphasis to reduce jargon-y nature of the various terms

@@
 section begins by describing the general design features that make \Cyclus both
-flexible and powerful: cluster-ready software and dynamic libraries.  The
+flexible and powerful: \emph{cluster-ready software} and \emph{dynamically
+loadable libraries}.  The
 \gls{ABM} framework is then described, focusing on its implementation and benefits
@@
 \Cycamore \cite{carlsen_cycamore_2014}, the \Cyclus additional module
-repository, provides a fundamental set of agent archetypes for basic simulation
+repository, provides a fundamental set of dynamically loadable libraries
+providing agent archetypes for basic simulation
 functionality within \Cyclus.  Since \Cyclus relies on external
@@
 simulation use cases \cite{carlsen_cycamore_2014}. Facilities added in version
-1.3 are marked with $^*$. 
+1.3 are marked with $^*$.}
 \label{tab:cycamore}
@@
 The \Cyclus toolkit provides two useful interfaces for querying physical parameters of \Class{Material}
-objects. First, the \Class{MatQuery} module
+objects. First, the \Class{MatQuery} tool
 provides a basic querying \gls{API}, including the atom and mass fractions of
@@
 \Class{Composition}), in a material. The
-\Class{Enrichment} module provides an \gls{API} for determining enrichment-related
+\Class{Enrichment} tool provides an \gls{API} for determining enrichment-related
 parameters of a material, including the \gls{SWU} and natural

### 2015-07-15 fundamentals/intro.tex
used some emphasis to reduce jargon-y nature of the various terms

@@
 many other measures of performance can be expressed in terms of these metrics.
-For example, economic feasibility is often measured in \gls{LCOE}, requiring
-calculation of lifetime fuel costs and electricity generation, while
+For example, economic feasibility is often measured in \gls{LCOE}, a
+combination of fuel and operating costs normalized by electricity generation, while
 environmental performance might be measured by spent fuel volume, toxicity, or
@@
 nonproliferation, resource adequacy and utilization, among others
-\cite{flicker_evaluation_2014}. With few exceptions these metrics are derived from
-mass balances and facility operation history calculated by a fuel cycle
+\cite{flicker_evaluation_2014}. With few exceptions, these metrics are derived from
+mass balances and facility operation histories calculated by a fuel cycle
 simulator. For example, where nuclear waste repository burden is derived from
@@
 some simulators discretely model batches of material and individual facilities,
-others aggregate facilities into fleets and materials into streams. Simulators
-can model a single aspect of the fuel cycle in great detail while neglecting
-others. For example, a simulator created for policy modeling might have
-excellent capability in economics while capabilities for tracking transformations in
-material isotopics and the effects of isotopics on technology performance are
-neglected.  The \gls{CAFCA}\cite{guerin_impact_2009} simulator is problem-oriented
-in this way, having elected to neglect isotopic resolution in favor of
-integral effects.
+others aggregate facilities into fleets and materials into streams. Some
+simulators were designed to model a single aspect of the fuel cycle in great
+detail while neglecting others. For example, a simulator created for policy
+modeling might have excellent capability in economics while capabilities for
+tracking transformations in material isotopics and the effects of isotopics on
+technology performance are neglected.  The \gls{CAFCA}\cite{guerin_impact_2009}
+simulator is problem-oriented in this way, having elected to neglect isotopic
+resolution in favor of integral effects.
 

### 2015-07-15 fundamentals/intro.tex
used multiple synonyms in various places to reduce jargon-y nature of the modular and dll terms. fixes #120

@@
 The \Cyclus nuclear fuel cycle simulator framework and its \emph{modeling
-ecosystem}, the suite of agents and other physics plugins compatible with it,
+ecosystem}, the suite of agents and other physics plug-in libraries compatible with it,
 incorporate modern insights from simulation science and software architecture
@@
 cultivates an ecosystem of modeling options. This ecosystem is \emph{modular},
-being comprised of flexible, interchangeable models of fuel cycle component
+being comprised of dynamically loadable, interchangeable, plug-in libraries of fuel cycle component
 process physics that vary in their scope, depth, and fidelity. This modularity
 allows users and developers to customise \Cyclus to analyze the cases that are
-of interest to them, rather than any custom applicaiton the simulator was
+of interest to them, rather than any custom application the simulator was
 originally developed to address.  The fundamental concepts of the \Cyclus

### 2015-07-15 fundamentals/intro.tex
toward #118, reduces marketing talk

@@
 nuclear fuel cycle analysis community to achieve two important goals: lower the
-barrier for innovative nuclear technologies to be included in fuel cycle analysis
-while improving the ability to compare simulations with and without those innovative
-concepts.  This essential capability is absent in
+barrier for users to include custom nuclear technologies in their fuel cycle
+analyses while improving the ability to compare simulations with and without
+those custom concepts.  This essential capability is absent in
 previous simulators where user customization and extensibility were not design

### 2015-07-15 fundamentals/intro.tex
toward #118, reduces marketing talk

@@
 \Cyclus is necessary to meet these goals, it is not sufficient.
-\emph{Agent interchangeability} is required to facilitates direct comparison
-of alternative modeling methodologies and facility concepts.  Finally, \Cyclus is
+\emph{Agent interchangeability} is also required to facilitates direct comparison
+of alternative modeling methodologies and facility concepts at levels of detail
+and validation appropriate for each user application. Finally, \Cyclus is
 applicable to a broader range of fidelities, scales, and applications than

### 2015-07-15 fundamentals/intro.tex
emphasizes platform enabling of potential capabilities rather than stating current capabilities

--- 2015-07-15 fundamentals/intro.tex
@@
 \Cyclus is necessary to meet these goals, it is not sufficient.
-\emph{Agent interchangeability} is required to facilitates direct comparison
-of alternative modeling methodologies and facility concepts.  Finally, \Cyclus is
-applicable to a broader range of fidelities, scales, and applications than
-other simulators, due to the flexibility and generality of its
-\emph{\gls{ABM}} paradigm and \emph{discrete, object-oriented approach}.
+\emph{Agent interchangeability} is also required to facilitates direct comparison
+of alternative modeling methodologies and facility concepts. With this concept
+at its core, \Cyclus provides a platform for users to quickly develop the
+capabilities at a level of detail and validation necessary for their
+unique applications.  Finally, \Cyclus is applicable to a broader range of
+fidelities, scales, and applications than other simulators, due to the
+flexibility and generality of its \emph{\gls{ABM}} paradigm and \emph{discrete,
+object-oriented approach}.
 

### 2015-07-15 fundamentals/intro.tex
emphasizes multiple fidelities toward solution to #118

@@
 allows users and developers to customise \Cyclus to analyze the cases that are
-of interest to them, rather than any custom application the simulator was
-originally developed to address.  The fundamental concepts of the \Cyclus
+of interest to them rather than any custom application the simulator was
+originally developed to address. Additionally, that customizability allows
+useres and developers to address those cases at the level of fidelity necessary
+for their application. The fundamental concepts of the \Cyclus
 nuclear fuel cycle simulator capture these modern insights so that novel

### 2015-07-15 fundamentals/intro.tex
Two sentences were added to the introduction to note the Next Generation Fuel Cycle Simulator Functions and Requirements arrived at by the DOE effort on the topics of modularity and openness. Fixes #123

@@
 materials rather than discrete resolution of those individual agents and
-objects.  Those software choices exhibit three main failure modes which present
-significant challenges to modeling fidelity, generality, efficiency,
-robustness, and scientific transparency. First, they discourage targeted
+objects. When the DOE-NE Fuel Cycles Technologies Systems Analysis Campaign
+developed requirements necessary in a next generation fuel cycle simulator,
+three main failure modes were associated with those software choices.
+First, they discourage targeted
 contribution and collaboration among experts. Next, they hobble efforts to
@@
 rendering most tools applicable to only a subset of desired simulation
-fidelities, scales, and applications.
+fidelities, scales, and applications. Those three constraints were identified
+as presenting significant challenges to modeling fidelity, generality, efficiency,
+robustness, and scientific transparency in the field of fuel cycle analysis
+\cite{huff_next_2010}.
 

### 2015-07-16 fundamentals/fcsreqs.tex
adds stuff to bib

@@
 \gls{COSI}, for example,
-has some support for modeling reactors individually, but according to a recent benchmark \cite{oecd_benchmark_2012}, it models many reactors operating in sync.
-That is, refuelling and discharging occur simultaneously for all reactors.
+has some support for modeling reactors individually, but according to a recent
+benchmark \cite{boucher_benchmark_2012}, it models many reactors operating in sync. That is, refuelling and discharging occur simultaneously for all reactors.
 While \Cyclus allows this type of fleet-based aggregation of reactor behavior, \Cyclus also enables operations in each facility to vary independently of any others in the simulation.

### 2015-07-16 fundamentals/intro.tex
adds stuff to bib

@@
 \cite{macal_agent-based_2010}. Furthermore, openness allows cross-institutional
-collaboration, increases software robustness \cite{cohen_modern_2010}, and
+collaboration, increases software robustness
+\cite{cohen_modern_2010,fagan_design_2002}, improves
+the strength and quality of results through peer review
+\cite{ince_case_2012,stodden_scientific_2010,wicherts_willingness_2011}, and
 cultivates an ecosystem of modeling options. This ecosystem is \emph{modular},

### 2015-07-16 fundamentals/intro.tex
adds petre to bib
adds donoho citation, toward #122
references sections for each confusing term in the intro. Fixes #125

@@
 the strength and quality of results through peer review
-\cite{ince_case_2012,stodden_scientific_2010,wicherts_willingness_2011}, and
+\cite{donoho_reproducible_2009,ince_case_2012,stodden_scientific_2010,wicherts_willingness_2011,petre_code_2014}, and
 cultivates an ecosystem of modeling options. This ecosystem is \emph{modular},
@@
 regional and institutional entities with customizable behavior and
-objectives. This capability is an innovation not pursued by any existing fuel
-cycle simulator.
+objectives. Each of these concepts (agent-based, resource tracking, and
+regional as well as institutional entities) will be described in their own
+sections (sections \ref{sec:abm}, \ref{sec:mats}, and \ref{sec:rif}
+respectively).  Together, they provide a capability for extension and reus
+beyond that pursued by any existing fuel cycle simulator.
 

### 2015-08-15 fundamentals/conclusion.tex
cleans up reference to physics in conclusion to make note of where physics modules exist. Toward a solution to #128

@@
 
-Similarly the fidelity-agnostic modular architecture facilitates simulations
+Similarly, the fidelity-agnostic, modular \Cyclus architecture facilitates simulations
 at every level of detail. Simulations relying on arbitrarily complex isotopic
 compositions are possible in \Cyclus, as are simulations not employing any
-physics at all. Indeed, agents of such varying fidelity can even exist in the
-same simulation. Researchers no longer need to reinvent the wheel in order to
-model a simulation focused on the aspects of the fuel cycle
-relevant to their research.
+physics at all. To support this, the \Cycamore library provides models 
+employing basic physics for core fuel cycle facilities and extension libraries 
+from the community more support detailed simulations. Indeed, agents of such 
+varying fidelity can even exist in the same simulation. Researchers no longer 
+need to reinvent the underlying simulator framework in order to model a simulation 
+focused on the aspects of the fuel cycle relevant to their research.
 

### 2015-08-15 fundamentals/examples.tex
uses a table to better capture the parameters in bullet points.

@@
 The success of the \Cyclus simulator can be measured in many ways.  The most
-compelling are demonstrations of fundamental simulation capability and of the
-feasibility of the \Cyclus community-driven development model. Promising
+compelling are early successes of the community-driven development model and 
+demonstrations of its fundamental simulation capabilities. Promising
 growth of the \Cyclus ecosystem at multiple institutions indicates that a fuel
@@
 \begin{enumerate}
-    \item Once through (no recycle)
-    \item 1-pass \gls{MOX} recycle
-    \item Infinite-pass \gls{MOX} recycle
+    \item No Recycle (once through)
+    \item 1-pass \gls{MOX} Recycle
+    \item Infinite-pass \gls{MOX} Recycle
 \end{enumerate}
@@
 toward continuous material flow results.  \Cyclus flexibility allows this
-transition to be examined.  The facilities used in these simulations are:
+transition to be examined.
 
+\begin{table}[h]
+\centering
+\begin{tabularx}{\textwidth}{|X|r|X|}
+\hline
+\textbf{Facility} &\textbf{Parameter} & \textbf{Value}\\
+\hline
+\textbf{LWR} & type & LWR\\
+\Class{cycamore::Reactor} & batches & $3$ [batches/cycle]\\
+                  & batch size & $20000$ [kg HM]\\
+                  & cycle length & $18$ [months]\\
+                  & refuelling time & $2$ [months]\\
+                  & requests & recycled MOX (1st preference)\\
+                  & requests & enriched UOX (2nd preference)\\
+\hline
+\textbf{Recycled Fuel Fabrication} & requests & depleted uranium\\
+\Class{cycamore::Fab} & requests & separated fissile material\\
+                      & offers & recycled MOX\\
+\hline
+\textbf{Separations} & requests & all spent fuel types \\
+\Class{cycamore::Separations} & offers & separated fissile material\\
+                      & efficiency & 0.99\\
+                      & Pu separation capacity & $6.0E4$ [kg/month] \\
+\hline
+\textbf{Repository} & requests & all waste\\
+\Class{cycamore::Sink} & capacity & $\infty$\\
+\hline
+\textbf{UOX Fabrication} & fffers & UOX\\
+\Class{cycamore::Source} & capacity & $\infty$\\
+\hline
+\textbf{DU Source} & offers & depleted U\\
+\Class{cycamore::Source} & capacity & $\infty$\\
+\hline
+\end{tabularx}
+\caption{Facility Configurations for Example Simulations}
+\label{tab:facconfigs}
+\end{table}
+
+As described in Table \ref{tab:facconfigs}, the facilities used in these simulations are:
 \begin{itemize}

### 2015-08-15 fundamentals/examples.tex
renames once through to No Recycle and 1-pass to Single-Pass Recycle and infinite-pass recycle to Inifinite-Pass Recycle

@@
 each of the facilities.  The reactor was configured to request recycled \gls{MOX}
-fuel with a higher preference than new \gls{UOX} fuel. For the once through case,
+fuel with a higher preference than new \gls{UOX} fuel. For the No Recycle case,
 the \Class{Reactor} was set to offer all spent fuel as waste.  For the 1-pass
 recycle case, the \Class{Reactor} offered spent \gls{UOX} into a spent fuel market,
-but spent \gls{MOX} is still offered as waste.  In the infinite-pass recycle case,
+but spent \gls{MOX} is still offered as waste.  In the Infinite-Pass Recycle case,
 the \Class{Reactor} offers all burned fuel into a spent fuel market. The
@@
 it as a waste commodity which is only requested by the repository.  The
-material flows for the 1-pass recycle case are shown in Figure
+material flows for the Single-Pass Recycle case are shown in Figure
 \ref{fig:flowmodopen}.
@@
 This results in the material flows in Figure \ref{fig:flowclosed}.  A
-similarly trivial change was used to switch from the once through to a 1-pass
+similarly trivial change was used to switch from the No Recycle to a 1-pass
 fuel cycle.  Note that because the reactors always transmute fuel into fixed
 compositions, the error in isotopic compositions is larger for the
-infinite-pass recycle case.
+Infinite-Pass Recycle case.
 
@@
 
-Figure \ref{fig:puseries1} shows the full-system plutonium buildup for once
-through (no recycle), 1-pass recycle, and infinite-pass recycle variations of
+Figure \ref{fig:puseries1} shows the full-system plutonium buildup for No 
+Recycle (once through), Single-Pass Recycle, and Infinite-Pass Recycle variations of
 the one-reactor scenario described above. The figure was generated directly
@@
 drop in the total fuel cycle system plutonium inventory.  This pattern repeats
-roughly every 10 cycles (200 months) for the 1-pass recycle case and every 9
-cycles (180 months) for the infinite-pass recycle case.  Because the 1-pass
+roughly every 10 cycles (200 months) for the Single-Pass Recycle case and every 9
+cycles (180 months) for the Infinite-Pass Recycle case.  Because the 1-pass
 recycle scenario does not re-recycle material, it takes the fabrication
@@
 Figure \ref{fig:puseriesn} shows plutonium buildup for the 10-reactor
-simulations of the once through, 1-pass recycle, and infinite-pass recycle
+simulations of the No Recycle, Single-Pass Recycle, and Infinite-Pass Recycle
 scenarios.  As the number of reactors (with staggered refueling) increases,

### 2015-08-28 fundamentals/intro.tex
spell check

@@
 originally developed to address. Additionally, that customizability allows
-useres and developers to address those cases at the level of fidelity necessary
+users and developers to address those cases at the level of fidelity necessary
 for their application. The fundamental concepts of the \Cyclus
@@
 sections (sections \ref{sec:abm}, \ref{sec:mats}, and \ref{sec:rif}
-respectively).  Together, they provide a capability for extension and reus
+respectively).  Together, they provide a capability for extension and reuse
 beyond that pursued by any existing fuel cycle simulator.

### 2015-08-28 fundamentals/conclusion.tex
fixes #128

@@
 compositions are possible in \Cyclus, as are simulations not employing any
-physics at all. To support this, the \Cycamore library provides models 
+physics at all (though the user must explicitly turn off radioactive decay of 
+materials if that is desired). To support this, the \Cycamore library provides models 
 employing basic physics for core fuel cycle facilities and extension libraries 
-from the community more support detailed simulations. Indeed, agents of such 
+from the community support more detailed simulations. Indeed, agents of such 
 varying fidelity can even exist in the same simulation. Researchers no longer 

### 2015-08-28 fundamentals/conclusion.tex
conclusion cleanup.

--- 2015-08-15 fundamentals/conclusion.tex
@@
 accessibility, but also enables transparency and community oversight. 
-
-The object-oriented \gls{ABM} simulation paradigm ensures more generic
+Furthermore, the object-oriented \gls{ABM} simulation paradigm ensures more generic
 simulation capability. It allows \Cyclus to address common analyses in a more
@@
 compositions are possible in \Cyclus, as are simulations not employing any
-physics at all. To support this, the \Cycamore library provides models 
-employing basic physics for core fuel cycle facilities and extension libraries 
-from the community more support detailed simulations. Indeed, agents of such 
-varying fidelity can even exist in the same simulation. Researchers no longer 
-need to reinvent the underlying simulator framework in order to model a simulation 
-focused on the aspects of the fuel cycle relevant to their research.
+physics at all. Physics is introduced through optional system-wide radioactive 
+decay of materials and through the use of physics-enabled facility libraries.  
+To support calculation of physical processes in nuclear facilities, the 
+\Cycamore library provides models employing basic physics for core fuel cycle 
+facilities and extension libraries from the community support more detailed 
+simulations. Indeed, agents of such varying fidelity can even exist in the same 
+simulation. Researchers no longer need to reinvent the underlying simulator 
+framework in order to model a simulation focused on the aspects of the fuel 
+cycle relevant to their research.
 

### 2015-08-28 fundamentals/impl.tex
references sections for each confusing term in the intro. Fixes #125
removes 'bring into relief the difference between qa and validation' bit
fixes #127

@@
 \subsubsection{Regions, Institutions, and Facilities}
+\label{sec:rif}
 
@@
 \subsubsection{Resources and Materials}
+\label{sec:mats}
 % Resources, Materials (note isotope tracking, decay behavior)
@@
 simulators that use other modeling paradigms are underway
-\cite{huff_extensions_2014}. However, such
-exercises are more likely to bring into relief the differences between the modeling
-paradigms than supply substantial \gls{QA} and validation.
+\cite{huff_extensions_2014}.
 
 Sections \ref{sec:qa-testing}-\ref{sec:qa-ci} discuss in greater detail the software
-development components that comprise the \Cyclus verification strategy.
-Each of these on its own is a valuable addition to \gls{QA} but it cannot be the
+development components that comprise the \Cyclus verification strategy, which 
+allows the simulation kernel and physics models to be tested explicitly and 
+separately.
+Each of these approaches on its own is a valuable addition to \gls{QA} but it cannot be the
 entire answer to the requirements imposed by \gls{NQA1}. Taken together and strictly

### 2015-08-28 cover_letter/cover_letter.tex
updates cover letter for advances in engineering software

@@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % Plain Cover Letter
@@
 
-\documentclass[10pt]{letter} % Default font size of the document, change to 10pt to fit more text
+\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text
 \usepackage{graphicx}
@@
 % Margins
-\topmargin=-1in % Moves the top of the document 1 inch above the default
-\textheight=10in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
-%\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
-%\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa
+\usepackage[left=1.25in,right=1.25in,top=1.5in,bottom=1.25in]{geometry}
+%\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right
 
-%\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right
-%\usepackage{wallpaper}
-%\ULCornerWallPaper{0.97}{bk_logo.eps}
-
+\usepackage{eso-pic,graphicx}
  \begin{document}
+\AddToShipoutPictureBG*{\includegraphics[width=\paperwidth,height=\paperheight]{background.pdf}}
 
@@
 
-\begin{letter}{N. Tsoulfanidis and A. Klein\\
+\begin{letter}{Prof. A.K. Noor, Prof. B.H.V. Topping\\
 Editors\\
-Nuclear Technology}
-
+Advances in Engineering Software}
 %----------------------------------------------------------------------------------------
@@
 
-\begin{center}
-\includegraphics[width=\textwidth]{bk_logo.eps}
-\end{center}
-
-\address{Department of Nuclear Engineering\\
+\address{Kathryn D. Huff\\
 4155 Etcheverry Hall\\
 MC 1730\\
-University of California, Berkeley\\
-Berkeley, CA 94720-1730}
-
-\name{\vspace{5mm}
-Kathryn Huff\\
-Postdoctoral Scholar\\
-huff@berkeley.edu}
+Berkeley, CA 94720}
 
@@
 
-\opening{Dear Dr. Klein and Dr. Tsoulfanidis:}
+\opening{Dear Professors Noor and Topping:}
 
 Please find enclosed a manuscript entitled: ``Fundamental Concepts in the 
-Cyclus Fuel Cycle Simulator Framework and Modeling Ecosystem'' which I am
-submitting for exclusive consideration of publication as a research article in
-Nuclear Technology.
+Cyclus Fuel Cycle Simulator Framework'' which I am submitting for exclusive 
+consideration of publication as a research article in Advances in Engineering 
+Software.
 
-This manuscript describes the fundamental concepts in the Cyclus fuel cycle
-simulator framework and its modeling ecosystem. These concepts and their
+This manuscript describes the fundamental concepts in the Cyclus nuclear fuel 
+cycle simulator framework and its modeling ecosystem. These concepts and their 
 implementations are described in the context of motivating challenges in 
-nuclear fuel cycle simulation. Additionally, the current capabilities of Cyclus
-are demonstrated for both an open and a closed fuel cycle.
+nuclear fuel cycle simulation. Accordingly, the current capabilities of Cyclus 
+are demonstrated for a range of representative fuel cycle scenarios including 
+open (no recycling), closed (complete recycling), and modified open (some 
+recycling) material routing schemes.
 
-We request that this manuscript be considered for joint publication alongside
-Scopatz et al., ``Cyclus Archetypes.'' These two papers are complementary, and we
-believe it would be ideal for both manuscripts to be published together in the
-same issue of Nuclear Technology.
+%We request that this manuscript be considered for joint publication alongside
+%Scopatz et al., ``Cyclus Archetypes.'' These two papers are complementary, and we
+%believe it would be ideal for both manuscripts to be published together in the
+%same issue of Advances in Engineering Software.
 
 Thank you for your consideration of this work. I expect it will be of interest
-to a broad readership concerned with nuclear fuel cycle simulation and
-computational methods. Please address all correspondence concerning this
-manuscript to me at UC Berkeley and feel free to correspond with me by e-mail.
+to a broad readership concerned with nuclear engineering, industrial and 
+systems engineering, fuel cycle simulation, and agent-based computational 
+methods. Please address all correspondence concerning this manuscript to me at 
+UC Berkeley and feel free to correspond with me by e-mail.
 
-\closing{Sincere regards,%
-\\
-\vspace{-20mm}\includegraphics[height=1.5cm]{signature.eps}
+\closing{Sincere regards,
+\includegraphics[height=2cm]{signature}\\
+\fromsig{Kathryn Huff}
 }
+
 %----------------------------------------------------------------------------------------

### 2015-09-03 fundamentals/impl.tex
added more description of sensitivity studies. closes #126

@@
 Cyclopts \cite{gidden_cyclopts_2015}, a proof of principle design and
-implementation of a \Cyclus-enabled application on such a large computer system,
-uses UW-Madison's HTCondor \gls{HTC} infrastructure to perform sensitivity
-studies. Cyclopts has run over $10^5$ jobs, comprising more than 60,000 total
-compute hours. The \gls{HTC} infrastructure has separately been utilized to
-run and collect information from full \Cyclus simulations running in parallel
-on $10^3$ machines reliably for order $10^5$ simulations.
+implementation of a \Cyclus-enabled application on such a large compute system,
+uses UW-Madison's HTCondor \gls{HTC} infrastructure to study DRE performance and
+outcomes. For example, an investigation of the effect of solution degeneracy, a
+commonly observed phenomenon in scenarios with individual facilities and basic
+(e.g., commodity-only) preference definitions, was performed for three different
+fuel cycles: once-through, \gls{MOX} fast reactor-thermal reactor cycles, and
+\gls{MOX}-\gls{ThOX} recycle in fast reactors-thermal reactor cycles. Objective
+coefficients were generated based on two factors: commodity-facility pairings
+and facility location. The population of the possible values of
+commodity-facility pairings is always small ($\mathcal{O}(10)$). The size of the
+population of possible values of the location effect was investigated for values
+of zero, ten, and infinity (i.e., any real number). The study additionally
+included an investigation of problem-scaling behavior in order to quantify the
+magnitude and rate-of-increase of DRE solution times as a function of the
+simulation-entity population for each fuel
+cycle\cite{gidden_agent-based_2015}. In total, Cyclopts has run over $10^5$
+jobs, comprising more than 60,000 compute hours. The \gls{HTC} infrastructure
+has separately been utilized to run and collect information from full \Cyclus
+simulations running in parallel on $10^3$ machines reliably for order $10^5$
+simulations.
 
@@
   priori}. Therefore, the logic engine defining resource interaction mechanisms
-among agents is crucial. The \gls{DRE} is that critical logic engine on which
-\Cyclus simulations are built.  Supporting the general \Cyclus philosophy,
-facilities are treated as black boxes and a supply-demand communication
-framework is defined.
+among agents is crucial. The \gls{DRE}, described in detail in
+\cite{gidden_agent-based_2015}, is that critical logic engine on which \Cyclus
+simulations are built.  Supporting the general \Cyclus philosophy, facilities
+are treated as black boxes and a supply-demand communication framework is
+defined.
 

### 2015-09-05 fundamentals/examples.tex
spell check
update to examples file, better wording

@@
 
-This section will discuss the creation and results of a few simple fuel cycle
-simulations to help illustrate the flexibility of \Cyclus. These examples are
-not the limit of \Cyclus' capabilities, which are extended with each new
+To illustrate the flexibility of \Cyclus, this section will discuss the 
+creation and results of a range of representative fuel cycle simulations.
+These examples are not the limit of \Cyclus' capabilities, which are extended with each new
 addition to the ecosystem, as discussed above.  Rather, these simulations are
-designed to illustrate that \Cyclus has capabilities matching those of any
-recipe-based simulator. Accordingly, many simplifying assumptions have been
+designed to illustrate that \Cyclus matches the capabilities of any
+recipe-based simulator and that variations on a single \Cyclus simulations can 
+be run with small changes to the input specification. For simplicity of the 
+demonstration, many simplifying assumptions have been
 made with respect to material compositions, fuel transmutation, among others.
@@
 \hline
-\textbf{UOX Fabrication} & fffers & UOX\\
+\textbf{UOX Fabrication} & offers & UOX\\
 \Class{cycamore::Source} & capacity & $\infty$\\
@@
 
-Modifying the input file specification to model each of the 3 fuel cycles was
-done by making simple adjustments to the commodities and trade preferences for
-each of the facilities.  The reactor was configured to request recycled \gls{MOX}
+To model each of the three fuel cycles, only simple 
+adjustments to the input file specification were necessary. Specifically,  
+only the commodity types and trade preferences for
+each of the facilities needed to be altered from one simulation to another.
+
+For all cases, the reactor was configured to request recycled \gls{MOX}
 fuel with a higher preference than new \gls{UOX} fuel. For the No Recycle case,

### 2015-09-05 cover_letter/cover_letter.tex
adjusts cover letter
customizes cover letter a bit more

@@
 
-\begin{letter}{Prof. A.K. Noor, Prof. B.H.V. Topping\\
-Editors\\
-Advances in Engineering Software}
+\begin{letter}{Professor A.K. Noor\\
+Professor B.H.V. Topping\\
+Editors, Advances in Engineering Software}
 %----------------------------------------------------------------------------------------
@@
 \address{Kathryn D. Huff\\
-4155 Etcheverry Hall\\
-MC 1730\\
+2150 Shattuck Ave.\\
+Suite 230\\
 Berkeley, CA 94720}
@@
 cycle simulator framework and its modeling ecosystem. These concepts and their 
-implementations are described in the context of motivating challenges in 
+implementations are motivated by and described in the context of challenges in 
 nuclear fuel cycle simulation. Accordingly, the current capabilities of Cyclus 
@@
 Thank you for your consideration of this work. I expect it will be of interest
-to a broad readership concerned with nuclear engineering, industrial and 
-systems engineering, fuel cycle simulation, and agent-based computational 
-methods. Please address all correspondence concerning this manuscript to me at 
-UC Berkeley and feel free to correspond with me by e-mail.
+to a broad readership concerned with applications of object-oriented simulation 
+to engineering problems nuclear engineering, algorithms for engineering systems 
+analysis, and agent-based computational methods. Please address all 
+correspondence concerning this manuscript to me at UC Berkeley and feel free to 
+correspond with me by e-mail.
 

### 2015-09-09 fundamentals/impl.tex
fix sim section typo
perhaps this is the right image?
remove apparently unrelated comments
Reworking of QA section

@@
 \begin{center}
-\includegraphics{./images/modifiedopen.eps}
+\includegraphics[width=0.5\textwidth]{./images/modifiedopen.eps}
 \end{center}
@@
 \begin{center}
-\includegraphics{./images/compositions}
+\includegraphics[width=\textwidth]{./images/compositions}
 \end{center}
@@
 
-\begin{table}[h]
+\begin{table}[H]
 \centering
@@
 \subsection{Quality Assurance}
-% Organize this section according to major topics
-% give each topic a section heading in boldface.
-% try to cover the major common points :
-%
-% problem design
-% methods of measurement
-% supporting models
-% supporting data
-% simulations run
-% results
 
-% Just write the section headings for each part and indicate what goes in that
-% section with words :
-%
-% heading
-% figures (with captions)
-% schematics (with captions and footnotes)
-% equations
-% tables
+% topics:
+%  - version control
+%  - PR policy
+%  - style guide
+%  - testing
+%  - CI
 
-% What does it mean?
-% What did I actually test?
-% What were the results?
-% Did the work yield a new method?
-% Did the work yield new knowledge?
-% What measurements did I make?
-% How were these measurements characterized?
-% What methods were used?
-% What were the results?
-% How were the measurements made and characterized?
-
-Simulation science - like experimental science - must distinguish trustworthy
-results from untrustworthy ones.
-Charles Babbage famously articulated this, ``On two occasions I have been asked,
-`Pray, Mr. Babbage, if you put into the machine wrong figures, will the right
-answers come out?' ... I am not able rightly to apprehend the kind of confusion
-of ideas that could provoke such a question.'' \cite{babbage_passages_2011}.
-A simulator must assure correctness and guard against the \emph{garbage
-in, garbage out} phenomenon.
-
-Multiple strategies, collectively known as \emph{\gls{QA}}, have
-been invented to mitigate structural and algorithmic errors
-in software. These include \emph{\gls{VV}}
-\cite{boehm_software_1989}, testing, and others.
+To garner the trust of a broad user and archetype developer community, the
+\Cyclus project must implement a strategy to assure the ongoing quality of the
+software it provides.  Multiple strategies, collectively known as
+\emph{\gls{QA}}, have been developed by the scientific software development
+community to mitigate structural and algorithmic errors in software. These
+include \emph{\gls{VV}} \cite{boehm_software_1989}, testing, and others.
 
 Nuclear engineering software quality is often governed by \gls{NQA1}, an
-\gls{ASME} specification
-whose latest revision appeared in 2009 \cite{asme_nqa-1a-2009_2009}.
-\Cyclus has adopted an \emph{agile} development process
-\cite{larman_agile_2004},
-interpreting \gls{NQA1} in a manner similar to the process adopted by the
-\gls{DOE} within \gls{NEAMS} \cite{neams_nuclear_2013} or by the PyNE toolkit
-\cite{biondo_quality_2014}.
+\gls{ASME} specification whose latest revision appeared in 2009
+\cite{asme_nqa-1a-2009_2009}.  \Cyclus has adopted an \emph{agile} development
+process \cite{larman_agile_2004}, interpreting \gls{NQA1} in a manner similar
+to the process adopted by the \gls{DOE} within \gls{NEAMS}
+\cite{neams_nuclear_2013} or by the PyNE toolkit \cite{biondo_quality_2014}.
 
-Verification may be defined as the question, ``Is \Cyclus being built correctly?''
-To answer this question, \Cyclus relies on software development best practices
-such as testing,
-documentation, version control, style guidelines, and continuous integration to
-ensure reliability and reproducibility. These verification techniques are
-discussed individually in the sections that follow.
+Validation of simulators like \Cyclus, that are intended to give forecasts of
+system behavior in uncertain futures, is not well defined as there are no
+experimental benchmarks upon which to rely.  Instead, code-to-code comparisons
+with fuel cycle simulators that use other modeling paradigms are underway as
+the best approach to establish confidence that \Cyclus produces correct
+answers. \cite{huff_extensions_2014}
 
-Validation, in contrast,  may be defined as the question,
-``Is \Cyclus the correct tool?''
-Since \Cyclus is alone in its class as an agent-based fuel cycle simulator, longitudinal
-validation is not possible. Nonetheless, code-to-code comparisons with fuel cycle
-simulators that use other modeling paradigms are underway
-\cite{huff_extensions_2014}.
+Verficiation of \Cyclus implementation relies on software development best
+practices such as version control, testing, continuous integration,
+documentation, and style guidelines to ensure reliability and
+reproducibility. Sections \ref{sec:qa-vc}-\ref{sec:qa-review} discuss in
+greater detail the software development components that comprise the \Cyclus
+verification strategy, which allows the simulation kernel and physics models
+to be tested explicitly and separately. Each of these approaches on its own is
+a valuable addition to \gls{QA} but it cannot be the entire answer to the
+requirements imposed by \gls{NQA1}. Taken together and strictly adhered to,
+they present a fortress to protect against poorly designed or otherwise
+undesirable code.
 
-Sections \ref{sec:qa-testing}-\ref{sec:qa-ci} discuss in greater detail the software
-development components that comprise the \Cyclus verification strategy, which 
-allows the simulation kernel and physics models to be tested explicitly and 
-separately.
-Each of these approaches on its own is a valuable addition to \gls{QA} but it cannot be the
-entire answer to the requirements imposed by \gls{NQA1}. Taken together and strictly
-adhered to, they present a fortress to protect against poorly designed or otherwise undesirable code.
+\subsubsection{Version Control}
+\label{sec:qa-vc}
+
+Automated version control, provided by the well-established \emph{distributed
+  version control} tool git \cite{software_freedom_conservancy_git_2014}, is
+at the heart of the QA strategy because it records the full history of any
+change, along with metadata such as the author, a timestamp, and an
+accompanying message. This makes it possible to identify when changes were
+introduced, how they related to other changes, and who made those changes.  If
+necessary, it also facilitates reversing individual changes from a long and
+intricate set of changes.  Version control also enables a code review process
+descried in section \ref{sec:qa-review} below.
 
@@
 Integration tests combine multiple elements of the
-\Cyclus interface and test that they work correctly with each other.  By analogy,
-simply because the gears (units) are made correctly does not imply that the
-clock (integration) will run smoothly, run at all, or give the correct time.
+\Cyclus interface and test that they work correctly with each other. 
 In \Cyclus and \Cycamore, integration tests are performed by running sample
@@
 
-\subsubsection{Documentation}
+\paragraph{Continuous Integration}
+
+\emph{Continuous integration (CI)} is the idea that software should be tested
+and validated as it is being developed, rather than as a final stage in a
+longer development cycle.  Under \gls{CI}, every pull request is automatically
+tested independently immediately as it is proposed. The results of this
+testing are shown to code reviewers in the GitHub interface.  The \Cyclus
+project currently uses the CircleCI service for continuous integration.
+Whenever a pull request is created, CircleCI builds a version of the \Cyclus
+source code that includes the requested changes and runs the complete test
+suite, reporting back whether or not those steps were successful. If \gls{CI}
+was not successful, the code author(s) must first identify and resolve the
+problems.
+
+Since these steps are performed for all incoming code, it is easy for the
+\Cyclus core team to determine whether or not an individual pull request
+actually works. This helps identify build and test problems prior to broken
+code being allowed into the main software development branch.
+
+\subsubsection{Code Review}
+\label{sec:qa-review}
+
+Autmoated testing including \gls{CI} is a necessary but not sufficient
+component of the \Cyclus \gls{QA} system: it keeps bad code out of
+\Cyclus. However, \Cyclus will always require human eyes and hands to let good
+code in.
+
+The main \Cyclus repository is hosted remotely and publicly on the GitHub
+website \cite{dabbish_social_2012}, in part because it provides tools that
+facilitate a culture of frequent and thorough code review.  A number of
+policies exist to ensure that a proposed set of changes, known as a \emph{pull
+  request}, adhere to the projects \gls{QA} standards. Every pull request must
+be reviewed and accepted by a member of the \Cyclus core team that was not
+involved in authoring the changes.  In addition to reviewing the algoirthmic
+design in the source code, the reviewer relies on tests to ensure correct
+behavior, and requires the authors to adhere to the style guide and provide
+sufficient documentation.  Only after the \gls{QA} standards have been met are
+the proposed changes merged into the software. This step has been repeatedly
+shown to improve code quality \cite{cohen_modern_2010}.
+
+Once \gls{CI} is successful, a code reviewer inspects not only the
+changes that are proposed to the software itself, but also the changes that
+have been proposed to tests.  It is important that the subset of tests that
+are relevant to the software change has a scope and completeness that will
+ensure that incorrect behavior will be automatically detected.  If there are
+sufficent tests and \gls{CI} is successful, the reviewer can proceed to
+considering the actual software changes themselves.
+
+Because of their role in facilitating code review during the change process,
+as well as their long term benefit to the maintainability of the project,
+documentation and coding style are also reviewed as part of this process.
+
+\paragraph{Documentation}
 
@@
 
-\subsubsection{Version Control}
-
-Version control preserves the development history, or \emph{provenance}, of
-source code files. \Cyclus uses a well-established \emph{distributed version
-control} tool called git \cite{software_freedom_conservancy_git_2014} for this
-purpose.  Distributed version control allows every
-user to have complete local copy of the \emph{repository} (the version control
-term for the collection of all possible histories).
-One feature that git performs exceptionally well is \emph{branching}.
-Branches are distinct pathways in the history that diverge from a mainline source
-tree and then may be \emph{merged} back in. Multiple simultaneous
-branches may exist at all points in time. Every change to the code is recorded
-in the history, along with metadata such as the author, a timestamp, and an
-accompanying message. Thus,
-it is possible for \Cyclus to accurately replay the entirety of who did what to the
-code when.
-
-\Cyclus uses a strategy known as \emph{git flow}
-\cite{kalliamvakou_code-centric_2014} to manage topical branches where
-individuals develop code in parallel. All proposed software changes from
-topical branches must have sufficient successful tests and comprehensive
-documentation to be allowed into \Cyclus.  As an example, a schematic of the
-development stages between reporting a bug and merging the fix is shown in
-Figure \ref{fig:gitprocess}.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[height=0.6\textheight]{./images/gitprocess}
-\end{center}
-\caption{A version-control enabled process for finding, reporting, and fixing a bug
-can take place within an issue tracker alongside multiple stages of software
-testing and review. In the \Cyclus case, the final review stage includes unit,
-regression, and integration testing as well as manual code inspection.}
-\label{fig:gitprocess}
-\end{figure}
-
-The act of proposing a change is known as a \emph{pull request}. The main \Cyclus repository is
-hosted remotely on the GitHub website \cite{dabbish_social_2012}. The online
-mechanism for pull requests allows for code review by a member of the \Cyclus
-core team, separate from the author, prior to any change being included. Non-members
-of the \Cyclus development team are allowed and encouraged to submit and review
-pull requests. However, only members of the \Cyclus core team are allowed to
-merge in any changes and only after the \gls{QA} standards have been met. This
-step has been repeatedly shown to improve code quality \cite{cohen_modern_2010}.
-
-\subsubsection{Style Guide}
+\paragraph{Style Guide}
 
@@
 improves code legibility and, therefore, robustness \cite{cohen_modern_2010}.
-
-\subsubsection{Continuous Integration}
-\label{sec:qa-ci}
-
-\emph{Continuous integration (CI)} is the idea that software should be tested and validated
-as it is being developed, rather than as a final stage in a longer development
-cycle.  Under \gls{CI}, every pull request (proposed code change) is tested independently immediately after
-it is proposed. Such tests are run on all officially supported platforms.
-\Cyclus uses a \gls{CI} platform called Polyphemus
-\cite{scopatz_polyphemus_2014}. Polyphemus serves as an intermediary between GitHub pull requests on the front-end
-and temporary \Cyclus servers on the back-end. These servers are hosted by
-the Build \& Test Laboratory (BaTLab) \cite{uw_batlab_team_batlab_2014} at the University of
-Wisconsin-Madison. Whenever a pull request is created, Polyphemus performs
-the following actions:
-
-\begin{enumerate}
-    \item Copies \Cyclus with the proposed new code to BaTLab,
-    \item Initializes Linux and Mac OSX servers,
-    \item Builds \Cyclus on all platforms,
-    \item Runs the complete \Cyclus test suite,
-    \item Reports whether or not the above steps succeeded.
-\end{enumerate}
-
-Since these steps are performed for all incoming code, it is easy for the
-\Cyclus core team to determine whether or not an individual pull request
-actually works. This helps identify build and test problems prior to
-broken code being allowed into the develop branch. \gls{CI} is a necessary
-but not sufficient addition to the \Cyclus \gls{QA}
-system: it keeps bad code out of \Cyclus. However, \Cyclus will always
-require human eyes and hands to let good code in.

### 2015-09-09 fundamentals/impl.tex
A variety of small changes:
* tighten up somewhat redundant API discussion
* there appears to be a missing RIF antecedent
* improve implied causality of preference adjustment

@@
 a set of classes on which agent plug-ins are based.  Agent plug-ins utilize the
-generic core \gls{API} to interact with one another.  For example, they use the
+generic core \glspl{API} that define agent-to-agent interaction as well as agent-to-environment interaction.
+For example, they use the
 resource exchange paradigm \gls{API} for trading resources with one another.  
+For the archetype developer, these interfaces provide enormous power
+very simply. The \gls{API} abstracts away unnecessary detail while providing
+all necessary functionality for interacting with the \Cyclus simulation kernel.
+For the user, multiple archetypes that inherit the same \glspl{API} are interchangeable
+in a simulation.
 
-Due to this plug-in architecture,
-implementations of agents in a given scenario can be easily
-interchanged. Critically, this novel functionality enables the comparison
-between agent implementations. For example, a low-physics-fidelity
-implementation of a reactor can be compared to an implementation with higher
-physics fidelity, allowing an analyst to discern the effect of reactor physical
-fidelity on a given fuel cycle.
-
-Interchangeability is accomplished by providing inheritable \glspl{API} that define agent-to-agent
-interaction and agent-to-environment interaction. For example,
+Critically, this novel functionality enables the comparison
+between agent implementations. For example, 
 an archetype that inherits the \Class{Region} interface, as in Figure
 \ref{fig:agent_uml}, is interchangeable with any other Region agent.
-For the archetype developer, this interface provides enormous power
-very simply. The \gls{API} abstracts away unnecessary detail while providing
-all necessary functionality for interacting with the \Cyclus simulation kernel.
 
@@
 provided functionality by inheriting from the appropriate class.
-\Cyclus implements a \gls{RIF} relationship through the
-parent-child hierarchy described in \S \ref{sec:interchangeability}, where
+\Cyclus implements a \gls{RIF} relationship through a
+parent-child hierarchy where
 regions are the parents of institutions which are, in turn, the parents of
@@
 \Class{Institution} interface. Second, the \Class{Facility} class implements the
-\Class{Trader} interface, and thus institutions and regions, respectively, can
+\Class{Trader} interface to participate in resource exchange, and institutions and regions, respectively, can
 adjust the resource flow preferences of their managed facilities. Importantly,

### 2015-09-10 fundamentals/fcsreqs.tex

@@
 facility to another is unique to \Cyclus. While some current simulators track
-materials in chunks, they do not necessarily preserve chunk identity as the
+materials in discrete quanta, they do not necessarily preserve the identity of each quantum as the
 materials move around the fuel cycle. When coupled with \Cyclus' individual

### 2015-09-10 fundamentals/impl.tex

@@
 accompanying message. This makes it possible to identify when changes were
-introduced, how they related to other changes, and who made those changes.  If
+introduced, how they are related to other changes, and who made those changes.  If
 necessary, it also facilitates reversing individual changes from a long and
@@
 
-\emph{Continuous integration (CI)} is the idea that software should be tested
+\Gls{CI} is the idea that software should be tested
 and validated as it is being developed, rather than as a final stage in a
 longer development cycle.  Under \gls{CI}, every pull request is automatically
-tested independently immediately as it is proposed. The results of this
-testing are shown to code reviewers in the GitHub interface.  The \Cyclus
-project currently uses the CircleCI service for continuous integration.
+tested independently, immediately as it is proposed. The results of this
+testing are shown to code reviewers prior to reviewing the software changes themselves.  The \Cyclus
+project currently uses the CircleCI \cite{circleci} service for continuous integration.
 Whenever a pull request is created, CircleCI builds a version of the \Cyclus

### 2015-09-10 fundamentals/abs.tex
helps with #116

@@
-\newpage
 \begin{abstract}
@@
 analyses of nuclear fuel cycles by simulators increase in importance.  To date,
-however, current tools are often rigid rather than flexible, fleet-based rather
-than discrete, or privately distributed rather than open source. Each of these
-choices presents a challenge to modeling fidelity, generality, efficiency,
-robustness, and scientific transparency.  The \Cyclus nuclear fuel cycle
-simulator framework and its modeling ecosystem incorporate modern insights from
-simulation science and software architecture to solve these problems so that
-challenges in nuclear fuel cycle analysis can be better addressed.  A summary
-of the \Cyclus fuel cycle simulator framework and its modeling ecosystem are
-presented. Additionally, the implementation of each is discussed in the context
-of motivating challenges in nuclear fuel cycle simulation.  Finally, the
-current capabilities of \Cyclus are demonstrated for both an open and a closed
-fuel cycle.
+however, current tools are often fleet-based rather than discrete and privately
+distributed rather than open source. Each of these choices presents a challenge
+to modeling fidelity, generality, efficiency, robustness, and scientific
+transparency.  The \Cyclus nuclear fuel cycle simulator framework and its
+modeling ecosystem incorporate modern insights from simulation science and
+software architecture to solve these problems so that challenges in nuclear
+fuel cycle analysis can be better addressed.  A summary of the \Cyclus fuel
+cycle simulator framework and its modeling ecosystem are presented.
+Additionally, the implementation of each is discussed in the context of
+motivating challenges in nuclear fuel cycle simulation.  Finally, the current
+capabilities of \Cyclus are demonstrated for both open and closed fuel
+cycles.
 \end{abstract}

### 2015-09-10 fundamentals/impl.tex
fixes misformatted quotes

@@
 \begin{itemize}
-    \item "manual" (currently implemented) is the default mode
+    \item ``manual'' (currently implemented) is the default mode
         where agents decay materials when requested by an archetype,
-    \item "never" (currently implemented) globally turns off all decay.
+    \item ``never'' (currently implemented) globally turns off all decay.
         The Material decay function does nothing,
-    \item "lazy" (currently implemented) decays material automatically whenever
+    \item ``lazy'' (currently implemented) decays material automatically whenever
          its composition is observed (e.g. when an agent queries information
          about a material's $^{239}$Pu content),
-    \item "periodic" (future) automatically decays all materials in a
+    \item ``periodic'' (future) automatically decays all materials in a
         simulation with some fixed frequency.
@@
 testing are shown to code reviewers prior to reviewing the software changes themselves.  The \Cyclus
-project currently uses the CircleCI \cite{circleci} service for continuous integration.
+project currently uses the CircleCI \cite{biggar_circleci_2015} service for continuous integration.
 Whenever a pull request is created, CircleCI builds a version of the \Cyclus

### 2015-09-10 fundamentals/examples.tex
converts to elsevier format
fixes misaligned quotes

@@
 \subsection{Simulations}
-\label{ref:simulations}
+\label{sec:simulations}
 %Inpro example (is this still running or did we deprecate it with 1.0?)
@@
         simple neutronics properties of the target fuel as closely as
-        possible.  The method used is based on a variation "equivalence
-        method" originally developed by Baker and Ross
+        possible.  The method used is based on a variation ``equivalence
+        method'' originally developed by Baker and Ross
         \cite{baker_comparison_1963}.  This technique has also been used in the
@@
 
-Cyclus' discrete materials make single-pass recycle straightforward to implement.  The
+\Cyclus' discrete materials make single-pass recycle straightforward to implement.  The
 reactors keep track of fuel as discrete batches. A reactor remembers where it
@@
 \begin{center}
-\includegraphics{./images/flow-mod-open-1.eps}
+\includegraphics[width=\textwidth]{./images/flow-mod-open-1.eps}
 \end{center}
@@
 \begin{center}
-\includegraphics{./images/flow-closed-1.eps}
+\includegraphics[width=\textwidth]{./images/flow-closed-1.eps}
 \end{center}
@@
 \begin{center}
-\includegraphics{./images/puseries-1.eps}
+\includegraphics[width=\textwidth]{./images/puseries-1.eps}
 \end{center}

### 2015-11-30 fundamentals/intro.tex
replaced 'current tools are typically privately distributed having been developed in industrial contexts' with 'current tools are typically distributed under restrictive rather than open source licenses, having been developed in industrial contexts or using commercial software platforms.'

@@
 
-To date, current tools are typically privately distributed rather than open
-source, having been developed in industrial contexts. Additionally, having
+To date, current tools are typically distributed under restrictive rather than open
+source licenses, having been developed in industrial contexts or using 
+commercial software platforms. Additionally, having
 often been developed for customized applications, many possess inflexible

### 2015-11-30 fundamentals/intro.tex
On line 17, replaced 'inflexible architectures' with 'inflexible architectures, never having been designed to enable new features or extensions.'
line 67, changed to radiotoxicity and mined uranium requirements. left out the suggestion of noting the energy normalization, given that the derived metrics are discussed later in the paragraph

@@
 often been developed for customized applications, many possess inflexible
-architectures. Finally, many model only fleet-level dynamics of facilities and
+architectures, never having been designed to enable new features or extensions.
+Finally, many model only fleet-level dynamics of facilities and
 materials rather than discrete resolution of those individual agents and
@@
 combination of fuel and operating costs normalized by electricity generation, while
-environmental performance might be measured by spent fuel volume, toxicity, or
-mined uranium.  A meta-analysis of fuel cycle systems studies identified over
+environmental performance might be measured by spent fuel volume, radiotoxicity, or
+mined uranium requirements. A meta-analysis of fuel cycle systems studies 
+identified over
 two dozen unique quantitative metrics spanning economics and cost,

### 2015-11-30 fundamentals/intro.tex
line 102 -- added 'and facility types'

@@
 nuclear fuel cycle analysis community to achieve two important goals: lower the
-barrier for users to include custom nuclear technologies in their fuel cycle
+barrier for users to include custom nuclear technologies and facility types in 
+their fuel cycle
 analyses while improving the ability to compare simulations with and without

### 2015-11-30 fundamentals/fcsreqs.tex
line 160 adds a note about what platform CAFCA relies on (VENSIM)

@@
 FAMILY21, \gls{NFCSim})\cite{juchau_modeling_2010}, including ORION,
-and \gls{VISION}.  Even when, as in the case of the MIT \gls{CAFCA} software,
-the source code is unrestricted, the platform on which it relies is often
-restricted or costly.  However, \Cyclus provides fully free and open access to
-all users and developers, foreign and domestic.
+and \gls{VISION}.  Even when the source code is unrestricted, the platform on which it relies (e.g. VENSIM) 
+is often restricted or costly. The MIT \gls{CAFCA} software, for example, 
+relies on the commercially licensed VENSIM product as a platform.
+\Cyclus, on the other hand, provides fully free 
+and open access to all users and developers, foreign and domestic.
 

### 2015-11-30 fundamentals/fcsreqs.tex
line 161 added a comment about cyclus written in c++ and, therefore, the availability of development tools and standards

@@
 relies on the commercially licensed VENSIM product as a platform.
-\Cyclus, on the other hand, provides fully free 
-and open access to all users and developers, foreign and domestic.
+\Cyclus, on the other hand, is written in C++ for which freely available 
+developement tools and an open standard are available. Further, \Cyclus relies 
+only on open source, freely available libraries. As such, it provides fully 
+free and open access to all users and developers, foreign and domestic.
 

### 2015-11-30 fundamentals/impl.tex
adds examples of resource computing as a parenthetical. Indeed, we did mean cloud and cluster computing

@@
 However, many fuel cycle simulators rely on \gls{COTS} and Windows-only software that limits
-performance on and compatibility with resource computing infrastructures. This
+performance on and compatibility with resource computing infrastructures (e.g. 
+cluster or cloud computing). This
 constrains the possible scope of simulations and increases the wall-clock time necessary to conduct parameterized sensitivity

### 2015-11-30 fundamentals/impl.tex
proof of principle -> proof-of-principle

@@
 
-Cyclopts \cite{gidden_cyclopts_2015}, a proof of principle design and
+Cyclopts \cite{gidden_cyclopts_2015}, a proof-of-principle design and
 implementation of a \Cyclus-enabled application on such a large compute system,

### 2015-11-30 fundamentals/impl.tex
line 339: made a slight change to the superiority claim about abm vs system dynamics. This will require a little more editing to satisfy the need to unpack the paragraph.
figure 3: makes figure 3 bigger

@@
 
-Furthermore, the \gls{ABM} paradigm is superior to the system dynamic approach used in
-current simulators.
+Furthermore, the \gls{ABM} paradigm more flexible than the system dynamic approach used in current simulators.
 System dynamics is a popular approach for modeling nuclear fuel cycles
@@
 For the archetype developer, these interfaces provide enormous power
-very simply. The \gls{API} abstracts away unnecessary detail while providing
+very simply. The \gls{API} abstracts away details unnecessary to specifying the 
+archetype behavior, while providing
 all necessary functionality for interacting with the \Cyclus simulation kernel.
@@
 \begin{center}
-\includegraphics[width=0.5\textwidth]{./images/agent_uml}
+\includegraphics[width=\textwidth]{./images/agent_uml}
 \end{center}

### 2015-11-30 fundamentals/impl.tex
line 398: adds example of spent fuel cask transport optimization

@@
 regions are the parents of institutions which are, in turn, the parents of
-facilities. In other words, \gls{RIF} hierarchies form a directed acyclic graph (DAG),
+facilities. In other words, \gls{RIF} hierarchies form a \gls{DAG},
 with regions as root nodes and facilities as leaf nodes.
@@
 of individual facilities and materials. As a result, many detailed performance
-metrics cannot be captured with previously existing fleet-based models. For all
+metrics cannot be captured with previously existing fleet-based models. For 
+example, to meaningfully optimize the cost and environmental impact of spent 
+nuclear fuel storage, transport, and disposal strategies, discrete casks and 
+their varying isotopic compositions must be taken into account.
+
+For all
 of the reasons that the \gls{ABM} paradigm in \ref{sec:abm} enables novel

### 2015-11-30 fundamentals/examples.tex
fixes figwidth
line 785 explains heavy metals

@@
 \Class{cycamore::Reactor} & batches & $3$ [batches/cycle]\\
-                  & batch size & $20000$ [kg HM]\\
+                  & batch size & $20$ [MTHM]\\
                   & cycle length & $18$ [months]\\
@@
         core. The reactor was configured to model a light water reactor
-        with a 3 batch core (20,000 kg HM per batch) operating on an 18 month
-        cycle with a 2 month refuel time.  The reactor was also configured to
+        with a 3 batch core operating on an 18 month
+        cycle with a 2 month refuel time.  The batches in the core each contain 
+        20 \gls{MTHM}, where heavy metals are actinide elements like thorium, 
+        uranium, and plutonium. The reactor was also configured to
         take in either enriched \gls{UOX} fuel or recycled \gls{MOX} fuel.
@@
 \begin{center}
-\includegraphics{./images/puseries-n.eps}
+\includegraphics[width=\textwidth]{./images/puseries-n.eps}
 \end{center}

### 2015-11-30 fundamentals/impl.tex
line 649 deleted unneccessary and somewhat untrue comment about regression tests
line 616: the authors did indeed mean git. We rearranged the sentence so that the word git does not appear near the word tool. this will avoid the concern that it might be a typo meaning toolkit. it will not fix the reviewers being English, however.

@@
 
-Automated version control, provided by the well-established \emph{distributed
-  version control} tool git \cite{software_freedom_conservancy_git_2014}, is
+Automated version control, provided by git, a well-established \emph{distributed
+  version control} tool \cite{software_freedom_conservancy_git_2014}, is
 at the heart of the QA strategy because it records the full history of any
@@
 Regression tests ensure significant unintended changes do not
-occur over the course of \Cyclus development. Such a change is called a
-\emph{regression} because the new version is almost always wrong.
+occur over the course of \Cyclus development.
 Regression tests are implemented similarly to integration tests.

### 2015-11-30 fundamentals/impl.tex
line 670: fixes automoated->automated
line 339: fleshing out the superior -> flexible statement a bit

@@
 
-Furthermore, the \gls{ABM} paradigm more flexible than the system dynamic approach used in current simulators.
+Furthermore, the \gls{ABM} paradigm more flexible and intuitive (from both a developer and user perspective) than the system dynamic approach used in current simulators.
 System dynamics is a popular approach for modeling nuclear fuel cycles
@@
 
-Autmoated testing including \gls{CI} is a necessary but not sufficient
+Autmated testing including \gls{CI} is a necessary but not sufficient
 component of the \Cyclus \gls{QA} system: it keeps bad code out of

### 2015-11-30 fundamentals/impl.tex
added a footnote about DAGs

@@
 regions are the parents of institutions which are, in turn, the parents of
-facilities. In other words, \gls{RIF} hierarchies form a \gls{DAG},
+facilities. In other words, \gls{RIF} hierarchies form a \gls{DAG}\footnote{
+\gls{DAG}s are common graph theoretic structures whose most important feature is a 
+lack of \emph{cycles}, i.e., there is a single path from the root node to any other 
+node in the graph. 
+},
 with regions as root nodes and facilities as leaf nodes.

### 2015-11-30 fundamentals/impl.tex
takes @gidden suggestion about rewording.

@@
 metrics cannot be captured with previously existing fleet-based models. For 
-example, to meaningfully optimize the cost and environmental impact of spent 
-nuclear fuel storage, transport, and disposal strategies, discrete casks and 
-their varying isotopic compositions must be taken into account.
+example, meaningful models of spent nuclear fuel storage transport, and
+disposal strategies, require representation of discrete casks and their varying
+isotopic compositions.
 

### 2015-12-11 fundamentals/fcsreqs.tex

@@
 discharged batch. By extension, \Cyclus can also report which individual
-facilities the batch passed through and in which it originated. The
-nonproliferation-related applications of this analysis capability are
-significant - allowing \Cyclus to answer questions that previous simulators
-have been unable to ask.
+facilities the batch passed through and in which it originated. 
+The ability to track a single material through the simulation, 
+though it might be split, transmuted, or merged with other materials along the 
+way, allows \Cyclus to answer more data-rich questions that previous simulators
+have been unable to ask. For example, it allows precise tracking of 
+specific material diversions, so queries about nonproliferation 
+robustness in a facility can be levied either in the context of a single event or 
+a series of nefarious acts.

### 2015-12-11 fundamentals/impl.tex

@@
 
-Furthermore, the \gls{ABM} paradigm more flexible and intuitive (from both a developer and user perspective) than the system dynamic approach used in current simulators.
+Furthermore, the \gls{ABM} paradigm is more flexible and intuitive (from both a developer and user perspective) than the system dynamic approach used in current simulators.
 System dynamics is a popular approach for modeling nuclear fuel cycles
@@
 
-Autmated testing including \gls{CI} is a necessary but not sufficient
+Automated testing including \gls{CI} is a necessary but not sufficient
 component of the \Cyclus \gls{QA} system: it keeps bad code out of

### 2015-12-12 fundamentals/fcsreqs.tex
going for brevity, I delete unneccessary uses of words like very and currently.

@@
 are narrowly confined and place no new requirements on the \Cyclus kernel.
-Furthermore, there are very few assumptions or heuristics that would otherwise
+Furthermore, there are few assumptions or heuristics that would otherwise
 restrict the algorithmic complexity that can be used to model the behavior of

### 2015-12-12 fundamentals/impl.tex
going for brevity, I delete unneccessary uses of words like very and currently.

@@
 For the archetype developer, these interfaces provide enormous power
-very simply. The \gls{API} abstracts away details unnecessary to specifying the 
+simply. The \gls{API} abstracts away details unnecessary to specifying the 
 archetype behavior, while providing
@@
 invoke the decay function on them as desired to decay them to the current
-simulation time. \Cyclus can currently operate in 3 decay modes, with 1 additional
+simulation time. \Cyclus can operate in 3 decay modes, with 1 additional
 mode likely to be added in a future release:
@@
 testing are shown to code reviewers prior to reviewing the software changes themselves.  The \Cyclus
-project currently uses the CircleCI \cite{biggar_circleci_2015} service for continuous integration.
+project uses the CircleCI \cite{biggar_circleci_2015} service for continuous integration.
 Whenever a pull request is created, CircleCI builds a version of the \Cyclus

### 2015-12-12 fundamentals/impl.tex
minor correction to the phrasing of the purpose of the modular architecture.

@@
 
-A modular, \acrfull{ABM} approach is ideal for solving the coupled,
+A modular, \acrfull{ABM} approach is ideal for modeling the coupled,
 physics-dependent supply chain problems involving material routing, facility
-deployment, and regional and institutional hierarchies which arise in \Cyclus. Additionally, the choice
+deployment, and regional and institutional hierarchies which arise in the 
+nuclear fuel cycle. Additionally, the choice
 to build \Cyclus on open source libraries in modern programming languages

### 2015-12-28 fundamentals/impl.tex
arise in cyclus -> arise in fuel cycle analysis

--- 2015-12-11 fundamentals/impl.tex
@@
 physics-dependent supply chain problems involving material routing, facility
-deployment, and regional and institutional hierarchies which arise in \Cyclus. Additionally, the choice
+deployment, and regional and institutional hierarchies which arise in fuel 
+cycle analysis. Additionally, the choice
 to build \Cyclus on open source libraries in modern programming languages

### 2015-12-29 fundamentals/examples.tex
line 754: indeed, we did mean figure 3, rather than figure 1. fixed.
clarifies HTC, formats figures for two column layout

@@
 \centering
-\begin{tabularx}{\textwidth}{|r|X|r|}
+\begin{tabularx}{\columnwidth}{|r|X|r|}
 \hline
@@
 Early progress has been promising. Many archetypes external to the \Cycamore
-library (Table \ref{tab:cycamore}) have been
+library (Table \ref{tab:archetypes}) have been
 \cite{huff_streamblender_2014,huff_commodconverter_2014} or are being
@@
 
-\begin{table}[H]
+\begin{table*}[H]
 \centering
-\begin{tabularx}{\textwidth}{|r|X|r|}
+\begin{tabularx}{\columnwidth}{|r|X|r|}
 \hline
@@
 \label{tab:archetypes}
-\end{table}
+\end{table*}
 
@@
 
-\begin{table}[H]
+\begin{table*}[H]
 \centering
-\begin{tabularx}{\textwidth}{|X|r|X|}
+\begin{tabularx}{\columnwidth}{|X|r|X|}
 \hline
@@
 \hline
-\textbf{Recycled Fuel Fabrication} & requests & depleted uranium\\
+\textbf{Spent Fuel Fabrication} & requests & depleted uranium\\
 \Class{cycamore::Fab} & requests & separated fissile material\\
@@
 \label{tab:facconfigs}
-\end{table}
+\end{table*}
 
@@
 
-    \item \textbf{Recycled Fuel Fabrication} (\Class{cycamore::Fab}): This
+    \item \textbf{Spent Fuel Fabrication} (\Class{cycamore::Fab}): This
         facility requests depleted uranium and separated fissile material and
@@
 \begin{center}
-\includegraphics[width=\textwidth]{./images/flow-mod-open-1.eps}
+\includegraphics[width=\columnwidth]{./images/flow-mod-open-1.eps}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=\textwidth]{./images/flow-closed-1.eps}
+\includegraphics[width=\columnwidth]{./images/flow-closed-1.eps}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=\textwidth]{./images/puseries-1.eps}
+\includegraphics[width=\columnwidth]{./images/puseries-1.eps}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=\textwidth]{./images/puseries-n.eps}
+\includegraphics[width=\columnwidth]{./images/puseries-n.eps}
 \end{center}

### 2015-12-29 fundamentals/impl.tex
clarifies HTC, formats figures for two column layout

@@
 
-Innovative approaches to designing and optimizing robust fuel cycle strategies can become available by leveraging modern parallel computing resources.
-For example, large scale sensitivity analyses to quantify the dependence of fuel cycle outcomes on potentially hundreds of uncertain parameters would only be feasible in a massively parallelized environment.
-However, many fuel cycle simulators rely on \gls{COTS} and Windows-only software that limits
-performance on and compatibility with resource computing infrastructures (e.g. 
-cluster or cloud computing). This
-constrains the possible scope of simulations and increases the wall-clock time necessary to conduct parameterized sensitivity
-analyses and other multi-simulation studies. \Cyclus, on the other hand, is
-primarily written in \texttt{C++} and relies on
-libraries supported by Linux and UNIX (including Ubuntu and OSX) platforms,
-which are flexible and support parallelization.
-Furthermore, the core infrastructure and related archetypes are free and
-open source, BSD-3-clause licensed.  \Cyclus can therefore be easily deployed
-on large computer systems, such as \gls{HTC} systems.
+Many fuel cycle simulators rely on \gls{COTS} and Windows-only software that 
+limits performance on and compatibility with resource computing infrastructures 
+(e.g.  cluster or cloud computing). This constrains the possible scope of 
+simulations and increases the wall-clock time necessary to conduct 
+parameterized sensitivity analyses and other multi-simulation studies.  For 
+example, large scale sensitivity analyses to quantify the dependence of fuel 
+cycle outcomes are only feasible in a massively parallelized environment.  
+To enable such research, \Cyclus, is primarily written in \texttt{C++} and 
+relies on libraries supported by Linux and UNIX (including Ubuntu and OSX) 
+platforms, which are flexible and support parallelization.
 
-Cyclopts \cite{gidden_cyclopts_2015}, a proof-of-principle design and
-implementation of a \Cyclus-enabled application on such a large compute system,
-uses UW-Madison's HTCondor \gls{HTC} infrastructure to study DRE performance and
+Cyclopts \cite{gidden_cyclopts_2015}, a proof-of-principle \Cyclus-enabled 
+application on such a large compute system,
+uses UW-Madison's HTCondor \gls{HTC} infrastructure to study \gls{DRE} performance and
 outcomes. For example, an investigation of the effect of solution degeneracy, a
@@
 \begin{center}
-\includegraphics[width=\textwidth]{./images/framework}
-\end{center}
+\includegraphics[width=\columnwidth]{./images/framework}
 \caption{The \Cyclus core provides \glspl{API} that abstract away the details in
@@
 fashion.}
+\end{center}
 \label{fig:framework}
@@
 \begin{center}
-\includegraphics[width=0.5\textwidth]{./images/modifiedopen.eps}
-\end{center}
+\includegraphics[width=\columnwidth]{./images/modifiedopen.eps}
 \caption{The \Cyclus framework enables fully open, partially open, and fully
 closed collaborations\cite{carlsen_cyclus_2014}.}
+\end{center}
 \label{fig:modifiedopen}
@@
 \begin{center}
-\includegraphics[width=\textwidth]{./images/agent_uml}
+\includegraphics[width=\columnwidth]{./images/agent_uml}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=\textwidth]{./images/compositions}
+\includegraphics[width=\columnwidth]{./images/compositions}
 \end{center}
@@
 
-\begin{table}[H]
+\begin{table*}[H]
 \centering
@@
 \label{tab:cycamore}
-\end{table}
+\end{table*}
 

### 2015-12-29 fundamentals/examples.tex
table cleanup

@@
 \hline
-Cycic &  Input control - embedded in Cyclist & \cite{flanagan_input_2013}\\
+Cycic &  Input control embedded in Cyclist & \cite{flanagan_input_2013}\\
 Cyclist & Interactive data exploration environment & \cite{livnat_cyclist_2014} \\

### 2015-12-29 fundamentals/impl.tex
figure and table adjustments for final submission
reduces length of qa section at request of reviewer 2

@@
 
-\begin{figure}[htbp!]
+\begin{figure}[htbp]
 \begin{center}
@@
 
-\begin{figure}[htbp!]
+\begin{figure}[htbp]
 \begin{center}
-\includegraphics[width=\columnwidth]{./images/modifiedopen.eps}
+\includegraphics[width=0.8\columnwidth]{./images/modifiedopen.eps}
 \caption{The \Cyclus framework enables fully open, partially open, and fully
@@
 
-\begin{table*}[H]
+\begin{table*}[htb]
 \centering
-\begin{tabularx}{\textwidth}{|r|l|X|}
+\begin{tabularx}{\textwidth}{rlX}
 \hline
@@
 Automated software \emph{testing} is the first line of defense against
-errors in implementation. It also acts as an early warning sign if the
-simulator does not work as intended on a new system.
-Testing serves a critical role in \gls{QA} because it directly compares the
-results of running software versus the expected behavior of the software.
+errors in implementation. Testing directly compares the
+actual results of running software versus the expected behavior of the software.
 In \Cyclus, three categories of tests are defined: unit tests, integration
-tests, and regression tests.  It is important to note that before a proposed
-code change is allowed into \Cyclus,  the change must be covered by a test, either new or existing, and all tests must pass.
+tests, and regression tests.  Before a proposed code change is allowed into 
+\Cyclus,  the change must be covered by a test, either new or existing, and all 
+tests must pass.
 
@@
 
-Unit tests compare the results of the smallest code \emph{unit}, typically a
+Unit tests verify behavior of the smallest code \emph{unit}, typically a
 single function or a class.  \Cyclus uses the Google Test framework
@@
 In \Cyclus and \Cycamore, integration tests are performed by running sample
-simulations for scenarios that are sufficiently simple to predict the results
-and verifying that results match those predictions. A set of standard input
+simulations for scenarios verifying that results match predictions. A set of standard input
 files are run, then the output is inspected and compared via Nose
-\cite{pellerin_nose_2007}, a Python test framework.  In this way, \Cyclus code
-units are tested in the full context that they will be
-executed. This category of testing is especially useful for ensuring that
-major \Cyclus components are functioning as expected.
+\cite{pellerin_nose_2007}, a Python test framework.
 
@@
 
-\Gls{CI} is the idea that software should be tested
+\Gls{CI} is the idea that software should be automatically tested
 and validated as it is being developed, rather than as a final stage in a
-longer development cycle.  Under \gls{CI}, every pull request is automatically
-tested independently, immediately as it is proposed. The results of this
+longer development cycle.  The results of this
 testing are shown to code reviewers prior to reviewing the software changes themselves.  The \Cyclus
 project currently uses the CircleCI \cite{biggar_circleci_2015} service for continuous integration.
-Whenever a pull request is created, CircleCI builds a version of the \Cyclus
+When a code change is submitted for review, CircleCI builds a version of the \Cyclus
 source code that includes the requested changes and runs the complete test
@@
 was not successful, the code author(s) must first identify and resolve the 
-problems.
-
-Since these steps are performed for all incoming code, it is easy for the
-\Cyclus core team to determine whether or not an individual pull request
-actually works. This helps identify build and test problems prior to broken
-code being allowed into the main software development branch.
+problems.  These steps are performed for all incoming code prior to inclusion, 
+so broken code never enters the main software development branch.
 
@@
 
-Once \gls{CI} is successful, a code reviewer inspects not only the
-changes that are proposed to the software itself, but also the changes that
-have been proposed to tests.  It is important that the subset of tests that
-are relevant to the software change has a scope and completeness that will
-ensure that incorrect behavior will be automatically detected.  If there are
-sufficent tests and \gls{CI} is successful, the reviewer can proceed to
-considering the actual software changes themselves.
+Once \gls{CI} is successful, a code reviewer inspects not only the changes that 
+are proposed to the software itself, but also the changes that have been 
+proposed to tests.
 
-Because of their role in facilitating code review during the change process,
-as well as their long term benefit to the maintainability of the project,
-documentation and coding style are also reviewed as part of this process.
-
-\paragraph{Documentation}
-
-All of the public interface (the \gls{API}) must be documented as required by
-the \Cyclus \gls{QA} policy. This certifies that the intended goals of an
-\gls{API} are communicated explicitly by the author in prose form.  In \Cyclus,
-this information is aggregated together into static websites with the Doxygen
-\cite{van_heesch_doxygen:_2008} and Sphinx \cite{brandl_sphinx_2014} tools, and
-can be accessed at \url{http://fuelcycle.org}.
-
-\paragraph{Style Guide}
-
-In any multi-person software project, there is a tension between how individuals
-wish to write code. Every person tends to have their own custom style. To remedy this,
-coding style guides are the software analogy to those for written language,
-such as the Chicago Manual of Style. \Cyclus strictly enforces the use of the
-Google C++ Style Guide \cite{weinberger_google_2008} for all software contributions.
-This means that all developers of \Cyclus nominally write \Cyclus code in the same
-way.  This homogenization may be a hurdle to new developers but ultimately
-improves code legibility and, therefore, robustness \cite{cohen_modern_2010}.
+Because of their long term benefit to the maintainability of the project, 
+documentation and coding style are also reviewed as part of this process.  The 
+\gls{API} must be documented as required by the \Cyclus \gls{QA} policy.  In 
+\Cyclus, this information is aggregated together into static websites with the 
+Doxygen \cite{van_heesch_doxygen:_2008} and Sphinx \cite{brandl_sphinx_2014} 
+tools, and can be accessed at \url{http://fuelcycle.org}. \Cyclus also strictly 
+enforces the use of the Google C++ Style Guide \cite{weinberger_google_2008} 
+for all software contributions.  This means that all developers of \Cyclus 
+write \Cyclus code in the same way.  This homogenization may be a hurdle to new 
+developers but ultimately improves code legibility and, therefore, robustness 
+\cite{cohen_modern_2010}.

### 2015-12-30 fundamentals/examples.tex
figure and table adjustments for final submission
reduces length of qa section at request of reviewer 2
Adds references to previous benchmarking work

@@
 
-\begin{table}[H]
+\begin{table*}[htb]
 \centering
-\begin{tabularx}{\columnwidth}{|r|X|r|}
+\begin{tabularx}{\textwidth}{rXr}
 \hline
-\textbf{Name} & \textbf{Description} & \textbf{Citation} \\
+\textbf{Name} & \textbf{Description} & \textbf{Ref.} \\
 \hline
@@
 \label{tab:coretools}
-\end{table}
+\end{table*}
 
@@
 
-\begin{table*}[H]
+\begin{table*}[htb]
 \centering
-\begin{tabularx}{\columnwidth}{|r|X|r|}
+\begin{tabularx}{\textwidth}{rXr}
 \hline
-\textbf{Name} & \textbf{Description} & \textbf{Citation} \\
+\textbf{Name} & \textbf{Description} & \textbf{Ref.} \\
 \hline
@@
 creation and results of a range of representative fuel cycle simulations.
-These examples are not the limit of \Cyclus' capabilities, which are extended with each new
+Previous benchmarks between 
+\Cyclus and system dynamics simulators for more complex problems, including 
+transition analyses, have been reported 
+elsewhere and \Cyclus has demonstrated satisfactory performance
+\cite{djokic_application_2015,scopatz_non-judgemental_2015,gidden_once-through_2012} . 
+The current examples are not the limit of \Cyclus' capabilities, which are extended with each new
 addition to the ecosystem, as discussed above.  Rather, these simulations are
@@
 recipe-based simulator and that variations on a single \Cyclus simulations can 
-be run with small changes to the input specification. For simplicity of the 
-demonstration, many simplifying assumptions have been
+be run with small changes to the input specification. 
+For simplicity of the current demonstration, many simplifying assumptions have been
 made with respect to material compositions, fuel transmutation, among others.
@@
 
-\begin{table*}[H]
+\begin{table*}[htb]
 \centering
-\begin{tabularx}{\columnwidth}{|X|r|X|}
+\begin{tabularx}{\textwidth}{XrX}
 \hline
@@
 \end{table*}
+\twocolumn
 
@@
 
-\begin{figure}[H]
+\begin{figure}
 \begin{center}
@@
 
-\begin{figure}[H]
+\begin{figure}[htb]
 \begin{center}

### 2015-12-30 fundamentals/examples.tex
adds image and eqns for LP formulation

@@
 elsewhere and \Cyclus has demonstrated satisfactory performance
-\cite{djokic_application_2015,scopatz_non-judgemental_2015,gidden_once-through_2012} . 
-The current examples are not the limit of \Cyclus' capabilities, which are extended with each new
+\cite{djokic_application_2015,scopatz_non-judgemental_2015,gidden_agent-based_2015,gidden_once-through_2012} . 
+The examples presented here are not the limit of \Cyclus' capabilities, which are extended with each new
 addition to the ecosystem, as discussed above.  Rather, these simulations are

### 2015-12-30 fundamentals/impl.tex
adds image and eqns for LP formulation

@@
 included an investigation of problem-scaling behavior in order to quantify the
-magnitude and rate-of-increase of DRE solution times as a function of the
+magnitude and rate-of-increase of \gls{DRE} solution times as a function of the
 simulation-entity population for each fuel
@@
 
-Given a full definition of supply and demand, the \gls{DRE} may be solved either
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[width=\columnwidth]{./images/bid_req}
+\end{center}
+\caption{The flow graph representing three suppliers (left), two requesters (right), 
+and the potential flows of various commodities among them. 
+The second consumer makes two different requests.
+Meanwhile, the second supplier can supply the commodities 
+requested by both consumers and has provided two bids accordingly 
+\cite{gidden_agent-based_2015}.}
+\label{fig:bid_req}
+\end{figure}
+
+Given a full definition of supply and demand, represented in Figure 
+\ref{fig:bid_req} as a flow graph, the \gls{DRE} may be solved either
 optimally using a mathematical program or approximately by a simulation-based
@@
 or exchanges must be represented as a \gls{MILP}. If no exclusive trades exist,
-a \gls{LP} model may be used. In practice, \glspl{LP} solve much faster than
+a \gls{LP} model may be used. The \gls{LP} formulation in \Cyclus is of the 
+form given by Gidden \cite{gidden_agent-based_2015}:
+
+\begin{align}
+\min_{x} z &= \sum_{i\in I}\sum_{j\in J} c_{i,j}x_{i,j}& &\\
+s.t & \sum_{i\in I_s}\sum_{j\in J} a_{i,j}^k x_{i,j} \le b_s^k & & \forall k\in K_s, \forall s\in S\\
+    & \sum_{J\in J_r}\sum_{i\in I} a_{i,j}^k x_{i,j} \le b_r^k & & \forall k\in K_r, \forall r\in R\\
+    & x_{i,j} \in [0,x_j] & & \forall i\in I, \forall j\in J
+\end{align}
+\begin{align}
+\intertext{where}
+S &= \mbox{suppliers}\nonumber\\
+R &= \mbox{requesters}\nonumber\\
+I_s &= \mbox{supply nodes for a supplier s}\nonumber\\
+J_r &= \mbox{all request nodes for a requester r}\nonumber\\
+K_s &= \mbox{constraints for a supplier s}\nonumber\\
+K_r &= \mbox{constraints for a requester r}\nonumber\\
+X &= \mbox{potential commodity flows}\nonumber\\
+c_{i,j} &= \mbox{unit cost of flow from i to j}\nonumber\\
+x_{i,j} &= \mbox{flow from node i to node j}\nonumber\\
+a^k_{i,j} &= \mbox{constraint coeffiecient between i and j}\nonumber\\
+b^k_s  &= \mbox{constraint k of supplier s}\nonumber\\
+b^k_r &= \mbox{constraint k of requester r}\nonumber\\
+\tilde{x}_j &= \mbox{requested quantity of request node j.}\nonumber
+\end{align}
+
+In practice, \glspl{LP} solve much faster than
 \glspl{MILP}. However, both capabilities exist in \Cyclus in order to

### 2015-12-31 fundamentals/impl.tex

@@
 \begin{align}
-\min_{x} z &= \sum_{i\in I}\sum_{j\in J} c_{i,j}x_{i,j}& &\\
-s.t & \sum_{i\in I_s}\sum_{j\in J} a_{i,j}^k x_{i,j} \le b_s^k & & \forall k\in K_s, \forall s\in S\\
-    & \sum_{J\in J_r}\sum_{i\in I} a_{i,j}^k x_{i,j} \le b_r^k & & \forall k\in K_r, \forall r\in R\\
-    & x_{i,j} \in [0,x_j] & & \forall i\in I, \forall j\in J
+\min_{x} \: \: & z = c^\top x \\
+\text{s.t.} \: \:  & A x \leq b \\
+    & x_{i,j} \in [0, \tilde{x}_j] \: \:  \forall i \in I, \forall j \in J
 \end{align}
@@
 \intertext{where}
-S &= \mbox{suppliers}\nonumber\\
-R &= \mbox{requesters}\nonumber\\
-I_s &= \mbox{supply nodes for a supplier s}\nonumber\\
-J_r &= \mbox{all request nodes for a requester r}\nonumber\\
-K_s &= \mbox{constraints for a supplier s}\nonumber\\
-K_r &= \mbox{constraints for a requester r}\nonumber\\
-X &= \mbox{potential commodity flows}\nonumber\\
+I &= \mbox{set of supply nodes}\nonumber\\
+J &= \mbox{set of request nodes}\nonumber\\
 c_{i,j} &= \mbox{unit cost of flow from i to j}\nonumber\\
 x_{i,j} &= \mbox{flow from node i to node j}\nonumber\\
-a^k_{i,j} &= \mbox{constraint coeffiecient between i and j}\nonumber\\
-b^k_s  &= \mbox{constraint k of supplier s}\nonumber\\
-b^k_r &= \mbox{constraint k of requester r}\nonumber\\
+a^k_{i,j} &= \mbox{coefficient for constraint k between i and j}\nonumber\\
+b^k_{s \mid r} &= \mbox{RHS for constraint k for a given supplier or requester}\nonumber\\
 \tilde{x}_j &= \mbox{requested quantity of request node j.}\nonumber

### 2016-01-05 fundamentals/review_response_aes.md

# Detailed Responses to Review Comments

The comments by each reviewer follow. A bullet point following each comment 
summarizes the changes we have made to the paper. We appreciate all of the 
suggestions made by the reviewers and dispute none of them.

## Reviewer 1

Line 15: You indicate "current tools are typically privately distributed" - 
such as? Reviewer can think of ORION and possibly COSI - are there others? 
(Indicate examples if possible)

- We replaced 'current tools are typically privately distributed having been 
  developed in industrial contexts' with 'current tools are typically 
  distributed under restrictive rather than open source licenses, having been 
  developed in industrial contexts or using commercial software platforms.'

Line 17: "inflexible architectures" - authors  explain this a little more later 
in the paper, but consider expanding your meaning briefly here.

- On line 17, we replaced 'inflexible architectures' with 'inflexible 
  architectures, never having been designed to enable new features or 
  extensions.'

Line 67: toxicity is best described as radiotoxicity; mined uranium is mined 
uranium requirements. Meanwhile it's probably useful to express these in terms 
of per unit energy.

- On line 67, we changed to radiotoxicity and mined uranium requirements. 
  Explanation of the energy normalization is covered by discussion of the 
  derived metrics are discussed later in the paragraph.

Line 102: "nuclear technologies" - probably better described as nuclear 
technologies and facility types.

- On line 102, we added 'and facility types.'

Line 160: What platform does CAFCA rely upon? (Simulink? PowerSim? VISION for 
example relies on PowerSim; even when universities are able to get their hands 
on it, modification is indeed difficult because of the proprietary software 
requirement).

- On line 160, we added a note about what platform CAFCA relies on (VENSIM).

Line 161: I think it's important to note here in this context that Cyclus is 
based on C++, where development tools are freely available and an open, 
well-documented standard.

- On line 161 we added a comment indicating that cyclus is written in c++ and, 
  therefore, the availability of development tools and standards.

Line 227: What kind of nonproliferation applications is this 
significant to? What kinds of questions *can* Cyclus answer? This need 
not be terribly explicit, but I would suggest giving some further 
detail rather than alluding to it and then leaving it unspecified.

- On line 227 we added an example of a type of nonproliferation analysis that 
  is enabled by discrete material tracking.

Line 270: "Resource computing infrastructures" - this term might 
warrant further definition. (I assume you mean systems like cloud 
computing and batch scheduling computing clusters.)

- We added examples of resource computing as a parenthetical. Indeed, we 
  did mean cloud and cluster computing

Line 278: proof-of-principle

- We fixed proof of principle -> proof-of-principle.

Line 339: "is superior to the system dynamic approach." I feel like a 
claim is being made here about superiority without much substantiation 
or expression of what the merit criteria is. This paragraph could use 
some further unpacking.

- On line 339 we made a change to the superiority claim about ABM vs 
  system dynamics to more clearly explain that the superiority is simply 
  greater generality. ABM is a more general modeling framework. All system 
  dynamics problems can be modeled in an ABM  paradigm, but the reverse is not 
  true. See Macal et al.

Line 353: "The API abstracts away unnecessary detail" => suggest 
phrasing as "abstracts away details unnecessary to the implementation 
of the archetype-specific behavior"

- We have now made this change exactly as suggested.

Figure 3 could be a bit bigger.

-  We have now made figure 3 the full width of the text column.

Line 379: Directed acyclic graph: I suspect most readers will not be 
familiar with graph theory. A brief explanation and unpacking of the 
relevant context would be useful here.

- We added a few sentences defining directed acyclic graphs in the context 
  of the DRE.

Line 398: "However, some questions require resolution at the level of 
individual facilities and materials." Such as? No need to go into 
explicit detail here, but given that you're building a case for 
flexible scoping, it would be helpful to produce a few examples that 
help to make your case. (For example, detailed isotopic analysis for 
thermal recycle vs. recipes. Nonproliferation applications. Etc.)

- On line 398 we added an example of spent fuel cask transport optimization.

Line 649: "because the new version is almost always wrong." This 
wording seems dangerously unclear. I think the intent is to say that 
deviation from prior, blessed results is almost always wrong (unless 
the change is expected, obviously). What is "wrong" are departures in 
results from a baseline.

- On line 649 we deleted the unnecessary comment about regression tests.

Line 785: Define heavy metal (and its abbreviation) for non-nuclear 
engineers.

- On line 785 we added a parenthetical explanation of heavy metals targeted at 
  non-nuclear engineers.

Line 798: Is uranium not also recovered in this simulation? (Is it 
directed into waste? It may be helpful to explicitly indicate this.)

- It is recovered along with the plutonium and fabricated into MOX. The metric 
  of interest, plutonium buildup, does not capture the uranium flows. This has 
  now been clarified in the text within the Spent Fuel Fabrication facility 
  description.

## Reviewer 2

(1) The article is not a manual. The manuscript provides unnecessary 
details which are not directly used in analysis at the end.

- We generally reduced the extent to which ancillary topics were discussed. 
  These include the Cyclus quality assurance process and the implementation 
  details of modular dynamic library loading. Such discussion was reduced
  significantly, resulting in a total length reduction of many paragraphs.

(2) Comparison between the code and existing system dynamics codes is 
useful to understand why the author's  model is better and needed.

- A summary and references to three previous code-to-code validation efforts 
  have been added. Those previous verification studies, published elsewhere, 
  cannot be replicated here in their entirety. However, their citations will 
  lead the reader to the comparisons needed.  Cyclus performed well in these 
  verifications and demonstrated, in particular, the importance of discrete 
  facility and material tracking during transition analyses. The example chosen 
  for this paper seeks to demonstrate the ease of making significant changes to 
  a simulation in Cyclus.

(3) Several figures have poor resolution.

- Figures 1 and 3 have been replaced with higher resolution images. The other 
  figures are scalable vector graphics which will now scale with the pdf in 
  production.

(4) The methodology part is long, but reviewer does not think it does not improve 
reproducibility of the authors' results. More figures or equations are needed.

- The methodology section was reduced as part of the response to comment 1 from 
  reviewer 2.  We have additionally added Figure 5 and accompanying 
  mathematical formulation (equations 1-4). These
  clarify the Dynamic Resource Exchange implementation key to the Agent Based 
  Model underlying Cyclus. If additional 
  clarifying images or equations are needed, we hope the reviewer will let us 
  know which particular parts of the discussion would benefit from such additions.

Section 1.2 Line 127 change facilitates to facilitate

- On line 127, we changed facilitates to facilitate.

Section 2.5.1 Line 616 Do the authors mean tool git or tool kit? In 
English English git is a pejorative term and will cause some amusement!

- On line 616, the authors did, indeed, mean "git". It (git) is a tool for 
  revision control. We rearranged the sentence so that the word git does not 
  appear near the word tool. This will avoid the concern that it might be a 
  typo meaning toolkit. English readers unaware of the git version control tool 
  will unavoidably continue to find this funny.

Section 2.5.3 Line 670 correct spelling of automated

- Quite so. We have now changed automoated->automated on line 670.

Section 3.1.2 line 754 Should the table being referenced be Table 3 rather than 
Table 1?

- Indeed, we did mean figure 3, rather than figure 1. This has been fixed on 
  line 754.

### 2016-01-05 fundamentals/impl.tex

@@
 
-A modular, \acrfull{ABM} approach is ideal for solving the coupled,
+A modular, \acrfull{ABM} approach is ideal for modeling the coupled,
 physics-dependent supply chain problems involving material routing, facility
@@
 testing are shown to code reviewers prior to reviewing the software changes themselves.  The \Cyclus
-project currently uses the CircleCI \cite{biggar_circleci_2015} service for continuous integration.
+project uses the CircleCI \cite{biggar_circleci_2015} service for continuous integration.
 When a code change is submitted for review, CircleCI builds a version of the \Cyclus

### 2016-01-05 fundamentals/intro.tex
line 127, changed facilitates to facilitate

@@
 systems analysis indicates that agent-based modeling enables more flexible
-simulation control, without loss of generality
+simulation control than system dynamics, without loss of generality
 \cite{macal_agent-based_2010}. Furthermore, openness allows cross-institutional
@@
 \Cyclus is necessary to meet these goals, it is not sufficient.
-\emph{Agent interchangeability} is also required to facilitates direct comparison
+\emph{Agent interchangeability} is also required to facilitate direct comparison
 of alternative modeling methodologies and facility concepts. With this concept

### 2016-02-04 fundamentals/acros.tex
adds neup
adds nrc
Massage the acknoledgements
Reviewer 2: page 18: SWUs please give a complete list of acronyms: here Separate Work Units
advances in engineering software remaining minor comment was to add an s to ton.
Add accent on "Énergie(s)"
Because even if most french do not know how to put accent on
upper case letters, it is not a reason not to do it.

@@
 \newacronym{DSNF}{DSNF}{DOE spent nuclear fuel}
-\newacronym{MTHM}{MTHM}{metric ton of heavy metal}
+\newacronym{MTHM}{MTHM}{metric tons of heavy metal}
 \newacronym{HTGR}{HTGR}{high temperature gas reactor}
@@
 \newacronym{MA}{MA}{minor actinide}
-\newacronym{CEA}{CEA}{Commissariat a l'Energie Atomique et aux Energies Alternatives}
+\newacronym{CEA}{CEA}{Commissariat a l'\'Energie Atomique et aux \'Energies Alternatives}
 \newacronym{SKB}{SKB}{Svensk Karnbranslehantering AB}
@@
 \newacronym{MOX}{MOX}{mixed oxide}
+\newacronym{ThOX}{ThOX}{thorium oxide}
 \newacronym{UOX}{UOX}{uranium oxide}
@@
 \newacronym{LP}{LP}{linear program}
+\newacronym{NEUP}{NEUP}{Nuclear Energy University Programs}
+\newacronym{NRC}{NRC}{Nuclear Regulatory Commission}
+\newacronym{NSF}{NSF}{National Science Foundation}
+\newacronym{NNSA}{NNSA}{National Nuclear Security Administration}
+\newacronym{DHS}{DHS}{Department of Homeland Security}
+\newacronym{SWU}{SWU}{Separative Work Unit}
 %\newacronym{<++>}{<++>}{<++>}
